\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices improving API throughput by 35\%, enhancing system resilience.}
        \resumeItem{Enhanced authentication security with \textbf{Spring Security}, reducing unauthorized access attempts by 40\% in production.}
        \resumeItem{Deployed AI-driven code review tool using \textbf{LLMs}, decreasing manual review effort by 45\% and accelerating integration.}
        \resumeItem{Automated deployment with \textbf{Jenkins} and \textbf{Docker}, cutting release cycle time by 40\% across multiple microservices.}
        \resumeItem{Collaborated cross-functionally to design secure software, improving compliance with identity and access control policies by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed SaaS data visualization platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users with zero downtime.}
        \resumeItem{Automated daily processing of 10,000+ stock entries via \textbf{Python} scripts, reducing manual workload by 80\%.}
        \resumeItem{Built role-based access control for ecommerce subscriptions with \textbf{PHP}, integrating \textbf{Stripe} payments securely.}
        \resumeItem{Created AI agents leveraging \textbf{LLMs} automating FINRA broker data downloads, cutting manual efforts by 80\%.}
        \resumeItem{Developed AI-powered LinkedIn outreach bot raising qualified leads by 40\%, automating content and target selection.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab infrastructure supporting cybersecurity experiments and student projects reliably.}
        \resumeItem{Helped students debug and deploy software modules, improving assignment completion rates by 20\%.}
        \resumeItem{Automated grading scripts to increase scoring accuracy and reduce instructor workload by 25\%.}
        \resumeItem{Conducted 15+ interactive sessions on Cryptography and Web Security, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized API endpoints in \textbf{TypeScript}, achieving average response times below 100ms with reliable throughput.}
        \resumeItem{Upgraded \textbf{Angular.js} frontend, increasing user engagement and feedback scores by 25\%.}
        \resumeItem{Developed backend services with \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Refined \textbf{PostgreSQL} stored procedures reducing UI load times by 15\%, enhancing database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000 concurrent users with sub-200ms response times.}
        \resumeItem{Implemented secure CI/CD pipelines on \textbf{AWS EC2} with \textbf{Docker}, enabling automated deployments.}
        \resumeItem{Built React.js project tracking UI improving page load speeds by 30\% and user experience.}
        \resumeItem{Created unit tests with \textbf{JUnit} achieving 90\% code coverage on critical microservice components.}
        \resumeItem{Collaborated in team to automate SDLC process, improving development velocity and reducing manual tasks.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Machine Identity Monitoring System} | Go, Python, Cloud IAM, Audit Logs}{}
          \resumeItemListStart
              \resumeItem{Built discovery and classification engine for non-human identities, improving policy enforcement accuracy by 30\%.}
              \resumeItem{Created scalable pipelines aggregating authorization and behavioral signals from multiple cloud services for risk analysis.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Behavioral Anomaly Detection Platform} | Python, Big Data, ML, OAuth/OIDC}{}
          \resumeItemListStart
              \resumeItem{Engineered policy engine to detect anomalous machine identity behaviors, reducing potential misuse by 25\%.}
              \resumeItem{Applied machine learning models on big data to enhance identity risk modeling, improving threat detection rates.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd

\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Go, Python, Java, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Security \& Identity:} & IAM, OAuth, OIDC, SSO, SCIM, Secrets Management, Policy Engines \\
                \textbf{Web \& Frameworks:} & Spring Boot, React.js, Laravel, Angular.js, .NET \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD pipelines \\
                \textbf{Data \& Analytics:} & Big Data, ML, SQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Tools \& Automation:} & Linux, Git, GitHub, REST APIs, LLMs, AI Agents, OpenAI API \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}