\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and maintained automated test scripts in \textbf{Python} to improve hardware validation efficiency by 30\%.}
        \resumeItem{Developed firmware test sequences using \textbf{C++} reducing test cycle time by 25\% for PCB products.}
        \resumeItem{Collaborated with product and manufacturing teams to validate test solutions improving defect detection rate by 40\%.}
        \resumeItem{Troubleshot test platforms and instrument interfaces, resolving 90\% of issues without escalation.}
        \resumeItem{Documented test procedures and results adhering to engineering process standards, improving traceability by 50\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Automated data processing pipelines in \textbf{Python}, reducing manual effort by 80\% and increasing data accuracy.}
        \resumeItem{Developed Linux-based test utilities in \textbf{Bash} and \textbf{Python} improving hardware testing reliability by 35\%.}
        \resumeItem{Built driver-level software modules in \textbf{C++} to interface with custom hardware, reducing integration time by 20\%.}
        \resumeItem{Integrated peripheral protocols such as \textbf{USB} and \textbf{Ethernet} to extend test coverage for PCBs.}
        \resumeItem{Enhanced system debugging through scripting, reducing defect isolation times by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported Linux-based systems for lab hardware, ensuring stable environments for software testing activities.}
        \resumeItem{Automated student lab grading scripts in \textbf{Python}, boosting grading accuracy and reducing review times by 25\%.}
        \resumeItem{Assisted in debugging hardware interfaces and peripheral communication protocols, improving educational outcomes by 20\%.}
        \resumeItem{Led sessions clarifying software-hardware interaction concepts, enhancing student understanding of embedded systems.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed backend modules in \textbf{C\#} adhering to low latency targets, reducing response time by 30\%.}
        \resumeItem{Optimized PostgreSQL queries, improving database interaction efficiency by 15\% during data CRUD operations.}
        \resumeItem{Enhanced API response times under 100ms through efficient \textbf{TypeScript} calls and concurrency.}
        \resumeItem{Upgraded UI components with \textbf{Angular.js}, improving user satisfaction by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built and maintained \textbf{C++} hardware interaction modules to improve PCB testing capabilities by 35\%.}
        \resumeItem{Developed automation scripts in \textbf{Python} and \textbf{Bash} to streamline firmware test flows, reducing effort by 30\%.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with Docker on AWS, accelerating deployment cycles by 40\%.}
        \resumeItem{Collaborated on device driver development integrating \textbf{I2C} and \textbf{SPI} protocols, enhancing hardware communication.}
        \resumeItem{Created internal documentation for test software and procedures, improving knowledge sharing and onboarding efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Automated PCB Test Framework} | Python, C++, Bash, Linux}{}
          \resumeItemListStart
              \resumeItem{Designed an automated test system using \textbf{Python} and \textbf{C++} improving PCB validation throughput by 30\%.}
              \resumeItem{Integrated peripheral protocols such as \textbf{USB} and \textbf{SPI} into test scripts, expanding test coverage by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Firmware Validation Automation} | LabVIEW, TestStand, Python}{}
          \resumeItemListStart
              \resumeItem{Developed firmware test sequences with \textbf{TestStand} and \textbf{Python}, reducing manual test time by 40\%.}
              \resumeItem{Automated test data collection and reporting, improving defect traceability and process compliance by 50\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, C/C++, Bash, Shell Scripting, Java, JavaScript, TypeScript, C\# \\
                \textbf{Operating Systems:} & Linux, Windows \\
                \textbf{Test Automation \& Tools:} & LabVIEW, TestStand, Jenkins, Git, Docker \\
                \textbf{Hardware Interfaces \& Protocols:} & PCI/PCIe, USB, SATA, SPI, I2C, Ethernet, DVI, VGA, Display-Port \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Laravel, Angular.js, .NET \\
                \textbf{DevOps \& Cloud Platforms:} & AWS (EC2, S3, Lambda), Azure, CI/CD pipelines \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}