\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{automation} scripts using \textbf{Python} to optimize infrastructure deployment and reduce manual errors by 30\%.}
        \resumeItem{Implemented \textbf{monitoring} dashboards with \textbf{Grafana} and \textbf{Prometheus}, improving SLA adherence by 25\%.}
        \resumeItem{Engineered \textbf{Jenkins} pipelines automating CI/CD workflows, reducing deployment times by 40\%.}
        \resumeItem{Analyzed system performance and optimized \textbf{Java Spring Boot} services to increase throughput by 20\%.}
        \resumeItem{Collaborated across teams to document and improve incident response plans, decreasing average resolution time by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Automated complex data pipelines in \textbf{Python} to process 10,000+ daily records, boosting accuracy by 30\%.}
        \resumeItem{Created \textbf{Kubernetes}-based deployment strategies, improving system scalability by supporting 50+ concurrent users.}
        \resumeItem{Developed \textbf{ELK stack} configurations for log aggregation and alerting, reducing incident detection time by 40\%.}
        \resumeItem{Designed role-based controls within \textbf{React} applications to enhance security and compliance by 20\%.}
        \resumeItem{Integrated \textbf{AI-driven} automation bots, increasing lead generation efficiency by 40\% and reducing manual outreach.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab servers ensuring 99\% uptime and stable environments for cybersecurity experiments.}
        \resumeItem{Automated grading scripts with \textbf{Python}, enhancing evaluation speed by 25\% and result accuracy by 15\%.}
        \resumeItem{Assisted students with troubleshooting network protocols and system security, improving comprehension by 20\%.}
        \resumeItem{Supported configuration management and secure deployment of lab environments, reducing setup errors by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{PostgreSQL} queries reducing data retrieval latency by 20\%, enhancing application responsiveness.}
        \resumeItem{Implemented scalable backend services in \textbf{C\# .NET}, reducing service downtime by 30\% during peak loads.}
        \resumeItem{Configured API integrations using \textbf{TypeScript}, achieving sub-100ms response times and seamless data flow.}
        \resumeItem{Upgraded user interface components with \textbf{Angular.js}, improving user engagement metrics by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Automated containerized deployments using \textbf{Docker} and \textbf{Jenkins}, reducing release failures by 40\%.}
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, improving request handling by 35\%.}
        \resumeItem{Managed bare-metal infrastructure using \textbf{IPMI} and \textbf{KVM}, ensuring 99.9\% hardware availability in data center.}
        \resumeItem{Created observability tools integrating \textbf{Prometheus} metrics and \textbf{ELK Stack} logs for quick fault detection.}
        \resumeItem{Collaborated on capacity planning estimates, optimizing resource utilization and reducing costs by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable Infrastructure Monitoring Pipeline} | Prometheus, Grafana, ELK Stack, Jenkins}{}
          \resumeItemListStart
              \resumeItem{Designed an automated monitoring pipeline integrating \textbf{Prometheus} and \textbf{ELK stack}, increasing alert accuracy by 30\%.}
              \resumeItem{Built \textbf{Jenkins} pipelines to automate dashboard deployments, reducing setup time by 50\% in multi-server environments.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Data Center Automation Toolkit} | Python, Go, Bash, IPMI, Redfish}{}
          \resumeItemListStart
              \resumeItem{Developed automation scripts using \textbf{Python} and \textbf{Go} to manage bare-metal servers with \textbf{IPMI} and \textbf{Redfish}, improving deployment speed by 40\%.}
              \resumeItem{Implemented custom alerting mechanisms aligned with SLAs to promptly detect hardware anomalies, reducing failures by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go, Bash, Java, JavaScript, TypeScript, C\# \\
                \textbf{Infrastructure \& Automation:} & Jenkins, Docker, Kubernetes, IPMI, Redfish, KVM, AWS EC2 \\
                \textbf{Monitoring \& Observability:} & Prometheus, Grafana, ELK Stack \\
                \textbf{Databases:} & MySQL, PostgreSQL \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js \\
                \textbf{Operating Systems \& Tools:} & Linux/Unix, Git, GitHub, REST APIs \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}