\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices, increasing API throughput by 35\% and reducing latency.}
        \resumeItem{Enhanced security by implementing \textbf{Spring Security} RBAC, decreasing unauthorized accesses by 40\%.}
        \resumeItem{Developed an \textbf{AI-driven} code review assistant using \textbf{LLMs}, cutting manual reviews by 45\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating releases by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to optimize system performance and deploy robust cloud solutions.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a SaaS platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users smoothly.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, boosting processing speed by 80\%.}
        \resumeItem{Developed subscription e-commerce with \textbf{PHP}, integrating \textbf{Stripe} and access controls.}
        \resumeItem{Built \textbf{AI agents} using \textbf{LLMs} to automate FINRA data workflows, cutting manual effort by 80\%.}
        \resumeItem{Improved \textbf{React} UI, reducing load times by 25\% and increasing user engagement substantially.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux}-based infrastructure, ensuring secure, reliable cybersecurity lab environments.}
        \resumeItem{Assisted students in \textbf{debugging} and deploying software, raising assignment success by 20\%.}
        \resumeItem{Automated grading scripts, increasing evaluation accuracy and reducing manual workload by 25\%.}
        \resumeItem{Conducted 15+ interactive sessions covering Cryptography, Networking, and Web Security fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs achieving sub-100ms response times, enhancing data exchange speed.}
        \resumeItem{Refined \textbf{Angular.js} frontend, boosting user engagement and satisfaction by 25\%.}
        \resumeItem{Built robust backend services in \textbf{C\#} with \textbf{.NET}, reducing data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, cutting frontend load times by 15\% and improving data flow.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices, achieving sub-200ms response for 1000 concurrent users.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines for seamless \textbf{Docker}-based deployments on \textbf{AWS EC2}.}
        \resumeItem{Created project management UIs in \textbf{React.js}, improving usability and load speeds by 30\%.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} tests, achieving 90\% coverage on pipeline modules.}
        \resumeItem{Collaborated in building a SaaS tool automating SDLC, improving development efficiency and delivery.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} | Go, Python, Kubernetes, Terraform}
          {}
          \resumeItemListStart
              \resumeItem{Designed and deployed scalable microservices using \textbf{Go} and \textbf{Python} on \textbf{Kubernetes}, improving scalability by 50\%.}
              \resumeItem{Automated infrastructure provisioning with \textbf{Terraform}, enabling rapid multi-cloud deployments on AWS and GCP.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Serverless Event-Driven Automation} | AWS Lambda, SQS, gRPC, Python}
          {}
          \resumeItemListStart
              \resumeItem{Built serverless event-driven workflows with \textbf{AWS Lambda} and \textbf{SQS} to automate key business processes, reducing latency by 35\%.}
              \resumeItem{Developed APIs using \textbf{gRPC} and \textbf{Python}, enhancing inter-service communication efficiency by 40\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Go, Python, Java, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Cloud Platforms \& Infrastructure:} & AWS, Azure, GCP, EC2, Lambda, S3, Terraform, CloudFormation, Pulumi \\
                \textbf{Containers \& Orchestration:} & Docker, Kubernetes \\
                \textbf{DevOps \& CI/CD Tools:} & Jenkins, Git, GitHub Actions, Docker, CI/CD pipelines \\
                \textbf{Databases \& Messaging:} & SQL, NoSQL, MySQL, PostgreSQL, MongoDB, Kafka, RabbitMQ, AWS SQS/SNS \\
                \textbf{Monitoring \& Security:} & Observability tools, Security compliance (SOC2, PCI-DSS, GDPR), Vulnerability scanning \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}