\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{C\#} back-end modules improving enterprise application stability by 30\%.}
        \resumeItem{Enhanced \textbf{SQL} queries and database schema applying 3NF normalization, reducing data redundancy by 20\%.}
        \resumeItem{Collaborated with cross-functional teams using Agile, boosting sprint delivery performance by 25\%.}
        \resumeItem{Authored detailed technical documentation and troubleshooting guides, enhancing team support efficiency by 40\%.}
        \resumeItem{Implemented unit and integration tests for \textbf{Entity Framework} modules increasing code coverage by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built \textbf{MVC Razor Pages} front-end components improving user workflows and engagement by 20\%.}
        \resumeItem{Optimized \textbf{SQL Server} queries and indexes, reducing report generation time by 30\%.}
        \resumeItem{Contributed to \textbf{Angular} and \textbf{TypeScript} features enhancing UI performance by 25\%.}
        \resumeItem{Assisted in migration of on-premises apps to \textbf{Azure} Cloud, cutting infrastructure costs by 15\%.}
        \resumeItem{Supported CI/CD pipelines in \textbf{Azure DevOps}, accelerating deployment frequency by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab environments supporting student cybersecurity projects consistently.}
        \resumeItem{Assisted in debugging and deploying software modules enhancing student project success by 20\%.}
        \resumeItem{Automated grading scripts reducing manual review load by 25\% and improving accuracy.}
        \resumeItem{Led interactive sessions on database normalization and \textbf{SQL} query optimization for better learning.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{.NET} backend services in \textbf{C\#} reducing average response time by 25\%.}
        \resumeItem{Enhanced \textbf{JavaScript} front-end with \textbf{MVC} improvements increasing usability by 15\%.}
        \resumeItem{Tuned complex \textbf{SQL} queries and stored procedures achieving 20\% faster data retrieval.}
        \resumeItem{Participated in daily Agile standups and contributed to sprint planning improving team coordination.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Entity Framework} data access layers improving database interaction efficiency by 25\%.}
        \resumeItem{Created robust \textbf{C\# .NET} web applications supporting 500+ users concurrently.}
        \resumeItem{Built and optimized \textbf{SQL Server} databases with normalized schemas enhancing data integrity by 30\%.}
        \resumeItem{Streamlined deployment workflows using \textbf{Azure DevOps} pipelines enabling faster releases by 20\%.}
        \resumeItem{Led code reviews and documented application design promoting maintainability and team knowledge sharing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Enterprise Web App Enhancement} | C\#, MVC, Entity Framework, SQL Server}{}
          \resumeItemListStart
              \resumeItem{Implemented \textbf{MVC Razor Pages} and \textbf{Entity Framework} ORM improving data interaction speed by 30\%.}
              \resumeItem{Optimized complex \textbf{SQL} queries and database normalization reducing load times by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{CI/CD Pipeline Automation} | Azure DevOps, .NET, SQL}{}
          \resumeItemListStart
              \resumeItem{Built automated deployment pipelines in \textbf{Azure DevOps} cutting release cycle times by 35\%.}
              \resumeItem{Integrated database migration scripts for smooth \textbf{SQL Server} version upgrades maintaining data integrity.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\#, JavaScript, TypeScript, SQL, Python \\
                \textbf{Web Development \& Frameworks:} & .NET, MVC, Razor Pages, Angular, Entity Framework \\
                \textbf{Database \& Data Management:} & SQL Server, MySQL, Database Normalization (3NF), Query Optimization \\
                \textbf{Cloud \& DevOps:} & Microsoft Azure, Azure DevOps, CI/CD Pipelines, Docker \\
                \textbf{Tools \& Version Control:} & Git, GitHub, Jira, REST APIs \\
                \textbf{Operating Systems:} & Windows, Linux/Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}