\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices improving API throughput by 35\% in high-load environments.}
        \resumeItem{Implemented advanced authentication with \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Built AI-powered code review assistant using \textbf{Python}, improving dev velocity by 25\% through automated suggestions.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating releases by 40\% and reducing manual errors.}
        \resumeItem{Collaborated cross-functionally to maintain fault-tolerant services supporting critical business workflows with 99.9\% uptime.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected large-scale data platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent client sessions flawlessly.}
        \resumeItem{Automated ETL pipelines in \textbf{Python}, processing 10,000+ daily stock records, increasing data accuracy by 75\%.}
        \resumeItem{Designed role-based e-commerce platform with \textbf{PHP}, integrating \textbf{Stripe} payment system, boosting subscription uptake by 30\%.}
        \resumeItem{Deployed AI agents with \textbf{LLMs}, automating data scraping and reducing manual work by 80\%.}
        \resumeItem{Optimized \textbf{React} frontend, decreasing load times by 25\%, enhancing user retention and engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux}-based systems for cybersecurity labs, ensuring secure and reliable operational environments.}
        \resumeItem{Assisted students in debugging and testing software ensuring 20\% higher assignment success rate.}
        \resumeItem{Automated grading scripts to increase review accuracy by 25\% and reduce manual instructor workload.}
        \resumeItem{Conducted over 15 instructional sessions explaining network protocols and security concepts to 100+ students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls reducing average response time below 100ms for seamless UX.}
        \resumeItem{Enhanced platform with \textbf{Angular.js} upgrades, raising user engagement metrics by 25\%.}
        \resumeItem{Developed \textbf{C\#} backend reducing data retrieval latency by 30\% using optimized algorithms.}
        \resumeItem{Refined \textbf{PostgreSQL} queries and procedures to improve database efficiency and decrease server load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices handling 1000+ concurrent users with sub-200ms response times.}
        \resumeItem{Engineered CI/CD pipelines deploying microservices on \textbf{AWS EC2} with containerization via \textbf{Docker}.}
        \resumeItem{Designed React.js UI for project tracking, boosting user interaction speed and page load by 30\%.}
        \resumeItem{Implemented unit tests covering ~90\% of pipelines module with \textbf{JUnit}, ensuring high code quality.}
        \resumeItem{Collaborated in Agile team to automate SDLC processes, improving deployment efficiency and reducing errors.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable Log Processing System} | Kubernetes, AWS, Elasticsearch}
          {}
          \resumeItemListStart
              \resumeItem{Designed a fault-tolerant distributed logging system processing millions of log events daily using \textbf{Elasticsearch} and \textbf{Kubernetes}.}
              \resumeItem{Integrated cloud-native monitoring setups on \textbf{AWS} and \textbf{GCP} to ensure 99.9\% availability and rapid anomaly detection.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{SRE Observability Dashboard} | Grafana, Prometheus, Go}
          {}
          \resumeItemListStart
              \resumeItem{Built \textbf{Go}-based observability dashboard displaying real-time system metrics and SLO/SLI tracking to improve incident response times by 30\%.}
              \resumeItem{Implemented alerting rules and log aggregation pipelines reducing downtime and enabling proactive system health management.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, Go, JavaScript, TypeScript, C\# \\
                \textbf{DevOps \& Cloud Platforms:} & Kubernetes, AWS, GCP, Docker, Jenkins, EC2, S3 \\
                \textbf{Logging \& Monitoring:} & Elasticsearch, Datadog, Prometheus, Grafana, Splunk, AWS Cloudwatch \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Operating Systems \& Networking:} & Linux/Unix, Shell Scripting, Networking Protocols, System Debugging \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}