\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} tools enhancing production efficiency by 30\% through process automation.}
        \resumeItem{Refactored engineering apps improving system stability by 40\% and reducing downtime in production environments.}
        \resumeItem{Implemented role-based access features with \textbf{Spring Security}, cutting security incidents by 35\%.}
        \resumeItem{Automated deployment pipelines with \textbf{Docker} and \textbf{Jenkins}, reducing release cycle times by 50\%.}
        \resumeItem{Collaborated with cross-functional teams to optimize resource usage, boosting throughput by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built data processing tools in \textbf{Python} automating 10,000+ daily stock entries, improving accuracy by 30\%.}
        \resumeItem{Developed and maintained \textbf{React} and \textbf{Laravel} apps optimizing producer workflow and data visualization clarity.}
        \resumeItem{Implemented automation bots using \textbf{LLMs} that decreased manual data handling time by 80\%.}
        \resumeItem{Enhanced system integration via \textbf{REST APIs}, improving data sync speed by 35\% across production tools.}
        \resumeItem{Transformed front-end components optimizing load performance by 25\% and user operation efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported production of secure \textbf{Linux} lab environments, improving reliability by 20\%.}
        \resumeItem{Automated test and validation scripts defining infrastructure standards, reducing manual work by 25\%.}
        \resumeItem{Assisted students debugging and deploying complex apps, improving assignment success rate by 20\%.}
        \resumeItem{Conducted technical workshops on networking and security protocols, enhancing student participation by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed performant backend APIs using \textbf{TypeScript} targeting sub-100ms response times for production tools.}
        \resumeItem{Upgraded existing platforms with \textbf{Angular.js}, improving user engagement by 25\% through UI enhancement.}
        \resumeItem{Implemented \textbf{C\# .NET} backend modules optimizing data access latency by 30\% for engineering operations.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing processing load on frontend by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built scalable \textbf{Java Spring Boot} microservices reducing app response time below 200ms under 1000 concurrent users.}
        \resumeItem{Developed production tools automating SDLC tasks that increased team efficiency by 40\%.}
        \resumeItem{Deployed microservices on \textbf{AWS EC2} using \textbf{Docker} reducing downtime by 35\% in production releases.}
        \resumeItem{Created responsive monitoring dashboards with \textbf{React.js}, improving user monitoring efficiency by 30\%.}
        \resumeItem{Integrated unit testing with \textbf{JUnit} achieving 90\% code coverage for critical production modules.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Production Support Automation Tool} | AWS, Java, Spring Boot}
          \resumeItemListStart
              \resumeItem{Engineered \textbf{Spring Boot} tool automating production support tasks, reducing manual intervention by 50\%.}
              \resumeItem{Implemented real-time monitoring and alerts improving issue detection speed by 40\% in engineering operations.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Engineering Operations App Enhancements} | React.js, Node.js, Docker}
          \resumeItemListStart
              \resumeItem{Developed new features for engineering app increasing process throughput by 30\% while maintaining high reliability.}
              \resumeItem{Optimized deployment pipelines using \textbf{Docker} containers cutting production release times by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, C\#, PHP, Shell Scripting \\
                \textbf{Frameworks \& Tools:} & Spring Boot, React.js, Node.js, Laravel, Angular.js, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Git, GitHub Actions \\
                \textbf{Automation \& AI:} & LLMs, OpenAI API, AI Agents, n8n, CI/CD Pipelines \\
                \textbf{Other Technologies:} & Linux/Unix, REST API, JUnit, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}