\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and maintained scalable microservices using \textbf{Java Spring Boot}, improving API throughput by 35\%.}
        \resumeItem{Implemented role-based access with \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Integrated \textbf{AI-driven} code review tool leveraging LLMs, accelerating development velocity by 25\%.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 40\%.}
        \resumeItem{Resolved production issues with emphasis on security, enhancing software reliability for mission-critical systems.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected a SaaS platform with \textbf{Laravel} and \textbf{React}, supporting 50+ users concurrently with solid performance.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, reducing manual work by 80\% and improving data accuracy.}
        \resumeItem{Built \textbf{AI-powered} agents with LLMs to automate FINRA data processing, cutting manual tasks by 80\%.}
        \resumeItem{Optimized React components, decreasing page load time by 25\% and increasing end-user engagement significantly.}
        \resumeItem{Developed role-based controls using \textbf{PHP} and Stripe APIs for secure e-commerce subscription management.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Configured and maintained \textbf{Linux} cybersecurity lab infrastructure, ensuring secure and stable environments.}
        \resumeItem{Assisted students in debugging and testing software, improving completion rates by 20\%.}
        \resumeItem{Automated grading scripts, boosting accuracy by 25\% and reducing instructor workload.}
        \resumeItem{Conducted interactive sessions covering Cryptography, Networking, and Web Security for 15+ students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls with sub-100ms response, ensuring efficient data exchange.}
        \resumeItem{Upgraded UI with \textbf{Angular.js}, resulting in 25\% higher user engagement and satisfaction.}
        \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET}, reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, cutting frontend load by 15\% and improving data handling.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed microservices in \textbf{Java Spring Boot} supporting 1000+ concurrent users with <200ms latency.}
        \resumeItem{Built \textbf{CI/CD} pipelines using \textbf{Docker} and \textbf{AWS EC2}, streamlining deployments for multiple services.}
        \resumeItem{Developed project management UI in \textbf{React.js}, improving user experience and load speed by 30\%.}
        \resumeItem{Implemented unit tests with \textbf{JUnit}, achieving 90\% coverage for pipelines module.}
        \resumeItem{Collaborated in a 5-member team to automate SDLC processes, increasing development efficiency significantly.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Video Security Enhancement} | Python, PyTorch, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed scalable AI models with \textbf{PyTorch} integrated into cloud infrastructure, improving video security detection accuracy by 30\%.}
              \resumeItem{Deployed inference pipelines on \textbf{AWS} with automated scaling, handling 1000+ concurrent video stream analyses efficiently.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure Distributed Microservices Architecture} | Go, Docker, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Engineered a secure microservices platform in \textbf{Go} with \textbf{Kubernetes}, ensuring high availability and 99.9\% uptime.}
              \resumeItem{Implemented security best practices and vulnerability mitigation, reducing security incidents by 45\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, C, C++, Go, Bash, Java, JavaScript, TypeScript \\
                \textbf{AI \& Machine Learning:} & PyTorch, TensorFlow, Deep Learning, Large Language Models (LLMs), Computer Vision \\
                \textbf{Cloud \& DevOps:} & AWS, GCP, Azure, Docker, Kubernetes, Jenkins, GitLab CI, GitOps \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, NoSQL, DynamoDB \\
                \textbf{Source Control \& Tools:} & Git, Bitbucket, Linux/Unix, Prometheus, Grafana, Ansible, Terraform \\
                \textbf{Protocols \& Multimedia:} & RTSP, H.264, H.265, ONVIF, Media Streaming Codecs \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}