\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{C/C++} driver software to interface medical hardware with application software, reducing bugs by 35\%.}
        \resumeItem{Collaborated with cross-functional teams to refine software requirements for next-generation intravascular ultrasound devices, enhancing feature accuracy.}
        \resumeItem{Authored comprehensive software requirement and design documents, improving development clarity and reducing rework by 25\%.}
        \resumeItem{Implemented diagnostic tools in \textbf{C++} enabling automated hardware communication testing, accelerating issue resolution by 40\%.}
        \resumeItem{Practiced \textbf{Test Driven Development} and \textbf{Agile} methodologies to maintain planned milestones efficiently for the Trinity Project.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and tested automated software solutions reducing manual effort by 30\%, following \textbf{Software Development Life Cycle (SDLC)} principles.}
        \resumeItem{Created robust API integrations and driver-level software modules to improve data communication reliability by 20\%.}
        \resumeItem{Enforced code quality through peer \textbf{code reviews} and implemented automated tests increasing coverage by 50\%.}
        \resumeItem{Utilized \textbf{DevOps} pipelines to deploy updates smoothly and reduce downtime by 35\%.}
        \resumeItem{Led \textbf{software test automation} efforts using \textbf{Python} and \textbf{JUnit}, boosting regression test efficiency by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based test environments integrating hardware and software for reliable ultrasound system simulations.}
        \resumeItem{Assisted students in debugging and testing device drivers, increasing lab assignment success by 20\%.}
        \resumeItem{Automated test scripts for software validation, reducing manual error by 30\% and speeding feedback.}
        \resumeItem{Conducted workshops on software debugging, testing, and \textbf{API} design protocols to enhance student learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Wrote and debugged \textbf{C\#} backend services to improve communication efficiency between application and data layers by 25\%.}
        \resumeItem{Developed \textbf{API} integrations with external systems to automate data retrieval, improving latency by 30\%.}
        \resumeItem{Optimized existing codebases and provided thorough unit testing following \textbf{TDD} practices, raising test coverage to 85\%.}
        \resumeItem{Participated in \textbf{agile} standups and sprint planning to ensure milestone adherence and delivery quality.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Architected and implemented \textbf{C++} driver software modules to interface hardware test fixtures, increasing accuracy by 30\%.}
        \resumeItem{Collaborated in refining device driver requirements across hardware and software teams, reducing defects by 20\%.}
        \resumeItem{Developed and automated diagnostic tools in \textbf{Java} to identify issues early, reducing test cycle time by 35\%.}
        \resumeItem{Led \textbf{code reviews} and enforced \textbf{API design} standards, improving code reliability and maintainability.}
        \resumeItem{Implemented continuous integration and deployment \textbf{DevOps} pipelines, accelerating software delivery by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Intravascular Ultrasound Device Driver} | C++, Agile, TDD}{}
          \resumeItemListStart
              \resumeItem{Designed and developed robust \textbf{C++} drivers to enable reliable communication between ultrasound devices and control software.}
              \resumeItem{Implemented \textbf{Test Driven Development} practices yielding 90\% code coverage and improving software reliability by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated Diagnostic Software} | C++, DevOps, API Integration}{}
          \resumeItemListStart
              \resumeItem{Built diagnostic software automating hardware tests, reducing manual intervention by 50\% and accelerating problem detection.}
              \resumeItem{Integrated APIs for seamless communication between hardware and application layers, increasing data accuracy by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C, C++, Java, Python, JavaScript, C\#, Shell Scripting \\
                \textbf{Software Development:} & Agile Methodology, Test Driven Development (TDD), SDLC, API Design and Integration \\
                \textbf{DevOps \& Automation:} & Jenkins, Docker, AWS, CI/CD Pipelines, Version Control (Git) \\
                \textbf{Frameworks \& Tools:} & Spring Boot, JUnit, React.js, .NET, Jira \\
                \textbf{Testing \& QA:} & Software Test Automation, Code Reviews, Debugging, Diagnostic Software \\
                \textbf{Operating Systems:} & Linux, Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}