\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented scalable backend services in \textbf{TypeScript} using \textbf{Prisma}, improving data handling by 40\%.}
        \resumeItem{Designed and validated complex data schemas with \textbf{Zod}, reducing runtime errors by 30\%.}
        \resumeItem{Created robust API tests leveraging \textbf{JEST}, raising overall code coverage to 95\%.}
        \resumeItem{Deployed and optimized serverless applications on \textbf{AWS}, reducing operational costs by 25\%.}
        \resumeItem{Collaborated cross-functionally to improve backend architecture, enhancing system scalability by 50\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built efficient backend APIs with \textbf{JavaScript} and \textbf{TypeScript}, supporting 1000+ concurrent users.}
        \resumeItem{Employed \textbf{Prisma} ORM for database management, achieving 35\% faster query execution.}
        \resumeItem{Implemented schema validation using \textbf{Zod} to ensure data integrity, reducing validation bugs by 40\%.}
        \resumeItem{Wrote comprehensive unit and API tests with \textbf{JEST}, improving deployment stability by 30\%.}
        \resumeItem{Integrated \textbf{AWS} cloud services to optimize application performance and uptime by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based lab environments, ensuring 99\% uptime for cybersecurity student projects.}
        \resumeItem{Assisted debugging and testing of backend APIs, increasing student project success rates by 20\%.}
        \resumeItem{Automated validation scripts, reducing grading time and improving accuracy by 25\%.}
        \resumeItem{Conducted workshops on network security, increasing student engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs achieving sub-100ms response, enhancing data accessibility.}
        \resumeItem{Upgraded UI with \textbf{Angular.js}, boosting user satisfaction by 25\%.}
        \resumeItem{Optimized backend data retrieval reducing latency by 30\% using \textbf{.NET} and \textbf{C\#}.}
        \resumeItem{Enhanced database efficiency through \textbf{PostgreSQL} stored procedure tuning, reducing load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable backend services with \textbf{TypeScript} and \textbf{Prisma}, improving response time by 25\%.}
        \resumeItem{Designed validation schemas using \textbf{Zod} ensuring robust API contracts and reducing errors by 30\%.}
        \resumeItem{Implemented API testing with \textbf{JEST}, raising test coverage to 90\% and increasing reliability.}
        \resumeItem{Deployed containerized microservices on \textbf{AWS} EC2, cutting infrastructure costs by 20\%.}
        \resumeItem{Leveraged \textbf{Ramda} library to optimize functional programming utilities, enhancing code maintainability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable Backend API with Prisma and Zod} | TypeScript, Prisma, Zod, AWS Lambda}
          \resumeItemListStart
              \resumeItem{Developed high-performance backend APIs using \textbf{Prisma} for ORM and \textbf{Zod} for schema validation.}
              \resumeItem{Deployed on \textbf{AWS Lambda}, achieving 30\% cost optimization and 40\% latency reduction.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated API Testing Framework} | JEST, TypeScript, REST API, GitHub Actions}
          \resumeItemListStart
              \resumeItem{Built automated \textbf{JEST}-based API testing suite improving test coverage by 95\%, reducing bugs in production.}
              \resumeItem{Integrated with \textbf{GitHub Actions} for CI/CD, accelerating deployment cycles by 35\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & TypeScript, JavaScript, Java, Python, C\#, PHP \\
                \textbf{Frameworks \& Libraries:} & Prisma, Zod, Ramda, Node.js, React.js, Angular.js, Spring Boot \\
                \textbf{Cloud \& DevOps:} & AWS (Lambda, EC2, S3), Docker, CI/CD, GitHub Actions \\
                \textbf{Testing \& Validation:} & JEST, API Testing, Unit Testing, Automated Validation Scripts \\
                \textbf{Database \& Data Storage:} & PostgreSQL, MySQL, MongoDB, DynamoDB \\
                \textbf{Tools \& Other:} & REST API, Linux, Git, JSON, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}