\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} APIs supporting scalable CRM platform, improving efficiency by 35\%.}
        \resumeItem{Implemented secure authentication and role-based controls with \textbf{Spring Security}, cutting breaches by 40\%.}
        \resumeItem{Automated code reviews via \textbf{AI tools}, reducing manual review times by 45\% and accelerating delivery by 25\%.}
        \resumeItem{Developed CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, decreasing deployment times by 40\%.}
        \resumeItem{Collaborated cross-functionally to design CRM solutions aligned with evolving business requirements and compliance.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered SaaS integration features connecting CRM with external \textbf{REST} APIs, supporting 50+ users concurrently.}
        \resumeItem{Automated data ingestion pipelines in \textbf{Python}, increasing data accuracy and saving 80\% manual processing time.}
        \resumeItem{Developed role-based access components using \textbf{React} and \textbf{PHP} for subscription-based platforms.}
        \resumeItem{Deployed AI-enabled automation bots reducing repetitive CRM data entry and increasing lead generation by 40\%.}
        \resumeItem{Optimized frontend \textbf{React} components enhancing load speed by 25\%, boosting user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab environments enhancing system uptime and student access by 20\%.}
        \resumeItem{Developed and debugged lab software modules, improving student completion rates with guided support.}
        \resumeItem{Automated grading scripts, increasing evaluation reliability and reducing manual effort by 25\%.}
        \resumeItem{Led interactive sessions on network protocols and security concepts, bolstering student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed \textbf{TypeScript} API integrations reducing response latency below 100ms for client-facing apps.}
        \resumeItem{Upgraded UI using \textbf{Angular.js}, elevating user engagement by 25\% with responsive design improvements.}
        \resumeItem{Built optimized backend microservices in \textbf{C\#} \textbf{.NET}, cutting data fetch latency by 30\%.}
        \resumeItem{Enhanced \textbf{PostgreSQL} procedures, reducing frontend load times and streamlining database calls by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices interfacing with CRM systems, supporting 1000+ concurrent users.}
        \resumeItem{Established CI/CD pipelines on \textbf{AWS EC2} using \textbf{Docker}, enhancing deployment frequency by 50\%.}
        \resumeItem{Built and optimized React-based UI dashboards improving user experience and reducing load time by 30\%.}
        \resumeItem{Implemented unit tests covering 90\% code base, enhancing system stability and reducing defects.}
        \resumeItem{Collaborated on data integration tasks using APIs, ensuring seamless communication between disparate systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {CRM Enrollment Integration Platform | Java, REST API, Spring Boot}
          {}
          \resumeItemListStart
              \resumeItem{Developed robust \textbf{Java Spring Boot} microservices to integrate CRM data with enrollment systems, improving data sync by 45\%.}
              \resumeItem{Implemented \textbf{RESTful API} endpoints ensuring seamless communication and secure data transfer between services.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {Imaging System Monitoring Tool | C\#, .NET, SOAP API}
          {}
          \resumeItemListStart
              \resumeItem{Engineered system monitoring tools for imaging applications, reducing downtime by 30\% through proactive issue detection.}
              \resumeItem{Collaborated with cross-functional teams to support SOAP APIs and troubleshoot escalated technical issues promptly.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, C\#, Python, JavaScript, TypeScript, PHP \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, .NET, React.js, Angular.js, Laravel, HTML, CSS \\
                \textbf{APIs \& Integration:} & REST, SOAP, JSON, XML, Web Services, API Design \\
                \textbf{Database \& Data Management:} & MySQL, PostgreSQL, SQL, Data Integration \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Tools \& Other Technologies:} & Git, Jira, JUnit, Linux/Unix, Salesforce CRM concepts \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}