\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} backend API performance by 35\%, enabling improved scalability and throughput.}
        \resumeItem{Developed responsive \textbf{React.js} components, reducing frontend load times by 25\% and boosting UX metrics.}
        \resumeItem{Implemented role-based access controls using \textbf{Spring Security}, decreasing unauthorized access attempts 40\%.}
        \resumeItem{Automated CI/CD pipelines via \textbf{Jenkins} and \textbf{Docker}, reducing deployment times by 40\%.}
        \resumeItem{Integrated API gateways with backend microservices, improving data consistency and reducing latency by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java} backend services for SaaS platform, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Refined \textbf{React.js} components and state management, reducing page load times 25\% and improving UX.}
        \resumeItem{Automated data ingestion pipelines in \textbf{Python}, increasing daily data processing efficiency by 80\%.}
        \resumeItem{Implemented role-based access controls integrating \textbf{Stripe}, enhancing subscription management security.}
        \resumeItem{Created AI-driven automation for broker data downloads, reducing manual efforts 80\% using LLMs.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux} infrastructure, improving lab security and reliability for cybersecurity software deployments.}
        \resumeItem{Assisted students debugging and testing software modules, enhancing assignment success by 20\%.}
        \resumeItem{Automated grading and validation scripts, increasing review accuracy by 25\% and reducing manual workload.}
        \resumeItem{Conducted 15+ sessions on Cryptography, Networking Protocols, and Web Security to improve student learning.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{TypeScript} API calls to achieve sub-100ms response times, enhancing frontend data fetch.}
        \resumeItem{Upgraded frontend using \textbf{Angular.js}, resulting in 25\% higher user engagement and satisfaction.}
        \resumeItem{Implemented backend services with \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Streamlined \textbf{PostgreSQL} stored procedures, reducing frontend load by 15\% and improving database response.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices supporting 1000 concurrent users with < 200ms latency.}
        \resumeItem{Built responsive \textbf{React.js} UI components, improving usability and load speeds by 30\%.}
        \resumeItem{Implemented CI/CD pipelines on \textbf{AWS EC2} with \textbf{Docker}, reducing deployment failures by 20\%.}
        \resumeItem{Collaborated on a SaaS automation tool's backend architecture, reducing software development time 15\%.}
        \resumeItem{Wrote unit tests achieving 90\% coverage for critical modules using \textbf{JUnit} framework, improving reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Real-Time Java Spring Boot API with React Frontend for E-commerce}{}
          \resumeItemListStart
              \resumeItem{Engineered a Java Spring Boot backend processing 1000+ requests/second with under 200ms response time.}
              \resumeItem{Developed a React frontend with Redux state management, improving page load speed by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {Employee Management System using Java Spring Boot and React}{}
          \resumeItemListStart
              \resumeItem{Implemented RESTful APIs with Spring Boot, reducing data retrieval latency by 25\%, improving system responsiveness.}
              \resumeItem{Designed React components and integrated \textbf{HTML/CSS}, enhancing UI consistency and user experience.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, JavaScript, TypeScript, Python, C\#, PHP \\
                \textbf{Web Technologies:} & React.js, Redux, Spring Boot, HTML, CSS, REST API, Node.js \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, SQL \\
                \textbf{DevOps \& Cloud:} & Docker, AWS (EC2, S3, Lambda), Jenkins \\
                \textbf{Tools \& Frameworks:} & Git, GitHub, JUnit, Angular.js, Spring Security \\
                \textbf{Automation \& AI:} & LLM Integration, OpenAI API, AI Agents, n8n \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}