\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java} microservices reliability, reducing system bugs by 30\% and improving response times.}
        \resumeItem{Implemented \textbf{C++} modules for real-time data processing, increasing throughput by 25\%.}
        \resumeItem{Automated debugging workflows using AI tools, cutting troubleshooting time by 35\%.}
        \resumeItem{Collaborated with cross-functional teams to debug software issues and optimize deployment pipelines.}
        \resumeItem{Maintained security standards in software, aligning with organizational TS clearance requirements.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{Java} improving API efficiency by 30\% and reducing bugs.}
        \resumeItem{Utilized \textbf{JavaScript} tooling to debug and update front-end system anomalies, improving stability.}
        \resumeItem{Collaborated with QA teams to diagnose and resolve software anomalies, increasing system uptime.}
        \resumeItem{Designed and implemented software fixes in \textbf{C++}, reducing crash incidents by 40\%.}
        \resumeItem{Automated testing of bug fixes, achieving a 98\% success rate across software patches.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Diagnosed and resolved software bugs in Linux-based cybersecurity environments, improving lab stability.}
        \resumeItem{Provided troubleshooting support for \textbf{Java} and \textbf{C++} based assignment software, raising success rates.}
        \resumeItem{Automated bug reporting tools, resulting in 20\% faster issue identification and resolution.}
        \resumeItem{Conducted training sessions improving students’ debugging skills and software problem solving.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and troubleshot \textbf{TypeScript} API integrations, reducing error rates by 15\%.}
        \resumeItem{Assisted in debugging \textbf{C\#} backend services, leading to a 20\% performance improvement.}
        \resumeItem{Monitored and fixed real-time anomalies in software, improving platform stability.}
        \resumeItem{Optimized database queries to reduce latency by 15\%, enhancing overall application responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Implemented and debugged \textbf{C++} modules in microservices, reducing system faults by 30\%.}
        \resumeItem{Designed software bug fixes in \textbf{Java} improving system availability by 25\%.}
        \resumeItem{Collaborated across teams for effective software maintenance and real-time anomaly resolution.}
        \resumeItem{Developed unit tests with \textbf{JUnit}, enhancing bug detection coverage to 90\%.}
        \resumeItem{Streamlined troubleshooting processes, decreasing bug resolution time by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Real-Time Anomaly Detection and Debugging Platform | C++, Java, Linux}{}
          \resumeItemListStart
              \resumeItem{Developed a platform to identify and debug software anomalies in real time, reducing downtime by 40\%.}
              \resumeItem{Integrated cross-team collaboration tools, improving bug tracking and resolution efficiency by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {Automated Software Maintenance Tool | Java, Spring Boot, Jenkins}{}
          \resumeItemListStart
              \resumeItem{Created an automated tool for diagnosing and fixing code bugs, cutting manual maintenance time by 50\%.}
              \resumeItem{Implemented CI/CD pipeline integration, accelerating deployment cycles by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & \textbf{C++}, \textbf{Java}, Python, TypeScript, C\#, JavaScript, PHP, Go, Shell Scripting \\
                \textbf{Software Development:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, .NET, Django \\
                \textbf{Real-Time & Debugging Tools:} & Jenkins, JUnit, Git, GitHub, REST API, gRPC, Postman \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{Cloud & DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Azure \\
                \textbf{Operating Systems:} & Linux/Unix, Windows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}