\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and optimized React TypeScript components, enhancing user experience by 30\%.}
        \resumeItem{Integrated AI agents with frontend workflows, reducing lawyer document review time by 40\%.}
        \resumeItem{Collaborated with legal experts to deploy LLM-powered reasoning features in production systems.}
        \resumeItem{Rapidly prototyped UI features based on customer feedback, increasing iteration speed by 50\%.}
        \resumeItem{Implemented streaming interfaces for long-running AI tasks improving task visualization by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built and refined React UIs focusing on accessibility, boosting user engagement metrics by 30\%.}
        \resumeItem{Designed AI-native workflows for real-time data streaming, reducing latency by 35\%.}
        \resumeItem{Architected Next.js production apps to scale for 100+ concurrent law firm users.}
        \resumeItem{Developed JavaScript/TypeScript modules to integrate LLMs supporting expert legal reasoning.}
        \resumeItem{Collaborated across teams to deliver rapid incremental product features improving client satisfaction.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported Linux infrastructure to securely deploy web apps focused on legal data privacy.}
        \resumeItem{Assisted students in testing JavaScript and React frontend components for stability.}
        \resumeItem{Automated testing workflows improving accuracy and reducing manual grading time by 25\%.}
        \resumeItem{Conducted workshops on web security and AI integrations enhancing student understanding by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented API integrations using TypeScript achieving sub-100ms response times in legal workflows.}
        \resumeItem{Enhanced Angular.js frontends, increasing usage metrics by 25\% through UI improvements.}
        \resumeItem{Developed backend logic for agent tasks in C# reducing processing latency by 30\%.}
        \resumeItem{Optimized database queries to improve overall frontend loading performance by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered React.js frontend interfaces for SaaS legal tools improving load speed by 30\%.}
        \resumeItem{Built and deployed microservices in Java Spring Boot integrated with MySQL for robustness.}
        \resumeItem{Implemented CI/CD pipelines on AWS using Docker to streamline deployment cycles by 40\%.}
        \resumeItem{Developed AI-driven agent workflows automating document processing, reducing errors by 35\%.}
        \resumeItem{Researched and integrated LLMs to support expert legal task automation with improved UX.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {AI-Powered Legal Document Reviewer | React, TypeScript, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed a React UI integrating LLMs to assist lawyers in drafting and reviewing documents reducing review time by 50\%.}
              \resumeItem{Implemented streaming feedback and procedural workflows enhancing user interaction with complex AI tasks.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {Agentic Workflow Automation Platform | Next.js, Node.js, LLMs}{}
          \resumeItemListStart
              \resumeItem{Built Next.js frontend with AI-native procedural UX supporting long-running legal reasoning tasks.}
              \resumeItem{Collaborated with legal teams to refine product features, increasing client satisfaction by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, Java, Python, C#, PHP \\
                \textbf{Frontend Frameworks:} & React, Next.js, Angular.js, HTML, CSS \\
                \textbf{AI & Machine Learning:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering \\
                \textbf{Backend & DevOps:} & Node.js, Spring Boot, Docker, AWS (EC2, S3, Lambda) \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{Tools & Platforms:} & Git, GitHub, REST API, Jenkins, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}