\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered robust \textbf{Java Spring Boot} microservices scaling to support 10,000+ daily bookings.}
        \resumeItem{Integrated \textbf{Spring Security} roles to ensure secure API access reducing breaches by 40\%.}
        \resumeItem{Developed automated \textbf{AI-assisted} code reviews using LLMs, accelerating release cycles by 25\%.}
        \resumeItem{Streamlined deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, cutting release times by 40\%.}
        \resumeItem{Implemented monitoring strategies to maintain 99.99\% uptime for mission-critical travel applications.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed \textbf{React} booking interfaces with real-time updates handling 50+ concurrent users flawlessly.}
        \resumeItem{Automated data pipelines in \textbf{Python} processing 10,000+ records daily for booking optimizations.}
        \resumeItem{Built subscription features integrating \textbf{Stripe} and WooCommerce supporting secure payments and access control.}
        \resumeItem{Incorporated \textbf{AI agents} leveraging \textbf{LLMs} to automate airline data extraction, saving 80\% manual effort.}
        \resumeItem{Enhanced \textbf{React} performance, reducing page load times by 25\% to improve customer experience.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux} lab environments ensuring secure, reliable infrastructure for travel booking system testing.}
        \resumeItem{Assisted students in debugging \textbf{network protocols} and \textbf{web security} critical for airline reservation integrations.}
        \resumeItem{Automated grading scripts improving validation accuracy by 25\% for secure code practices.}
        \resumeItem{Conducted 15+ sessions explaining cryptography concepts enhancing security awareness.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API calls optimizing response time below 100ms for real-time data needs.}
        \resumeItem{Improved frontend engagement by 25\% upgrading \textbf{Angular.js} booking components and UI workflows.}
        \resumeItem{Built a \textbf{C\# .NET} backend reducing data latency by 30\%, enhancing booking data retrieval speed.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures reducing frontend load by 15\% improving system scaling.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices handling 1000+ concurrent users with response time under 200ms.}
        \resumeItem{Designed scalable backend integrations connecting with airline reservation APIs using REST and messaging queues.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Docker} on \textbf{AWS EC2} to automate releases increasing deployment speed.}
        \resumeItem{Built dynamic \textbf{React.js} UIs enhancing booking platform usability and reducing page loads by 30\%.}
        \resumeItem{Achieved 90\% test coverage with \textbf{JUnit} unit tests to ensure reliability of travel-related modules.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Multi-modal Travel Booking Platform Integration | Sabre, Amadeus, React, Spring Boot}{}
          \resumeItemListStart
              \resumeItem{Developed airline reservation integrations using REST APIs to enable seamless bookings across providers.}
              \resumeItem{Implemented scalable backend features in \textbf{Spring Boot} supporting real-time seat availability updates.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {Real-Time Booking Notification System | Node.js, WebSockets, AWS, React}{}
          \resumeItemListStart
              \resumeItem{Implemented an event-driven system using \textbf{WebSockets} to deliver instant booking status updates to users.}
              \resumeItem{Deployed scalable microservices on \textbf{AWS} improving notification latency by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, TypeScript, JavaScript, C\#, PHP, Go, C++, Shell Scripting \\
                \textbf{Frameworks \& Web:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, .NET, Django \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipeline \\
                \textbf{APIs \& Protocols:} & REST, gRPC, WebSockets, Sabre API, Amadeus API \\
                \textbf{Tools \& Automation:} & Git, GitHub, Jenkins, JUnit, Linux, Jira, OpenAI API, LLM Integration \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}