\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices ensuring 99.99\% uptime and rapid booking transactions.}
        \resumeItem{Integrated role-based access with \textbf{Spring Security} reducing unauthorized access by 40\%.}
        \resumeItem{Implemented real-time booking features enhancing platform throughput by 35\% using \textbf{REST APIs}.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{Docker} cutting release time by 40\%.}
        \resumeItem{Collaborated with ops teams to align system scalability for high-volume travel-related data.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built multi-modal booking UI using \textbf{React} and backend services with \textbf{Laravel} for smooth user flow.}
        \resumeItem{Automated data ingestion pipelines in \textbf{Python}, processing 10,000+ entries daily to enhance accuracy.}
        \resumeItem{Developed subscription roles and permissions integrated with \textbf{Stripe} for secure transaction handling.}
        \resumeItem{Leveraged \textbf{LLMs} to create AI agents reducing manual broker data processing by 80\%.}
        \resumeItem{Optimized \textbf{React} components reducing frontend latency by 25\% and boosting user retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed secure \textbf{Linux} environments assuring reliable execution of mission-critical cybersecurity labs.}
        \resumeItem{Helped students deploy and debug software, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts to enhance accuracy and reduce manual grading time by 25\%.}
        \resumeItem{Conducted over 15 sessions on Cryptography, Networking, and Web Security principles.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Accelerated backend API performance using \textbf{TypeScript}, achieving sub-100ms response latency.}
        \resumeItem{Enhanced user engagement by 25\% through optimized \textbf{Angular.js} platform upgrades.}
        \resumeItem{Reduced data retrieval latency by 30\% with efficient \textbf{C\#} backend and \textbf{.NET} services.}
        \resumeItem{Refined \textbf{PostgreSQL} stored procedures improving database efficiency and reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Spring Boot} microservices for SDLC automation supporting 1000 concurrent users.}
        \resumeItem{Configured \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} using \textbf{Docker} containers.}
        \resumeItem{Built user-friendly project tracking UI with \textbf{React.js}, improving page load speed by 30\%.}
        \resumeItem{Implemented unit tests with \textbf{JUnit}, achieving 90\% coverage for pipeline modules.}
        \resumeItem{Ensured robust backend integration with \textbf{MySQL} databases for reliable transaction handling.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Airline Reservation System Integration Platform | Java, Spring Boot, REST APIs}{}
          \resumeItemListStart
              \resumeItem{Built backend services integrating \textbf{Sabre} and \textbf{Amadeus} APIs for seamless flight booking updates.}
              \resumeItem{Implemented scalable features handling 10,000+ real-time booking transactions daily with sub-second latency.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {Multi-Modal Booking Application | React, Node.js, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed user-friendly booking interface with \textbf{React} handling real-time seat availability and updates.}
              \resumeItem{Deployed backend on \textbf{AWS} ensuring platform availability of 99.99\% for mission-critical travel experiences.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Languages:} & Java, Python, TypeScript, JavaScript, PHP, C\#, SQL, Shell Scripting \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Node.js, Laravel, Angular.js, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD pipelines \\
                \textbf{APIs \& Protocols:} & REST, gRPC, Airline Reservation APIs (Sabre, Amadeus) \\
                \textbf{Tools \& Others:} & Git, Linux/Unix, Jira, JUnit, OpenAI API, LLM Integration \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}