\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Proactive software developer focused on building robust, scalable backend systems and frontend interfaces using React and TypeScript. Experienced in Agile workflows, CI/CD pipelines, automated testing, and API design. Adept at troubleshooting complex issues and collaborating cross-functionally to deliver efficient, high-quality tools in fast-paced environments. Passionate about enhancing user-centric applications within dynamic teams. 
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, PHP, Shell Scripting, SQL \\
                \textbf{Frontend \& Frameworks:} & React.js, HTML, CSS, GraphQL \\
                \textbf{Backend \& APIs:} & Node.js, REST API, GraphQL API, PHP, Linux \\
                \textbf{Testing \& CI/CD:} & Jest, PHPUnit, Selenium, Git, GitHub Actions, Jenkins \\
                \textbf{Databases:} & MySQL, PostgreSQL, Data Modeling, SQL Queries \\
                \textbf{Development Methodologies:} & Agile, Scrum, User-centered design, Documentation (Jira, Confluence) \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced backend services for configuration tools using \textbf{TypeScript} and \textbf{Node.js}, improving feature deployment speed by 30\%.}
        \resumeItem{Refactored and optimized \textbf{React} components, boosting UI responsiveness and reducing load times by 20\%.}
        \resumeItem{Established and maintained unit tests using \textbf{Jest}, achieving 85\% test coverage and reducing bugs pre-release by 35\%.}
        \resumeItem{Collaborated in Agile sprints, managing priorities effectively and coordinating with cross-functional teams to meet tight deadlines.}
        \resumeItem{Documented software specifications and workflows in \textbf{Jira} and \textbf{Confluence}, increasing knowledge sharing and process clarity.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable features in \textbf{React} and \textbf{TypeScript} for an enterprise web application, raising customer satisfaction by 25\%.}
        \resumeItem{Crafted complex \textbf{GraphQL} queries and optimized data fetching, reducing API latency by 30\%.}
        \resumeItem{Automated testing with \textbf{Jest} and \textbf{PHPUnit}, improving code reliability and decreasing production bugs by 40\%.}
        \resumeItem{Scripted \textbf{Shell} utilities on \textbf{Linux} to automate routine tasks, saving over 10+ hours of manual work weekly.}
        \resumeItem{Integrated API services with backend configurations to streamline product setup, increasing deployment efficiency by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained Linux servers and supported software deployment, improving lab uptime reliability by 15\% during academic sessions.}
        \resumeItem{Guided students in \textbf{testing} and debugging \textbf{JavaScript} and \textbf{PHP} assignments, enhancing comprehension and success rates by 20\%.}
        \resumeItem{Automated grading scripts using \textbf{Shell Scripting}, cutting evaluation time by 35\% and increasing accuracy.}
        \resumeItem{Enabled remote lab access via secure configuration management, increasing student participation in online classes by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed API endpoints in \textbf{TypeScript} to support frontend needs, boosting endpoint efficiency and decreasing response time by 22\%.}
        \resumeItem{Improved an \textbf{Angular.js} frontend for better user experience, increasing engagement metrics by 18\%.}
        \resumeItem{Implemented backend components in \textbf{C\#} within \textbf{.NET}, enhancing data processing speeds by 15\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries reducing system bottlenecks and improving concurrent user handling by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led backend development with \textbf{Java Spring Boot} for microservices supporting scalable SaaS applications used by 1000+ users.}
        \resumeItem{Designed and implemented efficient \textbf{SQL} data models and queries, reducing database response time by 25\%.}
        \resumeItem{Built frontend dashboards using \textbf{React.js} boosting customer usability and achieving 30\% faster data visualization loading.}
        \resumeItem{Automated deployment with \textbf{Docker} and configured CI/CD pipelines, decreasing release cycle time by 40\%.}
        \resumeItem{Developed and maintained unit tests with \textbf{JUnit}, achieving high code coverage and reducing regression bugs by 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Quality Analyzer} | GitHub Actions, OpenAI API, Jest}{}
          \resumeItemListStart
              \resumeItem{Designed an AI-assisted CI/CD tool to review pull requests, detect errors, and enforce testing standards, reducing bugs by 35\%.}
              \resumeItem{Automated Python docstring generation, ensuring 100\% documentation compliance and improving code readability across the team.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{React-Based Configuration UI for Product Management} | React.js, GraphQL, TypeScript}{}
          \resumeItemListStart
              \resumeItem{Developed dynamic React components with \textbf{GraphQL} data integration, enabling seamless configuration and reducing setup time by 30\%.}
              \resumeItem{Implemented state management and API error handling to increase UI stability and user satisfaction by over 20\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Automated Testing Framework for Web Applications} | Jest, Selenium, PHPUnit}{}
          \resumeItemListStart
              \resumeItem{Built a comprehensive automated testing framework integrating \textbf{Jest}, \textbf{Selenium}, and \textbf{PHPUnit}, cutting manual test times by 50\%.}
              \resumeItem{Enabled continuous integration testing and increased codebase reliability, detecting early faults and reducing production bugs by 40\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}