\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Skilled software engineer experienced in designing scalable data pipelines, orchestrating workflows, and ensuring data quality with cloud technologies. Passionate about collaborative innovation in payments and digital products, leveraging strong SQL, API integration, and cloud services to deliver impactful solutions with attention to detail and continuous improvement.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Cloud Platforms:} & Google Cloud Platform (Dataflow, BigQuery, Cloud Composer, Cloud Storage), AWS (EC2, S3, Lambda) \\
                \textbf{Programming \& Scripting:} & Python, Java, SQL, JavaScript, TypeScript, Shell Scripting \\
                \textbf{Data Engineering:} & Apache Beam, Apache Airflow, Data Pipeline Orchestration, Data Ingestion, Data Transformation, Data Quality, BigQuery SQL \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Node.js, Django \\
                \textbf{DevOps \& Tools:} & Git, Jenkins, Docker, CI/CD, Agile, Version Control \\
                \textbf{Databases \& APIs:} & MySQL, PostgreSQL, MongoDB, REST APIs, API Integration \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built and optimized scalable data pipelines with \textbf{GCP Dataflow} and \textbf{Apache Beam}, improving data throughput by 30\%.}
        \resumeItem{Orchestrated workflow scheduling and dependencies using \textbf{Cloud Composer} to improve pipeline reliability by 25\%.}
        \resumeItem{Developed APIs and ingestion processes from diverse data sources, reducing data latency by 40\%.}
        \resumeItem{Implemented comprehensive data validation and quality checks in \textbf{BigQuery SQL}, increasing data accuracy by 35\%.}
        \resumeItem{Collaborated cross-functionally to create datasets powering business intelligence tools, speeding reporting by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed interactive payment experience modules integrating \textbf{API data ingestion} enabling 50\% faster transaction processing.}
        \resumeItem{Automated data pipelines and cleaning workflows using \textbf{Python} and \textbf{BigQuery}, improving data freshness by 30\%.}
        \resumeItem{Implemented role-based access and \textbf{payment vehicle} support in e-commerce systems using \textbf{PHP} and \textbf{Stripe}.}
        \resumeItem{Established \textbf{CI/CD} pipelines through \textbf{Jenkins} for data platform deployments, enhancing release cadence by 35\%.}
        \resumeItem{Refined data transformations and error handling for payment events, reducing failures by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure \textbf{Linux} environments and helped debug and deploy codebases for student cybersecurity projects successfully.}
        \resumeItem{Automated lab grading and validation scripts, improving evaluation accuracy and reducing manual review time by 30\%.}
        \resumeItem{Educated students on secure coding and debugging practices, increasing lab completion rates by 20\%.}
        \resumeItem{Monitored system performance and troubleshot environment issues to ensure reliable lab access and usage.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed efficient API integrations using \textbf{TypeScript} with sub-100ms response times for payment data retrieval.}
        \resumeItem{Enhanced frontend experiences with \textbf{Angular.js}, raising user engagement metrics by 25\%.}
        \resumeItem{Built backend \textbf{C\# .NET} services to improve data processing speeds, reducing latency by 30\%.}
        \resumeItem{Optimized database queries and stored procedures in \textbf{PostgreSQL}, lowering server load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed microservices in \textbf{Java Spring Boot} for scalable payment platform supporting 1000+ concurrent users.}
        \resumeItem{Implemented data pipelines and automated deployments using \textbf{Docker} and \textbf{AWS EC2}, improving uptime by 30\%.}
        \resumeItem{Created data ingestion and transformation scripts with \textbf{SQL} and \textbf{Java}, reducing errors by 25\%.}
        \resumeItem{Built user interfaces with \textbf{React.js} to enhance customer payment experiences and reduce page load times by 20\%.}
        \resumeItem{Implemented automated testing with \textbf{JUnit} achieving 90\% coverage and improving code quality significantly.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Data Pipeline Optimizer} | Python, Apache Beam, GCP Dataflow}{}
          \resumeItemListStart
              \resumeItem{Engineered a data pipeline optimizer using \textbf{AI} to automatically adjust workflows and boost GCP pipeline throughput by 30\%.}
              \resumeItem{Integrated data quality checks and lineage tracking features, reducing data errors by 40\% across multiple sources.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Interactive Payment Experience Platform} | React.js, Node.js, Stripe API}{}
          \resumeItemListStart
              \resumeItem{Built a customer-facing payment platform enhancing interaction points and reducing checkout errors by 20\% through API integration.}
              \resumeItem{Implemented secure role-based access control, supporting multiple payment vehicles and improving user trust and satisfaction.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Automated Workflow Orchestrator} | Apache Airflow, Cloud Composer, GCP}{}
          \resumeItemListStart
              \resumeItem{Developed a data workflow orchestrator using \textbf{Apache Airflow} to schedule and maintain pipeline dependencies with 99\% uptime.}
              \resumeItem{Monitored execution logs and fixed pipeline failures, improving data availability for business intelligence by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}