\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Experienced software engineer specializing in cloud-native solutions and scalable distributed systems. Demonstrated ability to design and implement APIs, user-facing applications, and backend services with a focus on quality and security. Skilled in driving projects from prototype to production in agile environments, leveraging industry best practices to enhance healthcare and digital technologies.
\vspace{-5pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, TypeScript, C\#, Go, JavaScript, Shell Scripting \\
                \textbf{Cloud Platforms \& DevOps:} & AWS (EC2, Lambda, S3, SQS, IAM), Azure, Docker, Jenkins, CI/CD \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Node.js, Django, .NET \\
                \textbf{Data \& Storage Technologies:} & MySQL, PostgreSQL, MongoDB, DynamoDB, Big Data Systems \\
                \textbf{Microservices \& Architecture:} & Containerized Microservices, Serverless Functions, Event-driven Design \\
                \textbf{Tools \& Methodologies:} & Git, REST API, Agile, Test-driven Development, JUnit, Software Design Reviews \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led design and implementation of scalable \textbf{Java Spring Boot} microservices, improving system throughput by 40\% and resilience under load.}
        \resumeItem{Enhanced security posture by integrating \textbf{Spring Security} with multi-factor authentication, reducing unauthorized access incidents by 45\%.}
        \resumeItem{Developed automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, cutting deployment cycle times by 35\% while ensuring high quality standards.}
        \resumeItem{Collaborated on API design and code reviews, fostering adherence to test-driven development and continuous improvement across the engineering team.}
        \resumeItem{Implemented monitoring and alerting solutions to maintain production reliability, reducing incident response times by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected multi-tenant SaaS visualization platform with \textbf{Laravel} and \textbf{React}, supporting over 50 concurrent enterprise clients without degradation.}
        \resumeItem{Automated complex data ETL pipelines in \textbf{Python}, processing 10,000+ records daily with 85\% reduction in manual overhead.}
        \resumeItem{Integrated \textbf{AI-driven} automation using \textbf{LLMs} for broker data workflows, reducing processing time by 70\% and boosting accuracy.}
        \resumeItem{Built scalable \textbf{React} UI components optimized for performance, cutting page load times by 30\% and improving user retention.}
        \resumeItem{Devised backend role-based access controls leveraging \textbf{Stripe} and WooCommerce to securely manage subscription memberships and billing workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments, ensuring compliance with cybersecurity best practices and uninterrupted system availability.}
        \resumeItem{Developed and automated grading scripts, increasing assessment accuracy by 25\% and reducing instructor review time significantly.}
        \resumeItem{Supported student projects by diagnosing and debugging complex security software modules, improving course pass rates by 20\%.}
        \resumeItem{Conducted technical workshops on cryptography and secure networking protocols, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented high-performance RESTful APIs in \textbf{TypeScript}, achieving sub-100ms latency for critical data fetch operations.}
        \resumeItem{Refactored frontend using \textbf{Angular.js}, increasing user engagement by 25\% through UI/UX improvements and responsiveness.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, reducing data processing latency by 30\% in core business workflows.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, streamlining database interactions and decreasing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{Java Spring Boot} microservices handling 1000+ concurrent users, improving response times below 200ms.}
        \resumeItem{Built robust \textbf{React.js} interfaces for project management, increasing user task efficiency and reducing load times by 30\%.}
        \resumeItem{Automated CI/CD pipelines on \textbf{AWS EC2} using \textbf{Docker}, enabling seamless deployment of multiple services and minimizing downtime.}
        \resumeItem{Implemented comprehensive unit and integration tests using \textbf{JUnit}, achieving near 90\% code coverage and higher reliability.}
        \resumeItem{Collaborated with cross-functional teams to gather requirements, improving architecture documentation and aligning development with business goals.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Assistant} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed an automated CI/CD code review bot using \textbf{GitHub Actions} and \textbf{LLMs}, reducing manual review time by 40\%.}
              \resumeItem{Implemented automatic documentation generation, ensuring consistent code quality and 100\% coverage of new software modules.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Face Recognition Service} | AWS EC2, S3, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Engineered a highly available face recognition system with \textbf{AWS SQS} for asynchronous processing, handling 1000+ requests efficiently.}
              \resumeItem{Implemented custom auto-scaling policies and secure data storage on \textbf{S3}, improving processing speed and reliability.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Event-Driven Customer Support Agent} | Gmail API, n8n, LLMs, Google Sheets API}{}
          \resumeItemListStart
              \resumeItem{Built an AI-driven email classification and response system, automating 60\% of support queries and reducing response time by 40\%.}
              \resumeItem{Integrated human-in-the-loop workflows for complex inquiries, ensuring high accuracy and customer satisfaction.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}