\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Experienced Full Stack Developer specializing in building scalable microservices using \textbf{Java/Spring Boot} and rich client applications with \textbf{Angular}. Proficient in developing REST APIs, leveraging asynchronous messaging with \textbf{Kafka}, and managing cloud-based storage via \textbf{AWS S3}. Adept at collaborating cross-functionally to deliver user-focused, maintainable solutions that drive business objectives and improve system performance.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Backend \& Microservices:} & Java, Spring Boot, REST APIs, Microservices Architecture, Kafka \\
                \textbf{Frontend:} & Angular, TypeScript, HTML, CSS, Components, Services, Routing \\
                \textbf{Cloud \& Storage:} & AWS S3, EC2, Lambda, Docker, Jenkins, AWS IAM \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Tools:} & Git, GitHub, Jenkins, Docker, Jira, JUnit \\
                \textbf{Other Technologies:} & JSON, HTTP, RESTful APIs, Agile Methodologies \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices integrating \textbf{REST APIs} to enhance application responsiveness by 40\%.}
        \resumeItem{Implemented robust security features with \textbf{Spring Security}, decreasing unauthorized access attempts by 38\%.}
        \resumeItem{Automated deployment workflows with \textbf{Jenkins} and \textbf{Docker}, reducing release cycle times by 45\%.}
        \resumeItem{Collaborated in asynchronous message processing with \textbf{Kafka}, improving event handling efficiency by 30\%.}
        \resumeItem{Integrated \textbf{AWS S3} for asset storage, enhancing data retrieval speeds by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered modular \textbf{Java Spring Boot} backend services supporting scalable API endpoints for a SaaS platform serving 100+ users.}
        \resumeItem{Built interactive \textbf{Angular} frontend features consuming backend APIs, increasing UI responsiveness and user satisfaction by 18\%.}
        \resumeItem{Implemented \textbf{Kafka}-based event-driven communication to optimize real-time data processing, improving latency by 27\%.}
        \resumeItem{Managed cloud storage using \textbf{AWS S3} to handle digital assets, enhancing data durability and accessibility.}
        \resumeItem{Enhanced frontend state management and routing in \textbf{Angular}, reducing load times by 22\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure infrastructure setups on \textbf{Linux} VMs, ensuring lab environments adhered to cybersecurity best practices.}
        \resumeItem{Assisted students in debugging \textbf{RESTful APIs} and microservices, improving pass rates by 15\%.}
        \resumeItem{Automated grading systems using scripting, reducing manual evaluation time by 30\%.}
        \resumeItem{Conducted educational sessions on web security and backend service development concepts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API integrations to boost frontend-backend communication speed to sub-100ms response times.}
        \resumeItem{Updated \textbf{Angular.js} UI components to improve user engagement by 25\%.}
        \resumeItem{Designed backend services in \textbf{C\# .NET} achieving a 30\% data access latency reduction.}
        \resumeItem{Optimized database queries in \textbf{PostgreSQL}, decreasing load on frontend by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{microservices} with \textbf{Java} \textbf{Spring Boot}, handling 1200+ users with average response time under 200ms.}
        \resumeItem{Deployed containerized services using \textbf{Docker} on \textbf{AWS EC2} instances, improving deployment speed by 50\%.}
        \resumeItem{Created \textbf{RESTful APIs} enabling seamless communication between frontend and backend applications.}
        \resumeItem{Built user interfaces with \textbf{React.js}, improving project tracking efficiency by 35\%.}
        \resumeItem{Wrote unit tests using \textbf{JUnit}, achieving 90\%+ code coverage and reducing bugs pre-release by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Intelligent API Performance Analyzer} | Java, Spring Boot, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-augmented tool to monitor \textbf{REST API} performance and suggest improvements, reducing latency by 20\%.}
              \resumeItem{Implemented automated code analysis leveraging \textbf{OpenAI API} to detect inefficiencies within \textbf{Java Spring Boot} microservices.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Real-Time Event Stream Processor} | Kafka, Java, AWS S3}{}
          \resumeItemListStart
              \resumeItem{Built a scalable \textbf{Kafka}-based streaming processor to handle real-time data ingestion and storage in \textbf{AWS S3}, improving throughput by 30\%.}
              \resumeItem{Designed fault-tolerant microservices in \textbf{Java Spring Boot} to process and persist events efficiently across distributed systems.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Interactive Angular Dashboard} | Angular, REST API, AWS S3}{}
          \resumeItemListStart
              \resumeItem{Created an \textbf{Angular} frontend application consuming multiple backend \textbf{REST APIs}, enhancing user interaction speed by 28\%.}
              \resumeItem{Integrated \textbf{AWS S3} for asset management, facilitating seamless upload and retrieval of user content in real time.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}