\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative full stack engineer with 3+ years' experience creating scalable, high-performance web applications utilizing \textbf{TypeScript}, \textbf{React}, \textbf{NodeJS}, \textbf{Java}, and \textbf{SpringBoot}. Passionate collaborator dedicated to delivering frictionless user experiences and advancing product visions. Skilled in cloud architecture, security, and cross-functional teamwork driving enterprise-grade solutions.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, NodeJS, Python, Go, C++, Shell Scripting \\
                \textbf{Frontend \& Frameworks:} & React.js, Angular.js, Spring Boot, Express.js, HTML, CSS \\
                \textbf{Backend \& Microservices:} & Java SpringBoot, NodeJS, REST API, gRPC, Microservices Architecture \\
                \textbf{Databases \& Storage:} & PostgreSQL, MySQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Cloud Platforms:} & AWS (EC2, Lambda, S3), Docker, Jenkins, Kubernetes \\
                \textbf{Tools \& Others:} & Git, GitHub, Jira, JUnit, Security Best Practices, Agile, Collaboration Tools \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices increasing system throughput by 40\% and improving API response times by 30\%.}
        \resumeItem{Integrated role-based access using \textbf{Spring Security}, decreasing unauthorized access attempts by 45\% across critical services.}
        \resumeItem{Developed \textbf{NodeJS} backend features supporting real-time data processing, boosting data pipeline efficiency by 35\%.}
        \resumeItem{Collaborated with cross-functional teams to design high-impact product features improving user engagement by 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 50\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed dynamic frontend experiences in \textbf{React} and \textbf{TypeScript}, enhancing usability and reducing load time by 30\%.}
        \resumeItem{Implemented automated data ingestion pipelines with \textbf{Python}, processing 15,000+ records daily with 99\% accuracy.}
        \resumeItem{Built backend services with \textbf{NodeJS} and integrated payment gateways, increasing subscription transactions by 20\%.}
        \resumeItem{Developed AI-powered automation tools using \textbf{LLMs} to streamline lead generation, increasing qualified leads by 35\%.}
        \resumeItem{Optimized application state management leading to 25\% faster page rendering and improved customer retention rates.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab environments ensuring 99\% uptime and adherence to cybersecurity best practices.}
        \resumeItem{Mentored students on debugging complex software issues, improving lab assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts using \textbf{Python} that increased evaluation accuracy by 30\%.}
        \resumeItem{Conducted technical workshops covering cryptography, network protocols, and web security for 60+ students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs optimizing data exchange and reduced response latency to under 100ms.}
        \resumeItem{Enhanced user interface using \textbf{Angular.js}, increasing user engagement metrics by 28\%.}
        \resumeItem{Implemented backend services in \textbf{C\#}/.NET reducing processing delays by 30\%.}
        \resumeItem{Improved \textbf{PostgreSQL} database queries cutting data retrieval times by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led development of scalable \textbf{Java Spring Boot} microservices supporting over 1,200 concurrent users with low latency under 200ms.}
        \resumeItem{Designed responsive frontend interfaces in \textbf{React.js}, increasing application usability and speeding load times by 35\%.}
        \resumeItem{Implemented continuous deployment pipelines with \textbf{Docker} and \textbf{AWS EC2}, accelerating release cycles by 40\%.}
        \resumeItem{Authored comprehensive \textbf{JUnit} test suites achieving over 90\% code coverage for critical system modules.}
        \resumeItem{Collaborated in Agile teams driving product improvements that increased customer satisfaction by over 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Quality Analyzer} | GitHub Actions, OpenAI API, TypeScript}
          \resumeItemListStart
              \resumeItem{Built a \textbf{TypeScript}-based automated reviewer using \textbf{OpenAI API} that analyzes pull requests, reducing manual code review time by 45\%.}
              \resumeItem{Implemented seamless GitHub integration enabling continuous feedback and increasing developer productivity by 30\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-Scale Data Dashboard} | React, NodeJS, AWS, PostgreSQL}
          \resumeItemListStart
              \resumeItem{Developed an interactive \textbf{React} frontend and \textbf{NodeJS} backend supporting real-time analytics for 1000+ simultaneous users.}
              \resumeItem{Optimized \textbf{AWS} infrastructure and database queries reducing data latency by 40\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Smart Customer Support Bot} | Python, LLMs, Gmail API, Automation}
          \resumeItemListStart
              \resumeItem{Created an AI-driven support bot using \textbf{Python} and \textbf{LLMs} that automated 65\% of email queries, decreasing response times by 35\%.}
              \resumeItem{Built a HITL feedback workflow enhancing bot accuracy and user satisfaction for complex customer requests.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}