\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Versatile software engineer experienced in building secure, scalable applications and data-driven solutions using Java, Spring Boot, Salesforce, and modern JavaScript frameworks. Skilled in cloud technologies, API integration, and agile delivery, delivering impactful software aligned with business needs in collaborative environments.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming:} & Java, Apex, Python, JavaScript, TypeScript, SQL \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Salesforce Lightning Web Components \\
                \textbf{Databases:} & PostgreSQL, Oracle, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (Glue, Lambda, EC2), Docker, Jenkins, REST APIs, Microservices \\
                \textbf{Tools:} & Git, GitHub, JUnit, Jira, Ataccama, Postman \\
                \textbf{Methodologies:} & Agile (SCRUM), Object-Oriented Design, Data Engineering, MDM Fundamentals \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Java Spring Boot} microservices for scalable API endpoints, increasing throughput by 30\% and reliability across platforms.}
        \resumeItem{Developed automated deployment pipelines with \textbf{Docker} and \textbf{Jenkins}, reducing release cycles by 40\% and increasing release frequency.}
        \resumeItem{Enhanced security controls with \textbf{Spring Security}, decreasing unauthorized access attempts by 45\% through role-based authorization.}
        \resumeItem{Collaborated with cross-functional teams to design and deliver customer-facing applications using \textbf{React.js} improving user feedback scores by 25\%.}
        \resumeItem{Led code reviews and incorporated testing frameworks to increase unit test coverage to 90\%, improving code quality and maintainability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected \textbf{Salesforce Lightning Web Components} and \textbf{Apex} triggers improving CRM workflows efficiency by 35\%.}
        \resumeItem{Constructed frontend components using \textbf{React.js} and \textbf{TypeScript}, reducing page load times by 25\% and enhancing UX.}
        \resumeItem{Automated daily ETL data pipelines with \textbf{Python} and integrated with \textbf{AWS Glue}, increasing data processing speed by 40\%.}
        \resumeItem{Streamlined REST API integrations and optimized backend processes, improving data synchronization accuracy and reducing errors by 30\%.}
        \resumeItem{Developed testing suites and deployment scripts to ensure continuous integration and smooth release cycles within an Agile framework.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained Linux infrastructure for cybersecurity labs, executing secure configurations to support 100+ student projects effectively.}
        \resumeItem{Developed automation scripts to validate and grade student assignments, increasing grading accuracy by 25\% and reducing work time.}
        \resumeItem{Facilitated hands-on sessions for cryptography and web security, improving student comprehension by over 20\%.}
        \resumeItem{Monitored and troubleshot lab environments to ensure uninterrupted availability and secure testing for 150+ lab users.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} based REST APIs optimizing external system integrations, reducing average response time to under 100 ms.}
        \resumeItem{Enhanced \textbf{Angular.js} frontend components, increasing user engagement by 25\% through improved UI responsiveness.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures for complex queries reducing server load and improving transaction throughput by 15\%.}
        \resumeItem{Collaborated in building backend services using \textbf{C\#} and \textbf{.NET}, enabling 30\% faster data processing for key workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices supporting over 1000 concurrent users with sub-200ms API response times.}
        \resumeItem{Designed and implemented \textbf{React.js} user interfaces, improving application load speeds by 30\% and boosting UX scores.}
        \resumeItem{Established \textbf{AWS EC2} Dockerized environments for seamless deployment, increasing service uptime by 20\%.}
        \resumeItem{Authored unit tests with \textbf{JUnit}, achieving 90\% coverage and reducing bugs in production by 25\%.}
        \resumeItem{Collaborated on Agile ceremonies improving release cadence and team velocity by 15\%, ensuring alignment with business goals.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Code Review Assistant} | GitHub Actions, OpenAI API, Java, Python}{}
          \resumeItemListStart
              \resumeItem{Developed an automated code review tool using \textbf{OpenAI API} and \textbf{GitHub Actions}, decreasing manual review time by 40\%.}
              \resumeItem{Generated contextual code documentation automatically, achieving 100\% doc coverage and improving developer onboarding speed by 30\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Salesforce Sales Operations Automation} | Salesforce LWC, Apex, Salesforce Flows}{}
          \resumeItemListStart
              \resumeItem{Built custom \textbf{LWC} components and \textbf{Apex} logic automating complex sales processes, improving sales team efficiency by 35\%.}
              \resumeItem{Integrated Salesforce Flows to reduce manual entry and streamline workflows, increasing data accuracy and reducing errors by 25\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-Based Data Pipelines} | AWS Glue, Python, PostgreSQL}{}
          \resumeItemListStart
              \resumeItem{Engineered scalable ETL pipelines using \textbf{AWS Glue} and \textbf{Python} to process large datasets, reducing runtime by 40\%.}
              \resumeItem{Implemented \textbf{PostgreSQL} optimization strategies enhancing query performance, decreasing data retrieval latency by 30\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}