\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices improving system scalability and API throughput by 35\%, accelerating response times significantly.}
        \resumeItem{Integrated \textbf{Spring Security} authentication mechanisms, reducing unauthorized access by 40\% through improved role-based controls.}
        \resumeItem{Developed an AI-powered code review assistant using \textbf{LLMs} to reduce manual review efforts by 45\% and boost development speed by 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, decreasing build and release cycle times by 40\%.}
        \resumeItem{Led cross-functional Agile ceremonies to estimate and deliver production-quality features, improving sprint delivery accuracy by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and developed a \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ concurrent users with robust REST API integration.}
        \resumeItem{Designed and implemented multi-tier subscription e-commerce platform in \textbf{PHP}, integrating \textbf{Stripe} payments and role-based security.}
        \resumeItem{Automated stock data pipelines in \textbf{Python}, processing 10,000+ entries daily and reducing manual updates by 80\%.}
        \resumeItem{Developed customized \textbf{React} components and optimized state management, reducing page load times by 25\% and boosting engagement.}
        \resumeItem{Built AI-driven LinkedIn outreach and content automation bots, increasing qualified lead generation by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based cybersecurity labs by troubleshooting configuration issues, increasing lab uptime and usability by 20\%.}
        \resumeItem{Assisted students with debugging and deploying \textbf{software modules}, improving course success rates by 20\%.}
        \resumeItem{Automated lab grading with scripts, improving accuracy and reducing manual workload by 25\%.}
        \resumeItem{Conducted interactive sessions explaining cryptography, web security, and network protocols to 100+ students effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed sub-100ms response-time \textbf{TypeScript} API calls, supporting seamless integration and data exchange across systems.}
        \resumeItem{Upgraded platform UI using \textbf{Angular.js}, increasing user engagement and satisfaction metrics by 25\%.}
        \resumeItem{Developed high-performance backend services in \textbf{C#} \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend data load by 15\% and improving application responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Laravel} and \textbf{PHP} microservices supporting 1000 concurrent users with response times under 200ms.}
        \resumeItem{Led \textbf{CI/CD} pipeline implementation with \textbf{Docker} on \textbf{AWS EC2}, streamlining deployment workflows and reducing downtime.}
        \resumeItem{Designed and optimized \textbf{MySQL} database schemas and queries, improving data retrieval efficiency by 30\%.}
        \resumeItem{Built dynamic project management UI in \textbf{React.js}, enhancing usability and speeding page loads by 30\%.}
        \resumeItem{Implemented unit tests for core components using \textbf{PHPUnit} and \textbf{JUnit}, achieving 90\% coverage to ensure reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Operations Management System Enhancement} | PHP, Laravel, REST APIs}
          {}
          \resumeItemListStart
              \resumeItem{Developed and maintained core \textbf{PHP Laravel} modules to automate inventory and shipping workflows, reducing manual processing time by 35\%.}
              \resumeItem{Integrated third-party \textbf{ERP} and shipping APIs to streamline order fulfillment, improving accuracy and shipment speed by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Enterprise Application Refactoring} | PHP, PHPUnit, Docker, Azure}
          {}
          \resumeItemListStart
              \resumeItem{Led migration of legacy \textbf{PHP 7.x} codebase to \textbf{PHP 8.x}, improving performance and introducing modern coding standards.}
              \resumeItem{Implemented \textbf{unit and integration tests} and containerized applications with \textbf{Docker}, boosting deployment reliability and reducing bugs by 40\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & PHP, JavaScript, TypeScript, Java, Python, C\#, SQL \\
                \textbf{Web Development \& Frameworks:} & Laravel, Symfony, React.js, Angular.js, JQuery, Node.js, Spring Boot \\
                \textbf{Databases:} & MySQL, PostgreSQL, SQL Server, Redis \\
                \textbf{DevOps \& Cloud:} & Docker, Azure, AWS, CI/CD Pipelines, Git, Jenkins \\
                \textbf{Tools \& Others:} & REST APIs, PHPUnit, Jira, Agile Methodologies, GitHub, Webpack, Gulp \\
                \textbf{Enterprise Systems:} & ERP Integrations, MES, Message Queues (RabbitMQ) \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}