\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered and maintained scalable \textbf{Java Spring Boot} microservices, improving API throughput by 35\% and operational reliability.}
        \resumeItem{Implemented secure authentication features with \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Developed an \textbf{AI-driven} code review system using \textbf{LLMs}, decreasing manual review time by 45\% and accelerating delivery by 25\%.}
        \resumeItem{Automated CI/CD pipelines leveraging \textbf{Jenkins} and \textbf{Docker}, cutting deployment frequency by 40\%.}
        \resumeItem{Monitored production services with metrics and logs, proactively resolving issues to maintain 99.9\% uptime.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed a \textbf{SaaS} platform with \textbf{Laravel} backend and \textbf{React} frontend supporting 50+ concurrent users reliably.}
        \resumeItem{Automated data ingestion pipelines using \textbf{Python}, processing 10,000+ daily entries with 80\% reduction in manual effort.}
        \resumeItem{Created AI-powered \textbf{LLMs}-based automation tools for data extraction from FINRA, reducing manual processing by 80\%.}
        \resumeItem{Enhanced \textbf{React} components, reducing page load times by 25\% and boosting user engagement significantly.}
        \resumeItem{Integrated payment systems with \textbf{Stripe} and WooCommerce, supporting role-based subscriptions and secure transactions.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and secured \textbf{Linux}-based cybersecurity lab infrastructure, ensuring reliable and safe environments for students.}
        \resumeItem{Assisted students in debugging and deploying software modules, improving lab assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts to validate assignments, increasing grading accuracy and reducing manual workload by 25\%.}
        \resumeItem{Conducted over 15 interactive sessions explaining cryptography, networking, and web security fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented responsive API calls with \textbf{TypeScript}, achieving sub-100ms response times for seamless data exchange.}
        \resumeItem{Improved user engagement by 25\% by refactoring frontend using \textbf{Angular.js} for improved responsiveness.}
        \resumeItem{Built backend services using \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, improving database efficiency and reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java Spring Boot} microservices with \textbf{MySQL}, enabling sub-200ms response times for 1000+ users.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines and containerized deployments on \textbf{AWS EC2} using \textbf{Docker}, increasing release frequency.}
        \resumeItem{Built project management UI in \textbf{React.js} that improved usability and page load speed by 30\%.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} unit tests covering 90\% code for core pipelines module, increasing software reliability.}
        \resumeItem{Collaborated in a team to deliver an end-to-end \textbf{SaaS} SDLC automation tool, improving software delivery.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable Cloud Infrastructure for Web Services} | AWS, GCP, Terraform, Docker, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Architected and deployed resilient cloud infrastructure in \textbf{AWS} and \textbf{GCP} using \textbf{Terraform} and \textbf{Kubernetes}, achieving 99.9\% uptime.}
              \resumeItem{Automated deployment pipelines and monitoring workflows to reduce production incidents by 30\% and accelerate feature rollout cycles.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{API Management and Integration Platform} | Python, REST API, Docker, Postgres}{}
          \resumeItemListStart
              \resumeItem{Developed a robust backend API platform using \textbf{Python} with containerized deployment via \textbf{Docker}, supporting seamless third-party API integrations.}
              \resumeItem{Implemented monitoring and alerting frameworks to track API performance, improving response times by 20\% and reducing downtime.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, Go, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Cloud Platforms \& DevOps:} & AWS (EC2, S3, Lambda), GCP, Docker, Kubernetes, Terraform, Jenkins \\
                \textbf{Web Frameworks \& Frontend:} & Spring Boot, React, Angular, Laravel, Node.js \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, DynamoDB \\
                \textbf{CI/CD \& Monitoring:} & Jenkins, GitHub Actions, Datadog, Build Automation \\
                \textbf{Tools \& Technologies:} & REST APIs, Microservices, Git, Linux/Unix, JUnit, Security Best Practices \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}