\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Refactored \textbf{backend PHP/Laravel} services, improving API response times by 30\% for high-traffic endpoints.}
        \resumeItem{Implemented \textbf{test-driven development} practices, raising automated test coverage by 50\% to reduce production bugs.}
        \resumeItem{Designed and deployed \textbf{PostgreSQL} database schemas to support flexible data storage and efficient queries.}
        \resumeItem{Built and maintained \textbf{ETL} pipelines to automate data ingestion, boosting data accuracy by 25\%.}
        \resumeItem{Collaborated with cross-functional teams to scope projects and estimate timelines, improving delivery accuracy by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Laravel}-based APIs to integrate with client systems, reducing manual data entry by 40\%.}
        \resumeItem{Created flexible \textbf{PostgreSQL} data structures to support diverse client needs and legacy system integration.}
        \resumeItem{Automated build and deployment workflows using \textbf{Git} and \textbf{AWS}, decreasing deployment time by 35\%.}
        \resumeItem{Engaged with non-technical clients to refine requirements and translate them into effective software solutions.}
        \resumeItem{Debugged and optimized legacy codebases to improve system performance by 25\% and reliability.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} infrastructure for cybersecurity labs, ensuring secure environments for all users.}
        \resumeItem{Guided students through \textbf{debugging} and testing, improving project success rates by 20\%.}
        \resumeItem{Automated validation scripts, boosting grading accuracy by 25\% and reducing manual workloads.}
        \resumeItem{Conducted tutorial sessions explaining networking and security concepts to enhance student learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, reducing data retrieval time by 15\%.}
        \resumeItem{Implemented backend features using \textbf{C\# .NET}, improving system throughput by 20\%.}
        \resumeItem{Refined \textbf{TypeScript} API calls, maintaining average response time below 100ms for better UX.}
        \resumeItem{Modernized platform UI with \textbf{Angular.js}, driving a 25\% increase in user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{PHP/Laravel} microservices with \textbf{MySQL}, serving 1000+ concurrent users with 200ms response.}
        \resumeItem{Engineered flexible, scalable data models enabling cross-system data integration and client customization.}
        \resumeItem{Automated deployment with \textbf{Docker} on \textbf{AWS EC2}, reducing downtime by 30\%.}
        \resumeItem{Wrote unit and integration tests increasing code coverage to 90\%, minimizing production defects.}
        \resumeItem{Led project planning and timeline estimation efforts, enhancing team delivery predictability by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Dynamic API Platform} | Laravel, PostgreSQL, AWS}
          {}
          \resumeItemListStart
              \resumeItem{Built a modular \textbf{Laravel} API platform with dynamic data structures, serving multiple client domains efficiently.}
              \resumeItem{Implemented \textbf{ETL} workflows to securely ingest, transform, and store client data, increasing automation by 60\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-based Monitoring System} | PHP, Laravel, AWS, PostgreSQL}
          {}
          \resumeItemListStart
              \resumeItem{Designed and deployed a cloud-native monitoring tool with \textbf{Laravel} and \textbf{AWS}, improving client operational insights.}
              \resumeItem{Developed RESTful APIs and flexible data models that support real-time analytics and reporting features.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & PHP, Java, Python, JavaScript, TypeScript, C\#, Shell Scripting \\
                \textbf{Frameworks \& Libraries:} & Laravel, Spring Boot, React.js, Angular.js, .NET \\
                \textbf{Databases:} & PostgreSQL, MySQL, MSSQL, MongoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Git, GitHub, Jenkins \\
                \textbf{Development Practices:} & Test Driven Development (TDD), API Design, ETL Processes, CI/CD \\
                \textbf{Tools \& Others:} & REST APIs, Linux, JSON, Jira, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}