\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices to improve system reliability, increasing throughput by 35\% under load.}
        \resumeItem{Integrated monitoring dashboards using \textbf{Grafana} for real-time metrics, reducing production issue resolution time by 40\%.}
        \resumeItem{Built and maintained RESTful APIs for core services, enhancing data interchange speed by 30\% through optimized endpoints.}
        \resumeItem{Automated deployment pipelines with \textbf{Docker} and \textbf{Jenkins}, cutting release cycles by 35\% and improving software quality.}
        \resumeItem{Collaborated with cross-functional teams to design microservices adhering to best practices, improving code maintainability and reducing bugs 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered data processing pipelines in \textbf{Python} to automate stock data ingestion, improving processing speed by 80\%.}
        \resumeItem{Developed frontend features with \textbf{React} to enhance user experience, decreasing page load times by 25\%.}
        \resumeItem{Implemented role-based access control using \textbf{Spring Security} and \textbf{Java}, strengthening platform security and compliance.}
        \resumeItem{Created scalable RESTful APIs following microservices design principles, improving integration with third-party services by 40\%.}
        \resumeItem{Leveraged \textbf{Grafana} dashboards to monitor system health, enabling proactive issue identification and 30\% uptime improvement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed lab infrastructure supporting \textbf{Linux} and \textbf{Python} based software, ensuring 99\% uptime for student access.}
        \resumeItem{Assisted students in debugging and deploying secure code modules, enhancing assignment completion rates by 20\%.}
        \resumeItem{Automated grading workflows using scripts, reducing manual review time by 25\% and improving grading consistency.}
        \resumeItem{Conducted teaching sessions on secure coding and network protocols, increasing student comprehension and participation.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized backend services developed in \textbf{C\#} .NET, reducing data retrieval latency by 30\% through efficient queries.}
        \resumeItem{Enhanced \textbf{Angular.js} frontend components to improve UI responsiveness, resulting in 25\% higher user engagement.}
        \resumeItem{Implemented and optimized \textbf{PostgreSQL} queries to reduce database load and decrease application response time by 15\%.}
        \resumeItem{Integrated RESTful API endpoints with frontend using \textbf{TypeScript}, achieving sub-100ms response times for critical operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000+ users with optimized database \textbf{MySQL} queries achieving under 200ms response times.}
        \resumeItem{Designed and deployed Dockerized microservices on \textbf{AWS EC2}, automating CI/CD deployment pipelines for faster releases.}
        \resumeItem{Built a dynamic frontend using \textbf{React.js}, reducing load times by 30\% and improving overall user experience.}
        \resumeItem{Implemented unit testing with \textbf{JUnit} framework achieving 90\% code coverage for critical backend modules.}
        \resumeItem{Collaborated within Agile teams to design REST APIs, incorporating best practices that improved system scalability and maintainability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable RESTful Microservices Platform} | Java Spring Boot, Docker, AWS}
          \resumeItemListStart
              \resumeItem{Designed and developed microservices using \textbf{Java Spring Boot} deployed on \textbf{AWS} with Docker containers, increasing scalability by 50\%.}
              \resumeItem{Implemented health monitoring with \textbf{Grafana} dashboards, enabling 24/7 real-time system visibility and reducing downtime by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Python-based API and Frontend Integration} | Python, React, RESTful APIs}
          \resumeItemListStart
              \resumeItem{Built RESTful APIs in \textbf{Python} integrated with a \textbf{React} frontend, improving data synchronization speed by 40\%.}
              \resumeItem{Optimized API response times and enhanced error handling, raising application reliability and user satisfaction ratings by 20\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Docker, Kubernetes \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL, NoSQL \\
                \textbf{Cloud Platforms:} & AWS, Azure, Google Cloud Platform \\
                \textbf{Monitoring \& DevOps:} & Grafana, Git, GitHub, CI/CD Pipelines, Jenkins, Docker, Kubernetes \\
                \textbf{Other Technologies:} & RESTful APIs, Microservices Architecture, Kafka, RabbitMQ, Linux/Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}