\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Refactored \textbf{Java Spring Boot} microservices for improved scaling, boosting API response rates by 35\%.}
        \resumeItem{Enhanced security by integrating \textbf{Spring Security}, decreasing unauthorized access attempts by 40\%.}
        \resumeItem{Implemented an \textbf{AI-powered} code review bot to streamline pull requests, accelerating development by 25\%.}
        \resumeItem{Automated deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 40\%.}
        \resumeItem{Coordinated cross-team collaboration to improve software deployment reliability and monitor system performance metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed scalable \textbf{SaaS} data visualization platform with \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users.}
        \resumeItem{Automated large-scale data pipelines in \textbf{Python}, processing 10,000+ entries daily and reducing manual effort by 80\%.}
        \resumeItem{Developed AI-driven \textbf{LinkedIn} automation bot, boosting qualified lead generation by 40\%.}
        \resumeItem{Optimized \textbf{React} components for faster load times, increasing user engagement by 25\%.}
        \resumeItem{Established \textbf{AI agents} leveraging large language models to automate broker data workflows, cutting manual input by 80\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments, ensuring consistent and reliable cybersecurity practice setups.}
        \resumeItem{Assisted students deploying and debugging software modules, improving assignment pass rates by 20\%.}
        \resumeItem{Developed automation scripts to streamline grading, enhancing accuracy and reducing instructor workload by 25\%.}
        \resumeItem{Conducted multiple sessions explaining complex topics such as Cryptography and Web Security to enhance student comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls achieving sub-100ms response times for improved data exchange efficiency.}
        \resumeItem{Upgraded \textbf{Angular.js} frontend, increasing user engagement metrics by 25\%.}
        \resumeItem{Built high-performance backends using \textbf{C\#} and \textbf{.NET} frameworks, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, cutting frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{microservices} in \textbf{Java Spring Boot} with \textbf{MySQL}, ensuring response times under 200ms for 1000 concurrent users.}
        \resumeItem{Automated \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} with \textbf{Docker}, enhancing deployment speed and reliability.}
        \resumeItem{Created project management UIs in \textbf{React.js} improving usability and reducing page load time by 30\%.}
        \resumeItem{Implemented unit testing using \textbf{JUnit} achieving 90\% coverage reducing bugs before production.}
        \resumeItem{Collaborated on SaaS tool development automating SDLC processes, enhancing team productivity and reducing cycle times.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GCP-Enabled Scalable Microservices Platform} | FastAPI, Node.js, Google Cloud Platform}
          \resumeItemListStart
              \resumeItem{Built microservices using \textbf{FastAPI} and \textbf{Node.js} on \textbf{GCP} integrating \textbf{Cloud Run}, \textbf{Firestore}, and \textbf{BigQuery} for scalable data processing.}
              \resumeItem{Implemented secure \textbf{RESTful APIs} following best practices, resulting in 99.9\% uptime and efficient client-server interactions.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated CI/CD Pipeline with Testing} | GitHub Actions, Docker, Python, FastAPI}
          \resumeItemListStart
              \resumeItem{Designed CI/CD workflows using \textbf{GitHub Actions} with automated unit, integration, and end-to-end tests to ensure code quality and fast deployment.}
              \resumeItem{Containerized services with \textbf{Docker} enabling repeatable deployments and seamless integration into cloud environments.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, TypeScript, Node.js, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & Angular, React.js, FastAPI, Spring Boot, Laravel, .NET \\
                \textbf{Cloud Platforms \& Services:} & Google Cloud Platform (Cloud Storage, Cloud Functions, Cloud Run, API Gateway, Firestore, BigQuery), AWS (EC2, S3) \\
                \textbf{Databases:} & SQL (MySQL, PostgreSQL), NoSQL (Firestore, MongoDB, DynamoDB) \\
                \textbf{DevOps \& Containerization:} & Docker, CI/CD (GitHub Actions, Jenkins), Kubernetes (basic knowledge) \\
                \textbf{Testing \& Tools:} & Unit Testing, Integration Testing, End-to-End Testing, Git, GitHub, RESTful APIs \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}