\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced backend scalability using \textbf{PHP 8.3} and \textbf{Symfony 6}, boosting API throughput by 30\% with containerized \textbf{Docker} services.}
        \resumeItem{Implemented message queuing with \textbf{RabbitMQ} to streamline async processes, reducing response latency by 25\%.}
        \resumeItem{Integrated \textbf{MySQL 8} query optimizations, decreasing database response times by 40\% and supporting higher concurrent requests.}
        \resumeItem{Automated deployment pipelines using \textbf{Kubernetes} and \textbf{Argo CD}, increasing release frequency by 50\% with zero downtime.}
        \resumeItem{Designed GraphQL APIs, improving data retrieval flexibility and reducing client payload sizes by over 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed modular PHP services on \textbf{Symfony}, enhancing e-commerce platform performance and supporting 1000+ simultaneous users.}
        \resumeItem{Led \textbf{Docker}-based containerization efforts for seamless dev-to-prod consistency, reducing environment issues by 70\%.}
        \resumeItem{Built real-time inventory tracking using \textbf{Elasticsearch}, increasing search performance and accuracy by 35\%.}
        \resumeItem{Collaborated on message-driven microservices with \textbf{RabbitMQ}, improving system resilience and throughput by 30\%.}
        \resumeItem{Conducted code reviews enforcing \textbf{PHPStan} standards and custom static analysis, reducing bugs by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Secured Linux lab environments with hardening scripts, improving system integrity and reducing vulnerabilities by 25\%.}
        \resumeItem{Automated validation testing scripts, cutting grading time by 30\% while improving result accuracy for security assignments.}
        \resumeItem{Supported students debugging network security modules, elevating project completion rates by 20\%.}
        \resumeItem{Led educational sessions on cryptography and network protocols, enhancing class engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed backend features with \textbf{TypeScript} & \textbf{Node.js} APIs, reducing data fetch latency by 30\%.}
        \resumeItem{Enhanced existing \textbf{Angular.js} frontend features, increasing user retention by 20\% through improved interface flow.}
        \resumeItem{Optimized PostgreSQL queries, reducing server load by 25\% and accelerating data-driven page loads.}
        \resumeItem{Created efficient C\# microservices, trimming backend processing time by 15\%, supporting scaling efforts.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{PHP Symfony} microservices integrated with \textbf{MySQL}, improving response times by 35\% for SaaS clients.}
        \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{AWS EC2}, enhancing release reliability and deployment speed by 50\%.}
        \resumeItem{Optimized legacy code and reduced technical debt, increasing system maintainability and reducing bugs by 40\%.}
        \resumeItem{Developed project management UI in \textbf{React.js}, driving a 30\% faster user workflow and higher customer satisfaction.}
        \resumeItem{Implemented unit testing with \textbf{PHPUnit}, achieving 90\% code coverage and lowering regressions by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Real-time Warehouse Inventory API} | PHP, Symfony, MySQL, Elasticsearch}{}
          \resumeItemListStart
              \resumeItem{Built a high-performance REST API managing 100K+ daily transactions with \textbf{Symfony} and optimized \textbf{MySQL} queries cutting response time by 30\%.}
              \resumeItem{Integrated \textbf{Elasticsearch} for rapid search capabilities, boosting inventory data retrieval speed by 40\% and accuracy.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Containerized Microservices Platform} | Docker, Kubernetes, RabbitMQ, PHP}{}
          \resumeItemListStart
              \resumeItem{Deployed microservices using \textbf{Docker} and \textbf{Kubernetes}, enabling zero-downtime releases and scaling to handle double user load effectively.}
              \resumeItem{Implemented asynchronous processes with \textbf{RabbitMQ}, improving throughput by 25\% and reliable order processing under high concurrency.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & PHP 8.3, Java, Python, TypeScript, C\#, JavaScript, SQL, Shell Scripting \\
                \textbf{Frameworks \& Libraries:} & Symfony 6, Laravel, React.js, Spring Boot, Angular.js, Node.js \\
                \textbf{Databases:} & MySQL 8, PostgreSQL, Elasticsearch, MongoDB \\
                \textbf{DevOps \& Deployment:} & Docker, Kubernetes, AWS (EC2, S3), Jenkins, GitLab CI, Argo CD \\
                \textbf{Messaging \& APIs:} & RabbitMQ, REST, GraphQL, JSON, gRPC \\
                \textbf{Tools \& Monitoring:} & Git, PHPStan, PHPUnit, DataDog, Sentry, Opsgenie \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}