\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced backend API performance by 35\% through optimization of \textbf{Java Spring Boot} microservices architecture.}
        \resumeItem{Implemented \textbf{Spring Security} role-based access control, decreasing unauthorized access attempts by 40\%.}
        \resumeItem{Reduced manual code reviews by 45\% by deploying an \textbf{AI-driven} review assistant using \textbf{OpenAI API}.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating release frequency by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to align software features with business goals, improving delivery timelines by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Laravel} backend APIs enabling seamless integration for a SaaS data visualization platform.}
        \resumeItem{Automated ETL pipelines with \textbf{Python}, processing 10,000+ records daily and reducing manual work by 80\%.}
        \resumeItem{Built subscription e-commerce system with \textbf{PHP}, enhancing user access controls and payment workflows.}
        \resumeItem{Deployed AI agents using \textbf{LLMs} to automate broker data ingestion, cutting manual workflows by 80\%.}
        \resumeItem{Optimized \textbf{React} components, reducing page load times by 25\% and increasing user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} infrastructure for cybersecurity labs, ensuring high availability and compliance.}
        \resumeItem{Improved student assignment success by 20\% through targeted software debugging and deployment guidance.}
        \resumeItem{Automated grading with scripts, increasing accuracy and reducing manual workload by 25\%.}
        \resumeItem{Delivered technical tutorials on cryptography and network security, enhancing student understanding and participation.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, reducing data retrieval latency by 15\%.}
        \resumeItem{Developed responsive frontend features with \textbf{Angular.js}, boosting user engagement by 25\%.}
        \resumeItem{Implemented efficient backend services in \textbf{C\#} on \textbf{.NET}, cutting response times by 30\%.}
        \resumeItem{Executed \textbf{TypeScript} API calls to ensure sub-100ms response time and smooth data flow.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led \textbf{PHP/Laravel} backend development for SDLC automation SaaS tool used by 1000+ users.}
        \resumeItem{Designed and implemented scalable ETL pipelines and APIs, improving data throughput by 30\%.}
        \resumeItem{Setup \textbf{AWS EC2} \textbf{Docker} deployments automating CI/CD pipeline execution with zero downtime.}
        \resumeItem{Enhanced project management UI with \textbf{React.js}, reducing load time by 30\% and improving usability.}
        \resumeItem{Wrote unit and integration tests with \textbf{PHPUnit} to achieve 90\% code coverage and improve quality.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Flexible Laravel API Backend} | Designed dynamic backend API for scalable data structure and integration}
          \resumeItemListStart
              \resumeItem{Developed flexible \textbf{Laravel} API supporting dynamic data models, improving integration speed by 40\%.}
              \resumeItem{Implemented secure API authentication and authorization ensuring compliance with client access requirements.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud ETL Pipeline Automation} | Built automated ETL system on AWS to streamline data ingestion and processing}
          \resumeItemListStart
              \resumeItem{Created \textbf{ETL} pipelines using \textbf{AWS} services, automating data workflows and reducing manual handling by 75\%.}
              \resumeItem{Designed modular data transformation steps allowing flexible processing for diverse client data sources.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Backend Development:} & PHP, Laravel, Java, Spring Boot, Python \\
                \textbf{Databases:} & PostgreSQL, MSSQL, MySQL, SQL \\
                \textbf{Cloud \& DevOps:} & AWS, Docker, CI/CD, Jenkins, Laravel Vapor \\
                \textbf{Frontend Technologies:} & React.js, Angular.js, Tailwind CSS, htmx \\
                \textbf{APIs \& Automation:} & REST API, ETL Pipeline Development, Git, GitHub, OpenAI API \\
                \textbf{Other Skills:} & Test Driven Development (TDD), Agile Project Planning, AI Integration, Debugging, Performance Optimization \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}