\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented distributed microservices in \textbf{Java Spring Boot}, improving API scalability and throughput by 35\%.}
        \resumeItem{Enhanced authentication using \textbf{Spring Security}, decreasing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an \textbf{AI-assisted code review} bot, reducing manual review time by 45\% and accelerating delivery speed by 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, cutting release cycles by 40\%.}
        \resumeItem{Conducted performance tuning and profiling to optimize backend services for low-latency requirements.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built a scalable SaaS platform with \textbf{Laravel} and \textbf{React} supporting 50+ concurrent users flawlessly.}
        \resumeItem{Automated data ingestion pipelines in \textbf{Python}, processing 10,000+ daily records, reducing manual effort by 80\%.}
        \resumeItem{Led development of AI agents using \textbf{LLMs} to automate data downloads, reducing manual work by 80\%.}
        \resumeItem{Refined \textbf{React} components to reduce load times by 25\% and enhance user engagement.}
        \resumeItem{Implemented role-based access control for a multi-tier e-commerce subscription platform using \textbf{PHP} and \textbf{Stripe}.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab infrastructure, ensuring stable and reliable environments for cybersecurity research.}
        \resumeItem{Coached students in debugging and deploying software, increasing assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts, improving accuracy and reducing manual review workload by 25\%.}
        \resumeItem{Conducted 15+ technical sessions on Cryptography, Networking, and Security topics.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed performant API calls in \textbf{TypeScript}, achieving average response times under 100ms.}
        \resumeItem{Enhanced frontend with \textbf{Angular.js}, driving 25\% increase in user engagement.}
        \resumeItem{Built efficient backend APIs in \textbf{C\#} using \textbf{.NET}, decreasing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, reducing frontend load by 15\% and improving responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered Java \textbf{Spring Boot} microservices supporting 1,000 concurrent users, maintaining sub-200ms response times.}
        \resumeItem{Developed CI/CD pipeline with \textbf{Docker} for seamless deployment on \textbf{AWS EC2}, improving release efficiency.}
        \resumeItem{Built scalable project management UI in \textbf{React.js}, enhancing page load speeds by 30\%.}
        \resumeItem{Implemented robust unit tests with \textbf{JUnit} achieving 90\%+ coverage on core modules.}
        \resumeItem{Collaborated in a team to automate SDLC processes, reducing manual overhead significantly.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable Vector Search Infrastructure} | Go, C++, gRPC, Kafka}
          \resumeItemListStart
              \resumeItem{Designed and optimized a distributed vector embedding system enabling efficient nearest neighbor search at scale with sub-second latency.}
              \resumeItem{Implemented \textbf{Kafka}-based data ingestion and indexing pipelines, improving throughput by 50\% and ensuring fault tolerance.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Distributed Graph Database Query Optimizer} | C++, Cypher, ETCD}
          \resumeItemListStart
              \resumeItem{Built a query optimization engine leveraging \textbf{Cypher} for enhanced execution speed, reducing average query latency by 30\%.}
              \resumeItem{Developed replication and sharding mechanisms ensuring consistent, fault-tolerant distributed data access with high availability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C++, Go, Java, Python, TypeScript, C\#, PHP, JavaScript \\
                \textbf{Databases \& Query Languages:} & Vector Databases, Graph Databases, Cypher, SQL, PostgreSQL, MySQL \\
                \textbf{Distributed Systems:} & Kafka, ETCD, gRPC, REST APIs, Docker, Microservices \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3), Jenkins, Docker, CI/CD Pipelines \\
                \textbf{Web Development Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Tools \& Other:} & Linux, Git, Performance Profiling, Debugging, AI-assisted Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}