\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered robust frontend components using \textbf{JavaScript} improving user interaction and cutting UI bugs by 30\%.}
        \resumeItem{Collaborated closely with AI and backend teams to integrate APIs accelerating feature rollout by 20\%.}
        \resumeItem{Refactored legacy test suites migrating from outdated tools to \textbf{modern testing libraries}, increasing coverage by 35\%.}
        \resumeItem{Enhanced product scalability by optimizing \textbf{React} state management, reducing load times by 25\%.}
        \resumeItem{Drove UI/UX improvements based on customer feedback, boosting user satisfaction scores by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{React.js} applications for enterprise SaaS decreasing bug reports by 40\%.}
        \resumeItem{Automated UI testing using \textbf{Jest} and \textbf{Testing Library}, cutting regression bugs by 50\%.}
        \resumeItem{Collaborated with product and design teams to tailor UI workflows for business-critical functions, increasing feature adoption by 22\%.}
        \resumeItem{Supported integration of AI capabilities into frontend improving automation features and reducing manual input by 30\%.}
        \resumeItem{Optimized complex frontend logic enhancing performance for dashboards accessed by over 100 users daily.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments and assisted in deploying web applications with 99.9\% uptime.}
        \resumeItem{Helped students debug \textbf{JavaScript} and backend code, improving assignment clarity and submission success by 20\%.}
        \resumeItem{Automated grading scripts enhanced efficiency decreasing manual workload by 25\% while increasing accuracy.}
        \resumeItem{Demystified user-centered web security concepts through interactive teaching sessions fostering hands-on learning.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Designed frontend features using \textbf{TypeScript} and \textbf{Angular.js} enhancing platform responsiveness by 25\%.}
        \resumeItem{Improved backend API response times by 30\% through code optimization in \textbf{C\#} and \textbf{.NET} services.}
        \resumeItem{Streamlined database interactions via \textbf{PostgreSQL} optimizations, reducing query latency by 15\%.}
        \resumeItem{Collaborated in cross-team reviews to address user experience refinements aligned with enterprise demands.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{React.js} UI components focusing on user workflows resulting in 30\% faster load times and usability.}
        \resumeItem{Built scalable microservices with \textbf{Java Spring Boot} supporting 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Designed and maintained CI/CD pipelines using \textbf{Docker} and \textbf{AWS}, cutting deployment time by 40\%.}
        \resumeItem{Enhanced unit test coverage to over 90\% for backend modules using \textbf{JUnit}, improving code reliability.}
        \resumeItem{Collaborated with product managers to prioritize and refine feature set geared toward enterprise workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Desktop Modeling Tool Integration} | JavaScript, React.js, bpmn.io platform}
          \resumeItemListStart
              \resumeItem{Contributed code to enhance modularity and add Copilot support, improving AI-assisted modeling workflows by 25\%.}
              \resumeItem{Collaborated with cross-functional teams to deliver iterative improvements aligning with enterprise user experience goals.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Frontend Testing Library Migration} | JavaScript, Jest, Testing Library}
          \resumeItemListStart
              \resumeItem{Led migration from \textbf{Enzyme} to \textbf{Testing Library}, raising test reliability and reducing flaky tests by 40\%.}
              \resumeItem{Optimized test suites to shorten CI feedback cycles by 30\%, accelerating development velocity.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, bpmn.io platform, Node.js, Spring Boot \\
                \textbf{Testing \& Automation:} & Jest, Testing Library, JUnit, CI/CD pipelines, GitHub Actions \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3), Docker, Jenkins, GitHub, CI/CD \\
                \textbf{Design \& User Experience:} & User-centered design, UI/UX collaboration, Enterprise application workflows \\
                \textbf{AI \& Automation Technologies:} & AI Agents, LLM Integration, Copilot support, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}