\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Updated company web pages using \textbf{HTML, CSS}, and \textbf{JavaScript}, reducing backlog by 30\% within first quarter.}
        \resumeItem{Coordinated with marketing team to align web content with brand guidelines, improving consistency across 40+ pages.}
        \resumeItem{Troubleshot browser compatibility issues for dynamic content, achieving error-free rendering on 5 major browsers.}
        \resumeItem{Managed web content updates through CMS, decreasing page update time by 25\% and enhancing operational efficiency.}
        \resumeItem{Conducted quality assurance tests that increased mobile responsive design compliance by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Created and updated product pages on WordPress, improving content accuracy and increasing page views by 15\%.}
        \resumeItem{Collaborated with design team using \textbf{Figma} and \textbf{Photoshop} to convert designs into responsive web pages.}
        \resumeItem{Implemented basic JavaScript enhancements that boosted user interaction by 10\% on product pages.}
        \resumeItem{Maintained CMS back-end and resolved update issues, shortening content deployment cycle by 20\%.}
        \resumeItem{Ensured SEO best practices in content updates, contributing to a 12\% uplift in organic search traffic.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Assisted in webpage content updates and styling fixes using \textbf{HTML} and \textbf{CSS}, improving user lab experience.}
        \resumeItem{Supported responsive design testing to ensure functionality across devices, lifting mobile user satisfaction by 18\%.}
        \resumeItem{Helped create and maintain documentation for web updates, reducing implementation errors by 22\%.}
        \resumeItem{Collaborated with faculty to update educational content, enhancing accessibility compliance awareness by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Assisted in updating and fixing \textbf{HTML, CSS}, and \textbf{JavaScript} issues, improving application responsiveness by 15\%.}
        \resumeItem{Contributed to cross-browser testing and resolved compatibility bugs, raising site stability by 18\%.}
        \resumeItem{Collaborated on CMS integration tasks, reducing content update turnaround by 20\%.}
        \resumeItem{Documented frontend fixes and enhancements, elevating team knowledge sharing and decreasing error repeats by 10\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built product landing pages using \textbf{HTML} and \textbf{CSS} from \textbf{Figma} designs, improving brand consistency by 25\%.}
        \resumeItem{Managed website content updates on CMS platforms, reducing errors and increasing update speed by 30\%.}
        \resumeItem{Resolved UI bugs impacting cross-browser compatibility, achieving a 95\% positive feedback rate from users.}
        \resumeItem{Collaborated with marketing to enhance page SEO, boosting site search rankings by 18\%.}
        \resumeItem{Implemented content updates including images and links efficiently, lowering content downtime by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Responsive Product Page Builder} | WordPress, HTML, CSS, JavaScript}{}
          \resumeItemListStart
              \resumeItem{Developed a template-based product page system streamlining web updates and reducing page build time by 40\%.}
              \resumeItem{Integrated responsive design principles ensuring flawless display across desktop, tablet, and mobile devices.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Web Content Management Automation} | CMS, JavaScript, SEO Basics}{}
          \resumeItemListStart
              \resumeItem{Automated website content updating workflows using CMS tools, decreasing manual editing time by 35\%.}
              \resumeItem{Optimized content structure to improve SEO ranking, leading to a 15\% increase in organic traffic.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Web Development:} & HTML, CSS, JavaScript, Responsive Design, CMS (WordPress, Drupal), SEO Basics \\
                \textbf{Design Tools:} & Photoshop, Figma \\
                \textbf{Programming Languages:} & Java, Python, PHP, TypeScript, C\#, Go \\
                \textbf{Frameworks \& Libraries:} & React.js, Angular.js, Laravel, Spring Boot, .NET \\
                \textbf{Version Control \& DevOps:} & Git, GitHub, Docker, Jenkins, AWS, CI/CD \\
                \textbf{Other Tools \& Technologies:} & REST API, Linux/Unix, Jira, Web Accessibility Standards \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}