\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered automation tools in \textbf{Python} to streamline hardware testing, reducing server qualification time by 30\%.}
        \resumeItem{Collaborated with performance teams to benchmark software on new compute hardware, improving latency by 20\%.}
        \resumeItem{Designed scripts to deploy firmware updates across devices using \textbf{Linux} shell tools, slashing manual labor by 40\%.}
        \resumeItem{Spearheaded integration between provisioning systems and hardware fleet management, accelerating server onboarding by 25\%.}
        \resumeItem{Documented hardware qualification results through detailed reports and internal presentations that enhanced team knowledge sharing.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected data automation workflows using \textbf{Python} to manage large-scale server inventory and hardware telemetry.}
        \resumeItem{Collaborated with hardware vendors to analyze component performance metrics, enabling selection of optimized server parts.}
        \resumeItem{Developed monitoring dashboards utilizing \textbf{Grafana} and \textbf{Prometheus}, reducing hardware fault detection time by 30\%.}
        \resumeItem{Optimized server-side software using performance profiling, contributing to 15\% throughput improvement on new hardware.}
        \resumeItem{Automated remote management processes leveraging \textbf{IPMI} and \textbf{Redfish} protocols for scalable server firmware updates.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments supporting hardware interface testing and firmware deployment experiments.}
        \resumeItem{Led debugging sessions for low-level software interacting with \textbf{ARM} and \textbf{x86} architectures, improving diagnostic accuracy by 25\%.}
        \resumeItem{Automated lab validation scripts for firmware updates, reducing manual steps by 35\% and increasing repeatability.}
        \resumeItem{Trained users on remote server management technologies including \textbf{IPMI} and \textbf{Redfish} tools, raising operational efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced backend systems to collect hardware performance metrics, achieving 20\% improvement in data reporting accuracy.}
        \resumeItem{Automated API integrations using \textbf{TypeScript} and \textbf{.NET} improving system reliability by 30\%.}
        \resumeItem{Optimized database queries to accelerate logging of device health data, reducing latency by 15\% with \textbf{PostgreSQL}.}
        \resumeItem{Collaborated with cross-functional teams to incorporate hardware fault logs into monitoring systems using \textbf{Grafana}.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed microservices in \textbf{Java Spring Boot} that interfaced with hardware telemetry for real-time server health insights.}
        \resumeItem{Designed end-to-end automation pipelines deploying firmware updates across distributed server fleets using \textbf{Docker}.}
        \resumeItem{Integrated performance benchmarking tools to evaluate compute and memory throughput on targeted server architectures.}
        \resumeItem{Implemented remote management features using \textbf{Linux} shell scripting to control server components and power devices.}
        \resumeItem{Built interactive dashboards for operational teams to monitor hardware quality metrics and lifecycle KPIs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Server Hardware Qualification Framework} | Python, Bash, Linux}{}
          \resumeItemListStart
              \resumeItem{Developed an automated framework to qualify server hardware across EVT/DVT/PVT phases, reducing test cycle time by 35\%.}
              \resumeItem{Integrated performance benchmarking scripts to collect CPU, memory, and network metrics for hardware selection optimization.}
              \resumeItem{Implemented firmware update automation using \textbf{Redfish} and \textbf{IPMI}, improving fleet-wide deployment efficiency by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Remote Server Fleet Management Tool} | Go, Linux, Prometheus}{}
          \resumeItemListStart
              \resumeItem{Engineered a scalable remote management tool to monitor and manage 1000+ servers’ health and provisioning states.}
              \resumeItem{Implemented telemetry ingestion using \textbf{Prometheus}, enabling real-time alerting and 25\% faster fault detection.}
              \resumeItem{Collaborated with SRE teams to integrate provisioning systems with hardware management tools, cutting integration effort by 30\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Hardware \& Protocols:} & Server hardware design, \textbf{CPU (x86, ARM)}, memory technologies, \textbf{Redfish}, \textbf{IPMI}, firmware update mechanisms \\
                \textbf{Programming \& Scripting:} & \textbf{Python}, Bash, Java, Go, Shell Scripting, C, C++ \\
                \textbf{Operating Systems \& Tools:} & \textbf{Linux/Unix}, server remote management, \textbf{Docker}, Git, Jenkins \\
                \textbf{Performance \& Benchmarking:} & Hardware performance benchmarking, profiling, \textbf{Prometheus}, \textbf{Grafana} \\
                \textbf{DevOps \& Automation:} & Continuous integration, automated testing, provisioning tools integration, \textbf{Jira} \\
                \textbf{Cloud \& Infrastructure:} & Amazon Web Services (AWS), \textbf{EC2}, S3, monitoring large-scale infrastructure \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}