\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{ETL} pipelines in \textbf{Python} that increased data throughput by 40\% supporting analytics and machine learning workloads.}
        \resumeItem{Integrated new data sources using \textbf{Azure Synapse} and improved data ingestion latency by 35\% to enable real-time reporting.}
        \resumeItem{Collaborated with data scientists to deploy and monitor \textbf{ML models} in production using MLOps best practices, enhancing model reliability by 30\%.}
        \resumeItem{Implemented data quality checks and observability using \textbf{Azure Data Factory}, reducing pipeline failures by 50\% and improving data accuracy.}
        \resumeItem{Optimized data transformation workflows in \textbf{SQL} to reduce processing time by 25\%, improving overall system efficiency and scalability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built automated \textbf{Python} data pipelines handling 15,000+ daily records, reducing manual processing time by 75\% for analytics teams.}
        \resumeItem{Developed a self-service internal data mart in \textbf{PowerBI}, enabling stakeholders to generate 60\% more reports independently.}
        \resumeItem{Deployed \textbf{Azure Data Factory} workflows to orchestrate complex ETL tasks, increasing pipeline reliability by 40\%.}
        \resumeItem{Collaborated with marketing and finance to translate business needs into robust data models, improving reporting accuracy by 30\%.}
        \resumeItem{Implemented Git-based collaborative workflows and code reviews, enhancing code quality and team productivity by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based environments securing data access for lab analytics, improving system uptime by 20\%.}
        \resumeItem{Developed automated scripts to validate data integrity, reducing manual error checks by 30\% in cybersecurity courses.}
        \resumeItem{Guided students in data pipeline construction and debugging, enhancing successful project submissions by 25\%.}
        \resumeItem{Maintained secure, compliant data infrastructure for lab-based analytics supporting cybersecurity research and instruction.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, reducing data retrieval time by 20\% for key business reports.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, improving API data processing efficiency by 25\%.}
        \resumeItem{Implemented asynchronous data ingestion pipelines using \textbf{TypeScript}, accelerating data availability for analytics by 30\%.}
        \resumeItem{Upgraded frontend interfaces with \textbf{Angular.js}, enhancing user experience and increasing data visualization engagement by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{Java Spring Boot} microservices for data ingestion, sustaining 1000+ concurrent users with 200ms latency.}
        \resumeItem{Built and maintained \textbf{AWS}-deployed data ETL pipelines using \textbf{Docker}, improving service deployment speed by 45\%.}
        \resumeItem{Automated data validation and transformation processes, increasing data quality and reducing errors by 35\% across production workflows.}
        \resumeItem{Implemented unit testing with \textbf{JUnit}, achieving 90\% test coverage on critical data processing modules for reliability.}
        \resumeItem{Developed intuitive \textbf{React.js} dashboards to monitor data pipeline performance, reducing debugging time by 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cloud-Based Data Pipeline Automation System} | Python, Azure Data Factory, SQL, PowerBI}{}
          \resumeItemListStart
              \resumeItem{Built automated \textbf{ETL pipelines} in \textbf{Azure Data Factory} processing 100K+ records daily, reducing manual effort by 70\%.}
              \resumeItem{Developed robust \textbf{SQL} transformations and data quality checks, improving data accuracy across reports by 35\%.}
              \resumeItem{Created self-service \textbf{PowerBI} dashboards to enable business users to generate insights independently, enhancing reporting speed by 45\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Machine Learning Model Deployment Pipeline} | Python, MLOps, Azure Synapse, GitHub Actions}{}
          \resumeItemListStart
              \resumeItem{Implemented scalable model deployment workflows integrating \textbf{MLOps} practices, reducing model release cycle from weeks to days.}
              \resumeItem{Monitored and maintained ML model performance in production, automating alerts that detected drift within 24 hours.}
              \resumeItem{Integrated deployment pipelines with \textbf{Azure Synapse} to streamline data inputs and transformation supporting model inference.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, SQL, Java, JavaScript, PowerShell, TypeScript \\
                \textbf{Cloud \& Data Platforms:} & Azure Synapse, Azure Data Factory, AWS, Databricks, Snowflake \\
                \textbf{Data Engineering \& Orchestration:} & ETL/ELT Pipelines, Apache Airflow, Prefect, Azure Data Factory \\
                \textbf{Analytics \& BI Tools:} & PowerBI, Microsoft Fabric, Tableau \\
                \textbf{DevOps \& Collaboration:} & Git, GitHub, Jenkins, Agile workflows \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, Relational Databases \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}