\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered new data pipeline components in \textbf{Java Spring Boot} resulting in 30\% faster data ingestion and processing speeds.}
        \resumeItem{Enhanced data quality monitoring frameworks using \textbf{Spring Security} reducing data anomalies by 40\%.}
        \resumeItem{Automated integration tests with \textbf{Jenkins} and \textbf{Docker} reducing bugs in production by 25\%.}
        \resumeItem{Implemented microservices supporting large scale user analytics with \textbf{Java}, improving query throughput by 35\%.}
        \resumeItem{Collaborated with cross-functional teams to align product goals with evolving data infrastructure needs, boosting deployment success.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built automated \textbf{Python} data pipelines processing 10000+ records daily, cutting manual data handling time by 80\%.}
        \resumeItem{Architected analytics dashboards using \textbf{React} integrating SQL backend, increasing data-driven insights accessibility by 50\%.}
        \resumeItem{Developed AI-powered automation scripts leveraging \textbf{LLMs} to streamline data extraction workflows, enhancing accuracy by 40\%.}
        \resumeItem{Refined subscription platform features using \textbf{PHP} and \textbf{Stripe}, improving user retention by 20\%.}
        \resumeItem{Collaborated with product analysts to tailor data models, improving forecasting accuracy and user engagement tracking.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments ensuring 99.9\% uptime for cybersecurity lab infrastructure supporting 100+ students.}
        \resumeItem{Automated assignment grading scripts reducing manual task time by 25\% and improving scoring consistency for coding assignments.}
        \resumeItem{Assisted students with debugging and deploying network security tools, increasing lab success rates by 20\%.}
        \resumeItem{Delivered sessions on cryptography protocols and secure networking enhancing student comprehension and practical skills.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{PostgreSQL} queries reducing data retrieval latency by 15\%, improving application response times.}
        \resumeItem{Developed efficient backend services with \textbf{C\#} and \textbf{.NET}, decreasing API response time by 30\%.}
        \resumeItem{Implemented \textbf{TypeScript} APIs achieving average sub-100ms response times for enhanced user experience.}
        \resumeItem{Upgraded frontend \textbf{Angular.js} modules, increasing user engagement metrics by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices improving concurrent user handling to 1000+ and lowering latency under 200ms.}
        \resumeItem{Established CI/CD pipelines with \textbf{Docker} on \textbf{AWS EC2} for seamless deployment reducing downtime by 35\%.}
        \resumeItem{Created React.js frontend with improved data visualization, increasing user engagement by 30\%.}
        \resumeItem{Implemented unit and integration tests using \textbf{JUnit} achieving 90\% coverage and increasing code reliability.}
        \resumeItem{Collaborated with product teams to develop SDLC automation tools, enhancing development efficiency by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Data Pipeline Automation} | Python, SQL, AWS S3}
          {}
          \resumeItemListStart
              \resumeItem{Designed automated \textbf{Python} data pipelines integrating with \textbf{SQL} databases and \textbf{AWS S3}, cutting manual ETL efforts by 70\%.}
              \resumeItem{Implemented data quality checks reducing pipeline errors by 35\% and improving trusted analytics reporting.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{User Behavior Analytics Dashboard} | React, SQL, Python}
          {}
          \resumeItemListStart
              \resumeItem{Constructed an interactive dashboard using \textbf{React} with \textbf{SQL} backend and \textbf{Python} API, enhancing product user analytics visibility by 50\%.}
              \resumeItem{Collaborated with product managers to translate raw data into actionable insights improving user retention strategies.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, SQL, JavaScript, TypeScript, C\# \\
                \textbf{Data Engineering \& Databases:} & SQL databases, PostgreSQL, MySQL, MongoDB, Data pipelines, Data Modeling \\
                \textbf{Web Development \& Frameworks:} & React.js, Spring Boot, Angular.js, Laravel, .NET \\
                \textbf{Cloud Platforms \& Tools:} & AWS EC2, S3, Docker, Jenkins, CI/CD pipelines \\
                \textbf{Data Analysis \& Visualization:} & Python Data Analysis, Analytics Dashboards, Product Analytics \\
                \textbf{Collaboration \& Productivity:} & Git, GitHub, Jira, REST APIs \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}