\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Refactored \textbf{Java Spring Boot} microservices to increase system reliability, improving API response times by 35\%.}
        \resumeItem{Implemented role-based access control using \textbf{Spring Security}, decreasing unauthorized requests by 40\%.}
        \resumeItem{Developed an \textbf{AI-driven} code review assistant reducing manual review time by 45\% and increasing deployment velocity by 25\%.}
        \resumeItem{Automated \textbf{CI/CD} pipelines with \textbf{Jenkins} and \textbf{Docker}, cutting release cycle times by 40\%.}
        \resumeItem{Collaborated with security analysts to embed GRC features in key platform components, enhancing compliance adherence.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected a \textbf{SaaS} data visualization platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users efficiently.}
        \resumeItem{Automated data ingestion pipelines with \textbf{Python}, processing over 10,000 stock entries daily and reducing errors by 80\%.}
        \resumeItem{Built a multi-tier subscription platform using \textbf{PHP} and integrated \textbf{Stripe} with role-based access controls.}
        \resumeItem{Designed \textbf{AI agents} automating FINRA broker data download processes, reducing manual workload by 80\%.}
        \resumeItem{Developed an \textbf{AI-driven} LinkedIn outreach bot increasing qualified leads by 40\% via automated targeting and content posting.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based cybersecurity lab infrastructure, ensuring 99\% uptime and secure configurations.}
        \resumeItem{Assisted students in debugging and testing software modules, improving assignment pass rates by 20\%.}
        \resumeItem{Created automated grading scripts, reducing manual grading time by 30\% and increasing accuracy by 25\%.}
        \resumeItem{Conducted 15+ instructional sessions on Cryptography, Networking, and Web Security, enhancing student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API calls maintaining sub-100ms average response time for seamless data retrieval.}
        \resumeItem{Revamped platform with \textbf{Angular.js}, raising user engagement and satisfaction scores by 25\%.}
        \resumeItem{Created a backend service in \textbf{C\#} with \textbf{.NET}, reducing data processing latency by 30\%.}
        \resumeItem{Enhanced \textbf{PostgreSQL} procedures, decreasing frontend load by 15\% and improving database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL} to support 1000 concurrent users with <200ms latency.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines for seamless deployment on \textbf{AWS EC2} using \textbf{Docker}, improving delivery frequency.}
        \resumeItem{Developed project management UI components with \textbf{React.js}, increasing usability and speeding page loads by 30\%.}
        \resumeItem{Authored unit tests with \textbf{JUnit}, achieving 90\% code coverage for pipeline modules and improving stability.}
        \resumeItem{Collaborated on a SaaS tool automating SDLC processes, decreasing manual overhead by 50\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Governance and Compliance Automation Platform} | Python, Terraform, Rego, AWS}
          \resumeItemListStart
              \resumeItem{Developed automation tools enforcing security policies using \textbf{Rego} and \textbf{Terraform}, reducing compliance gaps by 35\%.}
              \resumeItem{Integrated \textbf{AWS} services with CI/CD workflows to monitor and report infrastructure compliance in real-time.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Security-focused CI/CD Pipeline Enhancements} | GitHub Actions, Jenkins, Docker, Python}
          \resumeItemListStart
              \resumeItem{Built automated code quality and security checks in \textbf{GitHub Actions} and \textbf{Jenkins}, reducing vulnerabilities by 40\%.}
              \resumeItem{Implemented containerized deployment pipelines using \textbf{Docker}, decreasing release times by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Python, Java, JavaScript, Rego, Terraform, TypeScript, C\#, PHP \\
                \textbf{Cloud \& DevOps Tools:} & AWS, Azure, Docker, Jenkins, GitHub Actions, Terraform, Ansible, CloudFormation \\
                \textbf{Frameworks \& Architectures:} & Spring Boot, React.js, Angular.js, Microservices, Distributed Systems \\
                \textbf{Databases \& Data Queues:} & MySQL, PostgreSQL, MongoDB, DynamoDB, Kafka, SQS, Kinesis \\
                \textbf{Security \& Compliance:} & SAST, DAST, SCA, PenTest, CVE, CWE, Threat Modeling, SOC, HIPAA, PCI Compliance \\
                \textbf{Monitoring \& Observability:} & OpenTelemetry, Splunk, CloudWatch, Dynatrace, DataDog \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}