\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable microservices using \textbf{Java Spring Boot}, increasing API throughput by 35\% and reliability under load.}
        \resumeItem{Implemented role-based access control via \textbf{Spring Security}, reducing security breaches by 40\%.}
        \resumeItem{Developed AI-powered code review assistant using \textbf{LLMs}, cutting manual reviews by 45\% and accelerating releases by 25\%.}
        \resumeItem{Automated \textbf{CI/CD} workflows with \textbf{Jenkins} and \textbf{Docker}, decreasing deployment times by 40\%.}
        \resumeItem{Collaborated on Kubernetes cluster performance optimizations, enhancing system stability and developer productivity.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed multi-cloud SaaS platform leveraging \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent AI-powered users.}
        \resumeItem{Automated stock data pipelines in \textbf{Python}, increasing processing efficiency by 80\%.}
        \resumeItem{Developed AI-driven agents with \textbf{LLMs} to automate data workflows, reducing manual processing time by 80\%.}
        \resumeItem{Enhanced \textbf{React} components to optimize load times by 25\%, boosting user engagement significantly.}
        \resumeItem{Implemented cloud cost monitoring and optimization strategies, cutting operational expenses by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} cybersecurity lab infrastructure, ensuring 99\% uptime and secure environment compliance.}
        \resumeItem{Guided students on debugging and deploying secure software, raising assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts in \textbf{Python}, reducing manual review time while improving accuracy by 25\%.}
        \resumeItem{Conducted technical sessions on Cryptography and Network Security, improving student knowledge retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency \textbf{TypeScript} APIs, achieving sub-100ms response times for high-demand applications.}
        \resumeItem{Revamped UI with \textbf{Angular.js}, boosting user engagement by 25\% and customer satisfaction levels.}
        \resumeItem{Built performant backend services in \textbf{C\#} and \textbf{.NET}, reducing data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, decreasing database load by 15\% and improving uptime.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{Java Spring Boot} microservices with \textbf{MySQL}, serving 1000+ concurrent users reliably.}
        \resumeItem{Automated containerized deployments on \textbf{AWS EC2} using \textbf{Docker}, accelerating delivery pipelines.}
        \resumeItem{Developed React-based project management UI, improving load times by 30\% and usability significantly.}
        \resumeItem{Implemented comprehensive unit tests with \textbf{JUnit}, achieving 90\% code coverage and higher quality releases.}
        \resumeItem{Led infrastructure improvements enabling scalable and secure web applications with cloud-native tools.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Kubernetes GPU Cluster Manager} $|$ Multi-Cloud, Kubernetes, Go, Python}{}
          \resumeItemListStart
              \resumeItem{Developed a multi-cloud \textbf{Kubernetes} GPU supercluster manager to orchestrate scalable AI workloads, increasing resource utilization efficiency by 30\%.}
              \resumeItem{Implemented monitoring dashboards enabling researchers to troubleshoot resource bottlenecks, reducing downtime by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI Researcher Self-Service Platform} $|$ Cloud Infrastructure, React, Python, GPU Workloads}{}
          \resumeItemListStart
              \resumeItem{Built self-service UI to facilitate AI model training and evaluation on GPU superclusters, accelerating experiment turnaround by 40\%.}
              \resumeItem{Optimized backend resource scheduling with cost-awareness, cutting cloud expenses by 20\% for AI workloads.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Go, Python, Java, JavaScript, TypeScript, C\#, Shell Scripting \\
                \textbf{Cloud \& Infrastructure:} & Kubernetes, AWS, Azure, Docker, Terraform, EC2, S3, Lambda \\
                \textbf{AI \& ML Infrastructure:} & GPU Workloads, RDMA Networking Awareness, CUDA Basics, ML Model Training Support \\
                \textbf{DevOps \& Automation:} & CI/CD (Jenkins, GitHub Actions), Infrastructure as Code, Monitoring, Logging, Alerting \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Laravel, Spring Boot, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}