\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented operating system components and services in \textbf{Java Spring Boot}, improving system stability by 30\%.}
        \resumeItem{Developed core distributed system features, enhancing throughput by 40\% through optimized inter-service communication.}
        \resumeItem{Automated deployment pipelines via \textbf{Jenkins} and \textbf{Docker}, boosting release efficiency and cutting delivery time by 35\%.}
        \resumeItem{Conducted performance analysis and debugging using \textbf{Linux} tools, reducing critical bugs by 25\% and improving uptime.}
        \resumeItem{Collaborated on scalable network distribution software, increasing user request handling capacity by 50\% with \textbf{Spring Security} enhancements.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Python}-based automation tools for large dataset processing, improving data pipeline speeds by 60\%.}
        \resumeItem{Developed backend services using \textbf{PHP} and \textbf{Laravel} with strong role-based access controls, reducing security breaches by 35\%.}
        \resumeItem{Improved frontend responsiveness by 25\% with advanced \textbf{React} state management and modular component design.}
        \resumeItem{Integrated \textbf{AI} agents to automate FINRA data extraction, decreasing manual data entry time by 75\%.}
        \resumeItem{Built and optimized RESTful APIs supporting SaaS applications, improving client-side load times by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab infrastructure, ensuring secure environment setups and reducing system downtime by 20\%.}
        \resumeItem{Assisted students with debugging and testing software modules, improving assignment completion rates by 18\%.}
        \resumeItem{Automated grading scripts with Python, increasing evaluation accuracy by 25\% and reducing manual effort.}
        \resumeItem{Conducted educational sessions on network protocols and security, enhancing student comprehension and lab performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed backend API features using \textbf{C\#} and \textbf{.NET}, decreasing data retrieval times by 30\%.}
        \resumeItem{Optimized frontend performance with \textbf{Angular.js}, improving user engagement by 25\%.}
        \resumeItem{Enhanced \textbf{PostgreSQL} queries and stored procedures to reduce database response latency by 15\%.}
        \resumeItem{Implemented asynchronous API calls with \textbf{TypeScript}, achieving sub-100ms response times.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed and deployed microservices in \textbf{Java Spring Boot} supporting 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Built web UIs in \textbf{React.js} to enhance user experience and reduce page load times by 30\%.}
        \resumeItem{Led creation of CI/CD pipelines with \textbf{Docker} and \textbf{AWS EC2}, ensuring 99.9\% deployment uptime.}
        \resumeItem{Authored unit tests covering 90\% of codebase using \textbf{JUnit}, improving system reliability and maintainability.}
        \resumeItem{Created tools automating SDLC processes, reducing manual tasks by 40\% and accelerating development cycles.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Distributed Operating System Simulator} | C++, Linux, Network Sockets}
          {}
          \resumeItemListStart
              \resumeItem{Designed a modular OS simulator to demonstrate process scheduling and memory management concepts in \textbf{C++}, improving learning outcomes by 30\%.}
              \resumeItem{Implemented IPC mechanisms using \textbf{Linux} sockets, achieving reliable communication with less than 5ms latency.}
              \resumeItem{Tested and debugged kernel-mode components, reducing system errors by 25\% and enhancing simulator stability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Compiler Frontend for Custom Language} | Python, Lex/Yacc, Linux}
          {}
          \resumeItemListStart
              \resumeItem{Built a compiler frontend using \textbf{Python} and \textbf{Lex/Yacc} to parse and generate intermediate code for custom language constructs.}
              \resumeItem{Optimized syntax analysis phases, reducing compile times by 35\% under typical workloads on \textbf{Linux} environment.}
              \resumeItem{Implemented semantic checks and error reporting, decreasing user debugging time by 20\% during development.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C, C++, C\#, Java, Python, JavaScript, PHP, SQL \\
                \textbf{Systems \& OS:} & Linux, UNIX, \textbf{nix} commands, File systems, Network sockets \\
                \textbf{Software Development:} & Code editors (VIM, Emacs), Git, Subversion, Jenkins, Docker, CI/CD \\
                \textbf{Web \& Frameworks:} & React.js, Angular.js, Spring Boot, Laravel, Node.js, .NET, HTML, CSS \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, SQL, DynamoDB \\
                \textbf{Networking \& Distributed Systems:} & REST API, gRPC, Network protocol design, Distributed computing principles \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}