\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered responsive UI components with \textbf{React} and \textbf{Node.js}, improving cross-device compatibility by 30\%.}
        \resumeItem{Refined API endpoints via \textbf{Spring Boot} enhancing application scalability and reducing data latency by 20\%.}
        \resumeItem{Collaborated on Agile teams to deliver features aligning with business goals, decreasing sprint cycle time by 15\%.}
        \resumeItem{Implemented unit and integration tests using \textbf{JUnit} and \textbf{Mockito}, raising code coverage to 90\%.}
        \resumeItem{Mentored team members on best practices for \textbf{React} and accessibility, boosting code quality and WCAG compliance by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed dynamic front-end pages with \textbf{React} and \textbf{Node.js}, reducing page load time by 25\% and enhancing UX.}
        \resumeItem{Defined and implemented user stories in an Agile environment, accelerating feature delivery by 30\%.}
        \resumeItem{Built and maintained RESTful APIs with \textbf{Laravel} for frontend-backend data sync, improving system reliability by 35\%.}
        \resumeItem{Improved accessibility by integrating WCAG standards leading to 40\% better usability for users with disabilities.}
        \resumeItem{Coordinated debugging and defect resolution in collaboration with QA reducing production bugs by 28\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported software deployment in \textbf{Linux} environments, increasing lab uptime and secure configurations by 15\%.}
        \resumeItem{Assisted students with debugging and testing networking software, improving assignment completion rates by 20\%.}
        \resumeItem{Automated validation scripts using \textbf{Python}, reducing manual grading errors by 25\%.}
        \resumeItem{Delivered 15+ workshops clarifying complex cybersecurity concepts, boosting student exam preparedness by 22\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} APIs with avg response time below 100ms, enhancing client-server interactions by 40\%.}
        \resumeItem{Revamped UI with \textbf{Angular.js}, raising user engagement scores by 25\% through improved responsiveness.}
        \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries cutting frontend loading delays by 15\%, improving overall app responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led \textbf{React.js} UI improvements increasing usability and load speed by 30\%, enhancing customer satisfaction rates.}
        \resumeItem{Developed \textbf{Spring Boot} microservices handling 1000+ concurrent users with sub-200ms response times efficiently.}
        \resumeItem{Automated deployment pipelines using \textbf{Docker} and \textbf{AWS EC2}, lowering deployment errors by 40\%.}
        \resumeItem{Wrote comprehensive unit tests using \textbf{JUnit}, achieving 90\% coverage and improving software reliability.}
        \resumeItem{Collaborated in Agile teams translating business requirements into robust and user-friendly applications.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Interactive UI Dashboard for Cross-Device Performance} | React.js, Node.js, WCAG}{}
          \resumeItemListStart
              \resumeItem{Built an accessible single-page application optimizing UI responsiveness for mobile and desktop, increasing user retention by 20\%.}
              \resumeItem{Implemented Agile refinements and unit tests boosting deployment frequency by 25\% while maintaining product quality.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Feature-Driven Web Application with Agile} | React.js, Node.js, Jest}{}
          \resumeItemListStart
              \resumeItem{Delivered modular web features with \textbf{React} & \textbf{Node.js}, enhancing system scalability and reducing bug reports by 30\%.}
              \resumeItem{Integrated WCAG accessibility standards and performed unit testing with \textbf{Jest}, improving compliance and reducing regressions.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, JavaScript, TypeScript, Python, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Node.js, Spring Boot, Angular.js, Laravel, .NET, HTML, CSS \\
                \textbf{Testing \& Debugging Tools:} & JUnit, Mockito, Jest, Debugging Techniques \\
                \textbf{Accessibility Standards:} & WCAG Implementation, Accessible Code Practices \\
                \textbf{DevOps \& Automation:} & Docker, Jenkins, AWS, Git, CI/CD Pipelines \\
                \textbf{Collaboration \& Methodologies:} & Agile, Scrum, Jira, Code Review, Unit Testing \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}