\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{microservices} with \textbf{Java Spring Boot}, boosting API throughput and reducing latency by 35\%.}
        \resumeItem{Enhanced security policies using \textbf{Spring Security}, lowering unauthorized access incidents by 40\%.}
        \resumeItem{Integrated \textbf{AI-driven} code review assistant, reducing manual PR reviews by 45\% and accelerating development cycle by 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, cutting deployment time by 40\%.}
        \resumeItem{Collaborated in cross-functional teams to troubleshoot and optimize backend infrastructure for higher reliability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{SaaS} visualization platform using \textbf{Laravel} and \textbf{React}, enabling seamless concurrent usage of 50+ users.}
        \resumeItem{Automated large-scale data processing pipelines in \textbf{Python}, decreasing manual effort by 80\%.}
        \resumeItem{Built a subscription platform with \textbf{PHP}, implementing role-based access and payment integration via \textbf{Stripe}.}
        \resumeItem{Deployed \textbf{AI-powered} agents with \textbf{LLMs} to automate broker data workflows, saving 80\% manual operations.}
        \resumeItem{Optimized \textbf{React} components, decreasing page load times by 25\% to enhance user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments for cybersecurity labs, ensuring dependable software testbeds.}
        \resumeItem{Guided students through debugging and testing processes, increasing assignment pass rates by 20\%.}
        \resumeItem{Developed automation scripts for grading and validation, reducing manual errors by 25\%.}
        \resumeItem{Led interactive sessions covering Cryptography, Networking, and Web Security topics to enhance student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented fast \textbf{TypeScript} API integrations, achieving sub-100ms response times for critical data calls.}
        \resumeItem{Refined \textbf{Angular.js} frontend workflows, raising user engagement metrics by 25\%.}
        \resumeItem{Built performant \textbf{C\# .NET} backend services, cutting data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, reducing frontend load times and streamlining data handling.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000+ users with optimized response times below 200ms.}
        \resumeItem{Streamlined \textbf{Docker}-based CI/CD pipelines deploying services on \textbf{AWS EC2}, enhancing release efficiency.}
        \resumeItem{Implemented robust management UI in \textbf{React.js}, increasing usability and speeding page loads by 30\%.}
        \resumeItem{Wrote unit tests using \textbf{JUnit}, achieving about 90\% coverage to ensure code quality.}
        \resumeItem{Collaborated with product teams to extend API functionality for third-party integration and enhanced monitoring.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Data Query Assistant} | Go, React, TypeScript, Grafana Plugin Development}{}
          \resumeItemListStart
              \resumeItem{Created an AI-enabled plugin for Grafana that enhances querying efficiency and visualization of diverse cloud data sources.}
              \resumeItem{Integrated APIs of Microsoft Azure and Clickhouse for seamless, real-time data retrieval in customized Grafana dashboards.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud Observability Dashboard} | Kubernetes, Docker, Go, React}{}
          \resumeItemListStart
              \resumeItem{Built a scalable observability platform using \textbf{Docker} and \textbf{Kubernetes} to unify metric, log, and trace visualization.}
              \resumeItem{Monitored microservices health via \textbf{Grafana} and \textbf{Prometheus}, improving issue response time by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Driven Open Source Plugin Maintainer Bot} | Go, Terraform, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI bot using \textbf{OpenAI API} to assist with configuration validation and issue detection in Terraform-managed plugins.}
              \resumeItem{Automated routine plugin maintenance tasks, reducing manual errors and increasing update frequency by 20\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Backend Technologies:} & Go, Java, Spring Boot, C\#, .NET, Python \\
                \textbf{Frontend Technologies:} & React, TypeScript, Angular.js \\
                \textbf{Cloud Platforms \& Infrastructure:} & Microsoft Azure, AWS, Docker, Kubernetes, Terraform \\
                \textbf{Data Storage \& Databases:} & MySQL, PostgreSQL, Clickhouse, MongoDB \\
                \textbf{Observability \& Monitoring:} & Grafana, Prometheus, Azure Monitor, Loki \\
                \textbf{DevOps \& Automation:} & CI/CD, Jenkins, GitHub Actions, Jsonnet, Linux/Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}