\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices for scalability, achieving 35\% faster API response and supported higher traffic loads.}
        \resumeItem{Implemented robust \textbf{Spring Security} for access control, reducing unauthorized attempts by 40\% across multiple services.}
        \resumeItem{Integrated an \textbf{AI-driven} code review assistant using \textbf{LLMs}, reducing manual code review effort by 45\% and speeding releases.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} pipelines, cutting build and deployment time by 40\%, improving delivery speed significantly.}
        \resumeItem{Collaborated on frontend-backend integration to improve API reliability by 30\%, enhancing overall system stability and user experience.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed scalable \textbf{React} frontend architecture, improving load times by 25\% and user engagement significantly.}
        \resumeItem{Automated daily processing of 10,000+ stock entries using \textbf{Python}, cutting manual effort by 80\% while ensuring accuracy.}
        \resumeItem{Implemented various AI agents based on \textbf{LLMs} for data automation, reducing manual data tasks by 80\% and improving efficiency.}
        \resumeItem{Developed subscription e-commerce platform with \textbf{PHP} and \textbf{Stripe}, enabling secure role-based access and multi-tier management.}
        \resumeItem{Refined frontend state management to enhance user interface responsiveness, reducing latency by 20\% and improving overall UX quality.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} infrastructure for cybersecurity labs, ensuring secure, stable environments for over 100 students and researchers.}
        \resumeItem{Developed automation scripts to grade assignments, improving grading efficiency and accuracy by 25\% across multiple courses.}
        \resumeItem{Provided technical support and troubleshooting training that enhanced student success rates by 20\% in software deployment and debugging.}
        \resumeItem{Conducted 15+ interactive sessions covering Cryptography, Networking Protocols, and Web Security, improving student understanding significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented responsive \textbf{TypeScript} API calls, achieving sub-100ms latency and ensuring seamless real-time user data exchange.}
        \resumeItem{Upgraded legacy platform using \textbf{Angular.js}, increasing user engagement by 25\% with enhanced UI features and workflows.}
        \resumeItem{Developed high-performance backend services in \textbf{C\# .NET}, improving data retrieval speed by 30\% and system reliability.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, reducing frontend data load by 15\% and improving responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Created scalable \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ users with sub-200ms latency.}
        \resumeItem{Led \textbf{CI/CD} pipeline implementation with \textbf{Docker} on \textbf{AWS EC2}, enabling automated, reliable deployment of 6 core microservices.}
        \resumeItem{Developed efficient project management UI in \textbf{React.js}, enhancing usability and decreasing page load times by 30\%.}
        \resumeItem{Implemented comprehensive \textbf{JUnit} tests covering 90\% API code, improving reliability and reducing bugs in production.}
        \resumeItem{Streamlined SDLC automation tools, reducing manual process time by 50\% to increase team productivity and deployment cadence.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Frontend Code Quality Analyzer} | GitHub Actions, OpenAI API, React.js}
          \resumeItemListStart
              \resumeItem{Built a \textbf{CI/CD} tool using \textbf{LLMs} to analyze pull requests and suggest frontend improvements, accelerating review process by 30\%.}
              \resumeItem{Automated documentation generation for React components, ensuring consistent code quality and reducing manual documentation by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Dynamic AWS Cost Optimization Dashboard} | AWS, React, Python, FastAPI, SQL}
          \resumeItemListStart
              \resumeItem{Developed an interactive dashboard using \textbf{React} and \textbf{FastAPI} to visualize AWS billing data, reducing cost waste by 50\%.}
              \resumeItem{Integrated real-time AWS cost data with backend \textbf{Python} services and \textbf{SQL} database, enabling predictive cost alerts and budgeting.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Cloud Infrastructure Monitor} | Kubernetes, Docker, Python, Flask}
          \resumeItemListStart
              \resumeItem{Designed a containerized monitoring system using \textbf{Kubernetes} and \textbf{Docker}, improving cloud infrastructure detection accuracy by 35\%.}
              \resumeItem{Implemented API endpoints in \textbf{Flask} to provide real-time status updates and automate issue alerts, reducing downtime by 20\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, Python, Java, C\#, PHP, Go \\
                \textbf{Frontend Frameworks:} & React.js, Next.js, Angular.js, Laravel \\
                \textbf{Backend Frameworks:} & Spring Boot, FastAPI, Flask, Django, .NET \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Kubernetes, Jenkins, CI/CD Pipelines \\
                \textbf{Databases:} & SQL, MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Tools \& Technologies:} & Git, REST APIs, GraphQL, Linux/Unix, AI/LLM Integration, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}