\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Refactored and enhanced \textbf{JavaScript} UI components, increasing modularity and maintainability by 40\% for large-scale applications.}
        \resumeItem{Designed and integrated RESTful \textbf{APIs} with backend services, improving data exchange efficiency and reducing latency by 30\%.}
        \resumeItem{Developed reusable web application modules with \textbf{React} and \textbf{TypeScript}, decreasing development times for new features by 25\%.}
        \resumeItem{Led cross-team code reviews and feedback sessions, raising overall code quality and reducing defect rates by 20\%.}
        \resumeItem{Contributed to agile ceremonies to ensure sprint goals were met, increasing team velocity by 15\% over two quarters.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented interactive \textbf{Vue.js} web interfaces using \textbf{HTML5} and \textbf{CSS3}, boosting user engagement metrics by 30\%.}
        \resumeItem{Developed AJAX-powered rich client features, enabling dynamic data loading with faster response times by 35\%.}
        \resumeItem{Optimized web applications to support cross-browser compatibility, reducing UI bugs by 25\% across Chrome, Firefox, and Safari.}
        \resumeItem{Automated testing suites for frontend components with Jest, increasing test coverage from 40\% to 85\%.}
        \resumeItem{Collaborated on designing REST APIs to enhance GIS data integration and front-end consumption using \textbf{JSON} protocols.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure development and testing of \textbf{JavaScript}-based lab modules, improving student project outcomes by 20\%.}
        \resumeItem{Assisted in debugging front-end issues and taught best practices for asynchronous programming with \textbf{AJAX} and \textbf{JSON}.}
        \resumeItem{Automated lab setup scripts to provision and validate \textbf{RESTful API} environments, reducing prep time by 30\%.}
        \resumeItem{Conducted workshops on web security focusing on cross-site scripting and DOM manipulation vulnerabilities.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed client-side features in \textbf{TypeScript} using \textbf{Angular.js}, increasing user interface responsiveness by 25\%.}
        \resumeItem{Integrated RESTful services with frontend modules, improving data retrieval efficiency by 20\% during peak usage.}
        \resumeItem{Implemented CSS optimizations and DOM updates to enhance cross-browser compatibility and reduce layout shifts by 30\%.}
        \resumeItem{Documented API interactions and technical design details, ensuring clear knowledge transfer and maintainability.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed reusable UI components with \textbf{React} and \textbf{TypeScript} for a microservices SaaS platform, improving code reusability by 35\%.}
        \resumeItem{Engineered RESTful \textbf{APIs} for GIS integration in \textbf{Spring Boot}, reducing average response times by 25\%.}
        \resumeItem{Implemented continuous integration and deployment pipelines using \textbf{Docker} and \textbf{AWS EC2} for rapid microservices delivery.}
        \resumeItem{Enhanced web application performance by optimizing \textbf{CSS} and JavaScript bundles, decreasing load times by 40\%.}
        \resumeItem{Produced comprehensive technical documentation and unit tests using \textbf{JUnit}, increasing test coverage to 90\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Assistant} | GitHub Actions, OpenAI API, TypeScript}
          {}
          \resumeItemListStart
              \resumeItem{Developed an \textbf{AI}-integrated code review tool for \textbf{JavaScript} projects, reducing manual review effort by 35\% and speeding delivery cycles.}
              \resumeItem{Automated generation of detailed \textbf{JavaScript} docstrings and coding standards enforcement, improving documentation quality by 100\%.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Interactive GIS Map Viewer} | React, ArcGIS API for JavaScript, CSS}
          {}
          \resumeItemListStart
              \resumeItem{Engineered a rich interactive web map viewer using \textbf{ArcGIS JavaScript API}, improving map rendering speed and user interaction by 40\%.}
              \resumeItem{Designed reusable UI modules for spatial data visualization, supporting seamless GIS integration across devices and browsers.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{RESTful Web Services for GIS Data} | Spring Boot, JSON, REST API}
          {}
          \resumeItemListStart
              \resumeItem{Built scalable REST \textbf{APIs} to expose GIS data and analytics, reducing average query time by 30\% for client applications.}
              \resumeItem{Ensured robust API security and role-based access control, decreasing unauthorized access incidents by 50\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Vue.js, ArcGIS API for JavaScript, HTML5, CSS3 \\
                \textbf{REST \& Data Formats:} & REST API, AJAX, JSON, XML \\
                \textbf{Version Control \& CI/CD:} & Git, GitHub Actions, Jenkins, Docker \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3), Docker, Linux \\
                \textbf{Testing \& Tools:} & Jest, JUnit, Agile Methodologies, Code Reviews \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}