\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Maintained and enhanced \textbf{Java} microservices improving API response times by 35\% while supporting remote engine features.}
        \resumeItem{Managed lifecycle of assets, implementing indexing and exporting features using \textbf{C++} and \textbf{Shell} scripts to optimize data workflows.}
        \resumeItem{Configured \textbf{Docker} containers orchestrated by \textbf{Kubernetes} improving deployment efficiency and reducing errors by 30\%.}
        \resumeItem{Architected cloud integrations on \textbf{AWS} and \textbf{Microsoft Azure} to ensure compatibility across storage platforms, boosting reliability by 20\%.}
        \resumeItem{Collaborated with cross-functional teams using \textbf{Git} and \textbf{Jenkins} to deliver timely software updates and streamline CI/CD pipelines.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed data browsing features in \textbf{Java} and \textbf{C++} to preview multiple file formats, increasing user efficiency by 40\%.}
        \resumeItem{Implemented resource broker components on \textbf{RedHat OpenShift} and \textbf{Docker}, supporting high availability for data integration products.}
        \resumeItem{Enhanced test framework compatibility on cloud storage platforms using \textbf{Azure} and \textbf{GCS}, improving automated test pass rates by 35\%.}
        \resumeItem{Designed and optimized message queues using \textbf{RabbitMQ} to reduce data processing latency by 25\%.}
        \resumeItem{Led database performance tuning using \textbf{PostgreSQL} and \textbf{MySQL}, improving query response times and system stability by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based environments supporting software testing, improving lab uptime and secure access by 15\%.}
        \resumeItem{Created scripts in \textbf{Shell} and \textbf{Python} to automate asset indexing and management, reducing manual work by 20\%.}
        \resumeItem{Assisted in research for data migration techniques compatible with \textbf{cloud} and on-premises systems, enhancing data handling processes.}
        \resumeItem{Supported virtualization and container orchestration tools including \textbf{Docker} and \textbf{Kubernetes} to streamline lab infrastructure deployment.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized API endpoints using \textbf{TypeScript} and \textbf{PostgreSQL}, reducing response latency by 20\% for data services.}
        \resumeItem{Refined \textbf{C++} modules for data ingestion and file processing, increasing throughput by 25\%.}
        \resumeItem{Developed containerized environments using \textbf{Docker} with orchestration on \textbf{Kubernetes}, improving deployment speed by 30\%.}
        \resumeItem{Automated data asset lifecycle tasks including import/export via \textbf{Shell} scripting, reducing errors by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Implemented microservice components in \textbf{Java} and \textbf{C++}, supporting asset lifecycle and remote engine features for enterprise solutions.}
        \resumeItem{Built and maintained containerized deployments using \textbf{Docker} and \textbf{RedHat OpenShift}, improving orchestration efficiency by 35\%.}
        \resumeItem{Developed scalable message brokering using \textbf{RabbitMQ} to support asynchronous workflows, reducing overall system latency by 25\%.}
        \resumeItem{Integrated multiple database systems including \textbf{MySQL} and \textbf{PostgreSQL} to manage schema and data transactions efficiently.}
        \resumeItem{Contributed to runtime and migration components ensuring seamless cloud compatibility with \textbf{Hadoop} and \textbf{HBase} storage layers.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Data Integration Quality Checker} | Java, Kubernetes, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed a cloud-based \textbf{Java} service to automate ruleset validation improving data quality by 30\% and reducing manual errors.}
              \resumeItem{Implemented scalable workflows using \textbf{Kubernetes} and \textbf{AWS} to support remote engine feature testing, reducing processing time 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud Asset Lifecycle Manager} | C++, Docker, Azure, Shell}{}
          \resumeItemListStart
              \resumeItem{Engineered asset lifecycle tooling with \textbf{C++} and \textbf{Shell} scripts managing creation, indexing, and export on \textbf{Azure} cloud, lowering asset errors by 40\%.}
              \resumeItem{Containerized services using \textbf{Docker}, achieving seamless deployments and reducing environment inconsistencies across development and production.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Data Format Browser} | RabbitMQ, Java, PostgreSQL, AI Models}{}
          \resumeItemListStart
              \resumeItem{Built an interactive data browsing tool using \textbf{Java} and \textbf{RabbitMQ} supporting multiple file formats, improving data preview efficiency by 35\%.}
              \resumeItem{Integrated AI components for intelligent data schema recognition, boosting user productivity by 20\% in complex data environments.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, C++, Shell Scripting, Python, TypeScript, SQL \\
                \textbf{Cloud \& Containerization:} & AWS, Microsoft Azure, RedHat OpenShift, Docker, Kubernetes \\
                \textbf{Messaging \& Workflow:} & RabbitMQ, Jenkins, CI/CD Pipelines \\
                \textbf{Databases \& Storage:} & PostgreSQL, MySQL, Hadoop, HBase, Cloud Object Storage \\
                \textbf{DevOps \& Tools:} & Git, Linux/Unix, Jenkins, REST APIs, Microservices \\
                \textbf{AI \& Automation:} & AI Models Integration, Automated Data Validation, Intelligent Data Browsing \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}