\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected \textbf{Java Spring Boot} microservices, enhancing system scalability and improving API throughput by 35\%.}
        \resumeItem{Implemented \textbf{Spring Security} solutions to upgrade authentication processes, cutting unauthorized access attempts 40\%.}
        \resumeItem{Developed AI-assisted code review tool, cutting manual review time by 45\% while boosting pull request quality.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, decreasing release cycle times by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to integrate new microservices maintaining 99.9\% uptime and fault tolerance.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and built a SaaS platform using \textbf{Laravel} and \textbf{React} supporting 50+ concurrent users with 99.7\% reliability.}
        \resumeItem{Automated daily data pipelines in \textbf{Python} that processed over 10,000 stock entries, improving accuracy and reducing manual effort.}
        \resumeItem{Created robust multi-tier subscription platform integrating \textbf{Stripe} and role-based access control to secure transactions.}
        \resumeItem{Developed AI agents using \textbf{LLMs} that streamlined regulatory data downloads, lowering manual work by 80\%.}
        \resumeItem{Enhanced \textbf{React} frontend components, cutting load times 25\% and improving user engagement and interaction rates.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux}-based systems ensuring secure, reliable environments for cybersecurity coursework and practical labs.}
        \resumeItem{Assisted students with debugging \textbf{Java} and scripting issues, increasing assignment success rates by 20\%.}
        \resumeItem{Automated grading and validation processes, reducing manual review time and improving scoring accuracy by 25\%.}
        \resumeItem{Conducted interactive sessions covering cryptography, networking protocols, and web security, improving student understanding significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented low-latency API calls in \textbf{TypeScript}, maintaining average response times below 100ms for smooth UX.}
        \resumeItem{Enhanced platform using \textbf{Angular.js}, increasing user engagement metrics by 25\% through improved UI responsiveness.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET} reducing data retrieval latency by 30\% for key features.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, lowering frontend load by 15\% and improving database transaction efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Delivered microservices using \textbf{Java} and \textbf{Spring Boot} that supported 1000 concurrent users with response times under 200ms.}
        \resumeItem{Developed and maintained \textbf{AWS EC2}-deployed containerized microservices using \textbf{Docker} for efficient cloud scalability.}
        \resumeItem{Led CI/CD pipeline implementation automating deployments to \textbf{AWS}, reducing integration time by 50\%.}
        \resumeItem{Created React.js frontend interfaces improving usability and page load speed by 30\% for project management tools.}
        \resumeItem{Implemented comprehensive unit tests using \textbf{JUnit} to maintain 90\% code coverage and ensure product stability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Assisted Code Review Bot} | GitHub Actions, OpenAI API, CI/CD}
          {}
          \resumeItemListStart
              \resumeItem{Created an AI-powered \textbf{GitHub} bot that analyzes pull requests for bugs and style issues, cutting review time by 25\%.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Scalable Face Recognition Service} | AWS EC2, SQS, S3, Python, Flask}
          {}
          \resumeItemListStart
              \resumeItem{Developed scalable face recognition service using \textbf{SQS} queues with custom auto-scaling to handle 1000 requests per minute.}
              \resumeItem{Leveraged \textbf{S3} for persistent storage and efficient image data retrieval to ensure fast processing times under load.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Cloud-Native Geospatial Web Service} | Java, Spring Boot, Kubernetes, Docker}
          {}
          \resumeItemListStart
              \resumeItem{Built a fault-tolerant geospatial data API with \textbf{Java Spring Boot} and containerized services orchestrated via \textbf{Kubernetes}.}
              \resumeItem{Implemented JSON/XML data support and optimized concurrent workload management enabling 99.9\% uptime on cloud infrastructure.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, TypeScript, C\#, PHP, JavaScript, Shell Scripting \\
                \textbf{Frameworks \& Technologies:} & Spring Boot, React.js, Angular.js, Laravel, Docker, Kubernetes, Maven, ANT \\
                \textbf{Cloud Platforms \& Tools:} & AWS (EC2, S3, SQS), Azure, Jenkins, Git, GitHub, Jenkins CI/CD \\
                \textbf{Databases:} & MySQL, PostgreSQL, SQL Server, Oracle, DB2 \\
                \textbf{Web Development Technologies:} & JavaEE (Servlets, JSP), REST APIs, JSON, XML, HTTP Monitoring (Fiddler) \\
                \textbf{Operating Systems \& Debugging:} & Linux/Unix, Eclipse/IntelliJ Debugger, JProfiler, jmap \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}