\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered and optimized scalable data pipelines using \textbf{Python} and \textbf{SQL} to improve data processing efficiency by 30\%.}
        \resumeItem{Collaborated with cross-functional teams to design metrics dashboards that increased decision-making speed by 25\%.}
        \resumeItem{Developed and maintained robust ETL workflows ensuring reliable data flow and 99.9\% data accuracy across platforms.}
        \resumeItem{Implemented data validation controls that reduced errors in critical reports by 40\%, enhancing business reliability.}
        \resumeItem{Communicated technical results and insights clearly to stakeholders, facilitating timely business strategy adaptations.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Automated daily data aggregation from 10,000+ sources using \textbf{Python}, saving 80\% of manual data processing effort.}
        \resumeItem{Created interactive dashboards with \textbf{React} and \textbf{SQL} that delivered actionable insights, boosting user engagement by 20\%.}
        \resumeItem{Built predictive data models using statistical methods to forecast customer churn, improving retention strategies by 15\%.}
        \resumeItem{Collaborated with data science and product teams to translate complex business needs into solvable data problems.}
        \resumeItem{Developed and deployed analytics solutions integrating \textbf{Stripe} payment data to track revenue growth and anomalies.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Automated grading pipelines using \textbf{Python} scripts that increased accuracy of software assessment outcomes by 25\%.}
        \resumeItem{Maintained Linux infrastructure supporting cybersecurity labs to ensure secure, stable environments with 99\% uptime.}
        \resumeItem{Optimized lab data collection processes to enable rapid analysis and feedback, reducing turnaround times by 20\%.}
        \resumeItem{Instructed students on data analysis and debugging procedures, enhancing their technical skills and lab success rates.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Improved API data retrieval performance by 30\% using optimized \textbf{TypeScript} and \textbf{PostgreSQL} stored procedures.}
        \resumeItem{Developed dashboard interfaces with \textbf{Angular.js} to visualize real-time analytics, increasing operational efficiency by 20\%.}
        \resumeItem{Implemented scalable backend microservices in \textbf{C\#} and \textbf{.NET} to handle high-throughput data workflows.}
        \resumeItem{Collaborated in cross-team code reviews and testing, improving code quality and reducing bugs by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and built highly performant \textbf{Java Spring Boot} microservices handling 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Developed and maintained robust \textbf{SQL} data pipelines to support data analytics, reducing load times by 35\%.}
        \resumeItem{Implemented continuous integration pipelines with \textbf{Docker} and \textbf{AWS EC2}, decreasing deployment times by 40\%.}
        \resumeItem{Collaborated on frontend \textbf{React.js} development for analytics dashboards boosting data accessibility and user experience.}
        \resumeItem{Authored unit and integration tests achieving 90\% coverage, enhancing system reliability and maintainability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Data Quality Monitoring System} | Python, SQL, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-based system to automatically detect anomalies in data pipelines, reducing error rates by 35\%.}
              \resumeItem{Integrated data quality alerts with dashboards providing real-time insights and enabling prompt corrective actions.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Customer Behavior Analytics Dashboard} | React, SQL, Python}{}
          \resumeItemListStart
              \resumeItem{Built a comprehensive dashboard tracking key metrics and customer behaviors, increasing data-driven decisions by 40\%.}
              \resumeItem{Implemented predictive analytics models to identify growth opportunities, raising forecast accuracy by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated AI Insights Bot for Business Reporting} | OpenAI API, Python, GitHub Actions}{}
          \resumeItemListStart
              \resumeItem{Engineered an AI agent using \textbf{OpenAI API} to generate natural language summaries of key business metrics daily.}
              \resumeItem{Reduced manual report generation time by 50\%, increasing efficiency and reliability of business insights delivery.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.34\linewidth} p{0.66\linewidth}}
                \textbf{Programming \& Scripting:} & Python, SQL, Java, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Data Technologies \& Frameworks:} & Hadoop, Spark, PostgreSQL, MySQL, MongoDB, DynamoDB, ETL Pipelines \\
                \textbf{Data Visualization \& BI Tools:} & React.js, Angular.js, Dashboards, Data Storytelling \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Statistical \& Analytical Skills:} & Statistical Modeling, Predictive Analytics, Data Mining \\
                \textbf{AI \& Automation Tools:} & OpenAI API, LLM Integration, AI Agents, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}