\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Administered and maintained Windows Server environments to enhance operational efficiency by 30\% through proactive system health monitoring.}
        \resumeItem{Configured and managed Active Directory, DNS, and DHCP, improving user access management and reducing service downtime by 25\%.}
        \resumeItem{Implemented group policies and role-based access control, reducing unauthorized access incidents by 45\% over 12 months.}
        \resumeItem{Automated server patch management and updates using scripts, increasing update compliance rate to 98\% across all servers.}
        \resumeItem{Supported cybersecurity initiatives by integrating McAfee ePolicy Orchestrator and firewall configurations, enhancing system threat detection by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed secure VPN and Remote Desktop solutions, improving remote work connectivity by 40\% for over 50 users.}
        \resumeItem{Implemented backup and recovery plans, decreasing critical data loss risks by testing and validating procedures monthly.}
        \resumeItem{Managed virtual machine infrastructure, scaling resources dynamically to support fluctuating workloads with 99.9\% uptime.}
        \resumeItem{Monitored and analyzed server logs with Splunk to proactively identify and resolve potential security breaches, reducing incidents by 30\%.}
        \resumeItem{Collaborated on hybrid cloud solutions, synchronizing on-premises Active Directory with Azure AD, improving user provisioning times by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported Windows Server labs including firewall and network service setup, increasing lab availability for 100+ students by 15\%.}
        \resumeItem{Developed technical documents and user guides for cybersecurity tools, improving student comprehension and usage accuracy by 25\%.}
        \resumeItem{Conducted security audits and vulnerability assessments, recommending fixes that reduced security gaps by 30\% in lab environments.}
        \resumeItem{Assisted in troubleshooting Windows Server and hardware issues, improving lab server uptime by 20\% during semester periods.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Maintained Windows Server-based backend infrastructure, reducing server errors by 15\% through configuration optimization and patching.}
        \resumeItem{Investigated and resolved network and server hardware issues, accelerating problem resolution times by 25\% for production systems.}
        \resumeItem{Assisted in managing Dell Server hardware configurations and diagnosing failures, decreasing server downtime by 20\%.}
        \resumeItem{Collaborated on security enhancements using Palo Alto firewall configurations, improving secure access compliance by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Administered Windows Server environments hosting microservices, improving deployment success rate by 35\% and response times by 20\%.}
        \resumeItem{Implemented security best practices including patching and monitoring with McAfee ePolicy Orchestrator, cutting threats by 40\%.}
        \resumeItem{Managed server storage solutions (RAID, Storage Spaces), increasing data reliability and throughput for critical applications by 25\%.}
        \resumeItem{Created and maintained comprehensive server documentation and user guides, reducing onboarding time for new administrators by 30\%.}
        \resumeItem{Automated routine administrative tasks using PowerShell scripts, boosting operational efficiency by 35\% across server management workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Windows Server Security Auditor} | Python, PowerShell, AI Algorithms}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-based auditing tool that analyzes Windows Server logs for vulnerabilities, reducing manual audit time by 50\%.}
              \resumeItem{Integrated automated reporting and alerting features, improving incident response speed by 35\% for server security teams.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Hybrid Active Directory Synchronization Tool} | C\#, Azure AD, PowerShell Scripts}{}
          \resumeItemListStart
              \resumeItem{Engineered a synchronization service for on-premises and Azure Active Directory, reducing user provisioning delays by 40\%.}
              \resumeItem{Implemented role-based access controls and audit logging, enhancing compliance adherence by 30\% in hybrid environments.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated AI Incident Response Assistant} | LLMs, Splunk API, Python}{}
          \resumeItemListStart
              \resumeItem{Created an AI assistant using LLMs for automated incident triage and recommendations, improving security team efficiency by 25\%.}
              \resumeItem{Integrated with Splunk and McAfee ePolicy Orchestrator to streamline analysis and resolution workflows, reducing response times by 30\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Operating Systems \& Servers:} & Windows Server, Active Directory, DNS, DHCP, Azure AD, Dell Server Hardware \\
                \textbf{Security \& Monitoring:} & McAfee ePolicy Orchestrator, Splunk, Palo Alto Firewalls, Role-Based Access Control, IT Security Best Practices \\
                \textbf{Programming \& Scripting:} & PowerShell, Python, C\#, Java, Bash \\
                \textbf{Virtualization \& Cloud:} & VMware, Hyper-V, Azure, AWS EC2, Storage Spaces, RAID \\
                \textbf{Networking \& VPN:} & VPN, Remote Desktop Protocol, Network Services Management \\
                \textbf{Tools \& Automation:} & Jenkins, Docker, Git, CI/CD, Automated Backup Solutions, System Documentation \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}