\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Okta} integrations to enhance identity workflows, improving system security and reducing unauthorized access by 35\%.}
        \resumeItem{Implemented role-based access controls using \textbf{Spring Security}, decreasing security incidents by 40\% through tighter authorization policies.}
        \resumeItem{Automated \textbf{Java Spring Boot} microservice deployments with \textbf{Jenkins} and \textbf{Docker}, accelerating delivery pipelines by 40\%.}
        \resumeItem{Enhanced multi-factor authentication by integrating \textbf{MFA} solutions, improving login security for 1000+ users.}
        \resumeItem{Collaborated on \textbf{IAM} policy design aligning with compliance standards, reducing audit findings and access violations by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{SaaS} platform with \textbf{Laravel} and \textbf{React}, supporting secure user authentication with \textbf{Okta} SSO.}
        \resumeItem{Automated data processes using \textbf{Python}, reducing manual data entry efforts by 80\% and strengthening access auditing.}
        \resumeItem{Implemented \textbf{Single Sign-On (SSO)} and \textbf{MFA} integrations, enhancing security across \textbf{AWS} and \textbf{Azure} platforms.}
        \resumeItem{Developed an \textbf{AI-driven} LinkedIn outreach bot to automate and secure user access, increasing qualified leads by 40\%.}
        \resumeItem{Optimized front-end components with \textbf{React}, boosting user engagement by 25\% through faster load and secure session handling.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} cybersecurity labs, ensuring secure configurations and seamless \textbf{IAM} integration for student projects.}
        \resumeItem{Automated grading scripts for security assignments, improving accuracy and reducing manual review workload by 25\%.}
        \resumeItem{Provided training on identity and access concepts, improving student proficiency in \textbf{MFA} and \textbf{SSO} implementations.}
        \resumeItem{Conducted system audits aligning with \textbf{HIPAA} and \textbf{GDPR} compliance requirements, minimizing security risks.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed secure \textbf{TypeScript} APIs supporting \textbf{SSO} and access token validation with sub-100ms response times.}
        \resumeItem{Enhanced legacy system with \textbf{Angular.js} to incorporate \textbf{MFA} flows, improving user authentication security by 30\%.}
        \resumeItem{Optimized backend \textbf{C\# .NET} services to manage identity data and reduce latency by 30\%.}
        \resumeItem{Refined \textbf{PostgreSQL} queries securing sensitive access logs and cutting database load by 15\% for compliance.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and integrated \textbf{Microsoft Identity Manager} (MIM) components to automate enterprise user provisioning.}
        \resumeItem{Developed \textbf{microservices} in \textbf{Java Spring Boot} managing identity synchronization with under 200ms response time.}
        \resumeItem{Created \textbf{CI/CD} pipelines using \textbf{Docker} on \textbf{AWS EC2}, accelerating IAM service deployments by 50\%.}
        \resumeItem{Built a \textbf{React.js} UI for identity lifecycle management, improving usability and reducing errors by 30\%.}
        \resumeItem{Conducted unit testing with \textbf{JUnit}, ensuring 90\% coverage on identity-related modules improving system reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Identity Access Monitoring Tool} | Python, AWS Lambda, Okta API}
          \resumeItemListStart
              \resumeItem{Engineered an AI system to analyze \textbf{Okta} access logs, detecting anomalies and reducing security breaches by 40\%.}
              \resumeItem{Implemented automated alerts and reporting, enhancing compliance with \textbf{HIPAA} and \textbf{GDPR} regulations.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Multi-Factor Authentication Integration} | Spring Boot, Microsoft Identity Manager}
          \resumeItemListStart
              \resumeItem{Developed robust \textbf{MFA} workflows integrated with \textbf{Microsoft Identity Manager}, improving login security for 1000+ users.}
              \resumeItem{Reduced unauthorized access incidents by 35\% through enhanced authentication mechanisms and seamless user experience.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated IAM Policy Compliance Auditor} | Python, OpenAI API, Azure}
          \resumeItemListStart
              \resumeItem{Built an AI-powered tool to audit IAM policies, ensuring adherence to industry standards and reducing audit times by 50\%.}
              \resumeItem{Automated compliance report generation leveraging \textbf{LLMs}, improving accuracy and reducing manual effort by 60\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Identity \& Access Management:} & Okta, Microsoft Identity Manager (MIM), IBM Tivoli, RSA SecurID, SailPoint, Oracle Identity Manager, SimpliGov \\
                \textbf{Cloud Platforms \& Integration:} & AWS, Azure, Office 365, EC2, S3, Lambda \\
                \textbf{Programming \& Scripting:} & Java, Python, Shell Scripting, TypeScript, C\#, PHP, Go \\
                \textbf{Security \& Compliance:} & SSO, MFA, HIPAA, GDPR, SOX, IAM policy enforcement \\
                \textbf{Web \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{DevOps \& Automation:} & Jenkins, Docker, Git, CI/CD, JUnit, Automation Scripting \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}