\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Android} features using \textbf{Kotlin} designed for enhanced user experience, improving app engagement by 30\%.}
        \resumeItem{Collaborated with cross-functional teams to integrate \textbf{RESTful APIs} and support dynamic content, reducing load times by 20\%.}
        \resumeItem{Implemented unit and integration tests using \textbf{JUnit} and \textbf{Espresso}, increasing test coverage by 45\% and reducing bugs in production.}
        \resumeItem{Participated in \textbf{code reviews} and agile ceremonies, fostering knowledge sharing and reducing bugs by 25\% in sprint releases.}
        \resumeItem{Refined UI components following \textbf{Android Jetpack} and \textbf{Compose} practices, enhancing accessibility compliance and overall app responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Android} app modules utilizing \textbf{Java} and \textbf{Kotlin}, improving app stability and feature modularity by 40\%.}
        \resumeItem{Implemented \textbf{ViewModels} and \textbf{Fragments} to manage UI state effectively, leading to 25\% reduced crashes and smoother navigation.}
        \resumeItem{Integrated \textbf{Retrofit} for efficient \textbf{REST API} consumption, decreasing network call failures by 30\%.}
        \resumeItem{Collaborated with designers to create responsive layouts following \textbf{material design} guidelines, increasing user satisfaction ratings by 15\%.}
        \resumeItem{Monitored app performance and optimized background tasks, reducing battery consumption by 20\% on Android devices.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure lab environments and configured \textbf{Linux} servers supporting student \textbf{Android SDK} development projects.}
        \resumeItem{Assisted students in debugging Android apps and interpreting \textbf{JSON} responses, improving their assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts for mobile app code including \textbf{JUnit} tests, reducing manual review time by 30\%.}
        \resumeItem{Conducted interactive tutorials on secure mobile coding practices and \textbf{Android} UI/UX basics to enhance learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed responsive UI features using \textbf{Angular.js}, improving front-end performance by 25\% and user engagement.}
        \resumeItem{Implemented backend services in \textbf{C\#} supporting mobile API endpoints with sub-100ms latency.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries to enhance data fetching speed by 15\%, improving app responsiveness and reducing load times.}
        \resumeItem{Collaborated on code reviews and bug fixes in \textbf{TypeScript}, increasing code quality and maintainability.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed microservices in \textbf{Java Spring Boot} with \textbf{MySQL}, supporting 1000+ concurrent users and reducing latency below 200ms.}
        \resumeItem{Developed frontend UI in \textbf{React.js} adhering to Android design principles, raising usability scores by 30\%.}
        \resumeItem{Implemented \textbf{JUnit} unit tests covering 90\% code to ensure reliable Android API integrations and reduce regressions.}
        \resumeItem{Automated Docker-based deployment pipelines on \textbf{AWS EC2}, reducing release downtime by 35\%.}
        \resumeItem{Participated in agile innovation sessions focused on improving Android SDK integration and app security practices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Android Code Review Assistant} | GitHub Actions, OpenAI API, Kotlin}
          \resumeItemListStart
              \resumeItem{Built an AI tool that analyzes \textbf{Kotlin} Android PRs to detect bugs and suggest improvements, reducing review times by 30\%.}
              \resumeItem{Automated documentation generation for Android APIs using \textbf{OpenAI}, achieving 100\% doc coverage across all modules.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Responsive Mobile UI Kit} | Android Jetpack Compose, Material Design}
          \resumeItemListStart
              \resumeItem{Developed customizable UI components in \textbf{Jetpack Compose} to enable responsive \textbf{Android} layouts improving developer productivity by 40\%.}
              \resumeItem{Implemented accessibility features ensuring \textbf{WCAG compliant} mobile experiences, boosting accessibility scores by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Mobile REST API Integration Framework} | Retrofit, JSON, Kotlin}
          \resumeItemListStart
              \resumeItem{Created a reusable Kotlin library for robust \textbf{RESTful JSON} communication, reducing app data fetch failures by 35\%.}
              \resumeItem{Integrated error handling and caching strategies improving \textbf{API} call reliability and response times by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Kotlin, Java, Python, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Mobile Development:} & Android SDK, Android Studio, Jetpack Compose, Retrofit, ViewModels, Fragments \\
                \textbf{Testing \& Tools:} & JUnit, Espresso, Git, GitHub, Agile Workflows, CI/CD, Jenkins \\
                \textbf{Web \& Backend Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js \\
                \textbf{Databases \& APIs:} & MySQL, PostgreSQL, RESTful APIs, JSON \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3), Docker, Jenkins, Linux/Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}