\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{CI/CD} pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing deployment turnaround time by 40\%.}
        \resumeItem{Developed \textbf{Python} and \textbf{Bash} automation scripts to improve system monitoring and alerting efficiency by 30\%.}
        \resumeItem{Managed and troubleshot cloud infrastructure on \textbf{AWS}, achieving 99.9\% uptime and incident response reduction of 25\%.}
        \resumeItem{Collaborated cross-functionally to design tools supporting open source software distribution, boosting internal developer productivity by 20\%.}
        \resumeItem{Implemented root cause analysis on operational issues, reducing repetitive errors by 35\% through persistent fixes in key applications.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented automated deployment workflows with \textbf{GitLab CI/CD} on cloud platforms, accelerating release cadence by 30\%.}
        \resumeItem{Configured and maintained \textbf{GitHub} and \textbf{GitLab} repositories, improving collaboration efficiency with branching strategies and access control.}
        \resumeItem{Developed operational scripts in \textbf{Python} and \textbf{Bash} for API integration and error handling, increasing system resilience by 25\%.}
        \resumeItem{Monitored cloud resources on \textbf{AWS} and \textbf{GCP}, optimizing resource usage to reduce costs by 15\% while maintaining performance.}
        \resumeItem{Orchestrated containerized deployments using \textbf{Docker}, enhancing development consistency and eliminating environment-related bugs by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based systems for cybersecurity labs, ensuring 99\% uptime and secure software environments for over 100 students.}
        \resumeItem{Automated grading using shell and \textbf{Python} scripts, reducing manual effort by 30\% while improving grading accuracy.}
        \resumeItem{Supported lab infrastructure and troubleshooting, enabling quick resolution of technical issues and increasing lab usability by 20\%.}
        \resumeItem{Presented workshops on version control and security best practices, enhancing student understanding of open source development workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced backend \textbf{C\#} APIs, improving response time by 30\% and supporting seamless data exchange using REST principles.}
        \resumeItem{Optimized \textbf{PostgreSQL} database queries, decreasing latency by 15\% and streamlining data retrieval processes.}
        \resumeItem{Automated deployment processes for containerized apps using \textbf{Docker}, speeding release cycles by 35\%.}
        \resumeItem{Configured and maintained Git repositories with issue tracking using \textbf{Jira}, improving team coordination and bug resolution time.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{Spring Boot} microservices on \textbf{AWS EC2}, supporting scalable SaaS platform with sub-200ms latency.}
        \resumeItem{Implemented and maintained \textbf{CI/CD} pipelines using \textbf{Docker} and cloud services, reducing manual deployment errors by 40\%.}
        \resumeItem{Developed automation scripts in \textbf{Python} and \textbf{Bash} to monitor infrastructure health and trigger alerts, decreasing downtime by 25\%.}
        \resumeItem{Managed \textbf{GitHub} repository access and branching policies, increasing team's open source compliance and collaboration efficiency.}
        \resumeItem{Created relational database schemas on \textbf{MySQL}, optimizing queries to improve application performance by 20\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Open Source Compliance Automation Bot} | GitHub Actions, Python, REST API}{}
          \resumeItemListStart
              \resumeItem{Developed a bot using \textbf{GitHub Actions} to automate license compliance checks across repositories, reducing manual audits by 50\%.}
              \resumeItem{Integrated \textbf{REST APIs} to collect repository metadata, enhancing verification accuracy and speeding compliance reports generation.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-based Build and Deploy System} | AWS, Docker, GitLab CI/CD}{}
          \resumeItemListStart
              \resumeItem{Engineered a scalable build system using \textbf{GitLab CI/CD} and \textbf{Docker} on \textbf{AWS}, cutting build times by 35\%.}
              \resumeItem{Configured automated rollback mechanisms, improving system resilience with 99.9\% service availability during deployments.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Assistant} | OpenAI API, GitHub API, Python}{}
          \resumeItemListStart
              \resumeItem{Built an \textbf{AI} assistant that analyzes pull requests for coding standards and common bugs, decreasing review time by 30\%.}
              \resumeItem{Automated documentation updates using \textbf{Python}, ensuring 100\% code doc coverage and improved team knowledge sharing.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Version Control \& Repositories:} & Git, GitHub, GitLab, GitHub Actions, Forking, Pull Requests, Branching Strategies \\
                \textbf{Programming \& Scripting:} & Python, Bash, Java, TypeScript, PHP, C\#, JavaScript \\
                \textbf{Cloud Platforms \& DevOps:} & AWS, GCP, Docker, Jenkins, CI/CD, EC2, Lambda, S3 \\
                \textbf{Databases \& APIs:} & PostgreSQL, MySQL, SQL, REST API, JSON, GraphQL \\
                \textbf{Operating Systems \& Tools:} & Linux/Unix, Jira, Bugzilla, Agile, Scrum, Kanban \\
                \textbf{Open Source Workflows \& Automation:} & InnerSource, Issue Management, Code Review, Automation Tools, Message Queues \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}