\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led design and implementation of scalable RESTful APIs using \textbf{Java Spring Boot}, improving throughput by 35\% on major services.}
        \resumeItem{Implemented role-based access control with \textbf{Spring Security} reducing unauthorized data access attempts by 40\%.}
        \resumeItem{Automated code quality checks via an \textbf{AI-powered} review assistant, reducing manual review time by 45\% and improving code consistency.}
        \resumeItem{Developed CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, cutting deployment time by 40\% and ensuring reliable releases.}
        \resumeItem{Collaborated with cross-functional teams to troubleshoot production issues, resulting in 30\% faster resolution times for critical bugs.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered a \textbf{SaaS} analytics platform with \textbf{Laravel} and \textbf{React}, supporting over 50 concurrent active users efficiently.}
        \resumeItem{Automated Python data ingestion pipelines processing 10,000+ records daily, reducing manual data entry effort by 80\%.}
        \resumeItem{Developed subscription e-commerce platform with \textbf{PHP}, integrating \textbf{Stripe} payments, enabling user role-based access control.}
        \resumeItem{Created AI-driven \textbf{LLM}-based agents automating broker data downloads, decreasing manual work by 80\%.}
        \resumeItem{Optimized \textbf{React} components, reducing page load times by 25\% and enhancing user engagement via smoother UI transitions.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure \textbf{Linux}-based environments for cybersecurity labs, maintaining stable execution for hands-on student projects.}
        \resumeItem{Assisted students in debugging and testing assignments, improving success rates by 20\% through targeted guidance and support.}
        \resumeItem{Automated grading scripts increased accuracy by 25\%, reducing manual review overhead for cybersecurity programming assignments.}
        \resumeItem{Conducted over 15 remote sessions explaining complex security and networking topics to enhance lab understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed \textbf{TypeScript} API calls achieving sub-100ms response times, enabling efficient data flow in client applications.}
        \resumeItem{Enhanced user engagement by 25\% through upgrading front-end components using \textbf{Angular.js} with improved UI responsiveness.}
        \resumeItem{Developed high-performance \textbf{C\#} backend services on \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, decreasing frontend data load by 15\% and improving system throughput.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Collaborated within a 5-person team to develop a \textbf{SaaS} tool automating software development lifecycle processes efficiently.}
        \resumeItem{Implemented \textbf{Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1,000 concurrent users with <200ms latency.}
        \resumeItem{Established \textbf{CI/CD} pipelines deploying 6 microservices on \textbf{AWS EC2} using \textbf{Docker}, accelerating release cycles.}
        \resumeItem{Developed React.js UI components to enhance project management UX, increasing page load speed by 30\%.}
        \resumeItem{Achieved 90\% unit test coverage on pipelines module using \textbf{JUnit}, improving code reliability and maintainability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Oracle APEX Application Automation} | Oracle Database, PL/SQL, APEX, Agile}{}
          \resumeItemListStart
              \resumeItem{Developed and deployed scalable APEX applications with \textbf{PL/SQL} tuning, reducing end-user query times by 30\%.}
              \resumeItem{Integrated Oracle cloud tools within applications to enhance functionality, increasing user satisfaction scores by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-driven Code Review Assistant} | OpenAI API, GitHub Actions, Python}{}
          \resumeItemListStart
              \resumeItem{Created an \textbf{AI-powered} assistant automating code review tasks using \textbf{LLMs}, decreasing manual review time by 35\%.}
              \resumeItem{Automated documentation generation for new code, achieving 100\% coverage and improving onboarding time for developers.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-based Performance Dashboard} | OCI, Oracle APEX, REST APIs}{}
          \resumeItemListStart
              \resumeItem{Built an interactive dashboard with \textbf{Oracle APEX} integrated with OCI services, enabling real-time monitoring and alerting.}
              \resumeItem{Optimized backend \textbf{PL/SQL} queries reducing report generation time by 40\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, PL/SQL, SQL, Python, TypeScript, C\#, JavaScript \\
                \textbf{Web Development \& Frameworks:} & Oracle APEX, React.js, Angular.js, Spring Boot, Laravel, .NET \\
                \textbf{Database \& Cloud:} & Oracle Database, MySQL, PostgreSQL, Oracle Cloud Infrastructure (OCI), Oracle Analytics Cloud (OAC) \\
                \textbf{DevOps \& Automation:} & Docker, Jenkins, GitHub Actions, AWS, CI/CD Pipelines \\
                \textbf{Tools \& IDEs:} & TOAD, Git, Jira, REST API, Agile Methodologies \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI-Driven Code Review, Automation Scripting \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}