\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices, boosting API throughput by 35\% and improving system responsiveness under peak loads.}
        \resumeItem{Implemented \textbf{Spring Security} improvements, reducing unauthorized access attempts by 40\% through tighter authentication controls.}
        \resumeItem{Designed and integrated an \textbf{AI-driven} code review assistant, decreasing manual review effort by 45\% and accelerating development velocity by 25\%.}
        \resumeItem{Automated \textbf{Jenkins}-based CI/CD pipelines and \textbf{Docker} deployments, cutting release cycles by 40\% while enhancing reliability.}
        \resumeItem{Collaborated cross-functionally to troubleshoot production bugs using centralized logging, improving issue resolution speed by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and developed a \textbf{React} and \textbf{Laravel}-based SaaS visualization tool supporting 50+ concurrent users flawlessly.}
        \resumeItem{Automated daily stock data processing pipelines in \textbf{Python}, reducing manual input time by 80\% and improving accuracy.}
        \resumeItem{Implemented AI-powered \textbf{LLM} agents for broker data automation, decreasing manual processing time by 80\%.}
        \resumeItem{Optimized \textbf{React} state management, reducing page load times by 25\% and boosting user engagement significantly.}
        \resumeItem{Developed a \textbf{LinkedIn} automation bot in \textbf{JavaScript} that increased qualified lead generation by 40\% via targeted outreach.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux} lab environments ensuring secure configurations, raising uptime and stability by 15\%.}
        \resumeItem{Facilitated debugging and testing workshops, improving student assignment pass rates by 20\% through hands-on support.}
        \resumeItem{Automated grading scripts for software validation, boosting grading accuracy by 25\% and reducing turnaround time.}
        \resumeItem{Led interactive sessions clarifying cryptography and networking protocols, increasing student engagement and understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency \textbf{TypeScript} API calls, achieving sub-100ms response times and seamless data flow.}
        \resumeItem{Refined \textbf{Angular.js} frontend components, improving user engagement rates by 25\% through enhanced UI performance.}
        \resumeItem{Engineered \textbf{C\# .NET} backend services, reducing data retrieval latency by 30\% and increasing throughput.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries, decreasing frontend load times by 15\% and accelerating database response.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Collaborated on \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users, reducing response time below 200ms.}
        \resumeItem{Developed scalable \textbf{React.js} UI components, enhancing application usability and reducing page load latency by 30\%.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{Docker} on \textbf{AWS EC2}, accelerating deployment frequency by 50\%.}
        \resumeItem{Wrote unit tests with \textbf{JUnit} ensuring 90\% coverage and improving code stability across key modules.}
        \resumeItem{Integrated and optimized \textbf{MySQL} queries, improving database transaction efficiency and reducing latency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Developed a bot using \textbf{GitHub Actions} and \textbf{OpenAI API} to automate PR analysis, reducing manual review time by 25\%.}
              \resumeItem{Implemented automated docstring generation for \textbf{Python} projects, ensuring consistent documentation coverage across the codebase.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Real-Time Event Streaming Platform} | Apache Kafka, Golang, SQL}{}
          \resumeItemListStart
              \resumeItem{Built a scalable event streaming backend in \textbf{Golang} using \textbf{Apache Kafka}, supporting high-throughput real-time data pipelines.}
              \resumeItem{Designed efficient \textbf{SQL} queries to analyze streaming data, optimizing latency and enabling timely insights for users.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Full Stack IoT Dashboard} | React, Python Flask, Neo4j}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{React} frontend and \textbf{Python Flask} backend dashboard interfacing with \textbf{Neo4j} graph database for device relationships.}
              \resumeItem{Implemented responsive UI and query optimizations, improving user task efficiency by 30\% and system data retrieval speed.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Python, Java, JavaScript, Golang, TypeScript, C\# \\
                \textbf{Frontend Frameworks:} & React.js, Angular.js, ES6, HTML, CSS \\
                \textbf{Backend Frameworks \& Technologies:} & Spring Boot, Flask, Node.js, .NET, Laravel \\
                \textbf{Databases:} & SQL, MySQL, PostgreSQL, Neo4j (Cypher queries) \\
                \textbf{Messaging \& Streaming:} & Apache Kafka, REST APIs, JSON \\
                \textbf{DevOps \& Tools:} & Linux, Jenkins, Docker, CI/CD pipelines, Git, GitHub, Centralized logging \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}