\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer specializing in backend and platform systems with strong expertise in microservices, cloud infrastructure, and AI integration. Skilled at building scalable, reliable systems that empower intelligent automation and data-driven solutions. Experienced in Linux, networking, and cloud services, eager to contribute to cutting-edge AI-driven platforms.

 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Go, C++, Python, C, C\#, JavaScript \\
                \textbf{Backend Frameworks:} & Spring Boot, Node.js, Django, .NET, Laravel \\
                \textbf{Cloud Platforms:} & AWS, Azure, GCP, Docker, Lambda, EC2, S3 \\
                \textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Docker, Kubernetes \\
                \textbf{Networking \& Protocols:} & TCP/IP, DNS, DHCP, BGP, VLANs, Linux \\
                \textbf{AI \& Automation:} & AI/ML concepts, LLM Integration, pyTest, Automation scripting \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices, increasing system throughput by 35\% while ensuring robust \textbf{API} integration and security enhancements.}
        \resumeItem{Enhanced authentication systems using \textbf{Spring Security}, decreasing unauthorized access attempts by 40\% across critical services.}
        \resumeItem{Developed an \textbf{AI-driven} code review assistant leveraging \textbf{LLMs}, reducing manual review time by 45\% and accelerating deployment by 25\%.}
        \resumeItem{Automated \textbf{CI/CD} pipelines using \textbf{Jenkins} and \textbf{Docker}, cutting release cycle duration by 40\% and improving deployment reliability.}
        \resumeItem{Collaborated with cross-functional teams to improve backend platform scalability on cloud infrastructure, supporting increased user load without performance loss.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and implemented \textbf{microservices} in \textbf{Laravel} and \textbf{React} to support 50+ concurrent users with seamless API communication.}
        \resumeItem{Automated data ingestion pipelines in \textbf{Python}, processing 10,000+ daily stock entries and reducing manual workload by 80\%.}
        \resumeItem{Developed AI-based agents using \textbf{LLMs} to automate data extraction workflows, increasing operational efficiency by 80\%.}
        \resumeItem{Built a LinkedIn outreach automation bot powered by \textbf{AI}, generating 40\% more qualified business leads through targeted campaigns.}
        \resumeItem{Optimized \textbf{React} components to reduce page load times by 25\%, improving user retention and interaction rates significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux}-based lab infrastructure, ensuring secure environments and consistent availability for cybersecurity coursework and experiments.}
        \resumeItem{Authored automation scripts to grade and validate student assignments, improving evaluation accuracy and reducing manual effort by 25\%.}
        \resumeItem{Guided students in debugging and deployment of software modules, elevating assignment completion rates by 20\% through personalized support.}
        \resumeItem{Conducted technical sessions covering fundamental networking and security protocols, enhancing student understanding of core concepts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed responsive APIs in \textbf{TypeScript} achieving sub-100ms latency, ensuring smooth data exchange between frontend and backend systems.}
        \resumeItem{Refined legacy frontend architecture with \textbf{Angular.js}, improving UI responsiveness and increasing user engagement by 25\%.}
        \resumeItem{Created performant backend services in \textbf{C\#} using \textbf{.NET}, reducing data retrieval times by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} database queries and stored procedures, enhancing transaction efficiency by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000+ users, achieving sub-200ms response times and high availability.}
        \resumeItem{Designed and implemented \textbf{CI/CD} pipelines with \textbf{Docker} and \textbf{AWS EC2}, reducing deployment errors by over 30\%.}
        \resumeItem{Collaborated in full-stack development using \textbf{React.js}, increasing frontend performance and usability by 30\%.}
        \resumeItem{Authored extensive unit tests with \textbf{JUnit} covering 90\% of backend modules, significantly increasing code reliability.}
        \resumeItem{Streamlined microservices architecture to improve scalability and maintainability, supporting ongoing product iterations efficiently.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, Java, Python}{}
          \resumeItemListStart
              \resumeItem{Created an \textbf{AI-assisted} review bot that scans PRs for bugs and style issues, reducing manual review time by 40\% while improving code quality.}
              \resumeItem{Automated generation of comprehensive documentation using \textbf{LLMs}, ensuring 100\% coverage and accelerating team knowledge sharing.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Backend Platform for Face Recognition} | AWS EC2, S3, SQS, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Built a decoupled, scalable backend architecture using \textbf{SQS} queues and \textbf{EC2}, handling 1000+ face recognition requests under 60 seconds.}
              \resumeItem{Integrated \textbf{S3} for secure data persistence, optimizing storage access and system reliability for large user bases.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} | Spring Boot, Docker, AWS EC2, Jenkins}{}
          \resumeItemListStart
              \resumeItem{Engineered containerized \textbf{microservices} deployed on \textbf{AWS EC2} with automated \textbf{CI/CD} pipelines, reducing system downtime by 30\%.}
              \resumeItem{Improved API reliability and scalability, supporting concurrent usage spikes without service degradation or data loss.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}