\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Versatile software engineer specializing in scalable backend and cloud infrastructure development, with hands-on experience in microservices, APIs, and distributed systems. Skilled in leveraging AI/ML concepts and automation to enhance operational efficiency and deliver reliable solutions that support business growth in dynamic environments.

 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Backend Programming:} & Java, Go, C++, Python, C, C\# \\
                \textbf{Cloud Platforms \& DevOps:} & AWS, Azure, GCP, Docker, Jenkins, CI/CD Pipelines, Lambda, EC2, S3, Terraform \\
                \textbf{Web \& Microservices Frameworks:} & Spring Boot, Node.js, Django, React.js, REST API, gRPC \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Networking \& Systems:} & Linux, TCP/IP, DNS, DHCP, BGP, VLANs \\
                \textbf{AI \& Automation:} & AI/ML Basics, pyTest, Automation Frameworks, LLM Integration, AI Agents \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Java Spring Boot} microservices improving system scalability and increasing API response speed by 35\% for distributed cloud platforms.}
        \resumeItem{Enhanced security by integrating \textbf{Spring Security} with role-based access, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an \textbf{AI-powered} code review system that cut manual review times by 45\% and accelerated development cycles by 25\%.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing release cycle times by 40\% and improving reliability.}
        \resumeItem{Collaborated on building backend infrastructure for AI analytics platforms supporting operational insights and business growth.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a scalable \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ users and improving data pipeline automation by 80\%.}
        \resumeItem{Automated stock data pipelines with \textbf{Python}, reducing manual data processing by 80\%.}
        \resumeItem{Engineered AI agents leveraging \textbf{LLMs} to automate financial data workflows, increasing accuracy and cutting processing time by 80\%.}
        \resumeItem{Developed AI-driven \textbf{LinkedIn} outreach automation, boosting qualified lead generation by 40\% through targeted content deployment.}
        \resumeItem{Refined \textbf{React} components improving UI responsiveness and reducing page load latency by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity infrastructure, ensuring stable lab environments aligned with secure networking protocols.}
        \resumeItem{Assisted students with debugging and deployment, enhancing assignment success rates by 20\% through guided troubleshooting.}
        \resumeItem{Automated software testing and grading with scripted validations, increasing review accuracy and reducing manual effort by 25\%.}
        \resumeItem{Delivered 15+ sessions covering cryptography, networking, and security protocols to enhance student learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API integrations achieving consistent sub-100ms response times for high throughput data services.}
        \resumeItem{Upgraded client interfaces using \textbf{Angular.js}, resulting in a 25\% increase in user engagement and satisfaction scores.}
        \resumeItem{Built performant \textbf{C\# .NET} backend services, reducing data retrieval latency by 30\% and optimizing resource utilization.}
        \resumeItem{Enhanced \textbf{PostgreSQL} queries and procedures, streamlining database operations and cutting frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices for a SaaS SDLC automation tool handling 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Configured \textbf{CI/CD} pipelines using \textbf{Docker} on \textbf{AWS EC2}, enabling smooth deployment of 6 key microservices.}
        \resumeItem{Implemented project tracking UI in \textbf{React.js}, improving usability and cutting page load times by 30\%.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} tests covering 90\% of pipeline module, increasing system reliability and maintainability.}
        \resumeItem{Collaborated cross-functionally to integrate backend services with cloud infrastructure enhancing scalability and robust API communication.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Backend Monitoring System} | Python, AWS CloudWatch, Lambda, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Implemented backend monitoring with \textbf{AWS Lambda} and \textbf{OpenAI} to detect anomalies in real-time, reducing incident response time by 30\%.}
              \resumeItem{Automated alert workflows using AI to classify issues, enabling precise operational decisions and improving platform reliability by 25\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Microservices for Data Analytics} | Java, Spring Boot, Docker, AWS EC2, REST API}{}
          \resumeItemListStart
              \resumeItem{Engineered microservices architecture with \textbf{Spring Boot} and \textbf{Docker} deployed on \textbf{AWS EC2} supporting 1000+ simultaneous analytics requests reliably.}
              \resumeItem{Designed RESTful APIs for data ingestion and processing pipelines, enhancing throughput by 40\% under load conditions.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Automated Test Suite with CI/CD Integration} | pyTest, Jenkins, Docker, GitHub Actions}{}
          \resumeItemListStart
              \resumeItem{Created automated testing pipelines using \textbf{pyTest} integrated with \textbf{Jenkins} and \textbf{GitHub Actions}, reducing regression bugs by 50\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}