\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Lead software engineer skilled in designing and scaling enterprise applications leveraging \textbf{.NET}, \textbf{Java}, and \textbf{Azure cloud services}. Expert in driving high-quality, maintainable code development with a strong focus on CI/CD and Agile methods to deliver reliable, scalable solutions in fast-paced environments.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming:} & Java, C\#, SQL, JavaScript, Python \\
                \textbf{Frameworks \& Platforms:} & .NET Framework, Spring Boot, Azure Cloud Services, Serverless Architecture \\
                \textbf{Databases:} & SQL Server, MySQL, PostgreSQL \\
                \textbf{DevOps \& CI/CD:} & Azure DevOps, Jenkins, Docker, Kubernetes \\
                \textbf{Methodologies \& Tools:} & Agile, Jira, Git, REST API, Microservices \\
                \textbf{Cloud Technologies:} & Azure Functions, Azure App Services, Azure Blob Storage \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered robust \textbf{.NET} microservices to improve application scalability, reducing processing times by 30\% across key workflows.}
        \resumeItem{Implemented \textbf{Azure} cloud solutions, facilitating efficient deployment and scaling of critical services with zero downtime.}
        \resumeItem{Automated testing and deployment using \textbf{Azure DevOps pipelines}, cutting release cycles by 40\%.}
        \resumeItem{Led code reviews and debugging sessions, enhancing code quality and reducing critical bugs in production by 35\%.}
        \resumeItem{Collaborated in Agile ceremonies to design and implement new features, boosting user satisfaction metrics by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{core Java} services integrated with \textbf{Azure Functions} to support scalable back-end infrastructures.}
        \resumeItem{Optimized complex \textbf{SQL Server} queries, improving database performance by 25\% and reducing timeout errors significantly.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, accelerating delivery while maintaining high application stability.}
        \resumeItem{Built and maintained \textbf{cloud-native} serverless applications, reducing infrastructure costs by 30\%.}
        \resumeItem{Enhanced team workflows with \textbf{Jira}, promoting Agile best practices and timely project deliveries.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} systems for lab environments, enforcing best practices to protect sensitive data.}
        \resumeItem{Guided students on software debugging and deployment, improving lab assignment success rate by 20\%.}
        \resumeItem{Automated grading processes using \textbf{Python} scripts, increasing evaluation speed by 30\%.}
        \resumeItem{Conducted technical sessions on Agile development, security protocols, and version control tools.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed backend REST APIs with \textbf{.NET} framework, enhancing data access speed by 30\%.}
        \resumeItem{Improved \textbf{PostgreSQL} database indexing, reducing query response times by 20\%.}
        \resumeItem{Upgraded front-end components using \textbf{Angular.js} to bolster user engagement by 25\%.}
        \resumeItem{Participated in daily Agile standups and retrospectives, accelerating sprint completion by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices with \textbf{MySQL}, reducing response latency under 200ms for 1000+ concurrent users.}
        \resumeItem{Implemented automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker} to streamline deployments on AWS EC2 instances.}
        \resumeItem{Architected microservices for enterprise SaaS solutions, boosting operational efficiency by 35\%.}
        \resumeItem{Developed project management interfaces with \textbf{React.js} improving usability and reducing load times by 30\%.}
        \resumeItem{Created unit tests with \textbf{JUnit} achieving 90\% code coverage for critical modules, increasing software reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Assistant} | GitHub Actions, OpenAI API, .NET, Azure DevOps}{}
          \resumeItemListStart
              \resumeItem{Built an AI assistant integrating \textbf{OpenAI API} and \textbf{Azure DevOps} to automate code reviews, reducing manual review time by 40\%.}
              \resumeItem{Automated generation of detailed code documentation and bug detection, increasing codebase maintainability and review accuracy.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-Native Serverless Application} | Azure Functions, .NET Core, SQL Server}{}
          \resumeItemListStart
              \resumeItem{Developed scalable serverless backend using \textbf{Azure Functions} and \textbf{.NET Core}, decreasing hosting costs by 25\%.}
              \resumeItem{Implemented optimized data operations with \textbf{SQL Server}, improving transaction efficiency and system throughput by 30\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{CI/CD Pipeline Automation} | Jenkins, Docker, Kubernetes, Azure DevOps}{}
          \resumeItemListStart
              \resumeItem{Designed and implemented CI/CD pipelines leveraging \textbf{Jenkins}, \textbf{Docker}, and \textbf{Azure DevOps}, cutting release time by 40\%.}
              \resumeItem{Automated container orchestration with \textbf{Kubernetes}, ensuring scalable deployments for high-demand enterprise applications.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}