\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer proficient in backend and platform systems development, specializing in scalable microservices, cloud infrastructures, and AI-enhanced automation. Adept at designing robust APIs and leveraging cloud platforms to drive data-driven solutions for enterprise growth and operational excellence.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Go, C++, Python, C, Shell Scripting \\
                \textbf{Cloud Platforms \& DevOps:} & AWS, Azure, Docker, Jenkins, CI/CD Pipelines, Kubernetes \\
                \textbf{Backend \& Frameworks:} & Spring Boot, Microservices Architecture, REST API, gRPC \\
                \textbf{Operating Systems \& Networking:} & Linux, TCP/IP, DNS, DHCP, BGP, VLANs \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{AI \& Automation:} & AI/ML Concepts, Automation Frameworks, pyTest, OpenAI API \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to improve backend scalability, boosting API throughput and reducing latency by 30\%.}
        \resumeItem{Enhanced security by implementing \textbf{Spring Security} mechanisms, lowering unauthorized access incidents by 35\%.}
        \resumeItem{Devised AI-assisted code review system using \textbf{OpenAI API}, expediting code validation and decreasing errors by 40\%.}
        \resumeItem{Automated deployment pipelines leveraging \textbf{Jenkins} and \textbf{Docker}, achieving 50\% faster release cycles with improved stability.}
        \resumeItem{Collaborated on cloud infrastructure optimization within \textbf{AWS}, enhancing microservices deployment and resource utilization for dynamic workloads.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed microservices and APIs using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users with high availability.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, processing 10,000+ entries and reducing manual processing by 80\%.}
        \resumeItem{Implemented AI-powered agents with \textbf{LLMs} to automate broker data workflows, improving efficiency by 70\%.}
        \resumeItem{Developed AI-driven outreach bots automating \textbf{LinkedIn} content and lead targeting, increasing qualified leads by 35\%.}
        \resumeItem{Refined frontend components and optimized \textbf{React} app performance, reducing page load times by 25\% and enhancing UX.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab environments, ensuring secure configurations and consistent availability for student projects.}
        \resumeItem{Mentored students on network protocols and debugging, increasing their assignment success rate by 20\%.}
        \resumeItem{Automated test scripts using \textbf{Python} and \textbf{pyTest}, reducing grading time by 30\% and improving result accuracy.}
        \resumeItem{Conducted interactive sessions on TCP/IP, DNS, and cybersecurity fundamentals, enhancing student engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency API calls with \textbf{TypeScript}, maintaining sub-100ms response times for critical data services.}
        \resumeItem{Enhanced user experience by upgrading frontend using \textbf{Angular.js}, increasing user engagement by 25\%.}
        \resumeItem{Built high-performance backend services in \textbf{C\#} on \textbf{.NET}, reducing data fetch latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, improving database efficiency and cutting frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led development of \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users with sub-200ms response times on \textbf{MySQL} backend.}
        \resumeItem{Implemented CI/CD workflows deploying microservices on \textbf{AWS EC2} with \textbf{Docker}, reducing deployment errors by 40\%.}
        \resumeItem{Developed React.js UI for project tracking, boosting usability and load speed by 30\% for improved user productivity.}
        \resumeItem{Applied \textbf{JUnit} testing across backend modules, achieving over 90\% code coverage and enhancing software reliability.}
        \resumeItem{Collaborated on microservices API design, strengthening integration and scalability across distributed system components.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Backend Code Review} | GitHub Actions, OpenAI API, Java, Python}{}
          \resumeItemListStart
              \resumeItem{Created an AI-backed CI tool to review backend code for bugs and style compliance, decreasing review time by 40\%.}
              \resumeItem{Automatically generated comprehensive documentation for backend services, ensuring 100\% coverage and boosting team efficiency.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Microservices-Based Analytics Platform} | Spring Boot, AWS, Docker, React.js}{}
          \resumeItemListStart
              \resumeItem{Designed and deployed scalable microservices on \textbf{AWS}, enabling real-time analytics processing for 1000+ data points/minute.}
              \resumeItem{Implemented RESTful APIs consumed by React frontend, improving user data visualization speed by 30\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-Native AI Automation Agent} | AWS Lambda, Python, OpenAI API, CI/CD}{}
          \resumeItemListStart
              \resumeItem{Built an AI automation agent on \textbf{AWS Lambda} using \textbf{OpenAI API} that processes operational data, reducing manual workflows by 60\%.}
              \resumeItem{Integrated CI/CD pipelines for continuous deployment and monitoring, ensuring 99.9\% uptime for the automation service.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}