\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer specializing in backend development and cloud infrastructure with strong expertise in microservices, APIs, and distributed systems. Skilled in Linux, networking, and cloud platforms like AWS and Azure, with a foundational understanding of AI/ML concepts to deliver robust, scalable systems supporting intelligent automation.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Backend Programming:} & Java, Go, C++, Python, C, C\# \\
                \textbf{Cloud \& DevOps:} & AWS, Azure, Docker, Jenkins, CI/CD pipelines, Kubernetes \\
                \textbf{Web \& API Technologies:} & REST APIs, gRPC, Spring Boot, React.js, Node.js \\
                \textbf{Operating Systems \& Networking:} & Linux, TCP/IP, DNS, DHCP, BGP, VLANs \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{AI \& Automation Tools:} & Machine Learning foundational knowledge, pyTest, OpenAI API, Automation scripting \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to improve system scalability, achieving 30\% faster response times and enhanced fault tolerance.}
        \resumeItem{Designed and implemented secure REST \textbf{APIs} supporting role-based access via \textbf{Spring Security}, reducing unauthorized access by 35\%.}
        \resumeItem{Developed automation scripts integrating \textbf{AI-driven} code analysis to accelerate pull request reviews, cutting manual assessment time by 40\%.}
        \resumeItem{Streamlined build and deployment by creating \textbf{Jenkins} pipelines with \textbf{Docker}, reducing release cycles by 38\%.}
        \resumeItem{Collaborated on cloud migration to \textbf{AWS}, optimizing compute resources and lowering operational costs by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built scalable data visualization services using \textbf{Laravel} and \textbf{React}, supporting 50+ users with optimized performance and uptime.}
        \resumeItem{Automated large-scale data pipelines in \textbf{Python}, reducing manual data processing time by 75\% through efficient workflows.}
        \resumeItem{Developed AI-powered \textbf{automation} agents leveraging \textbf{LLMs} to streamline FINRA data extraction, cutting manual tasks by 80\%.}
        \resumeItem{Implemented an \textbf{AI-based} LinkedIn outreach bot, increasing lead engagement rates by 40\% through targeted content automation.}
        \resumeItem{Enhanced \textbf{React} frontend components, decreasing initial load time by 25\% and improving user retention metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based infrastructure, ensuring 99.9\% uptime for cybersecurity lab environments with proper network configurations.}
        \resumeItem{Assisted students with debugging and deploying lab projects, increasing task completion rate by 20\% through effective guidance.}
        \resumeItem{Developed automated grading scripts that improved assessment accuracy by 25\% and reduced manual workload significantly.}
        \resumeItem{Conducted over 15 instructional sessions on networking protocols and Linux fundamentals, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls with average latency under 100ms, enhancing frontend responsiveness and user experience.}
        \resumeItem{Modernized platform components using \textbf{Angular.js}, resulting in 25\% higher user interaction and satisfaction scores.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, reducing data access latency by 30\% through optimized algorithms.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, decreasing data retrieval time by 15\% and improving database performance for users.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users, reducing response times to below 200ms.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{Docker} and \textbf{AWS EC2} for seamless deployment of six core services, increasing release frequency.}
        \resumeItem{Developed a React.js project management UI, improving load times by 30\% and enhancing user workflow efficiency.}
        \resumeItem{Wrote comprehensive unit tests using \textbf{JUnit} with 90\% coverage, ensuring high-quality code and regression prevention.}
        \resumeItem{Collaborated on building an automation SaaS tool improving SDLC processes, achieving higher team productivity and faster feature rollout.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Backend Code Review Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Created an AI bot integrating \textbf{GitHub Actions} to analyze backend code for bugs and style issues, reducing manual reviews by 40\%.}
              \resumeItem{Automated documentation generation with LLMs, achieving 100\% coverage and improving code maintainability across multiple microservices.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-Based Data Pipeline Automation} | AWS, Python, Docker}{}
          \resumeItemListStart
              \resumeItem{Engineered scalable data ingestion pipelines using \textbf{AWS Lambda} and \textbf{Docker}, automating processing of 10,000+ records daily efficiently.}
              \resumeItem{Reduced data pipeline latency by 30\% with optimized asynchronous processing and error handling strategies on distributed cloud infrastructure.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Distributed Microservices for Analytics Platform} | Java, Spring Boot, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Developed resilient \textbf{Java Spring Boot} microservices orchestrated by \textbf{Kubernetes}, increasing system scalability for analytics workloads by 50\%.}
              \resumeItem{Implemented secure API gateways managing data access and authentication, improving data integrity and compliance by 35\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}