\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Resourceful software engineer specializing in scalable backend systems and cloud-native infrastructure with strong expertise in microservices and API design. Skilled in Linux, networking fundamentals, and modern cloud platforms like AWS and Azure. Passionate about enabling AI-driven analytics by building robust, reliable software solutions that propel operational excellence and innovation at scale.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming:} & Java, Go, C/C++, Python, TypeScript, C\# \\
                \textbf{Backend \& Frameworks:} & Spring Boot, Node.js, Django, .NET, Microservices, REST APIs \\
                \textbf{Cloud Platforms:} & AWS (EC2, Lambda, S3), Azure, GCP \\
                \textbf{DevOps \& Automation:} & Docker, Jenkins, CI/CD pipelines, pyTest, Git \\
                \textbf{Networking \& OS:} & Linux, TCP/IP, DNS, DHCP, BGP, VLANs \\
                \textbf{AI \& Data:} & AI/ML concepts, OpenAI API, Data Pipelines, Analytics Platforms \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices' scalability, boosting \textbf{API} throughput by 38\%, enabling higher system reliability under load.}
        \resumeItem{Implemented secure role-based access via \textbf{Spring Security}, reducing unauthorized access attempts by 42\% through tighter authentication controls.}
        \resumeItem{Integrated an \textbf{AI-powered} code analysis tool, cutting manual review time by 45\% and increasing merge velocity by 28\%.}
        \resumeItem{Automated deployment workflows combining \textbf{Jenkins} and \textbf{Docker}, accelerating release cadence and cutting turnaround by 40\%.}
        \resumeItem{Collaborated on cloud infrastructure optimization, leveraging \textbf{AWS} best practices to reduce latency and increase resilience of backend services.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{microservices} using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users with zero downtime.}
        \resumeItem{Streamlined \textbf{Python}-based ETL pipelines processing 10,000+ stock entries daily, reducing manual intervention by 80\%.}
        \resumeItem{Created automated AI-powered agents leveraging \textbf{LLMs} to handle broker data workflows, enhancing accuracy and cutting time by 75\%.}
        \resumeItem{Built a targeted \textbf{LinkedIn AI outreach} bot, increasing qualified leads by 40\%, through automated messaging and data insight integration.}
        \resumeItem{Reduced frontend load times by 25\% by optimizing \textbf{React} components and state management for improved user experience.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab infrastructure, ensuring secure and stable environments for cybersecurity experiments.}
        \resumeItem{Assisted students in troubleshooting and deploying software, boosting assignment success rates by 20\% through guidance.}
        \resumeItem{Automated grading scripts improved validation accuracy by 25\% and minimized manual review efforts across multiple courses.}
        \resumeItem{Conducted interactive sessions covering networking, cryptography, and security fundamentals to enhance student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented rapid \textbf{TypeScript} API calls achieving under 100ms response, ensuring smooth data synchronization across systems.}
        \resumeItem{Upgraded UI components with \textbf{Angular.js} resulting in a 25\% increase in user engagement and system usability.}
        \resumeItem{Developed backend services in \textbf{C\# .NET} framework, reducing data retrieval times by 30\% through efficient coding.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, trimming frontend load by 15\%, enhancing overall platform responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Java Spring Boot} microservices supporting 1000+ users with response times under 200ms, increasing reliability.}
        \resumeItem{Automated deployment using \textbf{CI/CD} pipelines on \textbf{AWS EC2} with \textbf{Docker}, accelerating release cycles and stability.}
        \resumeItem{Developed a project tracking UI in \textbf{React.js} improving load times by 30\% and enhancing usability.}
        \resumeItem{Designed and executed \textbf{JUnit} unit tests achieving 90\% coverage, improving codebase reliability and reducing bugs.}
        \resumeItem{Collaborated with team to build SaaS tools simplifying software development lifecycle processes and increasing productivity.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Backend Analytics Platform} | Spring Boot, AWS, Docker, REST APIs}{}
          \resumeItemListStart
              \resumeItem{Engineered a scalable backend analytics system using \textbf{Spring Boot} and \textbf{AWS}, supporting real-time data processing with 99.9\% uptime.}
              \resumeItem{Integrated automated \textbf{CI/CD} pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 50\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Distributed Microservices for Cloud Data Processing} | Go, Kubernetes, GCP}{}
          \resumeItemListStart
              \resumeItem{Developed \textbf{Go}-based microservices deployed on \textbf{GCP} Kubernetes clusters, improving data processing throughput by 35\%.}
              \resumeItem{Implemented fault-tolerant communication between services using gRPC APIs to ensure system resiliency and scalability.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Automated AI Code Review Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Built an AI bot utilizing \textbf{OpenAI API} and \textbf{GitHub Actions} to automate code reviews, reducing manual effort by 40\%.}
              \resumeItem{Implemented Python scripts to generate documentation and flag potential bugs, improving code quality and maintainability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}