\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative Frontend Engineer with 2 years of experience developing responsive web applications. Proficient in JavaScript frameworks and keen to expand backend integration skills with APIs and security, delivering impactful, user-friendly interfaces in cross-functional teams across time zones.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, Java, HTML, CSS \\
                \textbf{Frontend Frameworks:} & React, Angular.js, Vue.js \\
                \textbf{Build Tools \& Package Managers:} & Webpack, npm, Babel \\
                \textbf{Version Control \& Collaboration:} & Git, GitHub, Jira \\
                \textbf{Backend Exposure:} & REST APIs, Spring Boot, Node.js \\
                \textbf{Cloud \& DevOps:} & AWS, Docker, Jenkins \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices for scalable API endpoints, improving data ingestion efficiency by 30\% across production systems.}
        \resumeItem{Integrated \textbf{Spring Security} for user authentication, reducing security vulnerabilities and unauthorized access attempts by 40\%.}
        \resumeItem{Developed frontend components in \textbf{React} to visualize complex operational data improving UI responsiveness by 28\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 35\% and increasing release reliability.}
        \resumeItem{Collaborated with cross-functional teams to refine API integrations, enhancing frontend-backend communication and data accuracy by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built scalable \textbf{React} interfaces for a SaaS platform, improving usability and supporting 50+ concurrent users without performance degradation.}
        \resumeItem{Automated data ingestion pipelines using \textbf{Python}, reducing manual data entry by more than 75\%.}
        \resumeItem{Enhanced frontend experience by optimizing \textbf{React} components, cutting page load times by 25\% and raising user engagement metrics.}
        \resumeItem{Developed AI-powered bots leveraging \textbf{LLMs} to automate data processing tasks, reducing manual workload by 80\%.}
        \resumeItem{Implemented multi-tier secure access using \textbf{Stripe} and role-based controls for subscription e-commerce platform features.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab environments ensuring secure and stable configurations for hands-on student experiments.}
        \resumeItem{Helped students debug and deploy software modules, improving project completion success rates by 20\%.}
        \resumeItem{Automated grading workflows using scripts, increasing accuracy by 25\% and reducing manual effort in lab assessments.}
        \resumeItem{Led interactive online training sessions explaining Cryptography and Web Security concepts to enhance learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API clients achieving response times under 100ms for smooth data communications with backend services.}
        \resumeItem{Refined frontend with \textbf{Angular.js}, increasing user engagement and satisfaction scores by 25\%.}
        \resumeItem{Built performant backend components in \textbf{C\#} using \textbf{.NET}, reducing data query latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, improving data retrieval speed by 15\% for frontend applications.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed microservices in \textbf{Java Spring Boot} integrated with \textbf{MySQL}, supporting over 1000 users with sub-200ms response.}
        \resumeItem{Developed dynamic frontend UI using \textbf{React.js} improving load time by 30\% and delivering a seamless user experience.}
        \resumeItem{Orchestrated CI/CD pipelines with \textbf{Docker} and \textbf{AWS EC2} for zero-downtime deployments and faster releases.}
        \resumeItem{Implemented unit and integration tests for backend services using \textbf{JUnit}, achieving 90\% coverage and high reliability.}
        \resumeItem{Collaborated in a team of 5 developing a SaaS automation tool, streamlining development flow and reducing manual efforts by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-assisted Frontend Code Analyzer} | GitHub Actions, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed a bot integrating \textbf{LLMs} with \textbf{GitHub Actions} to review frontend code and suggest improvements, reducing review time by 40\%.}
              \resumeItem{Automated generation of UI component documentation ensuring 100\% standardized comments, which improved team onboarding speed.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Real-time Data Visualization Dashboard} | React, WebSocket, REST API}{}
          \resumeItemListStart
              \resumeItem{Built a real-time dashboard using \textbf{React} and \textbf{WebSocket} to visualize backend data streams, boosting user decision speed by 30\%.}
              \resumeItem{Integrated RESTful APIs for seamless data flow between frontend and backend, improving data accuracy and refresh times by 25\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Automated Customer Query Agent} | Node.js, LLM, Gmail API}{}
          \resumeItemListStart
              \resumeItem{Engineered a Node.js-based AI agent using \textbf{LLMs} to classify and respond to support emails automating 60\% of queries and improving response speed.}
              \resumeItem{Orchestrated a human-in-the-loop workflow to escalate complex cases, ensuring customer satisfaction increased by 20\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}