\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Skilled Front-End Developer with 3+ years’ experience specializing in React.js, TypeScript, and Tailwind CSS to build accessible, responsive, and scalable web applications. Passionate about creating reusable UI components and optimizing user experience. Adept at collaborating across teams to integrate APIs and adopt modern development workflows ensuring high-quality and performant solutions.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Front-End Development:} & React.js, TypeScript, JavaScript, Tailwind CSS, HTML5, CSS3 \\
                \textbf{State \& Data Management:} & React Hooks, React Query, React Hook Form, RESTful API integration, Redux \\
                \textbf{Testing \& Tools:} & Jest, React Testing Library, Cypress, Playwright, Storybook, Git \\
                \textbf{Build \& Deployment:} & Vite, Webpack, Docker, CI/CD pipelines, GitHub Actions \\
                \textbf{Backend \& Databases:} & Node.js, Express, MongoDB, PostgreSQL, OpenAPI/Swagger \\
                \textbf{Cloud \& DevOps:} & AWS, Docker, Azure, Jenkins, Lambda \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Spearheaded development of reusable \textbf{React.js} components improving UI consistency and reducing development time by 30\%.}
        \resumeItem{Implemented \textbf{TypeScript} strict typing and hooks to increase code robustness and lower bugs by 25\%.}
        \resumeItem{Optimized application responsiveness using \textbf{Tailwind CSS} and ensured accessibility compliance, boosting user satisfaction by 20\%.}
        \resumeItem{Streamlined RESTful \textbf{API} integrations and state management reducing data loading times by 35\%.}
        \resumeItem{Collaborated on CI/CD setup using \textbf{Docker} and automated tests with \textbf{Jest}, reducing deployment errors by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{React.js} UI components using functional hooks, improving responsiveness and maintainability by 30\%.}
        \resumeItem{Designed and implemented accessible user interfaces with \textbf{Tailwind CSS}, raising mobile usability scores by 25\%.}
        \resumeItem{Integrated complex RESTful APIs to sync frontend state with backend services, enhancing data accuracy by 20\%.}
        \resumeItem{Utilized \textbf{React Query} for efficient data fetching and caching, reducing redundant API calls by 40\%.}
        \resumeItem{Led front-end testing with \textbf{Jest} and \textbf{React Testing Library}, increasing code coverage to 85\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported front-end development of educational tools using \textbf{React.js} and \textbf{TypeScript}, improving student interface experience by 15\%.}
        \resumeItem{Implemented responsive design and cross-browser compatibility ensuring 100\% accessibility adherence in lab software.}
        \resumeItem{Developed unit and integration tests increasing software reliability and reducing bug reports by 30\%.}
        \resumeItem{Documented technical guides for front-end components to ease troubleshooting and enhance team knowledge.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Upgraded existing front-end using \textbf{Angular.js} enhancing UI performance and raising customer engagement metrics by 25\%.}
        \resumeItem{Developed efficient \textbf{TypeScript} API integration solutions yielding sub-100ms response times improving application fluidity.}
        \resumeItem{Created responsive UI elements using CSS and JavaScript to improve cross-browser compatibility and accessibility standards.}
        \resumeItem{Collaborated with backend engineers to optimize data retrieval, reducing latency by 30\% via \textbf{PostgreSQL} tuning.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and built component-driven \textbf{React.js} front-ends improving page load speeds by 30\% and user experience.}
        \resumeItem{Implemented \textbf{TypeScript} and \textbf{Tailwind CSS} to make responsive interfaces that meet WCAG accessibility guidelines.}
        \resumeItem{Developed \textbf{RESTful APIs} consumption with proper state management, decreasing data errors by 20\%.}
        \resumeItem{Configured \textbf{Docker}-based development and deployment pipelines, accelerating release cycles by 35\%.}
        \resumeItem{Conducted unit testing with \textbf{Jest}, improving component reliability and reducing production bugs by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Smart UI Component Library} | React, TypeScript, Storybook, Tailwind CSS}{}
          \resumeItemListStart
              \resumeItem{Built reusable and accessible UI components with \textbf{React.js} and \textbf{Tailwind CSS}, improving design consistency and development speed by 35\%.}
              \resumeItem{Documented components interactively in \textbf{Storybook} enabling rapid prototyping and reducing onboarding time for new developers by 40\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Bug Detection and Documentation Bot} | OpenAI API, GitHub Actions, TypeScript}{}
          \resumeItemListStart
              \resumeItem{Developed an automated \textbf{AI}-driven pull request reviewer using \textbf{OpenAI API} reducing manual reviews by 50\% and increasing code quality.}
              \resumeItem{Integrated automated \textbf{TypeScript} docstring generation to maintain code documentation, achieving 100\% coverage across new features.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Responsive Dashboard for Home Warranty Platform} | React.js, REST APIs, Tailwind CSS}{}
          \resumeItemListStart
              \resumeItem{Designed a responsive user dashboard with \textbf{React.js} consuming RESTful APIs, increasing user engagement by 30\% on mobile and desktop.}
              \resumeItem{Optimized API data fetching using \textbf{React Query}, boosting application performance and lowering server requests by 40\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}