\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer specializing in high-performance C/C++ development for complex physical design and routing algorithms. Experienced in Linux environments and multi-threaded programming with strong analytical skills. Adept at collaborating with global teams to optimize semiconductor design flows and implement scalable, efficient solutions in cutting-edge IC design contexts.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C, C++, Python, Tcl, Shell Scripting, Java \\
                \textbf{Physical Design Tools:} & Timing Analysis, Routing Algorithms, Physical Synthesis Flows \\
                \textbf{System \& Platforms:} & Linux, Multi-threaded Programming, Distributed Systems \\
                \textbf{Software Engineering:} & Data Structures, Algorithms, Performance Optimization, Debugging \\
                \textbf{Cloud \& DevOps:} & Docker, Jenkins, AWS \\
                \textbf{EDA & IC Design Environment:} & Exposure to EDA Tools, IC Design Methodologies \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and optimized multi-threaded \textbf{C++} algorithms for data processing, improving throughput by 40\% in Linux-based systems.}
        \resumeItem{Engineered scalable software modules focused on routing and synthesis, reducing latency in complex distributed environments by 30\%.}
        \resumeItem{Collaborated cross-functionally with global teams to integrate physical design solutions, enhancing interoperability across multiple semiconductor flows.}
        \resumeItem{Debugged and resolved concurrency issues in large-scale multi-threaded systems, boosting system stability and reducing crashes by 25\%.}
        \resumeItem{Automated test suites using \textbf{Python} and \textbf{Tcl} scripts, increasing testing coverage and reducing manual workload by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented performance critical components in \textbf{C++} that accelerated digital routing workflows by 20\%.}
        \resumeItem{Built automation scripts in \textbf{Python} and \textbf{Tcl} to streamline physical synthesis tasks, improving engineering productivity by 30\%.}
        \resumeItem{Collaborated with engineers to optimize multi-threaded algorithms, resulting in 25\% faster runtimes on Linux platforms.}
        \resumeItem{Created monitoring tools to detect routing inefficiencies, contributing to 15\% improvement in design cycle durations.}
        \resumeItem{Led debugging of complex integration bugs between routing engines and synthesis tools, reducing defect turnaround time by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported Linux infrastructure and assisted debugging of multi-threaded software used to simulate network routing and security scenarios.}
        \resumeItem{Enhanced lab automation scripts in \textbf{Python} to validate system configurations, decreasing setup time by 25\%.}
        \resumeItem{Guided users in performance profiling and optimization for concurrent applications in a distributed environment.}
        \resumeItem{Resolved technical issues involving data structures and algorithmic efficiency, improving lab software reliability by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{C\#} backend components to optimize data routing, achieving a 30\% gain in API response efficiency.}
        \resumeItem{Upgraded performance of distributed system modules on Linux servers, contributing to 15\% reduction in resource utilization.}
        \resumeItem{Collaborated on debugging and improving large-scale database queries, enhancing throughput by 20\%.}
        \resumeItem{Developed and tested automated scripts in \textbf{Python} to support system monitoring and alerting processes.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented multi-threaded \textbf{C++} modules for physical synthesis engines, optimizing critical paths by 35\%.}
        \resumeItem{Participated in developing routing algorithms for IC design environment, boosting design tool accuracy by 18\%.}
        \resumeItem{Built and maintained backend microservices using \textbf{Java Spring Boot} deployed on \textbf{Linux} servers with \textbf{Docker}.}
        \resumeItem{Automated testing and deployment pipelines integrating \textbf{Jenkins} for continuous delivery, reducing deployment errors by 50\%.}
        \resumeItem{Collaborated in global teams to refine data structures and algorithms, enhancing software reliability and scalability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-assisted Routing Optimization} | C++, Python, Linux, Multi-threading}{}
          \resumeItemListStart
              \resumeItem{Developed multi-threaded \textbf{C++} algorithms for optimizing routing paths in IC design, improving runtime efficiency by 30\%.}
              \resumeItem{Implemented \textbf{Python} automation scripts to generate input test cases and analyze performance metrics, reducing manual effort by 40\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Physical Synthesis Automation Framework} | Tcl, Python, C++, Linux}{}
          \resumeItemListStart
              \resumeItem{Built modular \textbf{C++} components integrated with \textbf{Tcl} and \textbf{Python} to automate physical synthesis flows, cutting design cycle time by 25\%.}
              \resumeItem{Developed diagnostic tools to identify synthesis bottlenecks, increasing design throughput and quality by 20\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{AI-Driven Code Analysis Bot} | OpenAI API, GitHub Actions, Python}{}
          \resumeItemListStart
              \resumeItem{Engineered an AI bot leveraging \textbf{OpenAI} models to automatically review \textbf{C++} and \textbf{Python} code, reducing review time by 35\%.}
              \resumeItem{Integrated with \textbf{GitHub Actions} to provide real-time feedback on pull requests, improving code quality and documentation coverage.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}