\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Versatile software engineer specializing in designing, developing, and maintaining scalable \textbf{.NET} applications and APIs. Proficient in object-oriented design principles, relational databases, and delivering robust solutions aligned with business requirements. Experienced collaborating cross-functionally to enhance product quality and optimize deployment workflows in dynamic, agile environments.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\#, Java, Python, JavaScript, TypeScript, SQL \\
                \textbf{Frameworks \& Technologies:} & .NET Framework/Core, ASP.NET, Entity Framework, RESTful APIs, Angular.js, React.js \\
                \textbf{Databases:} & Microsoft SQL Server, MySQL, PostgreSQL, Writing Complex SQL Queries \\
                \textbf{Software Development Practices:} & Object-Oriented Design, Design Patterns, Unit Testing, CI/CD pipelines \\
                \textbf{DevOps \& Tools:} & Git, GitHub, Jenkins, Docker, Azure DevOps, Jira, Visual Studio \\
                \textbf{Cloud Platforms:} & Microsoft Azure, AWS EC2, S3, Lambda \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{C\# .NET Core} services to deliver reliable application modules, improving code reuse by 30\% and accelerating release cycles.}
        \resumeItem{Collaborated closely with product and quality teams to analyze requirements and design scalable features, reducing bugs by 25\%.}
        \resumeItem{Developed and maintained APIs leveraging \textbf{ASP.NET Core}, enhancing data integration capabilities with partner systems by 40\%.}
        \resumeItem{Created automated unit and integration tests, boosting code coverage to above 80\% and minimizing post-release defects.}
        \resumeItem{Provided production support on a rotational basis, troubleshooting complex issues and ensuring 99.9\% uptime SLA compliance.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{API endpoints} using \textbf{.NET Framework 4.8}, improving data throughput by 35\% for client applications.}
        \resumeItem{Refactored legacy components applying OOD principles, enhancing maintainability and reducing technical debt by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to define features and develop robust web solutions using \textbf{React.js} and \textbf{Angular.js}.}
        \resumeItem{Automated deployment pipelines utilizing \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 30\% and improving deployment reliability.}
        \resumeItem{Engaged in continuous improvement of QA environments and assisted in migration contingency planning for major product releases.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments, facilitating reliable hands-on cybersecurity practical sessions for students.}
        \resumeItem{Developed debugging guides and assisted in deployment of lab applications, increasing student project success rates by 20\%.}
        \resumeItem{Authored automated scripts to validate lab assignments, reducing instructor workload by 25\% and increasing grading accuracy.}
        \resumeItem{Conducted webinars explaining secure coding practices and network protocols, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Built and optimized backend components in \textbf{C\# .NET Framework}, decreasing data retrieval latency by 30\% in main platform.}
        \resumeItem{Implemented \textbf{TypeScript}-based API clients achieving sub-100ms response times, improving frontend data access speed.}
        \resumeItem{Enhanced user interface modules using \textbf{Angular.js}, boosting user engagement metrics by 25\% during internship tenure.}
        \resumeItem{Streamlined \textbf{PostgreSQL} database operations and optimized stored procedures, reducing query execution times by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users and fast load times.}
        \resumeItem{Led implementation of \textbf{CI/CD} pipelines using \textbf{Docker} and \textbf{AWS EC2}, reducing deployment errors and downtime by 50\%.}
        \resumeItem{Designed frontend UI components with \textbf{React.js}, improving usability metrics and reducing page load times by 30\%.}
        \resumeItem{Created extensive \textbf{JUnit} unit tests for backend services, achieving 90\% test coverage and smooth feature rollouts.}
        \resumeItem{Analyzed and refactored legacy code modules applying \textbf{OOD} principles, enhancing maintainability and reducing bugs by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Assistant} | GitHub Actions, OpenAI API, .NET Core}{}
          \resumeItemListStart
              \resumeItem{Developed an AI assistant integrating with \textbf{GitHub Actions} to automatically review \textbf{C\#} code and suggest improvements, reducing manual reviews by 40\%.}
              \resumeItem{Automated documentation generation for \textbf{.NET Core} modules using LLMs, improving code clarity and team onboarding efficiency by 35\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{RESTful API for Parts Supply Chain Management} | .NET Core, SQL Server, Azure}{}
          \resumeItemListStart
              \resumeItem{Designed and implemented a scalable \textbf{.NET Core} REST API for automotive parts inventory, improving supply chain data accuracy by 50\%.}
              \resumeItem{Deployed APIs on \textbf{Azure}, enabling real-time parts ordering and tracking, speeding up order processing by 30\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Web-based Repair Estimate Optimizer} | ASP.NET, Angular.js, SQL Server}{}
          \resumeItemListStart
              \resumeItem{Developed an interactive web app combining \textbf{ASP.NET} backend and \textbf{Angular.js} frontend to optimize automotive repair estimates, improving estimate accuracy by 20\%.}
              \resumeItem{Integrated complex SQL queries and design patterns to handle large datasets efficiently, reducing server response times by 25\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}