\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Resourceful software engineer with 5+ years experience developing high-performance C++ libraries and debugging tools for low latency environments. Skilled in building scalable RESTful APIs and cross-platform solutions on Linux and Windows. Adept at collaborating with quant teams to deliver optimized, data-driven trading technology. Proficient in Python automation and market data analysis.

 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C++, Python, C, Shell Scripting, JavaScript, TypeScript \\
                \textbf{Tools \& Frameworks:} & Boost, STL, RESTful APIs, gRPC, Git, Jenkins, Docker \\
                \textbf{Operating Systems:} & Linux, Windows, Unix \\
                \textbf{Data Structures \& Markets:} & Orderbook Management, Market Data Parsing, Low Latency Systems \\
                \textbf{Cloud \& DevOps:} & AWS, Jenkins, Docker, CI/CD Pipelines \\
                \textbf{Collaboration \& Others:} & Agile Methods, Jira, Code Review, Cross-team Communication \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered C++ libraries to parse high-frequency market data with 30\% faster processing speeds for real-time trading applications.}
        \resumeItem{Designed debugging tools that reduced troubleshooting time by 50\% through enhanced traceability and error analysis capabilities.}
        \resumeItem{Developed RESTful service interfaces for C++ applications enabling seamless data integrations in Windows and Linux environments.}
        \resumeItem{Collaborated across teams implementing advanced data structures optimized for low latency and high throughput trading scenarios.}
        \resumeItem{Automated test suites in Python decreasing manual debugging efforts by 40\% while improving code coverage and reliability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built Python and C++ tools for analyzing market data streams that increased decoding accuracy and reduced latency by 25\%.}
        \resumeItem{Integrated orderbook management libraries with frontend applications, achieving 20\% faster updates and improved UI responsiveness.}
        \resumeItem{Optimized multi-platform deployment process, streamlining releases for Linux and Windows with Docker and Jenkins automation.}
        \resumeItem{Partnered with quants to translate trading strategies into efficient software components used firm-wide.}
        \resumeItem{Implemented Python scripts for data validation and automated report generation, cutting manual processing time by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported Linux-based research environments, ensuring stable execution of market data parsing and debugging tools for student projects.}
        \resumeItem{Automated grading scripts using Python that improved evaluation speed and accuracy for data handling assignments by 25\%.}
        \resumeItem{Guided students in debugging and troubleshooting complex C++ and Python software to strengthen their technical problem-solving skills.}
        \resumeItem{Led workshops covering real-world applications of low latency data structures and market analysis techniques.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced backend data processing in C\# .NET, achieving 30\% faster retrieval time for high-volume transactional data sets.}
        \resumeItem{Implemented asynchronous API calls improving reliability and reducing average response latency to under 100ms.}
        \resumeItem{Refactored SQL procedures to streamline data queries, increasing efficiency by 15\% in complex report generation.}
        \resumeItem{Contributed to Angular.js frontend improvements reducing page load times by 20\% and boosting user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed microservices in \textbf{Java Spring Boot} that handled 1000+ concurrent users with sub-200ms response times.}
        \resumeItem{Built RESTful APIs consumed by multiple clients improving cross-team data sharing and real-time communication.}
        \resumeItem{Automated deployment pipelines with \textbf{Docker} and \textbf{Jenkins}, cutting release cycles by 35\%.}
        \resumeItem{Created interactive data visualization components in \textbf{React.js}, enhancing user comprehension of complex datasets by 30\%.}
        \resumeItem{Implemented unit and integration tests achieving 90\% code coverage, reducing production bugs by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Market Data Debugger} | Python, C++, REST API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-driven debugger leveraging \textbf{Python} and \textbf{C++} to quickly identify and resolve market data anomalies, reducing debug time by 45\%.}
              \resumeItem{Integrated RESTful services for real-time data analysis, enabling traders to monitor orderbook states with 30\% improved accuracy and speed.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Low Latency Orderbook Library} | C++, Boost, Linux}{}
          \resumeItemListStart
              \resumeItem{Engineered a high-performance C++ library for orderbook management capable of sustaining sub-millisecond latency in live trading environments.}
              \resumeItem{Optimized data structures and parsing routines achieving 35\% reduction in memory usage and 25\% faster event processing.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cross-Platform Market Data Toolkit} | C++, Python, Jenkins, Docker}{}
          \resumeItemListStart
              \resumeItem{Built tools supporting both Linux and Windows platforms to facilitate market data debugging and analysis, increasing operational efficiency by 40\%.}
              \resumeItem{Automated testing and deployment workflows using \textbf{Jenkins} and \textbf{Docker}, accelerating integration cycles by 30\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}