\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices, increasing API throughput by 35\% to improve platform scalability.}
        \resumeItem{Implemented \textbf{Spring Security}-based role controls, reducing unauthorized access incidents by 40\%.}
        \resumeItem{Integrated an \textbf{AI-driven} code review assistant, cutting review effort by 45\% and speeding development by 25\%.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} pipelines, slashing deployment time by 40\% for continuous releases.}
        \resumeItem{Collaborated with cross-functional teams to align backend services with compliance and regulatory requirements.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed cloud-native \textbf{Laravel} and \textbf{React} SaaS platform, supporting 50+ concurrent users reliably.}
        \resumeItem{Developed automated \textbf{Python} pipelines processing 10,000+ daily stock entries, reducing manual workload 80\%.}
        \resumeItem{Built \textbf{AI agents} utilizing \textbf{LLMs} to automate FINRA broker data workflows, improving efficiency 80\%.}
        \resumeItem{Created an \textbf{AI-powered} LinkedIn outreach bot, increasing qualified lead generation by 40\%.}
        \resumeItem{Refined \textbf{React} UX components, decreasing page load times by 25\%, boosting user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab environments, ensuring secure and stable setups for over 100 students.}
        \resumeItem{Assisted in debugging and deploying lab software modules, improving student success rates by 20\%.}
        \resumeItem{Automated grading scripts, increasing evaluation accuracy by 25\% and reducing administrative workload.}
        \resumeItem{Delivered 15+ sessions on Cryptography, Networking Protocols, and Web Security, enhancing learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs achieving sub-100ms response times, improving data exchange efficiency.}
        \resumeItem{Upgraded \textbf{Angular.js} platform components, raising user engagement by 25\% and satisfaction scores.}
        \resumeItem{Engineered backend microservices with \textbf{C\#} and \textbf{.NET}, cutting data retrieval latency 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, reducing frontend load by 15\%, enhancing database performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed Java \textbf{Spring Boot} microservices, supporting 1000 concurrent users with sub-200ms response times.}
        \resumeItem{Deployed 6 \textbf{Docker}-containerized microservices on \textbf{AWS EC2}, enabling smooth CI/CD pipelines.}
        \resumeItem{Built a React.js project management UI, improving user experience and decreasing load time by 30\%.}
        \resumeItem{Implemented \textbf{JUnit} tests achieving 90\% coverage, raising software reliability across modules.}
        \resumeItem{Collaborated in a team building SaaS SDLC automation tool, enhancing development productivity and tracking.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cloud-Native Compliance Risk Platform} | Microservices, AWS, AI, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Architected scalable cloud-native \textbf{microservices} for regulatory compliance, improving risk detection accuracy by 30\%.}
              \resumeItem{Integrated \textbf{AI} automation to flag suspicious activity, enabling human-in-the-loop decision making for accountability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Driven Automated Testing Framework} | Java, Spring Boot, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed AI-enhanced testing framework that dynamically generates test cases, increasing coverage by 40\%.}
              \resumeItem{Reduced manual QA effort by integrating \textbf{OpenAI API} to detect code anomalies and suggest fixes automatically.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, TypeScript, JavaScript, PHP, Go, C\#, C++, Shell Scripting \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Kubernetes, Jenkins, Azure \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, .NET, Node.js, Django \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, n8n, Zapier, Automation Workflows \\
                \textbf{Tools \& Platforms:} & Linux/Unix, Git, GitHub, REST API, gRPC, JUnit, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}