\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and maintained high-quality \textbf{Java Spring Boot} microservices, improving overall API throughput by 35\%.}
        \resumeItem{Implemented robust authentication and role-based controls using \textbf{Spring Security}, enhancing system security by 40\%.}
        \resumeItem{Integrated an \textbf{AI-driven} code review system that reduced manual review time by 45\% and sped development workflow by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, cutting down deployment times by 40\%.}
        \resumeItem{Collaborated across teams to optimize backend services, improving scalability and reliability in production environments.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered a \textbf{SaaS} data visualization platform with \textbf{Laravel} and \textbf{React}, supporting over 50 simultaneous users.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, processing 10,000+ stock entries, reducing manual effort by 80\%.}
        \resumeItem{Built a multi-tier \textbf{PHP}-based e-commerce platform integrating \textbf{Stripe} for subscriptions and role-based access control.}
        \resumeItem{Implemented AI agents using \textbf{LLMs} for automated data processing, decreasing manual workload by 80\%.}
        \resumeItem{Optimized React components improving page load times by 25\%, boosting user engagement and experience.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} systems for cybersecurity labs, ensuring stable and secure student development environments.}
        \resumeItem{Guided students in debugging and deploying projects, enhancing assignment completion rates by 20\%.}
        \resumeItem{Automated grading workflows that improved evaluation accuracy by 25\%, reducing instructor workload significantly.}
        \resumeItem{Delivered 15+ sessions simplifying complex topics such as Cryptography and Web Security to improve student comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed efficient API calls in \textbf{TypeScript} achieving fast average response times under 100ms to ensure data flow reliability.}
        \resumeItem{Enhanced \textbf{Angular.js} frontend UI, driving a 25\% increase in user engagement and overall client satisfaction.}
        \resumeItem{Implemented high-performance backend API in \textbf{C\#} with \textbf{.NET}, reducing data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures reducing frontend load by 15\%, improving system responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed scalable \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines using \textbf{Docker} on \textbf{AWS EC2}, enabling seamless deployments of key services.}
        \resumeItem{Developed responsive project management UI with \textbf{React.js}, improving page load speed and usability by 30\%.}
        \resumeItem{Authored unit and integration tests covering 90\% of code using \textbf{JUnit}, improving software reliability.}
        \resumeItem{Collaborated with cross-functional teams to deliver new features improving software lifecycle automation efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Quality and Review Bot} | GitHub Actions, OpenAI API, TypeScript}
          \resumeItemListStart
              \resumeItem{Built an AI-driven bot integrating \textbf{GitHub Actions} to automatically review pull requests, reducing manual review time by 25\%.}
              \resumeItem{Automated generation and updating of code documentation, achieving 100\% docstring coverage for all new \textbf{TypeScript} code.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{GraphQL API Integration Platform} | Next.js, TypeScript, GraphQL, Prisma}
          \resumeItemListStart
              \resumeItem{Developed a robust frontend with \textbf{Next.js} and \textbf{TypeScript} consuming \textbf{GraphQL} APIs for seamless data synchronization.}
              \resumeItem{Built reusable UI components to enhance accessibility and responsiveness, improving user engagement by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Customer Support AI Automation Agent} | Gmail API, LLMs, Node.js}
          \resumeItemListStart
              \resumeItem{Created an AI agent using \textbf{LLMs} and \textbf{Gmail API} that automated 60\% of email support responses, reducing response time by 40\%.}
              \resumeItem{Implemented a human-in-the-loop workflow to validate responses for sensitive cases, maintaining high response quality.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, JavaScript, Python, C\#, PHP, Shell Scripting \\
                \textbf{Frontend \& Frameworks:} & Next.js, React.js, Angular.js, Laravel, Node.js \\
                \textbf{Backend \& API Technologies:} & Spring Boot, RESTful APIs, GraphQL, Prisma \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, n8n \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}