\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices with resilience improvements, boosting system uptime by 30\% under high user loads.}
        \resumeItem{Implemented \textbf{Spring Security} to enhance role-based access, decreasing unauthorized access incidents by 35\%.}
        \resumeItem{Deployed an AI-assisted code review tool using \textbf{LLMs}, cutting manual review times by 40\% and improving code quality.}
        \resumeItem{Designed \textbf{Jenkins} and \textbf{Docker}-based CI/CD pipelines, accelerating deployment frequency by 50\% and reducing errors.}
        \resumeItem{Collaborated in Agile teams to deliver scalable APIs, resulting in 25\% better response times and improved customer satisfaction.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed SaaS platform backend using \textbf{GoLang}, supporting data compliance for distributed users across multiple regions.}
        \resumeItem{Automated large-scale stock data ETL pipelines in \textbf{Python}, reducing manual processing by 80\% and speeding up updates.}
        \resumeItem{Built subscription e-commerce platform integrating \textbf{Stripe} with role-based authorization, increasing conversion rates by 20\%.}
        \resumeItem{Integrated AI-powered \textbf{LLM} agents to automate FINRA broker data scraping, improving data accuracy by 35\%.}
        \resumeItem{Enhanced React frontend performance and usability, decreasing load times by 30\% and improving user retention by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based virtual lab infrastructure, ensuring 99.9\% uptime for over 200 users during cybersecurity coursework.}
        \resumeItem{Supported students in troubleshooting network security and cryptography exercises, raising assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts for lab assignments using \textbf{Python}, reducing manual efforts by 40\% and increasing consistency.}
        \resumeItem{Conducted webinars explaining distributed systems and security protocols, enhancing student engagement and knowledge retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed performant backend services in \textbf{C\# .NET} handling real-time data, cutting latency by 30\% in critical workflows.}
        \resumeItem{Optimized API response times below 100ms through efficient \textbf{TypeScript} code enhancements, improving system throughput.}
        \resumeItem{Upgraded frontend modules using \textbf{Angular.js}, resulting in a 25\% rise in user engagement and faster page loads.}
        \resumeItem{Improved complex \textbf{PostgreSQL} queries and stored procedures, reducing data retrieval time by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices supporting 1000 concurrent users with sub-200ms latency.}
        \resumeItem{Designed and implemented \textbf{CI/CD} pipelines using \textbf{Docker} and AWS EC2, improving deployment speed by 35\%.}
        \resumeItem{Created comprehensive REST APIs integrating \textbf{MySQL} databases for data consistency and reliability across distributed services.}
        \resumeItem{Built React-based dashboards with dynamic charts, increasing usability and reducing user navigation time by 30\%.}
        \resumeItem{Produced unit tests with \textbf{JUnit}, attaining 90\% coverage that enhanced reliability and reduced bugs in production.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Distributed System Monitoring} | Kubernetes, Prometheus, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Built an AI-powered monitoring tool using \textbf{Prometheus} and \textbf{OpenAI API} to proactively detect anomalies across distributed services.}
              \resumeItem{Implemented alerting and diagnostic summaries, reducing incident response times by 40\% in a containerized cloud environment.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud Compliance Automation System} | Terraform, AWS, GoLang}{}
          \resumeItemListStart
              \resumeItem{Created an infrastructure-as-code system with \textbf{Terraform} automating compliance enforcement across multiple cloud regions, improving audit readiness by 50\%.}
              \resumeItem{Developed \textbf{GoLang} microservices to validate data placement and access policies, enforcing regulatory standards effectively.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure Multi-Region Data Sharing Service} | Java, Kafka, Oracle Cloud}{}
          \resumeItemListStart
              \resumeItem{Engineered a resilient data sharing platform with \textbf{Java} and \textbf{Kafka}, ensuring secure replication across geographies under compliance constraints.}
              \resumeItem{Optimized message throughput while maintaining data encryption and auditability, improving data processing speed by 30\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Go, Python, TypeScript, C\#, PHP \\
                \textbf{Cloud Platforms \& DevOps:} & AWS, Oracle Cloud Infrastructure (OCI), Azure, Docker, Terraform, Jenkins \\
                \textbf{Distributed Systems \& Networking:} & Kafka, Kubernetes, REST APIs, Microservices Architecture, Load Balancing \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL, NoSQL \\
                \textbf{Security \& Compliance:} & Role-Based Access Control, Spring Security, Data Encryption, Cloud Compliance \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, CI/CD Automation, Infrastructure as Code \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}