\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices performance by 35\% through code optimization and scalability improvements.}
        \resumeItem{Implemented \textbf{Terraform} to automate infrastructure provisioning, reducing deployment time by 50\% and boosting reliability.}
        \resumeItem{Led integration of source code management tools to streamline CI/CD pipelines, decreasing release cycle by 30\%.}
        \resumeItem{Collaborated with DevOps to create monitoring and alerting tools, improving incident response time by 40\%.}
        \resumeItem{Developed secure microservices with \textbf{Spring Security}, reducing unauthorized access incidents by 45\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected cloud-native microservices on \textbf{AWS} with \textbf{Terraform} deployment, supporting 50+ concurrent users flawlessly.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, speeding up deployment frequency by 35\%.}
        \resumeItem{Built scalable data processing pipelines in \textbf{Python}, reducing manual effort by 80\% for stock ingestion tasks.}
        \resumeItem{Developed complex role-based access control using \textbf{React} with seamless OAuth integration, boosting security posture.}
        \resumeItem{Created AI tools with \textbf{LLMs} to automate broker data processing, cutting manual processing time by 75\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based infrastructure ensuring secure lab environments supporting 100+ students during coursework.}
        \resumeItem{Automated grading scripts, raising accuracy by 25\% and reducing manual workload for software debugging assignments.}
        \resumeItem{Provided technical assistance in deploying secure software, increasing assignment success rates by 20\%.}
        \resumeItem{Delivered 15+ educational sessions on Cryptography and Networking, enhancing student understanding and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs achieving sub-100ms response times, enhancing frontend-backend interactions.}
        \resumeItem{Upgraded platform UI with \textbf{Angular.js}, improving user engagement metrics by 25\%.}
        \resumeItem{Built high-performance backend services in \textbf{C\# .NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, cutting frontend load times by 15\% and improving database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices for SaaS platform supporting 1000+ concurrent users with 200ms latency.}
        \resumeItem{Configured and maintained CI/CD pipelines on \textbf{AWS EC2} using \textbf{Docker}, improving deployment reliability.}
        \resumeItem{Designed project management UI in \textbf{React.js}, enhancing usability and reducing load time by 30\%.}
        \resumeItem{Wrote 90\% unit test coverage using \textbf{JUnit} for critical pipeline components, improving code quality.}
        \resumeItem{Implemented microservices aligned to cloud-native best practices focusing on scalability and fault tolerance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-powered Code Quality Analyzer} | GitHub Actions, OpenAI API, Java}{}
          \resumeItemListStart
              \resumeItem{Built \textbf{Java}-based CI tool integrating \textbf{LLMs} to analyze code quality and suggest improvements, reducing review time by 30\%.}
              \resumeItem{Automated documentation generation for Java classes ensuring 100\% compliance with company standards and decreasing manual edits.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud Infrastructure Automation Platform} | Terraform, AWS, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Implemented \textbf{Terraform} modules to automate provisioning and scaling of Kubernetes clusters, reducing manual setup by 60\%.}
              \resumeItem{Developed monitoring integrations for cloud infrastructure enhancing incident response and reducing downtime by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure Microservice CI/CD Pipeline} | Docker, Jenkins, Spring Boot}{}
          \resumeItemListStart
              \resumeItem{Architected secure \textbf{CI/CD} pipelines using \textbf{Jenkins}, \textbf{Docker}, and \textbf{Spring Boot} services for fast, reliable deployments.}
              \resumeItem{Designed microservices system following distributed architecture principles, improving scalability and fault tolerance by 35\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, TypeScript, C\#, Bash, Ruby \\
                \textbf{Cloud Platforms \& Infra:} & Oracle Cloud Infrastructure (OCI), AWS, Azure, Google Cloud Platform, Terraform \\
                \textbf{DevOps \& CI/CD Tools:} & Jenkins, Docker, Kubernetes, GitHub Actions, Terraform, Jenkins \\
                \textbf{Frameworks \& Architectures:} & Spring Boot, React.js, Microservices Architecture, REST API, gRPC \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Automation Scripting \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}