\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Node.js/TypeScript} backend microservices, enhancing API response times by 40\% to support scalable operations.}
        \resumeItem{Refined payment and subscription management APIs, improving payment success rates by 30\% while ensuring seamless user experience.}
        \resumeItem{Collaborated to integrate \textbf{GCP} cloud functions for real-time analytics, boosting system throughput by 25\%.}
        \resumeItem{Automated deployment pipelines using \textbf{Docker} containers, accelerating release cycles by 35\% and reducing downtime.}
        \resumeItem{Led API architecture improvements for enhanced maintainability and performance, boosting service reliability by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed subscription and payment APIs with \textbf{Node.js}, increasing subscription processing speed by 30\%.}
        \resumeItem{Implemented containerized microservices using \textbf{Docker}, improving deployment consistency across environments by 40\%.}
        \resumeItem{Enhanced backend systems on \textbf{GCP} and \textbf{AWS}, reducing service latency by 25\% with autoscaling optimizations.}
        \resumeItem{Devised customizable B2B backend solutions, improving enterprise client integrations and satisfaction by 35\%.}
        \resumeItem{Streamlined authentication flows using secure token management, reducing unauthorized access issues by 45\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based backend infrastructure, ensuring uptime and security compliance for student cybersecurity labs.}
        \resumeItem{Automated data collection and grading scripts to improve throughput by 30\% and consistency of assignment evaluations.}
        \resumeItem{Guided students in deploying secure backend services improving assignment success and debugging efficiency by 20\%.}
        \resumeItem{Hosted webinars to educate students on advanced cybersecurity protocols, enhancing class engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Built RESTful APIs using \textbf{TypeScript}, improving data fetch speeds by 35\% and reliability for frontend use.}
        \resumeItem{Contributed to backend optimization in \textbf{C\# .NET}, decreasing data processing times by 30\%.}
        \resumeItem{Refined \textbf{PostgreSQL} queries, reducing database load by 20\% and improving retrieval efficiency.}
        \resumeItem{Upgraded UI components with \textbf{Angular.js}, increasing user satisfaction and engagement metrics by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable backend microservices with \textbf{Spring Boot} and \textbf{MySQL}, supporting 1000+ concurrent users with 99.9\% uptime.}
        \resumeItem{Created and maintained CI/CD pipelines deploying \textbf{Docker}-based services on \textbf{AWS EC2}, reducing downtime by 30\%.}
        \resumeItem{Designed and integrated authentication and subscription management APIs to support secure enterprise client onboarding.}
        \resumeItem{Implemented Kubernetes orchestration in staging environments to simulate production scalability requirements effectively.}
        \resumeItem{Increased system performance by optimizing backend architecture and reducing average API latency by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Backend API Monitor} | Node.js, TypeScript, OpenAI API, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Created an AI agent that monitors backend APIs' performance and error logs, automating issue detection and reducing downtime by 30\%.}
              \resumeItem{Integrated \textbf{OpenAI} for anomaly detection and automated alerting, increasing system reliability and faster incident responses.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Text-to-Speech API Platform} | Node.js, GCP, Docker, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Built a high-availability \textbf{TTS API} service deployed on \textbf{GCP} with \textbf{Kubernetes}, handling 1000+ requests per minute with sub-second latency.}
              \resumeItem{Configured containerized deployments improving release agility by 40\% and enabling zero-downtime updates in production.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Subscription and Payment Microservice} | Node.js, Stripe API, Docker, GCP}{}
          \resumeItemListStart
              \resumeItem{Developed a robust subscription payment microservice using \textbf{Node.js} and \textbf{Stripe} handling $>$10,000 transactions monthly with 99.95\% uptime.}
              \resumeItem{Containerized the service with \textbf{Docker} and designed scalable backend architecture on \textbf{GCP}, reducing failure rates by 20\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & TypeScript, Java, Python, JavaScript, C\#, PHP, Go \\
                \textbf{Backend Frameworks \& APIs:} & Node.js, Spring Boot, REST API, gRPC, Stripe API \\
                \textbf{Cloud Platforms \& DevOps:} & GCP, AWS, Azure, Docker, Kubernetes, Jenkins, CI/CD \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Web Technologies:} & React.js, Angular.js, Laravel, .NET \\
                \textbf{Tools \& Technologies:} & Linux/Unix, Git, GitHub, JSON, Jira, JUnit \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}