\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Automated critical internal workflows using \textbf{Python} scripting, increasing operational efficiency by 40\% and reducing manual errors.}
        \resumeItem{Enhanced system scalability by refactoring \textbf{Java Spring Boot} microservices, improving throughput by 35\% under peak loads.}
        \resumeItem{Designed robust validation scripts to ensure data integrity across \textbf{API} services, reducing data quality issues by 30\%.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, accelerating deployment frequency by 40\%.}
        \resumeItem{Collaborated with senior engineers to document reusable automation playbooks, simplifying onboarding and knowledge transfer processes.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed automated \textbf{Python} data pipelines handling over 10,000 records daily, cutting manual workload by 80\%.}
        \resumeItem{Integrated AI-driven automation agents leveraging \textbf{LLMs} to execute data extraction workflows, reducing manual steps by 70\%.}
        \resumeItem{Built scalable React front-end components, improving load times by 25\% and enhancing user experience.}
        \resumeItem{Automated LinkedIn outreach via custom bots, increasing qualified leads by 40\% through targeted content posting.}
        \resumeItem{Implemented role-based access control for subscription services using \textbf{PHP} and \textbf{Stripe} payment gateway, supporting secure user authentication.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Automated test grading using \textbf{Python} scripts, raising grading accuracy by 25\% and saving substantial manual effort.}
        \resumeItem{Maintained \textbf{Linux} infrastructure ensuring secure lab environments, improving system uptime and student access reliability.}
        \resumeItem{Developed data validation scripts to verify lab results, reducing errors and streamlining student feedback cycles by 15\%.}
        \resumeItem{Provided technical assistance on debugging and deploying security modules, improving student project success rates by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Automated backend workflows using \textbf{TypeScript} and \textbf{Angular.js}, improving data processing speed by 25\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, cutting frontend latency by 15\% and boosting responsiveness.}
        \resumeItem{Developed C\# modules on \textbf{.NET} to enhance system test automation, decreasing test execution time by 30\%.}
        \resumeItem{Collaborated on API design ensuring reliable data exchange with average response times below 100ms.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered microservices using \textbf{Java Spring Boot} to support 1000+ concurrent users, reducing response time below 200ms.}
        \resumeItem{Structured CI/CD pipelines with \textbf{Docker} containers on \textbf{AWS EC2}, improving deployment reliability by 35\%.}
        \resumeItem{Developed reusable automation scripts to replace manual testing workflows, cutting process time by 40\%.}
        \resumeItem{Built interactive React UIs, enhancing system maintainability and reducing page load latency by 30\%.}
        \resumeItem{Implemented unit and integration tests with \textbf{JUnit}, increasing code coverage to 90\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Automation Script Generator} | Python, OpenAI API, Automation}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-powered tool that generates reusable automation scripts, reducing manual coding effort by 50\% in workflow automation.}
              \resumeItem{Integrated data validation features to ensure automated pipeline accuracy and consistent data quality across processes.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable EC2-Based Automation Infrastructure} | AWS EC2, S3, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Implemented a scalable automation backend on \textbf{EC2} with decoupled messaging queues, handling 1000+ concurrent jobs efficiently.}
              \resumeItem{Applied robust data validation and error handling to maintain system reliability and performance at scale.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{CI/CD Enhanced AI Code Review Bot} | GitHub Actions, Python, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Created a \textbf{CI/CD} pipeline integrating an AI-driven code review bot that flags issues and suggests fixes, reducing manual reviews by 30\%.}
              \resumeItem{Automated documentation generation to maintain 100\% code coverage and enhance maintenance workflows.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Scripting \& Programming:} & Python, Bash, Java, JavaScript, TypeScript, C\#, Shell Scripting \\
                \textbf{Automation \& DevOps:} & Jenkins, Docker, AWS (EC2, S3, Lambda), CI/CD Pipelines, Infrastructure-as-Code \\
                \textbf{Web Technologies:} & React.js, Angular.js, Spring Boot, Laravel, .NET \\
                \textbf{Data \& Databases:} & MySQL, PostgreSQL, DynamoDB, MongoDB, Data Validation \\
                \textbf{Operating Systems \& Tools:} & Linux/Unix, Git, GitHub, REST APIs, JSON, Jira \\
                \textbf{AI \& Automation Frameworks:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, n8n, Zapier \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}