\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Improved \textbf{API} reliability by 35\% through optimizing \textbf{Java Spring Boot} microservices supporting scalable customer solutions.}
        \resumeItem{Enhanced security by reducing unauthorized access attempts 40\% via tighter \textbf{Spring Security} authentication and role-based access controls.}
        \resumeItem{Designed and integrated an \textbf{AI-driven} code review assistant using \textbf{LLMs}, accelerating development speed by 25\%.}
        \resumeItem{Automated deployment pipelines employing \textbf{Jenkins} and \textbf{Docker}, cutting release processes by 40\%.}
        \resumeItem{Collaborated with team members to identify and fix system production issues, boosting system uptime by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a multi-user \textbf{SaaS} platform using \textbf{Laravel} and \textbf{React} that enhanced user engagement by 30\%.}
        \resumeItem{Automated daily data processing pipelines in \textbf{Python}, increasing data accuracy and reducing manual effort by 80\%.}
        \resumeItem{Created role-based e-commerce subscription modules with \textbf{PHP}, improving subscription conversion rates by 15\%.}
        \resumeItem{Leveraged \textbf{LLMs} to build AI agents automating broker data processing, decreasing manual processing time by 80\%.}
        \resumeItem{Refined \textbf{React} front-end components, decreasing page load times by 25\% and enhancing customer satisfaction metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Secured \textbf{Linux}-based lab environments ensuring safe execution and reducing system vulnerabilities by 15\%.}
        \resumeItem{Mentored students to debug and deploy software modules, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts, increasing evaluation accuracy by 25\% and reducing manual workload significantly.}
        \resumeItem{Hosted 15+ sessions explaining cybersecurity concepts, boosting student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Reduced API response times by 15\% through optimized asynchronous calls developed using \textbf{TypeScript}.}
        \resumeItem{Implemented front-end improvements in \textbf{Angular.js}, enhancing user engagement by 25\%.}
        \resumeItem{Built and optimized backend services in \textbf{C\#} and \textbf{.NET}, cutting data retrieval latency by 30\%.}
        \resumeItem{Improved \textbf{PostgreSQL} stored procedures reducing frontend load by 15\% enhancing platform efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices handling 1000+ concurrent users with sub-200ms response times improving reliability.}
        \resumeItem{Collaborated on a team to design and deploy SaaS tooling automating key \textbf{SDLC} processes, reducing development cycle by 30\%.}
        \resumeItem{Developed \textbf{React.js} UI components increasing application usability and decreasing page load times by 30\%.}
        \resumeItem{Built CI/CD workflows using \textbf{Docker} and \textbf{AWS EC2} improving deployment efficiency and reducing downtime.}
        \resumeItem{Achieved 90\% unit test coverage for core modules using \textbf{JUnit} enhancing code quality and maintenance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Pull Request Code Review Tool} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Created an automated code review tool leveraging \textbf{LLMs} that analyzes pull requests and suggests improvements, reducing manual reviews by 25\%.}
              \resumeItem{Implemented docstring generation ensuring 100\% documentation coverage for Python code, improving project maintainability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Customer Support Email Automation Agent} | Gmail API, n8n Automation, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed an AI agent automating classification and response for 60\% of common support emails, reducing response time by 40\%.}
              \resumeItem{Designed HITL workflows for sensitive cases to maintain high accuracy while optimizing support team workload.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Real-Time Face Recognition Service} | AWS EC2, S3, SQS, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Engineered scalable face recognition infrastructure on \textbf{AWS EC2} with asynchronous queuing reducing processing latency to under 60 seconds.}
              \resumeItem{Implemented data persistence on \textbf{S3}, allowing reliable and fast access to images and results across services.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, PHP, C\#, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Ruby on Rails, React.js, React Native, Laravel, Angular.js, Spring Boot \\
                \textbf{Database \& Data Storage:} & MySQL, PostgreSQL, MongoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, GitHub Actions \\
                \textbf{Tools \& Technologies:} & Git, REST API, CI/CD, Agile Methodologies, Jira \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, n8n, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}