\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered and deployed microservices using \textbf{Java Spring Boot}, increasing API throughput by 35\% through optimized performance.}
        \resumeItem{Implemented robust authentication with \textbf{Spring Security}, reducing unauthorized accesses by 40\% via role-based controls.}
        \resumeItem{Integrated an \textbf{AI-driven} code review assistant leveraging \textbf{LLMs}, cutting manual review time by 45\% and speeding development by 25\%.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} pipelines to enhance build and deployment speeds, decreasing release timelines by 40\%.}
        \resumeItem{Collaborated on CI pipeline improvements, increasing deployment reliability and supporting on-call operational needs independently.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{SaaS} platform with \textbf{Laravel} and \textbf{React}, enabling 50+ users to visualize data concurrently without performance degradation.}
        \resumeItem{Automated daily data ingestion pipelines in \textbf{Python}, processing 10,000+ stock entries and reducing manual workload by 80\%.}
        \resumeItem{Developed a multi-tier subscription platform using \textbf{PHP} integrating \textbf{Stripe}, providing secure role-based subscription management.}
        \resumeItem{Built AI-powered \textbf{LLM} agents to fully automate FINRA broker data retrieval processes, cutting manual efforts by 80\%.}
        \resumeItem{Enhanced \textbf{React} components and states, decreasing page load times by 25\% and improving user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and troubleshot \textbf{Linux}-based cybersecurity labs, ensuring stable and secure software development environments.}
        \resumeItem{Mentored students in debugging and deploying software modules, improving assignment completion success rates by 20\%.}
        \resumeItem{Created automated grading scripts that elevated accuracy by 25\% and reduced manual review labor in coursework evaluation.}
        \resumeItem{Delivered over 15 instructional sessions covering cryptography, networking protocols, and web security concepts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed high-performance API calls in \textbf{TypeScript} achieving sub-100ms response times and smooth data integration.}
        \resumeItem{Refined front-end features using \textbf{Angular.js}, boosting user engagement and satisfaction by 25\%.}
        \resumeItem{Implemented backend optimizations in \textbf{C\#} with \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, improving data handling efficiency and cutting frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Co-developed a \textbf{SaaS} tool automating \textbf{SDLC} processes with a collaborative 5-member cross-functional team.}
        \resumeItem{Designed responsive UIs in \textbf{React.js} improving project tracking usability and page load speed by 30\%.}
        \resumeItem{Built scalable \textbf{Spring Boot} microservices integrated with \textbf{MySQL} supporting 1000+ users with response times under 200ms.}
        \resumeItem{Implemented and maintained \textbf{CI/CD} pipelines using \textbf{Docker} on AWS EC2, ensuring seamless microservice deployments.}
        \resumeItem{Developed unit tests for pipelines module with \textbf{JUnit}, achieving approximately 90\% code coverage and higher reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Feature Validation System} | React, GraphQL, Typescript, PostgreSQL}{}
          \resumeItemListStart
              \resumeItem{Built a full-stack system using \textbf{React} and \textbf{GraphQL} to validate new features with 95\% test coverage, accelerating release confidence.}
              \resumeItem{Automated real-time feature flag tracking and rollback in a \textbf{PostgreSQL}-backed database, reducing production issues by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Based Code Review Assistant} | GitHub API, OpenAI API, CI/CD}{}
          \resumeItemListStart
              \resumeItem{Developed an \textbf{AI-driven} pull request reviewer integrating \textbf{OpenAI API} to detect bugs and enforce style guidelines, cutting manual reviews 25\%.}
              \resumeItem{Implemented CI/CD pipeline hooks to automate documentation generation and ensure 100\% code comment coverage for new features.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Reusable Launch Data Tracker} | Next.js, Typescript, GraphQL, Postgres}{}
          \resumeItemListStart
              \resumeItem{Created a data tracking dashboard in \textbf{Next.js} with \textbf{GraphQL} backend, improving hardware test reporting speed by 40\%.}
              \resumeItem{Integrated automated test result ingestion and visualization, enabling rapid iteration cycles in reusable launch vehicle development.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, Python, JavaScript, C\#, PHP, Go, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Next.js, GraphQL, Spring Boot, Laravel, Angular.js, Node.js \\
                \textbf{Databases \& Data Storage:} & PostgreSQL, MySQL, MongoDB, SQL, DynamoDB \\
                \textbf{DevOps \& CI/CD:} & Docker, Jenkins, AWS (EC2, S3, Lambda), GitHub Actions, CI Pipeline Management \\
                \textbf{Tools \& Others:} & Linux/Unix, Git, REST API, JUnit, Jira, Agile \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, Automation Tools \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}