\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices to automate data aggregation, increasing data throughput by 35\% for forecasting models.}
        \resumeItem{Implemented role-based access control with \textbf{Spring Security}, reducing unauthorized access incidents in data pipelines by 40\%.}
        \resumeItem{Developed an \textbf{AI-driven} reporting assistant that auto-generates data insights, decreasing manual report prep time by 45\%.}
        \resumeItem{Built automated \textbf{Jenkins} and \textbf{Docker} pipelines, accelerating data deployment and reducing release time by 40\%.}
        \resumeItem{Collaborated on ETL process enhancements, integrating multiple \textbf{SQL} sources to enable real-time campaign optimization dashboards.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{SaaS} solution leveraging \textbf{Laravel} and \textbf{React} for multi-source data aggregation, supporting 50+ concurrent sessions.}
        \resumeItem{Automated large-scale data processing pipelines in \textbf{Python}, managing 10,000+ daily records with 80\% reduction in manual effort.}
        \resumeItem{Integrated \textbf{AI agents} using \textbf{LLMs} to automate data extraction and classification from stock datasets, boosting processing speed by 80\%.}
        \resumeItem{Deployed an \textbf{AI-powered} outreach bot leveraging \textbf{React} and \textbf{LLMs}, increasing lead capture by 40\%.}
        \resumeItem{Optimized \textbf{React} component performance, lowering page load times by 25\% and enhancing user interaction metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments supporting research in data modeling and statistical analysis tools.}
        \resumeItem{Assisted students in debugging and testing software modules involving \textbf{SQL} and data management queries, improving accuracy by 20\%.}
        \resumeItem{Automated grading scripts validating statistical models, raising grading efficiency and accuracy by 25\%.}
        \resumeItem{Conducted workshops on mathematical modeling, data querying, and business intelligence concepts for 60+ students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls to retrieve large datasets, reducing response latency to under 100ms.}
        \resumeItem{Refined \textbf{Angular.js} components to enhance dashboard responsiveness for multi-dimensional data visualization, lifting engagement by 25\%.}
        \resumeItem{Developed \textbf{C\#} backend logic for automated reporting, lowering data retrieval times by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries to streamline data ingestion, improving frontend load speeds by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Spring Boot} microservices backed by \textbf{MySQL} to process multidimensional data supporting forecasting models, serving 1000+ concurrent users.}
        \resumeItem{Designed and executed ETL workflows for large datasets, improving data accuracy and reducing processing time by 30\%.}
        \resumeItem{Orchestrated \textbf{CI/CD} pipelines enabling rapid deployment of key analytics services on \textbf{AWS EC2} using \textbf{Docker}.}
        \resumeItem{Created frontend dashboards with \textbf{React.js} to visualize complex business intelligence metrics, boosting user adoption by 30\%.}
        \resumeItem{Implemented automated unit tests for data transformation modules, achieving 90\% code coverage with \textbf{JUnit}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enabled Business Forecasting Model} | R, Python, SQL, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed statistical forecasting models using \textbf{R} and \textbf{Python} to predict sales trends, improving forecast accuracy by 20\%.}
              \resumeItem{Automated ETL workflows integrating multi-source datasets in \textbf{SQL} to enable real-time data refresh and business decision support.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated Campaign Optimization Tool} | SQL, Oracle, ETL, Tableau}{}
          \resumeItemListStart
              \resumeItem{Engineered ETL pipelines using \textbf{Oracle} and \textbf{SQL} to consolidate campaign data, reducing reporting latency by 30\%.}
              \resumeItem{Built interactive \textbf{Tableau} dashboards delivering real-time optimization recommendations, enhancing campaign ROI by 15\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Data Insight Agent} | OpenAI API, Python, LLMs}{}
          \resumeItemListStart
              \resumeItem{Created an AI agent using \textbf{OpenAI API} to analyze large datasets and generate actionable business intelligence reports, cutting analysis time by 50\%.}
              \resumeItem{Integrated natural language queries enabling non-technical users to extract insights from complex multi-dimensional data sources effortlessly.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, SQL, R, Java, JavaScript, TypeScript, C\# \\
                \textbf{Data Analysis \& BI Tools:} & Oracle, ETL, Tableau, SAS, SPSS, STATA \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel \\
                \textbf{Database \& Data Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, AI Agents, Automated Reporting Pipelines \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}