\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices ensuring 35\% API throughput increase and high availability for distributed environments.}
        \resumeItem{Implemented role-based access control with \textbf{Spring Security}, reducing unauthorized access incidents by 40\%.}
        \resumeItem{Deployed an AI-based code review assistant leveraging \textbf{LLMs}, automating 45\% of code review tasks and accelerating releases by 25\%.}
        \resumeItem{Automated CI/CD processes with \textbf{Jenkins} and \textbf{Docker}, cutting deployment time by 40\% and increasing pipeline reliability.}
        \resumeItem{Collaborated cross-functionally to design scalable web service infrastructure supporting concurrent users and robust debugging tools.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a scalable SaaS platform with \textbf{React} and \textbf{Laravel}, supporting 50+ concurrent users with role-based access management.}
        \resumeItem{Developed \textbf{Python} pipelines processing 10,000+ daily stock entries, automating manual workflows and increasing efficiency 80\%.}
        \resumeItem{Built AI-powered \textbf{LLM} agents automating FINRA broker data downloads, reducing manual processing efforts by 80\%.}
        \resumeItem{Improved \textbf{React} components and optimized state management, decreasing page load times by 25\% and boosting engagement.}
        \resumeItem{Implemented an AI-driven LinkedIn outreach tool automating content posting, increasing qualified lead generation by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and debugged \textbf{Linux}-based cybersecurity lab infrastructure, ensuring continuous secure operations and environment stability.}
        \resumeItem{Supported students in testing and deploying software modules, improving assignment completion rates by 20\%.}
        \resumeItem{Automated grading workflows using scripts, reducing manual grading time and increasing result accuracy by 25\%.}
        \resumeItem{Conducted 15+ sessions explaining secure coding, cryptography, and networking protocols, enhancing student understanding and performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed efficient \textbf{TypeScript} API calls achieving sub-100ms response times and reliable data flows across services.}
        \resumeItem{Enhanced \textbf{Angular.js} frontend, increasing user engagement by 25\% and improving UI responsiveness.}
        \resumeItem{Implemented backend services using \textbf{C\# .NET}, decreasing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} database queries reducing frontend load by 15\% and improving overall system throughput.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices optimized for concurrency with sub-200ms response times for 1000+ users.}
        \resumeItem{Designed and deployed \textbf{Docker}-based CI/CD pipelines on \textbf{AWS EC2}, enabling zero-downtime deployments.}
        \resumeItem{Built user-friendly project management UIs in \textbf{React.js}, increasing page load speed and usability by 30\%.}
        \resumeItem{Implemented 90\% unit test coverage with \textbf{JUnit} improving pipeline stability and code quality assurance.}
        \resumeItem{Collaborated on full lifecycle infrastructure projects incorporating distributed microservice architectures and scalable backend systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Microservice Performance Optimizer} | Kubernetes, Java, Python}
          {}
          \resumeItemListStart
              \resumeItem{Developed AI-based monitoring microservice using \textbf{Python} to analyze \textbf{Java} service metrics, improving scalability by 30\%.}
              \resumeItem{Implemented auto-tuning algorithms optimizing microservice resource allocation, reducing cloud costs by 20\% while maintaining reliability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Elastic Data Visualization Dashboard} | React, Elasticsearch, Kibana}
          {}
          \resumeItemListStart
              \resumeItem{Built a scalable dashboard integrating \textbf{Elasticsearch} and \textbf{Kibana} for real-time data tracking with 99.9\% uptime.}
              \resumeItem{Designed microservice APIs enabling multi-team access to visualized engineering data, improving operational insights by 40\%.}
              \resumeItem{Optimized data ingestion pipeline decreasing latency by 25\% while supporting distributed and concurrent user access globally.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, JavaScript, TypeScript, C\#, PHP, Go, C++, Shell Scripting \\
                \textbf{Web Frameworks \& Libraries:} & Spring Boot, React.js, Node.js, Angular.js, Laravel, Django, .NET \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, SQL, DynamoDB, Hadoop, Spark \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Kubernetes, Azure \\
                \textbf{Distributed Systems \& Messaging:} & Kafka, Elasticsearch, Kibana, Logstash \\
                \textbf{AI \& Automation:} & LLMs, OpenAI API, AI Agents, n8n, Zapier, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}