\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable microservices in \textbf{Java Spring Boot} improving API response times by 35\% to optimize platform performance.}
        \resumeItem{Implemented \textbf{Spring Security} enhancements, reducing unauthorized access attempts by 40\% through improved authentication controls.}
        \resumeItem{Deployed an AI-driven code review assistant using \textbf{LLMs}, reducing manual review effort by 45\% and accelerating code quality improvements.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, decreasing deployment cycle duration by 40\%.}
        \resumeItem{Collaborated cross-functionally to integrate frontend and backend systems, ensuring seamless data flow and improving user experience.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and built a responsive \textbf{React} web dashboard, enhancing real-time data visibility and supporting 50+ concurrent users.}
        \resumeItem{Automated daily data processing pipelines in \textbf{Python}, reducing manual workload by 80\% and improving accuracy.}
        \resumeItem{Developed role-based subscription access with \textbf{PHP} and \textbf{Stripe}, increasing subscription uptake by 30\%.}
        \resumeItem{Optimized \textbf{React} components and managed state efficiently, cutting page load times by 25\% and improving engagement.}
        \resumeItem{Implemented AI-powered LinkedIn outreach bot using \textbf{LLMs}, generating 40\% more qualified sales leads through automation.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Secured and maintained \textbf{Linux}-based lab environments, enhancing reliability and safeguarding against cybersecurity threats.}
        \resumeItem{Assisted students with debugging and deployment, improving lab assignment success rate by 20\%.}
        \resumeItem{Automated grading using custom scripts, increasing accuracy by 25\% and reducing manual workload significantly.}
        \resumeItem{Led 15+ interactive sessions on networking protocols, cryptography, and web security concepts improving student comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed low-latency API calls with \textbf{TypeScript} achieving sub-100ms response times and enhancing frontend responsiveness.}
        \resumeItem{Revamped legacy \textbf{Angular.js} platform, increasing user engagement and satisfaction by 25\% with improved UI/UX.}
        \resumeItem{Constructed backend microservices in \textbf{C\# .NET} optimizing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing database load by 15\% and improving application efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL} serving 1000+ users with response times below 200ms.}
        \resumeItem{Built project management UI in \textbf{React.js}, improving load speed by 30\% and enhancing overall user experience.}
        \resumeItem{Configured \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} using \textbf{Docker}, enabling robust releases.}
        \resumeItem{Implemented unit testing using \textbf{JUnit} with 90\% code coverage enhancing system reliability and maintainability.}
        \resumeItem{Collaborated in cross-functional teams executing full software development lifecycle adhering to Agile methodologies.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Interactive UX Insight Tool} | Angular, TypeScript, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Created an Angular-based tool that uses \textbf{OpenAI API} to gather real-time user interaction metrics, improving UX decisions by 30\%.}
              \resumeItem{Integrated asynchronous \textbf{RESTful API} calls to fetch and display dynamic simulation data with under 150ms latency across interfaces.}
              \resumeItem{Applied modern UX/UI design patterns to deliver responsive, visually appealing interfaces enhancing user satisfaction scores.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Real-Time Data Center Simulation Dashboard} | Angular, CSS3, TypeScript}{}
          \resumeItemListStart
              \resumeItem{Developed a responsive Angular frontend to visualize complex data center simulation models, reducing load times by 25\%.}
              \resumeItem{Collaborated with backend teams to integrate APIs, ensuring seamless, error-free data flows improving reliability by 40\%.}
              \resumeItem{Conducted usability testing sessions and implemented iterative enhancements, boosting user task completion efficiency by 20\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, JavaScript, Python, C\#, PHP \\
                \textbf{Frontend \& Frameworks:} & Angular, React.js, HTML5, CSS3, Angular.js \\
                \textbf{Backend \& API:} & Spring Boot, Node.js, RESTful APIs, .NET, Laravel \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{DevOps \& Tools:} & Docker, Jenkins, Git, AWS EC2, GitHub Actions \\
                \textbf{Security \& Protocols:} & OAuth, XSS Prevention, SQL Injection Mitigation, Linux Networking \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}