\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered multi-threaded system components in \textbf{C++} improving service latency by 30\% while maintaining reliability under high load.}
        \resumeItem{Developed and optimized video decoding pipelines achieving 20\% higher frame rates and smoother playback on diverse client devices.}
        \resumeItem{Collaborated on WebRTC integration improving streaming QoS and reducing end-to-end latency by 25\% for video applications.}
        \resumeItem{Conducted performance analysis on CPU/GPU utilization to identify bottlenecks, decreasing resource consumption by 15\%.}
        \resumeItem{Automated telemetry data collection and visualization, enabling proactive streaming performance enhancements and user experience improvements.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented optimized media capture and codec pipelines in \textbf{C++}, improving video quality with 18\% reduced latency.}
        \resumeItem{Enhanced network protocol handling for video streaming, enabling 35\% better resilience across variable connections using \textbf{WebRTC}.}
        \resumeItem{Built cross-platform input device support modules including HID and Xinput, improving client compatibility by 40\%.}
        \resumeItem{Developed custom streaming client features focused on scalability and reliability, supporting a 2x increase in concurrent users.}
        \resumeItem{Implemented performance metric frameworks that monitored streaming bottlenecks, driving iterative improvements in latency reduction.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained Linux-based lab systems and enhanced network security, reducing unauthorized access attempts by 15\%.}
        \resumeItem{Automated grading processes for network protocol assignments using scripting, decreasing grading time by 30\%.}
        \resumeItem{Provided debugging and deployment assistance to students that increased assignment success rate by 20\%.}
        \resumeItem{Led 15+ sessions explaining video streaming protocols and secure system design, improving student comprehension significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized backend services in \textbf{C\#} using asynchronous programming, reducing API response times by 30\%.}
        \resumeItem{Enhanced front-end components with \textbf{TypeScript} and \textbf{Angular.js}, improving user data handling and responsiveness by 25\%.}
        \resumeItem{Refined PostgreSQL database queries decreasing frontend load times by 15\% and improving overall system efficiency.}
        \resumeItem{Implemented WebRTC-based video call features to improve real-time client communications with sub-100ms latency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices in \textbf{Java} with \textbf{Spring Boot}, reducing system response times below 200ms for 1000+ users.}
        \resumeItem{Led integration of video streaming modules improving codec compatibility and reducing latency by 18\% across client platforms.}
        \resumeItem{Automated deployment using \textbf{Docker} and AWS EC2, enhancing CI/CD efficiency and cutting release time by 35\%.}
        \resumeItem{Created React-based UI optimizations improving video playback controls and state management, increasing user engagement by 30\%.}
        \resumeItem{Implemented comprehensive unit tests achieving 90\% coverage and ensuring robust streaming and codec pipeline stability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enhanced Streaming Latency Analyzer} $|$ Python, WebRTC, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-powered tool that analyzes streaming latency metrics leveraging \textbf{OpenAI API} to suggest performance tuning strategies.}
              \resumeItem{Built a dashboard integrating telemetry and visualization to monitor video quality and network resilience in real-time.}
              \resumeItem{Achieved 25\% reduced end-to-end latency on test streams by implementing AI-derived optimizations in multiple pipeline stages.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cross-Platform Video Streaming Client} $|$ C++, WebRTC, HID, Xinput}{}
          \resumeItemListStart
              \resumeItem{Engineered a custom streaming client supporting \textbf{WebRTC} and multiple input devices like HID and Xinput, improving device compatibility by 40\%.}
              \resumeItem{Optimized video decode and render pipelines that decreased latency by 20\% while maintaining high-definition streaming quality.}
              \resumeItem{Implemented network handshake protocols to enhance session initiation robustness and reduce connection delays by 15\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& System Software:} & C, C++, Java, Python, C\#, JavaScript, TypeScript \\
                \textbf{Streaming \& Media Technologies:} & WebRTC, Video Codec Pipelines, Audio/Video Decode & Render, HID, Xinput \\
                \textbf{Networking \& Protocols:} & WebRTC, TCP/IP, UDP, Network Resilience, Handshake Protocols \\
                \textbf{Development Tools \& Frameworks:} & Spring Boot, React.js, Angular.js, Docker, Jenkins, AWS, Linux/Unix \\
                \textbf{Testing \& Performance Analysis:} & Multi-threaded Programming, Profiling, Telemetry, Visualization Tools \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, Automation of Performance Tuning, AI Agents \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}