\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Angular} frontend components improving responsiveness and enhancing user interactions, boosting average session times by 25\%.}
        \resumeItem{Collaborated with product team to integrate RESTful APIs, ensuring seamless data flow and reducing frontend latency by 30\%.}
        \resumeItem{Optimized application load times and minimized resource usage, achieving a 40\% faster UI rendering performance.}
        \resumeItem{Implemented state-of-the-art UX patterns, increasing customer satisfaction scores by 20\% after deployment.}
        \resumeItem{Automated UI testing suites using \textbf{TypeScript}, increasing test coverage by 50\% and reducing bug rates post-release.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed responsive web applications with \textbf{Angular} and \textbf{TypeScript}, improving mobile usability and user engagement by 35\%.}
        \resumeItem{Refined UI/UX workflows collaborating with design teams, leading to a 30\% boost in task completion rates among users.}
        \resumeItem{Implemented asynchronous API integrations, reducing UI blocking times by 40\% in data-heavy visualizations.}
        \resumeItem{Enhanced frontend security by mitigating XSS and injection vulnerabilities, reducing security incidents by 70\%.}
        \resumeItem{Applied best practices for modular component design, promoting code reuse and shortening development cycles by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab environments, ensuring secure configurations and 99\% uptime for student and research use.}
        \resumeItem{Developed test scripts validating UI security aspects, identifying vulnerabilities and improving assessment accuracy by 30\%.}
        \resumeItem{Guided students through secure coding best practices, leading to a 25\% reduction in lab assignment security errors.}
        \resumeItem{Conducted demos explaining networking and web security protocols, enhancing student comprehension and participation by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Angular.js} UI components, increasing user engagement metrics by 25\% through improved interactivity and responsiveness.}
        \resumeItem{Implemented optimized \textbf{TypeScript} API calls achieving average response times under 100ms and enhanced frontend efficiency.}
        \resumeItem{Integrated backend services using RESTful principles, reducing data sync delays by 20\% and increasing stability.}
        \resumeItem{Enhanced PostgreSQL stored procedure performance by 15\%, lowering frontend load and improving overall app responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Angular} frontend modules improving user experience and supporting 1000 concurrent users with low latency.}
        \resumeItem{Built secure microservices with \textbf{Java Spring Boot} and integrated RESTful APIs to ensure smooth data exchange and system reliability.}
        \resumeItem{Automated deployment using \textbf{Docker} and CI/CD pipelines on \textbf{AWS EC2}, reducing software release times by 30\%.}
        \resumeItem{Collaborated on UI/UX design enhancements applying modern responsive web design, increasing customer retention by 15\%.}
        \resumeItem{Implemented unit and integration tests increasing code coverage to 90\%, enhancing application robustness and deployment stability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered UX Feedback Analyzer} | Angular, TypeScript, OpenAI API}
          {}
          \resumeItemListStart
              \resumeItem{Developed an interactive UI feedback tool using \textbf{Angular} and AI to analyze real-time user interactions improving UX design by 30\%.}
              \resumeItem{Integrated \textbf{OpenAI API} to generate contextual suggestions, reducing manual UX review time by 40\%.}
              \resumeItem{Implemented responsive design features ensuring 100\% compatibility across desktop and mobile devices boosting accessibility.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Interactive Data Center Simulation Dashboard} | Angular, REST API, CSS3}
          {}
          \resumeItemListStart
              \resumeItem{Built a dynamic frontend dashboard for data center simulations using \textbf{Angular}, improving user task efficiency by 35\%.}
              \resumeItem{Optimized component load time by 40\% and implemented real-time updates via asynchronous REST API calls.}
              \resumeItem{Collaborated with UX designers to create visually appealing, user-friendly interfaces that increased user satisfaction scores by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Angular, React.js, Spring Boot, Laravel, Node.js, HTML5, CSS3 \\
                \textbf{API \& Integration:} & RESTful APIs, Asynchronous Programming, JSON, Git, Agile Methodologies \\
                \textbf{Security \& Networking:} & Web Security (XSS, SQL Injection mitigation), Linux, Networking Protocols \\
                \textbf{DevOps \& Cloud:} & Docker, AWS (EC2, S3, Lambda), Jenkins, CI/CD Pipelines \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, AI Agents, Automation Tools (n8n, Zapier) \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}