\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable backend microservices with \textbf{Java Spring Boot} to boost API throughput by 35\% and reduce latency.}
        \resumeItem{Enhanced authentication using \textbf{Spring Security}, decreasing unauthorized attempts by 40\% and strengthening platform security.}
        \resumeItem{Designed an AI-assisted code review tool integrating \textbf{LLMs}, cutting manual review time by 45\% and accelerating delivery schedules.}
        \resumeItem{Streamlined CI/CD pipelines using \textbf{Docker} and \textbf{Jenkins}, reducing deployment duration by 40\% with automated tests.}
        \resumeItem{Collaborated in cross-team meetings to align software strategy improving system maintainability and performance in production environments.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed an intuitive SaaS platform with \textbf{Laravel} and \textbf{React} supporting 50+ users with 99.9\% uptime.}
        \resumeItem{Automated data ingestion pipelines in \textbf{Python}, reducing manual processing by 80\% for over 10,000 daily stock entries.}
        \resumeItem{Implemented AI-powered \textbf{LLM} agents to automate FINRA data processing, cutting manual labor by 80\% and improving accuracy.}
        \resumeItem{Optimized \textbf{React} components and state management, reducing page load time by 25\% and boosting user retention.}
        \resumeItem{Built a LinkedIn outreach bot leveraging AI, increasing qualified lead generation by 40\% through targeted content automation.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab infrastructure, ensuring consistent and reliable environment for cybersecurity coursework.}
        \resumeItem{Assisted students in debugging and deploying software modules, elevating assignment success rates by 20\% through clear guidance.}
        \resumeItem{Developed scripts to automate grading and validation, improving accuracy by 25\% and reducing instructor workload significantly.}
        \resumeItem{Led 15+ sessions explaining Cryptography, Networking, and Web Security topics, enhancing student engagement and understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed \textbf{TypeScript} API calls optimizing average response time to sub-100ms for seamless data synchronization.}
        \resumeItem{Refactored \textbf{Angular.js} UI components, increasing user engagement and satisfaction by 25\% through usability improvements.}
        \resumeItem{Developed a high-performance \textbf{C\# .NET} backend, reducing data retrieval latency by 30\% in the main platform.}
        \resumeItem{Enhanced \textbf{PostgreSQL} stored procedures, improving data processing efficiency and reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Contributed to SaaS tool development automating SDLC processes, boosting team productivity across multiple project phases.}
        \resumeItem{Built \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, serving 1000 concurrent users with responses under 200ms.}
        \resumeItem{Implemented \textbf{Docker}-based CI/CD pipelines for automated AWS EC2 deployments, improving release cycles and environment consistency.}
        \resumeItem{Developed user-friendly project tracking UI in \textbf{React.js}, enhancing load speed and user interaction by 30\%.}
        \resumeItem{Wrote robust unit tests using \textbf{JUnit}, achieving close to 90\% coverage and increasing code reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Quality Bot} | GitHub Actions, GitHub API, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Built an AI bot leveraging \textbf{LLMs} and GitHub Actions to auto-review pull requests, reducing manual reviews by 30\%.}
              \resumeItem{Automated docstring generation for Python code, ensuring 100\% documentation coverage and improving code maintainability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Customer Support Automation Agent} | Gmail API, n8n Automation, LLMs, Google Sheets API}{}
          \resumeItemListStart
              \resumeItem{Created AI agent using \textbf{LLMs} and Gmail API to automate 60\% of support email replies, reducing response times by 40\%.}
              \resumeItem{Implemented human-in-the-loop workflows for complex queries, maintaining response accuracy and customer satisfaction levels.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Face Recognition Platform} | AWS EC2, S3, SQS, IAM, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Developed face recognition service leveraging \textbf{AWS EC2} and \textbf{SQS} queues to handle 1000+ requests within 60 seconds.}
              \resumeItem{Designed backend to auto-scale and store data in \textbf{S3}, ensuring robustness and high availability under load.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, JavaScript, Python, TypeScript, C\#, PHP, Shell Scripting \\
                \textbf{Frontend \& Frameworks:} & React.js, Angular.js, CSS, HTML, Laravel, Node.js \\
                \textbf{Backend \& Databases:} & Spring Boot, GraphQL, MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, Lambda, S3), Docker, Jenkins, CI/CD pipelines \\
                \textbf{Security \& Automation:} & Cybersecurity best practices, Spring Security, AI Agents, LLM Integration, Automation tools \\
                \textbf{Tools \& Processes:} & Git, Jira, REST APIs, Docker, Agile methodologies \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}