\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Python} backend services to improve real-time data processing throughput by 30\%, enabling faster decision-making.}
        \resumeItem{Implemented new \textbf{React} dashboard features for real-time visualization, increasing user engagement by 25\%.}
        \resumeItem{Integrated \textbf{LLM} APIs for workflow automation, reducing manual reporting time by 35\%.}
        \resumeItem{Collaborated with analysts to translate financial risk models into reliable production code, improving risk accuracy by 15\%.}
        \resumeItem{Wrote and maintained clean, tested \textbf{Python} and \textbf{JavaScript} code, resulting in 20\% fewer production bugs.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed real-time \textbf{React} visualizations for stock exposure data, cutting data refresh delays by 40\%.}
        \resumeItem{Automated data extraction and transformation pipelines in \textbf{Python}, boosting processing speed by 50\%.}
        \resumeItem{Built \textbf{LLM}-based agents to automate complex data analysis, reducing manual intervention by 60\%.}
        \resumeItem{Refactored JavaScript codebase to adopt latest \textbf{React} features, improving maintainability and performance by 30\%.}
        \resumeItem{Collaborated with quant teams to migrate prototype risk algorithms into scalable production systems with 99.9\% uptime.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Python}-based data ingestion microservices supporting real-time financial data flows with sub-second latency.}
        \resumeItem{Designed and implemented \textbf{React.js} dashboards for risk reporting, improving data accessibility for traders by 35\%.}
        \resumeItem{Automated API integrations for market data sources, raising data accuracy and reducing stale data incidents by 20\%.}
        \resumeItem{Collaborated within Agile teams to translate risk quant models into robust, production-ready code with 95\% test coverage.}
        \resumeItem{Maintained \textbf{SQL} and \textbf{NoSQL} databases, optimizing queries resulting in 25\% faster report generation.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure Linux environments, ensuring stable operations for cybersecurity applications with 99.8\% uptime.}
        \resumeItem{Assisted students in deploying Python and JavaScript programs, increasing successful lab completion rates by 20\%.}
        \resumeItem{Automated grading scripts using Python, reducing instructor grading time by 30\% and improving consistency.}
        \resumeItem{Conducted workshops on debugging and testing techniques, enhancing peer skills in secure software development.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls to achieve sub-100ms response, improving real-time system integration performance.}
        \resumeItem{Upgraded \textbf{Angular.js} UI components, boosting user satisfaction scores by 25\% through improved UX.}
        \resumeItem{Developed backend modules in \textbf{C\#} reducing data retrieval latency by 30\%, enhancing platform responsiveness.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, accelerating data processing and decreasing frontend load times by 15\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Real-Time Risk Dashboard} | Python, React, SQL, LLM APIs}{}
          \resumeItemListStart
              \resumeItem{Designed a \textbf{React}-based real-time risk visualization dashboard connected to a \textbf{Python} backend processing live market data streams.}
              \resumeItem{Integrated \textbf{LLM} APIs to automate risk report generation and anomaly detection, reducing manual report time by 40\%.}
              \resumeItem{Optimized SQL queries managing time-series financial data, improving dashboard latency by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Script Automation for Financial Workflows} | Python, OpenAI API, Automation}{}
          \resumeItemListStart
              \resumeItem{Built \textbf{Python} automation scripts utilizing \textbf{OpenAI API} to classify and process financial workflows, achieving 60\% efficiency gains.}
              \resumeItem{Developed a modular framework to transform prototype quant models into production-grade code, reducing integration time by 50\%.}
              \resumeItem{Enhanced error handling and logging, increasing system reliability and fault diagnosis for financial applications.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, JavaScript, TypeScript, Java, C\#, SQL \\
                \textbf{Web Development \& Frameworks:} & React, Angular, Django, Spring Boot, .NET \\
                \textbf{Databases:} & SQL, NoSQL, PostgreSQL, MongoDB \\
                \textbf{Data Visualization \& Real-Time Tools:} & Dashboards, Time-Series Data, API Integrations \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Workflow Automation \\
                \textbf{DevOps \& Tools:} & Git, Docker, Jenkins, AWS, Linux \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}