\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{React} and \textbf{Node.js} applications improving API throughput by 35\%, enhancing user scalability significantly.}
        \resumeItem{Implemented secure \textbf{GraphQL} and RESTful APIs, reducing unauthorized access attempts by 40\% through enhanced authentication.}
        \resumeItem{Led CI/CD pipeline automation with \textbf{Docker} and \textbf{Jenkins}, shortening deployment cycles by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to define features, translating product needs into scalable technical solutions.}
        \resumeItem{Performed code reviews emphasizing maintainability and quality, increasing team efficiency and reducing bugs by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built a SaaS data visualization platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Optimized \textbf{React} components, enhancing page load speed by 25\% and increasing client engagement metrics.}
        \resumeItem{Automated daily stock data processing pipelines in \textbf{Python}, reducing manual input by 80\%.}
        \resumeItem{Engineered AI agents with \textbf{LLMs} to automate broker data extraction, boosting efficiency by 80\%.}
        \resumeItem{Developed LinkedIn automation with \textbf{React} and AI, increasing qualified leads by 40\% through targeted outreach.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab infrastructure, ensuring secure, reliable environments for 100+ students.}
        \resumeItem{Automated grading scripts for software modules, improving accuracy and reducing manual workload by 25\%.}
        \resumeItem{Led student training sessions on cryptography and web security, improving assignment success rates by 20\%.}
        \resumeItem{Assisted students in debugging and deploying modules using secure and scalable methodologies.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript}-based API calls, achieving sub-100ms response times to optimize data flow.}
        \resumeItem{Enhanced frontend performance by 25\% using \textbf{Angular.js} upgrades, boosting user satisfaction.}
        \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET} reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, reducing frontend load by 15\% and increasing database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000 concurrent users seamlessly.}
        \resumeItem{Led UI development with \textbf{React.js}, improving project tracking speed and usability by 30\%.}
        \resumeItem{Established \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} with containerization in \textbf{Docker}.}
        \resumeItem{Developed and maintained RESTful APIs ensuring robust, scalable data exchange for client applications.}
        \resumeItem{Implemented unit tests with \textbf{JUnit}, achieving 90\% coverage and improving code reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Automated AI Code Review Bot} | GitHub Actions, GitHub API, OpenAI API}
          \resumeItemListStart
              \resumeItem{Created a \textbf{GitHub} AI bot using \textbf{LLMs} to analyze pull requests, reducing manual code review time by 25\% while ensuring standards.}
              \resumeItem{Implemented automatic generation and update of documentation, guaranteeing 100\% coverage for new \textbf{Python} code changes.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Developer Platform API Enhancement} | Node.js, React, GraphQL}
          \resumeItemListStart
              \resumeItem{Designed and built scalable \textbf{GraphQL} APIs for enhanced data querying, increasing front-end response speed by 30\% for client apps.}
              \resumeItem{Optimized \textbf{React} state management components, reducing page load time by 20\% and improving UX significantly.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Customer Support Agent} | Gmail API, n8n Workflow, LLMs}
          \resumeItemListStart
              \resumeItem{Developed an automated email classification and response system using \textbf{LLMs}, cutting first response time by 40\% on support queries.}
              \resumeItem{Built a human-in-the-loop workflow ensuring sensitive cases remain manually reviewed for high quality and accuracy.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming:} & JavaScript (ES6+), Java, Python, TypeScript, C\#, PHP \\
                \textbf{Web Development:} & React.js, Node.js, Angular.js, Laravel, GraphQL, RESTful APIs \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, SQL \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Git, GitHub \\
                \textbf{AI \& Automation:} & Large Language Models (LLMs), OpenAI API, n8n, Automation Workflows \\
                \textbf{Tools \& Others:} & Linux/Unix, JUnit, Spring Boot, Agile Methodologies, CI/CD Pipelines \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}