\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices improving API throughput by 35\%, enhancing overall platform performance and reliability.}
        \resumeItem{Enhanced authentication with \textbf{Spring Security}, decreasing unauthorized access attempts by 40\% and strengthening system security.}
        \resumeItem{Integrated an \textbf{AI-driven} code review assistant, cutting manual code review efforts by 45\% and accelerating feature release velocity by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing build and deployment time by 40\% for faster releases.}
        \resumeItem{Collaborated cross-functionally to deliver secure, high-quality features focused on improving user activation and engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Laravel} and \textbf{React} SaaS platform driving seamless multi-user experiences and supporting 50+ concurrent customers.}
        \resumeItem{Automated \textbf{Python} data pipelines processing 10K+ stock entries daily, reducing manual data upkeep by 80\% and improving accuracy.}
        \resumeItem{Built AI agents with \textbf{LLMs} automating FINRA data downloads, cutting manual workload by 80\% and accelerating operational efficiency.}
        \resumeItem{Optimized \textbf{React} components and state management to reduce page load times by 25\% and increase user engagement significantly.}
        \resumeItem{Created an AI-powered LinkedIn outreach bot automating content and lead management, boosting qualified leads by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed secure Linux-based lab infrastructure, ensuring reliable performance and security for cybersecurity software and hardware tests.}
        \resumeItem{Coached students through debugging and software deployment, improving assignment success rates by 20\% through targeted guidance.}
        \resumeItem{Developed and automated grading scripts, increasing evaluation accuracy by 25\% and reducing manual workload for instructors.}
        \resumeItem{Delivered over 15 interactive educational sessions covering Cryptography and Web Security topics, enhancing student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented sub-100ms response APIs in \textbf{TypeScript} ensuring fluid data exchanges and improved frontend performance.}
        \resumeItem{Advanced platform UI with \textbf{Angular.js}, driving a 25\% increase in user engagement and improving satisfaction scores.}
        \resumeItem{Designed high-speed backend services with \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\% across critical workflows.}
        \resumeItem{Improved \textbf{PostgreSQL} stored procedures, lowering frontend database load by 15\% and optimizing query performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users with sub-200ms response times.}
        \resumeItem{Led \textbf{CI/CD} implementation deploying microservices on \textbf{AWS EC2} via \textbf{Docker}, ensuring seamless and reliable releases.}
        \resumeItem{Created project management UI in \textbf{React.js}, improving usability and page load speed by 30\% and increasing team productivity.}
        \resumeItem{Implemented extensive unit tests with \textbf{JUnit} achieving ~90\% coverage to ensure reliability and maintainability of core modules.}
        \resumeItem{Collaborated with product and engineering teams to iteratively enhance SaaS features that improved customer activation rates.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Feature Experimentation Dashboard} | React, TypeScript, GraphQL, Go}{}
          \resumeItemListStart
              \resumeItem{Built a scalable dashboard using \textbf{React} and \textbf{GraphQL} to manage and analyze product growth experiments effectively.}
              \resumeItem{Designed full experiment lifecycle with \textbf{Go} backend, enabling hypothesis tracking, statistical analysis, and goal metric reporting.}
              \resumeItem{Integrated AI tools to automate experiment result summaries, accelerating insight generation and iteration cycle by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated AI Development Assistant} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Engineered an AI-powered assistant leveraging \textbf{OpenAI API} to review code and suggest improvements, shortening review time by 25\%.}
              \resumeItem{Automated documentation updates inline with code changes, ensuring 100\% documentation coverage and improving developer onboarding speed.}
              \resumeItem{Implemented secure usage protocols and governance workflows, maintaining code quality while employing AI tools safely in development.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Go, TypeScript, JavaScript, Python, C\#, PHP \\
                \textbf{Frontend Frameworks:} & React, Angular.js, Laravel, Node.js \\
                \textbf{Backend Frameworks & APIs:} & Spring Boot, GraphQL, REST, .NET, Flask \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps & Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD pipelines \\
                \textbf{AI & Automation:} & OpenAI API, LLM Integration, GitHub Copilot, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}