\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced back-end services with \textbf{Elixir}, improving API response times by 30\% and feature scalability across distributed systems.}
        \resumeItem{Collaborated with product managers to define scope and deliverables for new financial application modules, increasing deployment accuracy.}
        \resumeItem{Authored secure, tested code adhering to web security principles, reducing vulnerability incidents in production by 25\%.}
        \resumeItem{Led peer code reviews, providing actionable feedback, resulting in a 20\% improvement in code quality and team productivity.}
        \resumeItem{Automated repetitive testing tasks in CI/CD pipeline, cutting release cycle duration by 35\% and improving deployment confidence.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable \textbf{React} components improving client-side rendering efficiency by 35\% for financial dashboards.}
        \resumeItem{Developed and maintained \textbf{Elixir Phoenix}-style API endpoints, increasing backend throughput by 30\% with optimized queries.}
        \resumeItem{Coordinated feature development with product teams to meet milestone deadlines, achieving 100\% on-time delivery for quarterly releases.}
        \resumeItem{Wrote comprehensive unit and integration tests for complex modules, boosting test coverage to 92\% and reducing bugs.}
        \resumeItem{Refined application security using best practices, lowering exposure to common threats and securing sensitive user data effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments for student cybersecurity labs, improving uptime and reducing configuration errors by 15\%.}
        \resumeItem{Assisted students in debugging and testing software, which increased successful assignment submissions by 20\%.}
        \resumeItem{Automated grading scripts to enhance accuracy and efficiency, reducing manual workload by 25\%.}
        \resumeItem{Conducted detailed sessions on cryptography and web security, increasing student understanding and lab participation.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{React} frontend features improving user experience and engagement by 25\% on the company’s financial platform.}
        \resumeItem{Built performant \textbf{TypeScript} API integrations, ensuring sub-100ms response times across key application modules.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, reducing latency by 15\% for critical database operations.}
        \resumeItem{Implemented backend features using \textbf{.NET} and \textbf{C\#}, cutting data retrieval latency by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Elixir} microservices to automate workflows, reducing process time by 40\% for client financial applications.}
        \resumeItem{Integrated \textbf{PostgreSQL} with backend services, improving data reliability and reducing query time by 20\%.}
        \resumeItem{Implemented frontend features in \textbf{React.js} to enhance UI responsiveness by 30\% for financial dashboards.}
        \resumeItem{Built and maintained CI/CD pipelines deploying microservices on \textbf{Kubernetes} clusters in AWS, improving deployment frequency.}
        \resumeItem{Wrote unit and integration tests reaching 90\% code coverage, improving reliability and reducing bugs pre-release.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enhanced Code Review Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{CI/CD} bot integrating \textbf{OpenAI API} to analyze pull requests, catching 90\% of common bugs automatically.}
              \resumeItem{Automated docstring generation to ensure 100\% coverage on new code, reducing reviewer workload by 25\%.}
              \resumeItem{Increased codebase quality and consistency by providing instant feedback directly within \textbf{GitHub} pull requests.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Bitcoin Financial Dashboard} | Elixir, Phoenix, React, PostgreSQL}{}
          \resumeItemListStart
              \resumeItem{Built an interactive \textbf{React} dashboard displaying real-time Bitcoin balances, increasing user engagement by 30\%.}
              \resumeItem{Implemented backend APIs in \textbf{Elixir Phoenix} to securely fetch and update Bitcoin wallet data with 99.9\% uptime.}
              \resumeItem{Optimized database queries in \textbf{PostgreSQL}, reducing latency by 20\% for large data sets.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Elixir, Java, Python, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Frameworks \& Libraries:} & Phoenix, React, Laravel, Spring Boot, .NET, Angular.js \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB \\
                \textbf{DevOps \& Orchestration:} & Docker, Jenkins, Kubernetes, AWS (EC2, S3, Lambda) \\
                \textbf{Security \& Testing:} & Web Security Fundamentals, Spring Security, JUnit, Unit/Integration Testing \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, GitHub Actions, Automation Bots \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}