\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices, enhancing \textbf{API} throughput by 35\% under heavy transaction loads.}
        \resumeItem{Strengthened security by integrating \textbf{Spring Security} with role-based access, cutting unauthorized access attempts by 40\%.}
        \resumeItem{Deployed \textbf{AI}-powered code review assistant, accelerating PR review speed by 25\% and reducing manual code checks by 45\%.}
        \resumeItem{Automated CI/CD pipeline with \textbf{Jenkins} and \textbf{Docker}, reducing deployment times by 40\% and improving release reliability.}
        \resumeItem{Collaborated on AWS migration plans, optimizing resource use and cutting cloud costs by 20\% via \textbf{EC2} and container-based deployment.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed \textbf{SaaS} visualization platform with \textbf{Laravel} and \textbf{React} supporting 50+ concurrent users with zero downtime.}
        \resumeItem{Automated daily stock processing pipelines using \textbf{Python}, reducing manual entry time by 80\% and error rates by 30\%.}
        \resumeItem{Developed a subscription e-commerce platform using \textbf{PHP} with \textbf{Stripe} integration, enabling secure role-based access controls.}
        \resumeItem{Integrated AI-driven \textbf{LLM} agents for automated FINRA data retrieval, cutting manual efforts by 80\% in compliance workflows.}
        \resumeItem{Enhanced \textbf{React.js} UI components, improving client-side load times by 25\% and enriching user experience engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} lab infrastructure ensuring secure, reliable execution environments for 100+ cybersecurity students.}
        \resumeItem{Mentored students on software deployment and debugging, improving lab assignment success rates by 20\%.}
        \resumeItem{Created automated grading scripts, increasing assessment accuracy by 25\% and reducing manual review workload significantly.}
        \resumeItem{Led 15+ educational webinars on Cryptography and Network Security, increasing student engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Processed high-throughput \textbf{TypeScript} API calls achieving sub-100ms response times for seamless data delivery.}
        \resumeItem{Refined \textbf{Angular.js} frontend, increasing user engagement by 25\% via optimized component reusability and performance.}
        \resumeItem{Designed and implemented \textbf{C\# .NET} backend services, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, lowering frontend database load by 15\% and improving speed.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Collaborated on a \textbf{SaaS} SDLC automation tool that enhanced project lifecycle efficiency within a 5-member Agile team.}
        \resumeItem{Developed \textbf{Spring Boot} microservices in \textbf{Java} with \textbf{MySQL}, sustaining 1000 concurrent users under 200ms response time.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} using \textbf{Docker}, reducing deployment errors by 35\%.}
        \resumeItem{Crafted React.js UI improving project management usability and boosting page load speeds by 30\%.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} unit tests covering 90\% of pipeline modules to ensure software reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-driven API Security Analyzer} | Java, AWS Lambda, REST API, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-powered tool using \textbf{OpenAI API} for automated security analysis of \textbf{REST APIs}, reducing vulnerability discovery time by 40\%.}
              \resumeItem{Integrated \textbf{AWS Lambda} functions for scalable automated testing, enhancing API security adherence across client implementations.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Token-Based Authentication Microservice} | Java, Spring Boot, OAuth2, SSO}{}
          \resumeItemListStart
              \resumeItem{Engineered a robust \textbf{token authentication} microservice with \textbf{OAuth2} and \textbf{SSO} support, increasing client login security by 50\%.}
              \resumeItem{Reduced authentication latency by 30\% through efficient session and token management in distributed systems.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Client Implementation Tracker} | React, Node.js, REST API, SQL}{}
          \resumeItemListStart
              \resumeItem{Built a project tracker web app improving client rollout visibility, reducing implementation delays by 35\% using \textbf{React} and \textbf{SQL}.}
              \resumeItem{Automated data sync across platforms with \textbf{Node.js} REST API integration, enhancing project collaboration efficiency.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, PHP, C\#, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, .NET \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD, Azure \\
                \textbf{Databases:} & Oracle SQL, MySQL, PostgreSQL, DynamoDB \\
                \textbf{API \& Security:} & REST, SOAP, OAuth2, SSO, Token Authentication, JWT \\
                \textbf{Tools \& Others:} & Linux/Unix, Git, Jira, JUnit, OpenAI API, LLM Integration, AI Agents \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}