\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} services’ scalability, increasing API request throughput by 35\%, supporting high-volume financial data exchange.}
        \resumeItem{Implemented \textbf{Spring Security} role-based access and authentication, decreasing unauthorized access incidents by 40\%.}
        \resumeItem{Deployed AI-powered code review bot using \textbf{LLMs}, cutting manual review time by 45\% and accelerating deployment cycles by 25\%.}
        \resumeItem{Automated deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, improving release frequency and reducing time by 40\%.}
        \resumeItem{Collaborated on cross-team agile processes, using \textbf{SCRUM} to deliver scalable backend solutions impacting multiple product lines.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{React} and \textbf{Laravel} SaaS platform supporting 50+ concurrent users with optimized data workflows.}
        \resumeItem{Automated financial data pipelines using \textbf{Python}, processing over 10,000 entries daily and reducing manual processing by 80\%.}
        \resumeItem{Developed role-based e-commerce subscription system integrating \textbf{Stripe} and \textbf{WooCommerce}, enhancing access security.}
        \resumeItem{Created AI agents leveraging \textbf{LLMs} to automate FINRA broker dataset downloads, cutting manual work by 80\%.}
        \resumeItem{Refined \textbf{React} component state management, reducing page load times by 25\% and increasing user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure \textbf{Linux}-based cybersecurity labs, maintaining reliable setups for over 100 students and faculty.}
        \resumeItem{Guided students in debugging and deploying software modules, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts to improve accuracy by 25\%, reducing manual workload for lab instructors.}
        \resumeItem{Conducted 15+ interactive sessions on Cryptography, Networking, and Web Security to enhance student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API integrations achieving sub-100ms response times, ensuring smooth data exchange for clients.}
        \resumeItem{Migrated UI to \textbf{Angular.js}, enhancing user engagement and satisfaction metrics by 25\%.}
        \resumeItem{Developed high-performance \textbf{C\#} backend microservices on \textbf{.NET} to reduce data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend load by 15\% and improving overall query efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrency with response times under 200ms.}
        \resumeItem{Built project management UIs in \textbf{React.js}, increasing usability and reducing page load time by 30\%.}
        \resumeItem{Designed and maintained CI/CD pipelines using \textbf{Docker} and deployed services on \textbf{AWS EC2} to support efficient rollouts.}
        \resumeItem{Achieved 90\% unit test coverage on core modules using \textbf{JUnit} to ensure backend reliability and minimize defects.}
        \resumeItem{Collaborated effectively with a 5-member agile team to automate key SDLC workflows, improving deployment speed and consistency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Pull Request Code Reviewer} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Built an automated \textbf{CI/CD} tool integrating \textbf{LLMs} that analyzed PRs for defects and style, cutting review time 25\%.}
              \resumeItem{Implemented automatic generation of Python docstrings enhancing documentation coverage to 100\%, improving codebase maintainability and clarity.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Financial Data Aggregation Platform} | Java, Spring Boot, REST APIs, Docker}{}
          \resumeItemListStart
              \resumeItem{Developed a scalable backend system to ingest and normalize financial transactions from 10,000+ sources with 99.9\% uptime.}
              \resumeItem{Created RESTful APIs enabling seamless integration of data with client applications, boosting data retrieval efficiency by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated Support Email Classification Agent} | Gmail API, n8n, LLM Integration}{}
          \resumeItemListStart
              \resumeItem{Engineered an AI-driven email classifier that automated response handling for 60\% common queries, reducing response latency by 40\%.}
              \resumeItem{Implemented HITL workflow ensuring manual oversight on sensitive cases, improving accuracy and customer satisfaction.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, JavaScript, TypeScript, C\#, PHP, Go, C++ \\
                \textbf{Web Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, .NET \\
                \textbf{APIs \& Protocols:} & REST APIs, GraphQL, gRPC, JSON \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Testing \& Methodologies:} & Unit Testing, Test-Driven Development (TDD), Agile (SCRUM, Kanban) \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}