\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices performance by 35\% to improve scalability and robustness of core education APIs.}
        \resumeItem{Implemented \textbf{Spring Security} features, reducing unauthorized access by 40\% and improving platform data protection.}
        \resumeItem{Developed \textbf{AI-driven} code review tool, reducing manual review time by 45\% and accelerating development velocity by 25\%.}
        \resumeItem{Automated \textbf{Docker} and \textbf{Jenkins}-based CI/CD pipelines, cutting deployment time by 40\% for frequent software releases.}
        \resumeItem{Collaborated with cross-functional teams to ensure software met accessibility and performance standards in diverse classroom environments.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built a scalable SaaS data visualization platform with \textbf{React} and \textbf{Laravel}, supporting 50+ concurrent users efficiently.}
        \resumeItem{Automated \textbf{Python} pipelines processing 10,000+ daily records, reducing manual workload by 80\% and improving accuracy.}
        \resumeItem{Developed role-based access control platform integrating \textbf{Stripe} and WooCommerce, increasing subscription management efficiency.}
        \resumeItem{Implemented \textbf{AI agents} with LLMs to automate broker data workflows, reducing manual processing effort by 80\%.}
        \resumeItem{Optimized \textbf{React} components to cut page load time by 25\%, boosting user engagement and system responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed secure \textbf{Linux} infrastructure for cybersecurity labs, maintaining reliable and tamper-proof environments for students.}
        \resumeItem{Assisted in debugging and deploying software modules, improving student assignment success rates by 20\% through targeted support.}
        \resumeItem{Automated grading scripts enhancing manual review accuracy by 25\%, increasing lab process efficiency and reliability.}
        \resumeItem{Conducted 15+ sessions explaining cryptography and web security concepts, boosting student comprehension and participation.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls optimizing data flow with average response times under 100ms for key applications.}
        \resumeItem{Upgraded platform frontend with \textbf{Angular.js}, increasing user engagement metrics by 25\% due to improved UI/UX.}
        \resumeItem{Engineered backend services using \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries which decreased frontend data load time by 15\%, enhancing application responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users under 200ms response time.}
        \resumeItem{Led the implementation of \textbf{Docker}-based \textbf{CI/CD} pipelines on \textbf{AWS EC2}, enabling seamless deployments for six microservices.}
        \resumeItem{Built user-friendly project tracking UI with \textbf{React.js}, improving load speeds and usability by 30\%.}
        \resumeItem{Wrote \textbf{JUnit} unit tests covering 90\% of code for pipelines, ensuring high reliability and reducing bugs in production.}
        \resumeItem{Collaborated with team to develop SaaS tools automating SDLC workflows, increasing development speed and operational efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Literacy Assessment Tool} | Python, GraphQL, AWS Lambdas}
          {}
          \resumeItemListStart
              \resumeItem{Designed a scalable assessment platform using \textbf{Python} and \textbf{GraphQL} APIs, improving reading skill diagnostics by 30\%.}
              \resumeItem{Implemented real-time data processing with \textbf{AWS Lambdas}, ensuring prompt reporting for educators and personalized student feedback.}
              \resumeItem{Collaborated with education experts to optimize tool accessibility and reliability for diverse K–12 classroom environments.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated AI Code Review Assistant} | GitHub Actions, OpenAI API, LLMs}
          {}
          \resumeItemListStart
              \resumeItem{Built a \textbf{CI/CD} automation bot using \textbf{GitHub Actions} and \textbf{OpenAI API} to analyze pull requests, reducing manual review by 40\%.}
              \resumeItem{Developed automatic docstring generation ensuring 100\% documentation coverage for new \textbf{Python} code, improving maintainability.}
              \resumeItem{Integrated feedback loop improving code quality through AI-driven suggestions, accelerating developer productivity by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, TypeScript, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Spring Boot, Angular.js, Laravel, Node.js, .NET, Django \\
                \textbf{Databases \& Data Storage:} & PostgreSQL, MySQL, DynamoDB, MongoDB, Snowflake \\
                \textbf{Cloud \& DevOps:} & AWS (Lambdas, EC2, S3, AppSync), Docker, Terraform, Jenkins \\
                \textbf{Testing \& Automation:} & Jest, WebdriverIO, JUnit, Automated Testing Frameworks \\
                \textbf{AI \& APIs:} & OpenAI API, LLM Integration, RESTful APIs, GraphQL APIs \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}