\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed robust integrations using \textbf{Java Spring Boot} APIs increasing third-party connectivity by 40\% and platform scalability by 25\%.}
        \resumeItem{Led design and implementation of RESTful API services improving data exchange efficiency by 30\% with external applications.}
        \resumeItem{Automated troubleshooting workflows reducing integration downtime by 50\% and enhancing system reliability for client-facing services.}
        \resumeItem{Collaborated on API architecture redesign to support increased load, achieving 99.9\% uptime and reducing latency by 20\%.}
        \resumeItem{Maintained detailed API documentation ensuring developer usability increased by 35\% and reducing onboarding time for new engineers.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered API-based integrations between SaaS platform and third-party services, improving system interoperability and user retention by 15\%.}
        \resumeItem{Created React components optimized for performance, reducing page load times by 25\% and improving user engagement metrics.}
        \resumeItem{Implemented AI-driven automation workflows using \textbf{LLMs} to streamline data processing, cutting manual processing time by 80\%.}
        \resumeItem{Deployed secure OAuth 2.0 frameworks for external API connections enhancing user data safety and compliance with privacy standards.}
        \resumeItem{Diagnosed and resolved API connectivity issues lowering support tickets related to integrations by 45\% and improving customer satisfaction.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported configuration and security of Linux servers used for API testing and integration labs, increasing uptime by 20\%.}
        \resumeItem{Developed scripts to automate validation of API calls, reducing manual testing effort by 30\% and improving test accuracy.}
        \resumeItem{Conducted workshops on network protocols and API security, enhancing student comprehension and lab performance by 25\%.}
        \resumeItem{Assisted in debugging API integration tasks for student projects, improving successful completion rate by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls ensuring efficient integration with frontend, reducing response latency to under 100ms.}
        \resumeItem{Upgraded legacy Angular.js components, increasing user engagement by 25\% through improved integration and responsive interfaces.}
        \resumeItem{Developed backend microservices in \textbf{C\#} improving data retrieval time by 30\% to support smoother API interactions.}
        \resumeItem{Optimized database queries in \textbf{PostgreSQL} lowering frontend API load by 15\% and enhancing overall system performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed API microservices with \textbf{Java Spring Boot}, supporting 1000+ concurrent users and reducing response time to below 200ms.}
        \resumeItem{Implemented and maintained API integrations between SaaS tool and external services increasing data synchronization accuracy by 99\%.}
        \resumeItem{Built React.js UIs improving API-driven user workflows and reducing page load speeds by 30\%.}
        \resumeItem{Constructed CI/CD pipelines automating Docker-based deployments on \textbf{AWS EC2}, cutting release times by 40\%.}
        \resumeItem{Wrote comprehensive unit tests using \textbf{JUnit} achieving 90\% test coverage and enhancing API reliability across services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-driven API Integration Troubleshooter} | GitHub Actions, OpenAI API, Node.js}
          \resumeItemListStart
              \resumeItem{Developed an AI tool leveraging \textbf{OpenAI API} to automatically diagnose and resolve complex API integration errors, reducing downtime by 35\%.}
              \resumeItem{Integrated the tool with CI/CD workflows to proactively monitor API health, increasing system uptime and reliability by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Multi-Service Construction Management Connector} | JavaScript, REST API, AWS Lambda}
          \resumeItemListStart
              \resumeItem{Built a serverless integration service connecting construction management platforms via \textbf{REST APIs}, improving data flow accuracy by 40\%.}
              \resumeItem{Optimized API requests handling with \textbf{AWS Lambda}, reducing average response time to under 150ms for external service calls.}
              \resumeItem{Maintained detailed API documentation increasing developer efficiency and reducing onboarding time by 30\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, C\#, PHP, Shell Scripting \\
                \textbf{API \& Integration Technologies:} & REST APIs, OAuth 2.0, JSON, gRPC, API Design, API Documentation \\
                \textbf{Web Development Frameworks:} & React.js, Angular.js, Node.js, Spring Boot, .NET, Laravel \\
                \textbf{Cloud \& DevOps:} & AWS (Lambda, EC2, S3), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{AI \& Automation Tools:} & OpenAI API, LLM Integration, n8n, Zapier, AI Agents \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}