\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{React.js} interfaces to improve responsiveness and accessibility, boosting user interaction metrics by 28\%.}
        \resumeItem{Engineered backend services with \textbf{Node.js} optimizing API response time by 30\% and handling 20\% higher concurrent requests.}
        \resumeItem{Led integration of an \textbf{AI-powered} testing tool reducing bug detection time by 35\% during development cycles.}
        \resumeItem{Spearheaded automation of \textbf{CI/CD} pipelines using \textbf{Kubernetes} and \textbf{Jenkins}, accelerating deployment frequency by 40\%.}
        \resumeItem{Collaborated cross-functionally with UI/UX and marketing teams, expediting new feature launches by 25\% through improved workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{React} components improving page load speed by 30\% and increasing user retention rates.}
        \resumeItem{Built scalable \textbf{Node.js} microservices integrating with \textbf{PostgreSQL} improving data throughput by 40\%.}
        \resumeItem{Implemented an AI-powered content recommendation engine that raised engagement metrics by 22\%.}
        \resumeItem{Improved subscription e-commerce platform’s backend with \textbf{Stripe} API integration, cutting payment errors by 15\%.}
        \resumeItem{Automated marketing campaign tools using \textbf{LLM} models boosting lead qualification efficiency by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} infrastructure and secured lab environments, increasing uptime reliability by 20\%.}
        \resumeItem{Assisted students in deploying and debugging web applications, resulting in a 15\% increase in assignment completion rates.}
        \resumeItem{Automated grading scripts reducing instructor workload by 30\% and improving grading accuracy.}
        \resumeItem{Delivered 15+ engaging sessions covering Cryptography and Networking best practices, enhancing student engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Designed efficient \textbf{TypeScript} APIs achieving sub-100ms response times, improving frontend performance.}
        \resumeItem{Refactored frontend components using \textbf{Angular.js} that increased user satisfaction by 25\%.}
        \resumeItem{Built robust backend modules in \textbf{C\#} with \textbf{.NET}, reducing data access latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries leading to 15\% faster data retrieval and improved app responsiveness.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{React.js} interfaces increasing page load speed by 30\% and enhancing user experience.}
        \resumeItem{Created high-performance \textbf{Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users.}
        \resumeItem{Implemented end-to-end \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS} with \textbf{Docker}, reducing downtime by 35\%.}
        \resumeItem{Collaborated on redesigning internal tools using \textbf{Node.js}, improving team's development efficiency by 20\%.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} tests achieving 90\% coverage, enhancing software reliability and quality.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Augmented Web Feature Deployment} | React, Node.js, Next.js, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{Next.js} web toolkit integrated with \textbf{AI} to automate code generation and reduce feature rollout time by 30\%.}
              \resumeItem{Created a modular \textbf{React} component library shared across teams, decreasing new feature build time by 20\%.}
              \resumeItem{Implemented \textbf{Node.js} backend services with automated testing, improving system stability during multiple product launches.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Customer Interaction Bot} | Node.js, React, LLMs, REST API}{}
          \resumeItemListStart
              \resumeItem{Engineered a \textbf{Node.js} chatbot leveraging \textbf{LLMs} to classify customer intents, reducing support load by 40\%.}
              \resumeItem{Built dynamic front-end in \textbf{React} for seamless user interactions, increasing engagement by 25\%.}
              \resumeItem{Integrated real-time feedback loops to continuously improve bot response accuracy through user data analysis.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Web Development:} & JavaScript, React.js, Next.js, Node.js, HTML, CSS, PHP \\
                \textbf{Backend \& Infrastructure:} & Spring Boot, Express.js, PostgreSQL, MySQL, Nginx, Kubernetes, CI/CD \\
                \textbf{Programming Languages:} & Java, Python, TypeScript, C\#, Go \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Kubernetes \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering \\
                \textbf{Tools \& Others:} & Git, GitHub, REST APIs, Agile, CMS, Design Systems \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}