\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to increase API throughput by 35\%, improving overall system scalability and stability.}
        \resumeItem{Implemented \textbf{Spring Security} to upgrade authentication, decreasing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an AI-based code review bot reducing manual reviews by 45\%, accelerating development velocity by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, slashing release cycle time by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to optimize backend services supporting 1000+ daily users with robust APIs.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed \textbf{RESTful APIs} using \textbf{Java Spring Boot} and integrated them with frontend \textbf{React} components.}
        \resumeItem{Developed CI/CD workflows to deploy backend services using \textbf{Jenkins}, achieving 30\% faster deployment.}
        \resumeItem{Utilized \textbf{Postman} to script automated API tests, increasing test coverage and reducing defects by 35\%.}
        \resumeItem{Refined frontend \textbf{ReactJS} state management, improving page load speed by 25\% and user engagement.}
        \resumeItem{Built secure authentication flows leveraging role-based access with OAuth and JWT tokens, enhancing data protection.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure \textbf{Linux} infrastructures, maintaining lab environments for reliable cybersecurity experiments.}
        \resumeItem{Automated grading scripts, improving assessment accuracy by 25\% while reducing manual review efforts.}
        \resumeItem{Trained students in debugging and testing software modules, increasing assignment success rate by 20\%.}
        \resumeItem{Hosted interactive sessions on network security protocols, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized API endpoints using \textbf{TypeScript}, reducing average response time below 100ms for real-time data.}
        \resumeItem{Revamped platform frontend with \textbf{Angular.js}, increasing user engagement by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, cutting data retrieval latency by 30\%.}
        \resumeItem{Improved \textbf{PostgreSQL} stored procedures, decreasing frontend load times and increasing efficiency by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices handling 1000+ concurrent users with sub-200ms response times.}
        \resumeItem{Built CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker} for seamless deployment on \textbf{AWS EC2}.}
        \resumeItem{Implemented unit tests with \textbf{JUnit}, achieving 90\% coverage across backend services to reduce production bugs.}
        \resumeItem{Designed and developed \textbf{REST APIs} integrated with \textbf{Google Apigee Edge} for secure API management.}
        \resumeItem{Created frontend components using \textbf{React.js}, improving UI responsiveness by 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered API Testing Bot} | GitHub, OpenAI API, Postman, Jenkins}
          {}
          \resumeItemListStart
              \resumeItem{Developed AI bot integrating \textbf{OpenAI API} and \textbf{Postman} to automatically generate and run API tests, reducing manual test creation by 60\%.}
              \resumeItem{Automated CI/CD testing using \textbf{Jenkins}, improving deployment reliability by 35\% through continuous API quality validation.}
              \resumeItem{Enhanced API coverage by designing versatile test suites aligned with \textbf{REST API} design principles and best practices.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} | Google Cloud, Kubernetes, Apigee, Spring Boot}
          {}
          \resumeItemListStart
              \resumeItem{Designed scalable microservices with \textbf{Spring Boot} deployed on \textbf{Google Kubernetes Engine}, boosting platform stability under high load.}
              \resumeItem{Implemented \textbf{Google Apigee X} for centralized API management, enabling secure and governed API consumption across services.}
              \resumeItem{Optimized asynchronous messaging via \textbf{Google PubSub}, improving event-driven communication latency by 30\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, TypeScript, C\#, JavaScript, PHP, Go \\
                \textbf{Frameworks \& Platforms:} & Spring Boot, React.js, Angular.js, Jenkins, Docker, Google Apigee Edge/X \\
                \textbf{Cloud \& DevOps:} & Google Cloud (GKE), AWS, Kubernetes, Docker, CI/CD pipelines, Jenkins \\
                \textbf{API \& Integration Tools:} & REST API, Postman, Google PubSub, OAuth, JWT, Apigee API Gateway \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Testing \& Automation:} & JUnit, Postman Scripts, Git, GitHub Actions \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}