\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices, boosting API throughput by 35\% to support increased customer demand efficiently.}
        \resumeItem{Integrated \textbf{Spring Security} to enhance authentication protocols, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant using \textbf{LLMs}, cutting manual review time by 45\% and accelerating release cycles.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} pipelines, decreasing build and deployment time by 40\% across key services.}
        \resumeItem{Collaborated cross-functionally to deliver high-quality software aligned with product timelines and customer requirements.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{React}-based SaaS platform with dynamic AI integrations, supporting 50+ concurrent users with adaptive UI layouts.}
        \resumeItem{Automated data workflows using \textbf{Python}, increasing processing efficiency of 10,000+ daily stock entries by 80\%.}
        \resumeItem{Designed \textbf{AI agents} leveraging \textbf{LLMs} for financial data automation, reducing manual effort by 80\% effectively.}
        \resumeItem{Created an AI-powered LinkedIn outreach bot that generated 40\% more qualified leads through targeted automated campaigns.}
        \resumeItem{Optimized \textbf{React} state management with \textbf{Zustand}, enhancing responsiveness and reducing page load times by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity labs, ensuring secure configurations and continuous operational availability.}
        \resumeItem{Supported students in debugging, deploying, and testing software modules, improving assignment success rate by 20\%.}
        \resumeItem{Automated grading scripts, raising review accuracy by 25\% and streamlining assessment workflows.}
        \resumeItem{Conducted 15+ interactive online seminars explaining cryptography and networking, boosting student comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented API endpoints in \textbf{TypeScript}, achieving sub-100ms response times for seamless frontend-backend data exchange.}
        \resumeItem{Updated the \textbf{Angular.js} frontend, enhancing user engagement by 25\% through improved interaction design.}
        \resumeItem{Developed high-performance backend services in \textbf{C\#} with \textbf{.NET}, cutting data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend load by 15\% and improving database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000 concurrent users with under 200ms latency.}
        \resumeItem{Implemented a React.js UI for project tracking, achieving 30\% faster page loads and enhanced user experience.}
        \resumeItem{Built and maintained CI/CD pipelines deploying 6 microservices on \textbf{AWS EC2} using \textbf{Docker} for reliable releases.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} tests covering 90\% of the pipelines module, ensuring high system reliability.}
        \resumeItem{Collaborated in a team of 5 to develop a SaaS tool automating the \textbf{SDLC}, improving development workflow efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Dynamic Web Interface} | React, TypeScript, OpenAI API, Zustand}{}
          \resumeItemListStart
              \resumeItem{Designed a responsive \textbf{React} UI with \textbf{Zustand} state management delivering adaptive, AI-driven content personalization.}
              \resumeItem{Integrated \textbf{OpenAI API} to create intelligent agents providing real-time UI customization based on user interactions.}
              \resumeItem{Achieved 30\% improvement in user engagement metrics through dynamic AI enhancements and seamless frontend responsiveness.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{LLM-Based Document Retrieval System} | Python, GPT, RAG, AWS}{}
          \resumeItemListStart
              \resumeItem{Implemented a Retrieval-Augmented Generation (RAG) system utilizing \textbf{GPT} APIs to provide accurate AI-powered document search.}
              \resumeItem{Deployed scalable backend services on \textbf{AWS}, achieving sub-second response times under load with fault tolerance.}
              \resumeItem{Leveraged prompt engineering techniques to boost retrieval precision by 25\% compared to baseline implementations.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, TypeScript, JavaScript, PHP, C\#, Go, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Spring Boot, Laravel, Angular.js, Node.js, .NET, HTML, CSS Grid, Flexbox \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, RAG, Agentic AI \\
                \textbf{State Management:} & Zustand, Redux, Context APIs \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, Lambda, S3), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}