\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to increase throughput by 35\% and scalability for high-traffic production workloads.}
        \resumeItem{Enhanced role-based access control via \textbf{Spring Security}, decreasing unauthorized access attempts by 40\% and boosting application security.}
        \resumeItem{Created an \textbf{AI-driven} code review tool using \textbf{LLMs}, reducing manual review time by 45\% and accelerating deployment by 25\%.}
        \resumeItem{Automated build and deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, decreasing release cycles by 40\% and improving reliability.}
        \resumeItem{Collaborated in cross-functional teams conducting thorough code reviews, improving code quality and system robustness company-wide.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented a \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ concurrent users with reliable data visualization.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, processing 10,000+ entries and cutting manual data handling effort by 80\%.}
        \resumeItem{Developed AI automation agents using \textbf{LLMs} to manage broker data, reducing manual workload by 80\% and enhancing accuracy.}
        \resumeItem{Built an \textbf{AI-powered} LinkedIn outreach bot, automating content posting and increasing qualified lead generation by 40\%.}
        \resumeItem{Optimized \textbf{React} components to improve user engagement and reduce page load times by 25\% across the platform.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab environments, implementing secure configurations to support reliable student experiments.}
        \resumeItem{Mentored students on software debugging and testing, increasing assignment success rates by 20\% through hands-on guidance.}
        \resumeItem{Developed automation scripts for grading and validation, improving accuracy by 25\% and reducing manual workload significantly.}
        \resumeItem{Conducted interactive sessions on cryptography and network security, clarifying complex concepts for over 15 student cohorts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency API calls in \textbf{TypeScript} achieving under 100ms response time and enhancing data exchange efficiency.}
        \resumeItem{Upgraded frontend with \textbf{Angular.js}, increasing user engagement metrics by 25\% through improved UI responsiveness.}
        \resumeItem{Implemented backend enhancements in \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\% for customer-facing systems.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures reducing frontend load by 15\%, streamlining overall database performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Architected \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, serving 1000+ users with sub-200ms response times.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} via \textbf{Docker}, increasing deployment frequency and reliability.}
        \resumeItem{Created a React.js project management UI enhancing user experience and reducing page load times by 30\% consistently.}
        \resumeItem{Wrote comprehensive unit tests using \textbf{JUnit} to maintain 90\% code coverage, enhancing system reliability and maintainability.}
        \resumeItem{Collaborated across teams to design scalable APIs and optimize backend systems for performance and ease of integration.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI Model Integration for Predictive Analytics} | Python, TensorFlow, Flask, REST API}{}
          \resumeItemListStart
              \resumeItem{Implemented \textbf{TensorFlow} models into a Flask API, enabling real-time predictive analytics with 90\% accuracy on test data.}
              \resumeItem{Designed RESTful APIs for seamless integration with client applications, improving response times by 30\% under load testing.}
              \resumeItem{Optimized data preprocessing pipelines in \textbf{Python}, reducing model inference latency by 20\% and improving scalability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-based Scalable Microservice Architecture} | AWS, Docker, Kubernetes, Java Spring Boot}{}
          \resumeItemListStart
              \resumeItem{Developed Dockerized microservices deployed on AWS EKS, achieving automated scaling to handle 1000+ requests per minute efficiently.}
              \resumeItem{Integrated distributed tracing and logging, reducing mean time to diagnose issues by 35\% in production environments.}
              \resumeItem{Implemented secure API gateways with authentication and role-based access control, enhancing system security by 40\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, C\#, JavaScript, TypeScript, C++, PHP \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, Django, Flask \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda, EKS), Docker, Kubernetes, Jenkins, CI/CD Pipelines \\
                \textbf{Software Engineering Tools:} & Git, GitHub, RESTful API, GraphQL, JUnit, Agile Methodologies \\
                \textbf{AI \& Machine Learning:} & TensorFlow, PyTorch, scikit-learn, MLOps, LLM Integration, OpenAI API \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}