\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices to improve scalability, raising API performance by 35\% for customer-facing services.}
        \resumeItem{Implemented \textbf{Spring Security} upgrades for authentication and role-based access control, reducing breaches by 40\%.}
        \resumeItem{Launched an \textbf{AI-driven} code review assistant using \textbf{LLMs}, cutting manual review time by 45\% and speeding development by 25\%.}
        \resumeItem{Automated \textbf{CI/CD} pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating release frequency by 40\% for multiple projects.}
        \resumeItem{Collaborated asynchronously with cross-functional teams improving system integration and reducing customer onboarding time by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and deployed a \textbf{SaaS} data visualization platform using \textbf{Laravel} and \textbf{React}, supporting 50+ users concurrently.}
        \resumeItem{Automated daily stock data pipelines with \textbf{Python}, processing 10,000+ entries and reducing manual efforts by 80\%.}
        \resumeItem{Developed an \textbf{AI-powered} LinkedIn outreach bot increasing qualified leads by 40\% through automated content and targeting.}
        \resumeItem{Refined \textbf{React} components improving state management, lowering page load times by 25\% and enhancing engagement.}
        \resumeItem{Led backend development to integrate \textbf{Stripe} and WooCommerce, enabling secure role-based access in subscription platform.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained Linux infrastructure for cybersecurity lab environments, ensuring stable and secure remote access for over 100 students.}
        \resumeItem{Automated grading scripts enhancing accuracy by 25\%, reducing instructor workload during multiple course offerings.}
        \resumeItem{Guided students in debugging and deploying software, improving assignment success rates by 20\% through hands-on support sessions.}
        \resumeItem{Conducted 15+ interactive webinars explaining network security, cryptography, and protocols for diverse student groups.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed high-performance \textbf{TypeScript} APIs achieving sub-100ms responses for seamless data flow across microservices.}
        \resumeItem{Improved user engagement by 25\% through \textbf{Angular.js} platform upgrades and interactive UI component enhancements.}
        \resumeItem{Reduced data retrieval latency by 30\% by optimizing \textbf{.NET} backend and rewriting key business logic modules.}
        \resumeItem{Enhanced \textbf{PostgreSQL} stored procedures, lessening frontend database load by 15\% and speeding transaction processing.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices handling 1000 users concurrently, improving response times under 200ms.}
        \resumeItem{Built React.js management UI, enhancing usability and boosting page speed by 30\% for project tracking tool.}
        \resumeItem{Created \textbf{CI/CD} pipelines for Docker-deployed microservices on \textbf{AWS EC2}, streamlining releases and reducing downtime.}
        \resumeItem{Implemented \textbf{JUnit} tests achieving 90\% coverage, increasing reliability of core microservice modules.}
        \resumeItem{Collaborated on SaaS tool automating SDLC processes, reducing manual developer tasks and accelerating deployment cycles.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Onboarding Automation} | Node.js, React, AWS Lambda, GraphQL}
          \resumeItemListStart
              \resumeItem{Designed an automated onboarding flow with \textbf{GraphQL} APIs enabling 30\% faster customer sign-up and conversion improvement.}
              \resumeItem{Integrated \textbf{AWS Lambda} functions automating backend processes, reducing average onboarding time by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{End-to-End Insurance Purchase Flow Revamp} | TypeScript, Nest.js, React Native, DynamoDB}
          \resumeItemListStart
              \resumeItem{Refactored shopping and purchase flows using \textbf{Nest.js} backend and \textbf{React Native}, increasing user conversions by 20\%.}
              \resumeItem{Streamlined cross-team systems interaction with \textbf{DynamoDB} data consistency improvements, reducing bugs by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Driven Customer Communication Bot} | OpenAI API, TypeScript, AWS, Node.js}
          \resumeItemListStart
              \resumeItem{Built an AI chatbot system leveraging \textbf{OpenAI API} that automated 60\% of customer support queries with human fallback.}
              \resumeItem{Reduced customer response times by 40\% through asynchronous message processing and smart intent classification.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & TypeScript, JavaScript, Java, Python, PHP, C\#, Shell Scripting \\
                \textbf{Frontend \& Backend Frameworks:} & React, React Native, Next.js, Nest.js, Node.js, Spring Boot, Laravel \\
                \textbf{Databases \& Data Storage:} & PostgreSQL, DynamoDB, MySQL, Redis, Clickhouse \\
                \textbf{Cloud \& Infrastructure:} & AWS (Lambda, ECS, EKS, S3, EC2), Docker, Microservices, Containerization \\
                \textbf{APIs \& Automation:} & GraphQL, REST, OpenAI API, LLM Integration, AI Agents, Automation Workflows \\
                \textbf{Tools \& Methodologies:} & Git, Jenkins, Jira, Agile, Asynchronous Collaboration, CI/CD Pipelines \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}