\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered modular \textbf{Java Spring Boot} microservices improving scalability by 35\% and throughput for mission-critical applications.}
        \resumeItem{Enhanced security by integrating \textbf{Spring Security} for authentication, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant that cut manual review time by 45\% and accelerated development velocity by 25\%.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} pipelines, reducing deployment cycle time by 40\% and increasing release reliability.}
        \resumeItem{Collaborated cross-functionally to design robust APIs supporting seamless integration and enhanced data flow across platforms.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led development of dynamic \textbf{SaaS} data visualization tools in \textbf{Laravel} and \textbf{React}, supporting 50+ simultaneous users.}
        \resumeItem{Streamlined data processing pipelines with \textbf{Python}, automating 10,000+ daily stock entries and reducing manual effort by 80\%.}
        \resumeItem{Implemented role-based access and subscription features using \textbf{PHP}, \textbf{Stripe}, and \textbf{WooCommerce} improving customer retention.}
        \resumeItem{Built AI agents leveraging \textbf{LLMs} automating FINRA broker data downloads, cutting manual data handling time by 80\%.}
        \resumeItem{Optimized \textbf{React} component state management, reducing load times by 25\% and increasing user engagement metrics significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab infrastructure ensuring consistent and reliable execution environments for cybersecurity research.}
        \resumeItem{Assisted students in debugging, deploying, and testing, improving software module completion rates by 20\%.}
        \resumeItem{Developed automation scripts for grading and validation, increasing grading accuracy by 25\% and decreasing workload.}
        \resumeItem{Facilitated 15+ technical sessions on cryptography, networking protocols, and web security, enhancing student learning engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls achieving under 100ms response times and improving frontend responsiveness.}
        \resumeItem{Refined frontend with \textbf{Angular.js}, boosting user engagement by 25\% through improved UI/UX design and interaction.}
        \resumeItem{Engineered scalable \textbf{C\# .NET} backend services reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend database load by 15\% and improving query efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{Java Spring Boot} microservices for SDLC automation, supporting 1000 concurrent users with sub-200ms latency.}
        \resumeItem{Developed \textbf{React.js} project tracking UI enhancing usability and speeding page load times by 30\%.}
        \resumeItem{Managed CI/CD pipelines utilizing \textbf{Docker} on \textbf{AWS EC2}, enabling smooth deployments of multiple microservices.}
        \resumeItem{Wrote unit tests with \textbf{JUnit} achieving 90\% coverage and improving pipeline reliability and maintainability.}
        \resumeItem{Collaborated within a 5-member team to evolve SaaS tools, driving process optimization and enhanced system modularity.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Assisted Code Review Bot} | GitHub Actions, OpenAI API, Python}
          \resumeItemListStart
              \resumeItem{Created an AI-powered bot analyzing pull requests for issues and auto-generating docstrings, cutting review time by 25\%.}
              \resumeItem{Integrated with \textbf{GitHub Actions} to enforce code standards and maintain 100\% documentation coverage across Python projects.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Modular Web UI Components for SaaS Platform} | TypeScript, Vue.js, Node.js}
          \resumeItemListStart
              \resumeItem{Developed reusable \textbf{Vue.js} components with TypeScript enhancing frontend scalability and reducing development overhead by 30\%.}
              \resumeItem{Collaborated on API design enabling seamless interaction between backend \textbf{Node.js} services and dynamic UI components.}
              \resumeItem{Implemented automated testing and continuous integration to ensure code quality and reliable deployment pipelines.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & TypeScript, JavaScript, Java, Python, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & Vue.js (v3), Node.js, React.js, Angular.js, Laravel, Spring Boot, HTML5, CSS3 \\
                \textbf{Databases \& Storage:} & PostgreSQL, MySQL, MongoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3), Docker, Jenkins, CI/CD pipelines \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, AI Agents, Automation workflows \\
                \textbf{Tools \& Others:} & Git, GitHub, REST APIs, Webpack, VueCLI, Linux/Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}