\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed scalable \textbf{Java Spring Boot} microservices enhancing API throughput by 35\% and optimizing system responsiveness.}
        \resumeItem{Implemented role-based security with \textbf{Spring Security}, reducing unauthorized access attempts by 40\% across critical services.}
        \resumeItem{Developed an \textbf{AI-driven} code review assistant using \textbf{LLMs}, improving PR review efficiency by 45\% and reducing bugs in production.}
        \resumeItem{Automated CI/CD workflows through \textbf{Jenkins} and \textbf{Docker}, accelerating deployment cycles and shortening release time by 40\%.}
        \resumeItem{Collaborated extensively with cross-functional teams to deliver software upgrades adhering to enterprise architecture standards.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a robust \textbf{SaaS} platform using \textbf{Laravel} and \textbf{React}, supporting concurrent access for 50+ users with seamless UX.}
        \resumeItem{Automated \textbf{Python}-based data pipelines processing 10,000+ stocks daily, reducing manual data entry by 80\% and improving accuracy.}
        \resumeItem{Engineered AI agents with \textbf{LLM} integration to automate FINRA broker data downloads, streamlining workflow by 80\% and cutting errors.}
        \resumeItem{Built a LinkedIn outreach bot leveraging AI for content automation and lead targeting, increasing qualified leads by 40\% through personalization.}
        \resumeItem{Optimized \textbf{React} components and state management, reducing page load times by 25\% and enhancing user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab infrastructure supporting student cybersecurity projects and protocols with 99\% uptime.}
        \resumeItem{Facilitated students' debugging and deployment of software modules, increasing assignment pass rate by 20\% through guided support.}
        \resumeItem{Automated grading scripts for assignments, improving evaluation accuracy and reducing manual review workload by 25\%.}
        \resumeItem{Conducted interactive sessions on Cryptography and Web Security, improving student comprehension and engagement in complex topics.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed high-performance backend services in \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Enhanced \textbf{Angular.js} frontend components, resulting in a 25\% increase in user satisfaction and engagement metrics.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, lowering frontend load by 15\% and improving system database efficiency.}
        \resumeItem{Implemented asynchronous API calls in \textbf{TypeScript}, maintaining sub-100ms average response time for critical user requests.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Contributed to a 5-member team developing a \textbf{SaaS} tool that automates SDLC processes, reducing release times substantially.}
        \resumeItem{Built and deployed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, handling 1000+ concurrent users with under 200ms latency.}
        \resumeItem{Designed and maintained \textbf{CI/CD} pipelines using \textbf{Docker} on \textbf{AWS EC2} to enable smooth microservice deployments.}
        \resumeItem{Developed project management UI in \textbf{React.js}, increasing usability and load speed by 30\% for end users.}
        \resumeItem{Achieved 90\% unit test coverage on pipelines using \textbf{JUnit}, improving system reliability and reducing defects.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Application Code Analyzer} | Python, OpenAI API, CI/CD Automation}{}
          \resumeItemListStart
              \resumeItem{Developed an AI tool integrating \textbf{OpenAI API} to automatically review and document \textbf{C\#} code changes, reducing review time by 30\%.}
              \resumeItem{Automated deployment of this tool within \textbf{Azure DevOps} pipelines, accelerating release cycles and improving codebase quality.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Enterprise Web Service Integration} | .NET, WCF, SOAP, SQL Server}{}
          \resumeItemListStart
              \resumeItem{Engineered secure \textbf{WCF} web services enabling seamless data exchange between internal \textbf{SQL Server} databases and external partners.}
              \resumeItem{Implemented application design adhering to N-Tier architecture, improving maintainability and reducing coupling across service layers.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Workflow Automation using Windows Workflow Foundation} | WWF, C\#, Azure DevOps}{}
          \resumeItemListStart
              \resumeItem{Designed automated business processes with \textbf{Windows Workflow Foundation}, cutting manual task times by 40\% and improving system accuracy.}
              \resumeItem{Integrated workflow deployments within \textbf{Azure DevOps} CI/CD pipelines to streamline updates and improve release reliability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & C\#, .NET 4.8+, Java, Python, JavaScript, Spring Boot, React.js \\
                \textbf{Web Services \& Architecture:} & WCF, SOAP, REST, Service-Oriented Architecture (SOA), N-Tier Architecture \\
                \textbf{Databases \& Reporting:} & SQL Server, Oracle, ANSI SQL, Crystal Reports, LLBLGen ORM \\
                \textbf{DevOps \& CI/CD:} & Azure DevOps, Jenkins, Docker, CI/CD Pipelines, AWS EC2, S3 \\
                \textbf{Workflow \& Enterprise Tools:} & Windows Workflow Foundation (WWF), IBM FileNet, HP Exstream \\
                \textbf{Methodologies \& Practices:} & Agile, Scrum, Waterfall, Iterative Development, Code Reviews, Security Risk Assessment \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}