\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced full stack web features with \textbf{React} and \textbf{Node.js}, increasing user page engagement by 30\%.}
        \resumeItem{Collaborated with design and marketing teams to implement dynamic content updates, reducing release time by 25\%.}
        \resumeItem{Contributed to internal design system updates, boosting component reusability by 40\%.}
        \resumeItem{Streamlined deployment pipelines using \textbf{CI/CD} tools, cutting build failures by 35\%.}
        \resumeItem{Led architectural improvements with focus on scalability and maintainability, improving system uptime by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed responsive \textbf{React} components, decreasing page load time by 25\% and increasing conversion rates.}
        \resumeItem{Automated integrations with marketing tools to streamline product launch processes, reducing manual steps by 50\%.}
        \resumeItem{Implemented backend APIs with \textbf{Node.js} and \textbf{PostgreSQL}, supporting 45\% more concurrent users.}
        \resumeItem{Built AI-powered outreach tools to enhance lead generation, increasing qualified leads by 40\%.}
        \resumeItem{Maintained content management system upgrades ensuring seamless updates for public facing properties.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported secure Linux environments for labs, enhancing reliability and reducing system downtime by 15\%.}
        \resumeItem{Coached students on code deployment and troubleshooting, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading workflows using Python scripts, increasing grading speed and accuracy by 25\%.}
        \resumeItem{Led technical sessions on Networking and Web Security to improve student comprehension and interest.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient API solutions in \textbf{TypeScript}, achieving response times under 100ms.}
        \resumeItem{Modernized front-end features with \textbf{Angular.js}, boosting user engagement by 25\%.}
        \resumeItem{Developed high-performance \textbf{C\#} backend services, reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and procedures, enhancing database efficiency by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered microservices in \textbf{Java Spring Boot} handling 1000+ users with sub-200ms response times.}
        \resumeItem{Implemented \textbf{Node.js} services and front-end features using \textbf{React.js}, improving UX speed by 30\%.}
        \resumeItem{Designed and maintained CI/CD pipelines with \textbf{Docker} and \textbf{AWS EC2}, reducing deployment failures by 40\%.}
        \resumeItem{Developed scalable database schemas in \textbf{MySQL} supporting complex user roles and product launch features.}
        \resumeItem{Authored unit and integration tests using \textbf{JUnit}, achieving 90\% coverage across key modules.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Web Content Automation} | React, Node.js, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an automation tool that generates and updates marketing content using \textbf{OpenAI API}, reducing manual content creation by 60\%.}
              \resumeItem{Integrated front-end \textbf{React} components with backend \textbf{Node.js} APIs to deliver dynamic, personalized user experiences.}
              \resumeItem{Optimized deployment workflows with automated testing and updates, accelerating release cycles by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Next.js Scalable CMS Platform} | Next.js, PostgreSQL, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Built a modular \textbf{Next.js} CMS platform with backend powered by \textbf{PostgreSQL} to support high traffic marketing sites.}
              \resumeItem{Deployed containerized services orchestrated by \textbf{Kubernetes}, enabling scalable and fault-tolerant infrastructure.}
              \resumeItem{Implemented CI/CD pipelines to automate build, test, and deployment, reducing errors by 35\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Frontend Development:} & JavaScript, React.js, Next.js, HTML, CSS, Angular.js \\
                \textbf{Backend Development:} & Node.js, Java Spring Boot, PHP, Python, C\#, .NET \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB \\
                \textbf{DevOps \& Deployment:} & Docker, Kubernetes, CI/CD, Jenkins, AWS EC2, S3 \\
                \textbf{Tools \& Platforms:} & Git, GitHub, REST API, Nginx, Jira \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}