\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices to improve device monitoring throughput by 35%, supporting reliability at scale.}
        \resumeItem{Implemented automated incident response tools that reduced outage detection time by 40\% and improved system uptime.}
        \resumeItem{Designed and deployed data analytics pipelines using \textbf{Python} for real-time device health trend analysis across multiple platforms.}
        \resumeItem{Led cross-team efforts to integrate new monitoring metrics into existing dashboards, improving visibility into device issues by 30\%.}
        \resumeItem{Built secure authentication enhancements with \textbf{Spring Security} to safeguard API access, reducing unauthorized requests by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Python} automation for large-scale log data parsing that improved issue triaging speed by 50\%.}
        \resumeItem{Created AI-driven monitoring dashboards with \textbf{React} and \textbf{Node.js} enhancing data visualization reliability insights for partners.}
        \resumeItem{Automated deployment pipelines using \textbf{Docker} and cloud services, reducing release cycle times by 35\%.}
        \resumeItem{Built an AI-powered alert system to proactively notify issues, lowering incident response times by 45\%.}
        \resumeItem{Collaborated with security teams to integrate DRM compliance checks, improving content protection across services by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained Linux-based environments ensuring secure, stable infrastructure supporting cybersecurity labs with 99.9\% uptime.}
        \resumeItem{Automated software deployment and validation scripts using \textbf{Python}, reducing manual grading workload by 25\%.}
        \resumeItem{Supported student debugging sessions, increasing assignment completion success rates by 20\%.}
        \resumeItem{Developed documentation for lab environments improving onboarding efficiency for new users by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, reducing database latency by 15\% to improve system responsiveness.}
        \resumeItem{Improved backend \textbf{C\# .NET} service throughput by 30\% with optimized threading and resource management.}
        \resumeItem{Engineered fast-responding APIs using \textbf{TypeScript} achieving sub-100ms latency across client-server communications.}
        \resumeItem{Upgraded \textbf{Angular.js} frontend components to enhance client experience, resulting in 25\% increased user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Spring Boot} microservices handling 1000+ concurrent users, reducing average response times below 200ms.}
        \resumeItem{Implemented CI/CD pipelines on \textbf{AWS EC2} with \textbf{Docker} to automate reliable deployments for critical services.}
        \resumeItem{Built React.js UI for project tracking, enhancing usability and reducing page load times by 30\%.}
        \resumeItem{Authored unit tests with \textbf{JUnit}, achieving 90\% coverage to enhance software reliability and maintainability.}
        \resumeItem{Collaborated with cross-functional teams to solve complex issues, improving production stability by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Device Health Monitoring System} | Python, AWS, Data Visualization APIs}{}
          \resumeItemListStart
              \resumeItem{Created real-time monitoring with \textbf{Python} and cloud services to analyze device metrics across hundreds of smart devices.}
              \resumeItem{Developed automated anomaly detection algorithms to identify deviations, reducing incident detection time by 40\%.}
              \resumeItem{Implemented interactive dashboards consolidating health data, improving operational decisions and reliability by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated Incident Response AI Agent} | LLMs, Node.js, GitHub API}{}
          \resumeItemListStart
              \resumeItem{Built an AI agent integrating \textbf{LLMs} to analyze incident logs and recommend fixes, reducing mean time to recovery by 35\%.}
              \resumeItem{Automated pull request reviews with \textbf{GitHub API} and \textbf{Node.js}, accelerating code quality checks by 25\%.}
              \resumeItem{Designed the system to support continuous deployment workflows, enhancing team productivity and operational reliability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, TypeScript, Node.js, C\# \\
                \textbf{Embedded \& Device Tech:} & DRM, Device Security Concepts, Video Pipeline Basics, Consumer Embedded Devices \\
                \textbf{Data \& Analytics:} & SQL, PostgreSQL, Data Visualization, Large Data Set Analysis \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Automation \& AI Tools:} & LLM Integration, GitHub API, AI Agents, Automation Tools Development \\
                \textbf{Web Frameworks \& Tools:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}