\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable backend microservices using \textbf{Java Spring Boot} enhancing API throughput by 35\% under heavy loads.}
        \resumeItem{Implemented robust \textbf{Spring Security} features that cut unauthorized access attempts by 40\% through enhanced auth controls.}
        \resumeItem{Automated code review with \textbf{AI-driven} assistant using \textbf{LLMs}, reducing manual effort by 45\% and speeding development by 25\%.}
        \resumeItem{Configured \textbf{Jenkins} and \textbf{Docker} CI/CD pipelines to reduce build and deployment cycle times by 40\%.}
        \resumeItem{Collaborated cross-functionally to deliver reliable software features meeting high scalability and customer experience standards.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed SaaS data visualization platform with \textbf{Laravel} and \textbf{React} supporting 50+ concurrent users smoothly.}
        \resumeItem{Automated daily processing of 10,000+ stock entries with \textbf{Python} pipelines, reducing manual workload by 80\%.}
        \resumeItem{Built multi-tier subscription platform using \textbf{PHP}, implementing role-based access and \textbf{Stripe} payment integration.}
        \resumeItem{Developed AI agents using \textbf{LLMs} automating FINRA data downloads, reducing manual intervention by 80\%.}
        \resumeItem{Optimized \textbf{React} components to boost UI responsiveness, cutting page load times by 25\% and increasing user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab infrastructures ensuring security configurations and system reliability.}
        \resumeItem{Assisted students with debugging and deploying software modules improving successful software runs by 20\%.}
        \resumeItem{Automated grading scripts minimizing manual workload and increasing grading accuracy by 25\%.}
        \resumeItem{Conducted 15+ interactive sessions demystifying cryptography, network protocols, and web security topics for students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed efficient \textbf{TypeScript} API calls achieving sub-100ms responses supporting seamless frontend/backend interaction.}
        \resumeItem{Enhanced platform using \textbf{Angular.js} improving user engagement and satisfaction by 25\% via UI upgrades.}
        \resumeItem{Built and optimized performant backend services in \textbf{C\#} and \textbf{.NET}, reducing data latency by 30\%.}
        \resumeItem{Streamlined database operations through optimized \textbf{PostgreSQL} stored procedures, lowering load times by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000 users with sub-200ms response times enhancing SaaS platform.}
        \resumeItem{Deployed 6 microservices on \textbf{AWS EC2} using \textbf{Docker} and automated CI/CD pipelines accelerating releases by 30\%.}
        \resumeItem{Created project management UI in \textbf{React.js}, improving usability and page load speeds by 30\%.}
        \resumeItem{Achieved 90\% code coverage by implementing \textbf{JUnit} unit tests for critical microservice components.}
        \resumeItem{Collaborated closely in agile teams driving cross-functional development and deployment of distributed system services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Real-time Distributed Control Plane for Data Streams} | Node.js, TypeScript, AWS}{}
          \resumeItemListStart
              \resumeItem{Built a distributed control plane managing real-time data streams using scalable \textbf{Node.js} services on \textbf{AWS}, handling 10K+ events/second.}
              \resumeItem{Implemented REST and gRPC APIs to enable seamless orchestration of distributed nodes, improving deployment speed by 20\%.}
              \resumeItem{Developed automated testing pipelines for control plane features with \textbf{Jest} ensuring 95\% code coverage and high reliability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Telemetry Data Transformation & Processing Framework} | Java, Spring Boot, Kafka}{}
          \resumeItemListStart
              \resumeItem{Designed a high-throughput telemetry pipeline using \textbf{Spring Boot} and \textbf{Kafka} processing 50K+ log events/min with 99.9\% uptime.}
              \resumeItem{Optimized transformation algorithms increasing processing efficiency by 30\% and reducing latency under peak loads.}
              \resumeItem{Established integration tests and monitoring dashboards to ensure data accuracy and system observability in real time.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, JavaScript, Node.js, Python, C\#, PHP \\
                \textbf{Web \& Backend Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET, Express.js \\
                \textbf{Cloud Platforms:} & AWS (EC2, S3, Lambda), Azure, GCP \\
                \textbf{Data Streaming \& Messaging:} & Kafka, gRPC, REST API, WebSockets \\
                \textbf{Testing \& Automation:} & Jest, Mocha, Playwright, Jenkins, Docker, CI/CD pipelines \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}