\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices, boosting API throughput by 35\% to support high-volume financial analytics.}
        \resumeItem{Implemented \textbf{Spring Security} role-based authentication, decreasing unauthorized access incidents by 40\%.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant, reducing manual code review time by 45\% and accelerating deployment by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, decreasing release frequency cycle time by 40\%.}
        \resumeItem{Collaborated within a team to manage distributed systems and maintain multi-threaded code for scalable cloud deployment.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{SaaS} data visualization platform with \textbf{Laravel} and \textbf{React}, enabling 50+ users concurrent access flawlessly.}
        \resumeItem{Automated daily stock data pipelines in \textbf{Python}, reducing manual workload by 80\% and improving data accuracy.}
        \resumeItem{Created AI-based \textbf{LLM} agents automating FINRA broker data downloads, cutting manual processing time by 80\%.}
        \resumeItem{Optimized \textbf{React} components, reducing page load times by 25\% and increasing overall client engagement.}
        \resumeItem{Implemented role-based access control with \textbf{Stripe} and WooCommerce, enhancing e-commerce workflow and security.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} systems for cybersecurity labs, ensuring stable execution environments for 20+ students.}
        \resumeItem{Automated validation scripts, improving grading accuracy by 25\% and reducing instructor manual workload.}
        \resumeItem{Supported student debugging and deployment of software, raising assignment success rates by 20\%.}
        \resumeItem{Conducted 15+ technical sessions on Cryptography, Networking, and Web Security, enhancing class understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Delivered API enhancements in \textbf{TypeScript}, achieving response times under 100ms for seamless data flow.}
        \resumeItem{Refined \textbf{Angular.js} frontend, increasing user engagement and satisfaction rates by 25\%.}
        \resumeItem{Engineered backend services using \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures to improve database efficiency and reduce front-end load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, handling 1000 users with sub-200ms response.}
        \resumeItem{Automated deployments of six core microservices on \textbf{AWS EC2} using \textbf{Docker}, streamlining CI/CD pipeline.}
        \resumeItem{Developed project management UI with \textbf{React.js}, improving usability metrics and reducing page load times by 30\%.}
        \resumeItem{Wrote \textbf{JUnit} unit tests covering 90\% of pipelines module, enhancing code reliability and maintainability.}
        \resumeItem{Collaborated on a team to develop SDLC automation SaaS tool, significantly improving development workflow efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cloud-Based Financial Analytics Dashboard} | AWS, React, Node.js, PostgreSQL}{}
          \resumeItemListStart
              \resumeItem{Engineered a scalable dashboard using \textbf{React} and \textbf{Node.js}, providing real-time analytics to 1000+ finance users.}
              \resumeItem{Implemented backend APIs with \textbf{PostgreSQL} data queries, achieving sub-200ms response for complex financial data requests.}
              \resumeItem{Managed deployments on \textbf{AWS} with auto-scaling, ensuring 99.9\% uptime under variable traffic conditions.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Multi-threaded Stock Data Processing System} | Python, Kafka, Cassandra, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed a multi-threaded data pipeline using \textbf{Python} and \textbf{Kafka} to process over 10K stock entries daily efficiently.}
              \resumeItem{Utilized \textbf{Cassandra} for fast unstructured data storage, reducing query times by 30\% during peak loads.}
              \resumeItem{Deployed on \textbf{AWS} cloud stack, achieving high availability and fault tolerance for critical financial data operations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, C\#, C++, JavaScript, TypeScript, Ruby, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Vue, Laravel, Node.js, .NET, HTML5, CSS3 \\
                \textbf{Database Technologies:} & PostgreSQL, MySQL, Cassandra, Kafka, SQL, MongoDB \\
                \textbf{Cloud Platforms \& DevOps:} & AWS (EC2, S3, Lambda), Azure, Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Operating Systems \& Tools:} & Linux, Windows, Git, REST API, gRPC, Jira, JUnit \\
                \textbf{AI \& Automation:} & Machine Learning, OpenAI API, LLM Integration, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}