\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices enhancing API scalability, achieving 35\% performance improvements across multiple endpoints.}
        \resumeItem{Implemented \textbf{Spring Security} role-based access control, reducing unauthorized access attempts by 40\% through tightened authentication.}
        \resumeItem{Deployed an AI-driven code review assistant using \textbf{LLMs}, decreasing manual review time by 45\% and accelerating development cycles 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing deployment release times by 40\% and improving reliability.}
        \resumeItem{Designed and maintained API interfaces that improved integration with legacy systems, boosting data consistency and access speed by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{React} and \textbf{Laravel} SaaS platform unifying data sources, supporting 50+ concurrent users with seamless scalability.}
        \resumeItem{Automated Python ETL pipelines processing 10,000+ daily records, cutting manual data handling workloads by 80\% and enhancing output accuracy.}
        \resumeItem{Built subscription e-commerce platform using \textbf{PHP} integrated with \textbf{Stripe}, enabling granular role-based access control and secure payments.}
        \resumeItem{Led AI agent development leveraging \textbf{LLMs} automating broker data downloads, slashing operational efforts by 80\% and speeding data refresh.}
        \resumeItem{Optimized \textbf{React} components improving UX and reducing page load times by 25\%, increasing user engagement significantly within product dashboards.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments, ensuring reliable infrastructure and timely software deployment for cybersecurity coursework.}
        \resumeItem{Led student support sessions, improving debugging and deployment skills that increased assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts increasing accuracy and reducing manual effort by 25\%, streamlining coursework evaluation for instructors.}
        \resumeItem{Conducted over 15 technical workshops on cryptography, networking protocols, and security fundamentals improving student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced API integration using \textbf{TypeScript} achieving sub-100ms response times, improving real-time data access across services.}
        \resumeItem{Modernized platform frontend with \textbf{Angular.js}, increasing user engagement and satisfaction metrics by 25\% through UI improvements.}
        \resumeItem{Developed high-performance backend services in \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, cutting frontend load by 15\% and enhancing overall database query efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built microservices in \textbf{Spring Boot} integrated with \textbf{MySQL}, supporting 1000+ users and reducing response times below 200ms.}
        \resumeItem{Implemented CI/CD pipelines deploying six microservices on \textbf{AWS EC2} using \textbf{Docker}, ensuring zero downtime releases.}
        \resumeItem{Developed React-based project management UI boosting usability and decreasing load times by 30\%, enhancing client satisfaction.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} tests achieving 90\% coverage, raising code quality and reducing defect rates.}
        \resumeItem{Collaborated on full-stack SaaS automation tools, streamlining SDLC processes and increasing team productivity significantly.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Unified Construction API Gateway} | Node.js, Express, React}{}
          \resumeItemListStart
              \resumeItem{Developed a unified API platform integrating fragmented construction software systems, increasing data accessibility by 50\%.}
              \resumeItem{Built scalable backend services with \textbf{Node.js} standardizing pagination, filtering, authentication, and caching features across client systems.}
              \resumeItem{Designed React frontend to dogfood the API internally, improving real-time data interaction and user feedback by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered API Testing and Release Pipeline} | Python, GitHub Actions, LLMs}{}
          \resumeItemListStart
              \resumeItem{Automated testing for 1000+ API endpoints using AI-driven scripting, increasing test coverage by 40\% and reducing manual errors.}
              \resumeItem{Implemented continuous integration with \textbf{GitHub Actions} and \textbf{LLM}-based validation, reducing release cycle time by 35\%.}
              \resumeItem{Incorporated dynamic test case generation based on API change logs, improving release reliability and reducing downtime.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, JavaScript, TypeScript, C\#, PHP, Go, C++, Shell Scripting \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Node.js, Laravel, Angular.js, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, GitHub Actions \\
                \textbf{API \& Integration:} & REST API, gRPC, JSON, OAuth, API Gateway Design \\
                \textbf{AI \& Automation:} & LLM integration, OpenAI API, n8n, Zapier, AI agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}