\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices, boosting API throughput by 35\% through optimization of backend logic.}
        \resumeItem{Integrated \textbf{Spring Security} for role-based access, decreasing unauthorized access incidents by 40\%.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant using LLMs, cutting manual review time by 45\% and speeding development by 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 40\% across multiple services.}
        \resumeItem{Collaborated cross-functionally to enhance full stack APIs, facilitating seamless third-party integrations and securing endpoints.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed a \textbf{React} + \textbf{Laravel} SaaS platform supporting 50+ concurrent users with real-time data visualizations.}
        \resumeItem{Automated daily stock data pipelines in \textbf{Python}, reducing manual processing time by 80\% and increasing accuracy.}
        \resumeItem{Implemented AI-powered LLM agents for FINRA data automation, cutting manual tasks by 80\% and improving data quality.}
        \resumeItem{Enhanced React UI components, reducing page load times by 25\% and increasing user engagement metrics significantly.}
        \resumeItem{Built a LinkedIn outreach bot using \textbf{AI} to automate posts and lead targeting, generating 40\% more qualified leads.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} infrastructure and secure configurations for cybersecurity labs, increasing uptime and reliability by 20\%.}
        \resumeItem{Provided debugging guidance on software modules, improving student assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts, reducing manual evaluation workload and improving accuracy by 25\%.}
        \resumeItem{Conducted over 15 interactive online sessions covering Cryptography, Networking, and Web Security topics.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency API endpoints in \textbf{TypeScript}, achieving sub-100ms response times critical to platform performance.}
        \resumeItem{Enhanced user experience by upgrading \textbf{Angular.js} frontend, increasing user engagement by 25\%.}
        \resumeItem{Built performant backend services using \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, improving frontend load times by 15\% and database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users with response times below 200ms.}
        \resumeItem{Built full stack UI in \textbf{React.js} improving page load speed by 30\% and enhancing user usability.}
        \resumeItem{Streamlined deployments with \textbf{Docker}-based CI/CD pipelines on \textbf{AWS EC2}, reducing rollout times significantly.}
        \resumeItem{Implemented unit tests covering 90\%+ of pipelines using \textbf{JUnit}, increasing overall product quality.}
        \resumeItem{Collaborated on SaaS tool development automating SDLC processes, improving team productivity and deployment accuracy.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Healthcare Navigator} | React, Node.js, Python, AWS}
          {}
          \resumeItemListStart
              \resumeItem{Designed a full-stack scalable AI healthcare platform integrating \textbf{LLMs} to deliver personalized treatment and provider recommendations.}
              \resumeItem{Implemented secure patient input workflows with encrypted data handling, improving trust and compliance with healthcare regulations.}
              \resumeItem{Collaborated with data and AI engineers to unify medical record streams into seamless user interactions.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Real-Time Streaming Chatbot Interface} | React, WebSockets, Python}
          {}
          \resumeItemListStart
              \resumeItem{Built interactive UI widgets including tables, forms, and maps supporting live streaming of LLM chatbot responses.}
              \resumeItem{Integrated \textbf{WebSocket} streaming APIs for real-time patient communication, reducing response latency by 50\%.}
              \resumeItem{Deployed rapid prototypes using \textbf{Vercel} for iterative testing, accelerating feature delivery by 30\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Node.js, Spring Boot, Laravel, Angular.js, Django \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, CI/CD (Jenkins, GitHub Actions), Vercel, Netlify \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL, NoSQL \\
                \textbf{AI \& Automation:} & LLM Integration, OpenAI API, AI Agents, Prompt Engineering, WebSockets, Streaming APIs \\
                \textbf{Tools \& Other Technologies:} & Linux, Git, REST API, WebRTC, Authentication/Authorization, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}