\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{Java Spring Boot} backend services, improving API throughput by 35\% while aligning with 12-factor app principles.}
        \resumeItem{Developed reactive \textbf{React} frontends integrating backend APIs, reducing user interface load times by 25\% and enhancing user experience.}
        \resumeItem{Established continuous integration and deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 40\%.}
        \resumeItem{Led paired programming sessions enforcing test-driven development to increase code quality and reduce defects by 30\% in key modules.}
        \resumeItem{Collaborated cross-functionally for system design decisions that simplified architecture, cutting backend service latency by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered a scalable \textbf{React} frontend and RESTful \textbf{Java Spring Boot} backend, supporting 50+ concurrent SaaS users efficiently.}
        \resumeItem{Automated data ingestion and processing pipelines in \textbf{Python}, resulting in 80\% reduction of manual data handling tasks.}
        \resumeItem{Implemented continuous integration workflows ensuring seamless deployment with zero downtime for microservice updates.}
        \resumeItem{Refined application state management and UI components in \textbf{React}, improving page load speeds by 25\%.}
        \resumeItem{Enhanced security features with token-based authentication and role-based access control, decreasing unauthorized access by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported and maintained \textbf{Linux}-based lab environments to ensure secure and stable systems for student projects.}
        \resumeItem{Assisted students with debugging, deploying, and testing software modules, improving project success rates by 20\%.}
        \resumeItem{Automated lab assignment validation scripts, increasing accuracy by 25\% and reducing manual grading workload.}
        \resumeItem{Conducted interactive educational sessions covering networking protocols and web security concepts to enhance learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented responsive API endpoints in \textbf{TypeScript}, achieving consistent sub-100ms backend response times for users.}
        \resumeItem{Revamped legacy \textbf{Angular.js} frontend features, increasing user engagement and satisfaction by 25\%.}
        \resumeItem{Developed \textbf{C\# .NET} backend enhancements that reduced data retrieval latency by 30\% for core services.}
        \resumeItem{Optimized \textbf{PostgreSQL} database queries and stored procedures to decrease frontend load times by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users with under 200ms latency.}
        \resumeItem{Implemented end-to-end \textbf{CI/CD} pipelines using \textbf{Docker} and \textbf{AWS EC2}, reducing deployment times by 35\%.}
        \resumeItem{Developed and optimized \textbf{React.js} frontend components, improving usability and page load speed by 30\%.}
        \resumeItem{Practiced test-driven development writing \textbf{JUnit} unit tests covering 90\% of core backend modules.}
        \resumeItem{Collaborated in paired programming and team retrospectives, improving codebase quality and team productivity by 20\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{12-Factor Compliant Web Application} | Java Spring Boot, React, Jenkins}{}
          \resumeItemListStart
              \resumeItem{Designed and built a full stack web app following 12-factor principles, improving modularity and deployment readiness by 40\%.}
              \resumeItem{Implemented continuous integration and deployment pipelines with \textbf{Jenkins}, automating testing and releases for rapid iteration cycles.}
              \resumeItem{Leveraged test-driven development to create robust backend APIs and frontends with over 90\% test coverage, reducing bugs by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Agile Task Management Dashboard} | React, Java Spring Boot, Docker}{}
          \resumeItemListStart
              \resumeItem{Engineered a task management tool with \textbf{React} frontend and \textbf{Spring Boot} REST APIs, enhancing team collaboration efficiency by 35\%.}
              \resumeItem{Containerized services using \textbf{Docker} and deployed on cloud infrastructure, enabling scalable, consistent runtime environments.}
              \resumeItem{Incorporated paired programming and continuous integration practices, accelerating development cycles and improving software quality.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, JavaScript, Python, TypeScript, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Jenkins, Docker \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{DevOps \& Cloud:} & AWS EC2, Docker, Jenkins, Continuous Integration/Delivery \\
                \textbf{Methodologies \& Practices:} & Test-Driven Development, Paired Programming, 12-Factor App Principles \\
                \textbf{Tools \& Other Technologies:} & Git, REST APIs, Agile, JUnit, Linux/Unix \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}