\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered responsive \textbf{React} components improving UI load speed by 30\% and enhancing user engagement across multiple devices.}
        \resumeItem{Collaborated with backend team using \textbf{Node.js} and \textbf{Express} to integrate APIs, reducing data latency by 20\%.}
        \resumeItem{Streamlined CI/CD with \textbf{Jenkins} and \textbf{Docker}, decreasing deployment times by 40\% and improving release reliability.}
        \resumeItem{Implemented unit and integration tests using \textbf{Jest}, increasing code coverage by 35\% and reducing bug rates in production.}
        \resumeItem{Spearheaded accessibility enhancements across web apps leading to WCAG 2.1 compliance and improving user satisfaction by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed reusable \textbf{React} components and improved state management, reducing page load times by 25\% and boosting engagement.}
        \resumeItem{Automated backend workflows with \textbf{Node.js} and \textbf{Express}, improving API response times by 30\% and system scalability.}
        \resumeItem{Implemented UI responsiveness and cross-browser compatibility, increasing mobile user retention rates by 20\%.}
        \resumeItem{Integrated SQL databases and optimized queries, reducing data retrieval latency by 15\% and improving app performance.}
        \resumeItem{Developed interactive dashboards with \textbf{React} and \textbf{TypeScript}, enhancing data visualization for 50+ users.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure Linux lab environments and provided technical support, increasing lab uptime reliability by 15\%.}
        \resumeItem{Assisted students in debugging and deploying software components, improving assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts using Python, improving throughput and accuracy of lab submission evaluations by 25\%.}
        \resumeItem{Delivered technical workshops on web security and protocols, boosting student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed frontend modules in \textbf{TypeScript} with sub-100ms response times, improving data delivery speed and UX.}
        \resumeItem{Optimized \textbf{Angular.js} UI components, increasing user engagement by 25\% and application responsiveness.}
        \resumeItem{Built a performant backend using \textbf{C\#} and \textbf{.NET}, reducing data processing latency by 30\%.}
        \resumeItem{Improved \textbf{PostgreSQL} query efficiency, decreasing frontend load times by 15\% and enhancing overall system speed.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{React.js} web components improving page speed by 30\% and user interface consistency.}
        \resumeItem{Led \textbf{Node.js} and \textbf{Express} backend microservices development supporting 1000+ concurrent users with sub-200ms response.}
        \resumeItem{Automated continuous deployment pipelines with \textbf{Docker} on AWS EC2, accelerating release cycles by 35\%.}
        \resumeItem{Implemented SQL queries for \textbf{MySQL} databases optimizing data access and reducing retrieval times by 20\%.}
        \resumeItem{Tested critical modules using \textbf{JUnit}, achieving 90\% coverage and reducing post-release defects by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enhanced Code Review Assistant} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-driven \textbf{GitHub Actions} bot to analyze pull requests, reducing manual review times by 25\%.}
              \resumeItem{Automated \textbf{Python} docstring generation ensuring 100\% documentation coverage and improving code maintainability.}
              \resumeItem{Integrated LLMs to detect bugs and style violations, increasing code quality and speeding up development cycles.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Dynamic Workforce Management Web App} | React.js, Node.js, SQL}{}
          \resumeItemListStart
              \resumeItem{Built a responsive \textbf{React} frontend with mobile compatibility enhancing user experience across devices by 30\%.}
              \resumeItem{Designed scalable backend APIs using \textbf{Node.js} and \textbf{Express} reducing data retrieval latency by 20\%.}
              \resumeItem{Implemented SQL database schema and queries to efficiently manage real-time labor availability and scheduling.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, PHP, C\#, SQL \\
                \textbf{Frontend Development:} & React.js, HTML, CSS, Angular.js, Responsive Design, Accessibility \\
                \textbf{Backend Development:} & Node.js, Express, Spring Boot, .NET, RESTful APIs \\
                \textbf{Databases:} & MySQL, PostgreSQL, SQL, MongoDB \\
                \textbf{DevOps \& Automation:} & Docker, Jenkins, AWS (EC2, S3), CI/CD pipelines \\
                \textbf{AI \& Automation Technologies:} & OpenAI API, LLM Integration, AI Agents, Automation workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}