\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{Java Spring Boot} microservices increasing system throughput by 35\% under high concurrency usage.}
        \resumeItem{Refined authentication mechanisms with \textbf{Spring Security} enhancing application security and reducing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an AI-based code review tool using \textbf{LLMs} that reduced manual review time by 25\% and boosted team productivity.}
        \resumeItem{Automated containerized build and deployment processes with \textbf{Jenkins} and \textbf{Docker}, accelerating release cycles by 40\%.}
        \resumeItem{Collaborated with cross-functional teams improving RESTful API designs that scaled effectively for increasing data and traffic volumes.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a data visualization platform using \textbf{Laravel} and \textbf{React} supporting 50+ concurrent users with zero downtime.}
        \resumeItem{Automated daily data ingestion pipelines with \textbf{Python}, reducing manual efforts by 80\% and increasing data freshness.}
        \resumeItem{Built an AI-based LinkedIn outreach bot improving lead generation by 40\% via automated content posting and targeting.}
        \resumeItem{Implemented multi-tier e-commerce subscription system integrating \textbf{Stripe} and WooCommerce with role-based access controls.}
        \resumeItem{Optimized \textbf{React} components reducing page load times by 25\%, resulting in higher user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based environments for cybersecurity labs increasing system uptime to 99.9\%.}
        \resumeItem{Guided students on debugging and deploying software, elevating assignment success rates by 20\%.}
        \resumeItem{Automated test and grading scripts boosting evaluation accuracy by 25\% and reducing manual review time.}
        \resumeItem{Conducted 15+ sessions on Cryptography and network security enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} APIs achieving sub-100ms response times and seamless integration across modules.}
        \resumeItem{Enhanced user experience by upgrading platform with \textbf{Angular.js}, raising user engagement by 25\%.}
        \resumeItem{Built scalable backend services using \textbf{C\#} and \textbf{.NET} improving data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries reducing frontend server load by 15\%, improving database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices, maintaining sub-200ms response times under 1000 concurrent users.}
        \resumeItem{Constructed \textbf{Docker}-based CI/CD pipelines deploying microservices on \textbf{AWS EC2} to ensure seamless releases.}
        \resumeItem{Built a responsive project management UI using \textbf{React.js} boosting page load speed by 30\%.}
        \resumeItem{Implemented robust unit tests for pipelines with \textbf{JUnit} achieving 90\% test coverage and high code quality.}
        \resumeItem{Collaborated in team to architect a SaaS tool automating SDLC processes, reducing manual steps by 50\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cloud-based Clinical Data Microservices} | Go, Python, Kubernetes, AWS}{}
          \resumeItemListStart
              \resumeItem{Engineered cloud-native microservices in \textbf{Go} and \textbf{Python}, scaling data processing by 3x to support clinical analytics applications.}
              \resumeItem{Implemented automated deployments using \textbf{Kubernetes} and \textbf{Terraform}, enhancing service uptime and reducing failures by 40\%.}
              \resumeItem{Collaborated with product and platform teams to deliver APIs supporting big data and machine learning workloads in healthcare context.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Healthcare Predictive Analytics Platform} | Azure, Java, SQL, Machine Learning}{}
          \resumeItemListStart
              \resumeItem{Built predictive analytics backend in \textbf{Java} on \textbf{Azure} cloud, enabling clinical decision support for patient care improvements.}
              \resumeItem{Designed scalable \textbf{SQL} data warehouse pipelines to integrate multi-source healthcare data, improving data liquidity by 50\%.}
              \resumeItem{Implemented RESTful services optimizing machine learning model deployment, reducing prediction latency by 35\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, Go, C\#, TypeScript, C++, PHP \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Azure, Docker, Kubernetes, Terraform, Jenkins \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Databases \& Analytics:} & SQL, MySQL, PostgreSQL, MongoDB, Data Warehousing, Big Data Systems \\
                \textbf{Software Engineering & Practices:} & Agile, CI/CD, Unit Testing, Code Reviews, Source Control (Git) \\
                \textbf{AI \& Machine Learning:} & Machine Learning, Data Science, LLMs, Automation, AI Agents \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}