\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices architecture to improve scalability and response time by 35\%, increasing user satisfaction.}
        \resumeItem{Implemented role-based access control with \textbf{Spring Security}, reducing unauthorized access attempts by 40\% and strengthening system security.}
        \resumeItem{Deployed \textbf{AI-driven} code review assistant leveraging \textbf{OpenAI API}, reducing manual review time by 45\% and accelerating development cycles.}
        \resumeItem{Automated \textbf{Jenkins} pipelines with \textbf{Docker} containerization, decreasing build and deployment time by 40\% for faster releases.}
        \resumeItem{Collaborated with cross-functional teams to suggest architectural improvements, boosting overall software maintainability and performance.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{SaaS} platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users with zero downtime during peak usage.}
        \resumeItem{Automated data ingestion pipelines with \textbf{Python}, processing 10,000+ stock entries daily and reducing manual workload by 80\%.}
        \resumeItem{Built multi-tier subscription system integrating \textbf{PHP} and \textbf{Stripe}, enforcing fine-grained role-based access control.}
        \resumeItem{Created \textbf{LLM-based} AI agents for FINRA broker data automation, cutting manual processing time by 80\%.}
        \resumeItem{Optimized \textbf{React} front-end components, reducing page load times by 25\% and increasing user retention rates significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments for cybersecurity labs, ensuring reliable software testing and execution for 100+ students.}
        \resumeItem{Assisted students with debugging and deploying software modules, improving assignment success rates by 20\% through clear guidance.}
        \resumeItem{Automated grading scripts using \textbf{Python}, boosting accuracy by 25\% and reducing manual assessment time significantly.}
        \resumeItem{Conducted over 15 tutorials explaining cryptography and security protocols, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed efficient \textbf{TypeScript} APIs achieving sub-100ms response times, enhancing frontend-backend integration and UX.}
        \resumeItem{Revamped UI with \textbf{Angular.js}, increasing user engagement by 25\% through improved interactivity and responsiveness.}
        \resumeItem{Implemented \textbf{C#/.NET} backend services reducing data retrieval latency by 30\%, improving overall application performance.}
        \resumeItem{Optimized \textbf{PostgreSQL} scripts, streamlining database operations and cutting frontend wait times by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed microservices in \textbf{Java Spring Boot} supporting 1000+ concurrent users, reducing response time under 200ms for improved UX.}
        \resumeItem{Deployed 6 microservices using \textbf{Docker} on \textbf{AWS EC2}, automating CI/CD pipelines to reduce deployment time by 50\%.}
        \resumeItem{Built project management UI in \textbf{React.js}, enhancing usability and decreasing page load speed by 30\%.}
        \resumeItem{Created unit tests with \textbf{JUnit} achieving 90\% coverage, improving code reliability and reducing bugs in production.}
        \resumeItem{Collaborated on SaaS automation tools, accelerating SDLC processes and improving development efficiency across teams.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Microservice-Based Order Management System} | Spring Boot, Docker, AWS EC2}
          {}
          \resumeItemListStart
              \resumeItem{Designed and implemented microservices architecture achieving scalable order processing supporting 1000+ concurrent requests efficiently.}
              \resumeItem{Automated deployment using \textbf{Docker} and \textbf{AWS EC2}, reducing release times by 35\% while maintaining high system availability.}
              \resumeItem{Implemented robust \textbf{Spring Security} role-based access, decreasing unauthorized access incidents by 40\% in production environment.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Adaptive Fault-Tolerant API Gateway} | Java, Spring Cloud, Kubernetes}
          {}
          \resumeItemListStart
              \resumeItem{Developed an API Gateway supporting dynamic routing & load balancing, improving system fault tolerance and uptime by 30\%.}
              \resumeItem{Integrated microservice patterns enabling seamless scaling on \textbf{Kubernetes}, reducing failure recovery time by 50\%.}
              \resumeItem{Enhanced monitoring with custom logging, allowing proactive issue detection and accelerating bug resolution by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Go, C\#, C++, JavaScript, Python, PHP, TypeScript \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, .NET, Node.js \\
                \textbf{Microservices \& Architecture:} & Microservice Patterns, REST API, Spring Security, Kubernetes, Docker \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines, Kubernetes \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Tools \& Others:} & Git, Linux/Unix, JUnit, Jira, AI Agent Integration, LLM APIs \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}