\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Improved \textbf{Java Spring Boot} microservices design, increasing system scalability and throughput by 35\%, supporting higher user loads.}
        \resumeItem{Enhanced authentication policies with \textbf{Spring Security}, cutting unauthorized access attempts by 40\% through better role-based controls.}
        \resumeItem{Deployed an \textbf{AI-driven} code review tool that cut manual review time by 45\%, accelerating development velocity by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing build and deployment time by 40\%.}
        \resumeItem{Collaborated across teams to design and implement scalable backend services, improving cross-team feature delivery efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built a scalable \textbf{SaaS} platform using \textbf{Laravel} and \textbf{React}, supporting over 50 concurrent users without performance loss.}
        \resumeItem{Automated \textbf{Python} pipelines processing 10,000+ stock entries daily, reducing manual work by 80\% and improving accuracy.}
        \resumeItem{Developed AI-powered agents utilizing \textbf{LLMs} to automate broker data downloads, reducing manual processing overhead by 80\%.}
        \resumeItem{Implemented an AI-driven LinkedIn outreach bot that increased qualified lead generation by 40\% through automated content posting.}
        \resumeItem{Optimized \textbf{React} components, reducing page load times by 25\% and significantly improving user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab infrastructure, ensuring reliable environments for cybersecurity experimentations.}
        \resumeItem{Assisted students in debugging and deploying modules, boosting assignment completion rates by 20\% through hands-on support.}
        \resumeItem{Created automated grading scripts, improving result accuracy by 25\% and reducing manual workload for instructors.}
        \resumeItem{Led 15+ interactive sessions covering cryptography, networking, and web security topics, enhancing student understanding effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Built and optimized \textbf{TypeScript} API calls, achieving sub-100ms response times that boosted data exchange reliability.}
        \resumeItem{Upgraded frontend using \textbf{Angular.js}, lifting user engagement by 25\% through improved UI responsiveness.}
        \resumeItem{Developed a \textbf{C\# .NET} backend that cut data retrieval latency by 30\%, enhancing overall system performance.}
        \resumeItem{Streamlined \textbf{PostgreSQL} procedures, decreasing frontend load by 15\% and accelerating database operations efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, ensuring sub-200ms response times under heavy load.}
        \resumeItem{Designed and deployed \textbf{Docker}-based CI/CD pipelines on \textbf{AWS EC2}, enabling seamless microservice delivery and scaling.}
        \resumeItem{Created user-friendly \textbf{React.js} UI enhancing project management efficiency by 30\% through faster load times and usability.}
        \resumeItem{Implemented unit tests with \textbf{JUnit}, achieving 90\% code coverage and improving software reliability significantly.}
        \resumeItem{Collaborated with a team to build an automated \textbf{SDLC} tool, streamlining development cycles and increasing productivity.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{CI/CD} bot leveraging \textbf{LLMs} to auto-identify bugs and style issues, reducing manual review time by 25\%.}
              \resumeItem{Automated documentation generation for \textbf{Python} projects, achieving 100\% docstring coverage on new code and improving maintainability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable AI Customer Support Agent} | Gmail API, LLMs, Automation}{}
          \resumeItemListStart
              \resumeItem{Built an automated email classification and response bot using \textbf{LLMs} that handled 60\% of support queries, cutting response times by 40\%.}
              \resumeItem{Implemented a human-in-the-loop system for sensitive queries, ensuring accuracy while increasing automation efficiency.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, C++, C\#, TypeScript, PHP, JavaScript \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins \\
                \textbf{Tools \& Tech:} & Git, Linux/Unix, REST APIs, JUnit, Agile Methodologies \\
                \textbf{AI \& Automation:} & OpenAI API, Large Language Models, AI Agents, CI/CD Automation \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}