\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} services improving API throughput by 35\%, enhancing scalability and system responsiveness.}
        \resumeItem{Integrated \textbf{Spring Security} for role-based access, cutting unauthorized access attempts by 40\%.}
        \resumeItem{Implemented an \textbf{AI-driven} code review assistant, reducing manual review time by 45\% and boosting delivery speed by 25\%.}
        \resumeItem{Automated build-test-deploy pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing release cycles by 40\%.}
        \resumeItem{Collaborated in cross-functional teams to design and maintain software modules per engineering standards, increasing code maintainability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed robust data pipelines in \textbf{Python}, reducing manual data processing time by 80\%.}
        \resumeItem{Architected SaaS platform using \textbf{Laravel} and \textbf{React}, supporting over 50 users with high concurrency.}
        \resumeItem{Built role-based multi-tier subscription platform integrating \textbf{Stripe} and \textbf{WooCommerce} services.}
        \resumeItem{Created AI agents leveraging \textbf{LLMs} to automate regulatory data extraction, cutting effort by 80\%.}
        \resumeItem{Optimized \textbf{React} components reducing page load time by 25\%, improving user experience and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity labs providing secure environments for software development and testing.}
        \resumeItem{Assisted students in debugging and deploying code, improving lab assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts, increasing assessment accuracy by 25\% and reducing manual workloads.}
        \resumeItem{Hosted online sessions on cryptography, network protocols, and web security for enhanced learning.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls achieving under 100ms response times for frontend data exchanges.}
        \resumeItem{Modernized platform features with \textbf{Angular.js}, boosting user engagement metrics by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, easing database operations and lowering frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000 concurrent users efficiently.}
        \resumeItem{Implemented CI/CD pipelines for microservices deployment on \textbf{AWS EC2} using \textbf{Docker}, enhancing release automation.}
        \resumeItem{Built project management UI with \textbf{React.js}, improving usability and reducing load time by 30\%.}
        \resumeItem{Authored unit tests with \textbf{JUnit} achieving 90\% coverage, improving code quality and reliability.}
        \resumeItem{Collaborated on SaaS tool development automating SDLC processes, increasing team efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cloud-Native Data API Microservice} | Java, Spring Boot, REST APIs, Azure Cloud}{}
          \resumeItemListStart
              \resumeItem{Developed a scalable microservice with \textbf{Spring Boot} and \textbf{REST APIs}, deployed to \textbf{Azure}, improving data accessibility by 50\%.}
              \resumeItem{Implemented robust error handling and logging to reduce downtime by 30\% and improve service reliability.}
              \resumeItem{Integrated with \textbf{SQL} database to enable efficient data queries, improving processing speed by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated Batch Data Processing Framework} | Python, Shell Scripting, SQL, Linux}{}
          \resumeItemListStart
              \resumeItem{Engineered a batch processing system using \textbf{Python} and \textbf{Shell Scripting}, automating data workflows and enhancing throughput by 60\%.}
              \resumeItem{Optimized \textbf{SQL} queries to process high volume datasets, reducing execution time by 35\%.}
              \resumeItem{Leveraged \textbf{Linux} command scripting for system automation, improving maintainability and deployment speed.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, SQL, Shell Scripting, JavaScript, TypeScript \\
                \textbf{Frameworks \& Web:} & Spring Boot, Angular, React, REST APIs, Laravel, Spring Security \\
                \textbf{Cloud Platforms:} & Azure, AWS (EC2, S3), Docker, Jenkins \\
                \textbf{Databases:} & Oracle, MySQL, PostgreSQL, Hyperion Planning, DRM \\
                \textbf{Operating Systems \& Tools:} & Linux, Git, GitHub, JUnit, IDEs (Eclipse, IntelliJ) \\
                \textbf{Data Analysis \& Automation:} & Data structures, batch scripting, SQL query optimization, AI integrations \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}