\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices, enhancing API throughput by 35\% to support growing user demands.}
        \resumeItem{Implemented robust \textbf{Spring Security} features, decreasing unauthorized access attempts by 40\% across enterprise applications.}
        \resumeItem{Designed and deployed an \textbf{AI-driven} code review assistant using \textbf{LLMs}, slashing manual review time by 45\%.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} pipelines for CI/CD, cutting release deployment time by 40\%.}
        \resumeItem{Collaborated cross-functionally to optimize software architecture for reliability and maintainability, improving system uptime by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{React} and \textbf{Laravel} based SaaS platform, supporting 50+ concurrent users with zero downtime.}
        \resumeItem{Automated \textbf{Python} data pipelines processing 10,000+ entries daily, reducing manual workload by 80\%.}
        \resumeItem{Built multi-tier e-commerce platform integrating \textbf{Stripe}, enabling role-based access for different user levels.}
        \resumeItem{Configured AI agents with \textbf{LLMs} for automated data extraction, improving data handling speed by 80\%.}
        \resumeItem{Optimized \textbf{React} UI components, reducing page load time by 25\% and increasing user retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity labs ensuring secure configurations and 99\% uptime throughout academic terms.}
        \resumeItem{Assisted students in debugging and testing software modules, boosting assignment success rates by 20\%.}
        \resumeItem{Developed automation scripts for grading, improving accuracy by 25\% and decreasing manual review times.}
        \resumeItem{Led 15+ interactive sessions explaining complex cybersecurity topics to enhance student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{TypeScript} API calls, achieving sub-100ms response times for frontend requests.}
        \resumeItem{Refined \textbf{Angular.js} interfaces, increasing user engagement and satisfaction metrics by 25\%.}
        \resumeItem{Engineered high-performance backends with \textbf{C\#} and \textbf{.NET} framework, reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, slashing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices with \textbf{MySQL}, supporting 1000+ concurrent users and under 200ms response time.}
        \resumeItem{Built \textbf{React.js} project management UIs, boosting task efficiency and reducing load speed by 30\%.}
        \resumeItem{Established \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} using \textbf{Docker} containers smoothly.}
        \resumeItem{Authored 90\% test coverage unit tests for SDLC automation modules utilizing \textbf{JUnit}.}
        \resumeItem{Collaborated with cross-functional teams to streamline software development lifecycle, enhancing product delivery speed by 20\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enabled Education Platform for Healthcare Providers} | Next.js, Python FastAPI, MongoDB, GCP}{}
          \resumeItemListStart
              \resumeItem{Designed and developed full-stack features using \textbf{Next.js} and \textbf{FastAPI}, improving platform engagement by 30\%.}
              \resumeItem{Integrated scalable \textbf{MongoDB} schemas and leveraged \textbf{GCP} cloud services to optimize data storage and retrieval times.}
              \resumeItem{Implemented AI-powered personalized learning modules, increasing student success rates by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{REST API Development for AI Healthcare Applications} | Python FastAPI, Node.js, MongoDB}{}
          \resumeItemListStart
              \resumeItem{Developed and integrated robust \textbf{REST APIs} in \textbf{FastAPI} and \textbf{Node.js} for efficient AI data flow.}
              \resumeItem{Optimized API response times by 35\%, supporting real-time data processing for healthcare education tools.}
              \resumeItem{Collaborated with AI teams to incorporate ML model endpoints, enhancing platform predictive capabilities.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, C\# \\
                \textbf{Web Development \& Frameworks:} & Next.js, React.js, Node.js, FastAPI, Spring Boot, Django, Angular.js \\
                \textbf{Databases:} & MongoDB, MySQL, PostgreSQL, DynamoDB \\
                \textbf{Cloud \& DevOps:} & Google Cloud Platform (GCP), AWS, Docker, Jenkins, CI/CD \\
                \textbf{AI \& Machine Learning:} & AI Integration, LLMs, OpenAI API, Machine Learning Concepts \\
                \textbf{Tools \& Platforms:} & REST API Development, Git, Linux, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}