\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed SaaS data visualization platform on Laravel and React for 50+ users, ensuring stable cloud-based operations.}
        \resumeItem{Automated Python data pipelines processing 10,000+ daily entries, minimizing manual errors by 80\%, enhancing operational efficiency.}
        \resumeItem{Implemented role-based access control in e-commerce platform, improving security and customer experience.}
        \resumeItem{Developed AI LLM agents automating broker data workflows, reducing manual labor by 80\%, enhancing cloud network data reliability.}
        \resumeItem{Optimized React components cutting page load by 25\%, increasing user engagement and system responsiveness in cloud environments.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Maintained Linux-based cybersecurity lab infrastructure, ensuring secure configurations and stable execution environments.}
        \resumeItem{Automated grading scripts improving accuracy by 25\% and streamlining validation for network security assignments.}
        \resumeItem{Facilitated 15+ training sessions on network protocols and security, enhancing student comprehension by 20\%.}
        \resumeItem{Collaborated with faculty to troubleshoot lab system failures, reducing downtime and improving network stability by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Developed sub-100ms TypeScript API calls ensuring fast cloud data exchange and seamless frontend-backend integration.}
        \resumeItem{Refined Angular.js platform boosting user engagement by 25\%, enhancing client cloud service experience.}
        \resumeItem{Built performant backend services in C\# .NET, reducing data latency by 30\% for cloud applications.}
        \resumeItem{Optimized PostgreSQL queries decreasing load by 15\%, ensuring database stability for high volume cloud operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Led development of Java Spring Boot microservices with MySQL, supporting 1000 concurrent users and sub-200ms response times.}
        \resumeItem{Implemented CI/CD pipelines with Docker and AWS EC2, achieving seamless deployment and reducing downtime by 30\%.}
        \resumeItem{Built React project management UI enhancing usability and page load speed by 30\%, improving operational efficiency.}
        \resumeItem{Wrote JUnit unit tests with 90\% coverage ensuring reliability in cloud-deployed microservices.}
        \resumeItem{Resolved database and performance issues quickly, utilizing MySQL optimization to enhance cloud service stability.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Collaborated with a 5-member team to develop a \textbf{SaaS tool} that automates the \textbf{SDLC} process.}
        \resumeItem{Developed \textbf{microservices} in \textbf{Java} using the \textbf{Spring Boot} framework integrated with \textbf{MySQL}, supporting 1000 concurrent users and reducing response time below 200ms.}
        \resumeItem{Organized \textbf{CI/CD} pipelines to enable seamless deployment of 6 key microservices on \textbf{AWS EC2} servers using \textbf{Docker}.}
        \resumeItem{Built project tracking and management UI in \textbf{React.js}, improving usability and page load speed by 30\%.}
        \resumeItem{Implemented unit tests for the pipelines module using the \textbf{JUnit} framework with approximately 90\% test coverage.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Automated AI Code Reviewer \& Documentation Bot} $|$ GitHub Actions, GitHub API, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{CI/CD} bot using \textbf{GitHub Actions} and \textbf{LLMs} to automatically analyze pull requests for bugs and style violations while generating/updating \textbf{Python} docstrings, ensuring 100\% documentation coverage for new code and reducing manual review time by an estimated 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI Customer Support Email Agent} $|$ Gmail API, n8n/Automation, LLMs, Google Sheets API}{}
          \resumeItemListStart
              \resumeItem{Engineered an automated email agent using \textbf{Gmail API} and \textbf{LLMs} to classify email intent/sentiment and execute a \textbf{HITL workflow}, automating responses for 60\% of common support queries and cutting average first-response time by 40\% while ensuring manual review for sensitive cases.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Elastic Face Recognition IaaS} $|$ AWS, EC2, S3, SQS, IAM, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Engineered a scalable face recognition system on \textbf{EC2} with \textbf{SQS} to decouple frontend and backend, implemented custom auto-scaling to handle 1000 requests in under 60 seconds, and used \textbf{S3} for data persistence.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, Go, TypeScript, JavaScript, PHP, C\#, C++, C, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, Django, HTML, CSS, .NET \\
                \textbf{Database \& Data Storage:} & MySQL, Redis, SQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Automation:} & Amazon Web Services (AWS), Docker, Azure, Lambda, EC2, S3 \\
                \textbf{Tools \& Other Technologies:} & Linux/Unix, Git, GitHub, REST API, gRPC, JSON, Jira, JUnit, CMS, WordPress \\
                \textbf{AI \& Automation:} & n8n, Zapier, Apify, OpenAI API, LLM Integration, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}

