\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{Java Spring Boot} microservices to enhance scalability and throughput, improving \textbf{API} performance by 35\%.}
        \resumeItem{Upgraded authentication and role-based access control with \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Set up an \textbf{AI-driven} code review assistant that analyzed pull requests and suggested optimizations, reducing manual review effort by 45\% and accelerating development by 25\%.}
        \resumeItem{Automated build, testing, and deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing release time by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected a \textbf{SaaS} data visualization platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Automated data pipelines in \textbf{Python} to process 10,000+ stock entries daily, reducing manual effort by 80\%.}
        \resumeItem{Built a multi-tier e-commerce subscription platform with \textbf{PHP} using \textbf{Stripe} and WooCommerce, enabling role-based access control.}
        \resumeItem{Established \textbf{AI agents} leveraging \textbf{LLMs} to automate FINRA broker data downloads and processing, reducing manual effort by 80\%.}
        \resumeItem{Built an \textbf{AI-driven} LinkedIn outreach bot that automated content posting and lead targeting, generating 40\% more qualified leads.}
        \resumeItem{Refined \textbf{React} components and state management, cutting page load times by 25\% and boosting user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based infrastructure for cybersecurity labs, ensuring secure configurations and reliable execution environments.}
        \resumeItem{Guided students in \textbf{debugging}, \textbf{deploying}, and \textbf{testing} software modules, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading and \textbf{validation} scripts, reducing manual review workload and increasing accuracy of results by 25\%.}
        \resumeItem{Conducted 15+ interactive online sessions to explain complex topics like Cryptography,Networking Protocols, and Web Security.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed API calls in \textbf{TypeScript}, achieving sub-100ms average response time and ensuring seamless data exchange.}
        \resumeItem{Upgraded existing platform using \textbf{Angular.js}, resulting in a 25\% rise in user engagement and satisfaction.}
        \resumeItem{Established a high-performance backend in \textbf{C\#} with the \textbf{.NET} framework, resulting in a 30\% reduction in data retrieval latency.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend load by 15\% and streamlining database operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Collaborated with a 5-member team to develop a \textbf{SaaS tool} that automates the \textbf{SDLC} process.}
        \resumeItem{Developed \textbf{microservices} in \textbf{Java} using the \textbf{Spring Boot} framework integrated with \textbf{MySQL}, supporting 1000 concurrent users and reducing response time below 200ms.}
        \resumeItem{Organized \textbf{CI/CD} pipelines to enable seamless deployment of 6 key microservices on \textbf{AWS EC2} servers using \textbf{Docker}.}
        \resumeItem{Built project tracking and management UI in \textbf{React.js}, improving usability and page load speed by 30\%.}
        \resumeItem{Implemented unit tests for the pipelines module using the \textbf{JUnit} framework with approximately 90\% test coverage.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Automated AI Code Reviewer \& Documentation Bot} $|$ GitHub Actions, GitHub API, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{CI/CD} bot using \textbf{GitHub Actions} and \textbf{LLMs} to automatically analyze pull requests for bugs and style violations while generating/updating \textbf{Python} docstrings, ensuring 100\% documentation coverage for new code and reducing manual review time by an estimated 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI Customer Support Email Agent} $|$ Gmail API, n8n/Automation, LLMs, Google Sheets API}{}
          \resumeItemListStart
              \resumeItem{Engineered an automated email agent using \textbf{Gmail API} and \textbf{LLMs} to classify email intent/sentiment and execute a \textbf{HITL workflow}, automating responses for 60\% of common support queries and cutting average first-response time by 40\% while ensuring manual review for sensitive cases.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Elastic Face Recognition IaaS} $|$ AWS, EC2, S3, SQS, IAM, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Engineered a scalable face recognition system on \textbf{EC2} with \textbf{SQS} to decouple frontend and backend, implemented custom auto-scaling to handle 1000 requests in under 60 seconds, and used \textbf{S3} for data persistence.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go, Shell Scripting, Java, JavaScript, TypeScript, C\#, PHP, C++, C \\
                \textbf{Web Development \& Frameworks:} & React.js, Spring Boot, Angular.js, Laravel, Node.js, Django, HTML, CSS, .NET \\
                \textbf{Database \& Data Storage:} & MySQL, SQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Automation:} & Docker, Amazon Web Services (AWS), Azure, Git, Jenkins, GitHub Actions, Terraform, Ansible, Lambda, EC2, S3 \\
                \textbf{Tools \& Other Technologies:} & Linux/Unix, GitHub, REST API, JSON, Prometheus, Grafana, Kustomize, Helm, Jira, JUnit, CMS, WordPress \\
                \textbf{AI \& Automation:} & n8n, Zapier, Apify, OpenAI API, LLM Integration, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}

