\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Backend developer skilled in building scalable APIs and services using modern languages and cloud platforms. Experienced in Agile environments, version control, and CI/CD pipelines. Adept at collaborating across teams to deliver efficient, well-documented backend solutions. Passionate about continuous learning and solving complex backend architecture challenges.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, Golang, C++, Bash, Perl \\
                \textbf{Web Frameworks \& APIs:} & RESTful APIs, Spring Boot, Django, Node.js \\
                \textbf{Databases:} & SQL (MySQL, PostgreSQL), NoSQL (MongoDB, DynamoDB) \\
                \textbf{DevOps \& Cloud:} & AWS, Azure, GCP, Docker, Jenkins, GitHub Actions, CI/CD Pipelines \\
                \textbf{Version Control \& Tools:} & Git, Linux/Unix, Agile methodologies (Scrum, DevOps) \\
                \textbf{Collaboration \& Soft Skills:} & Problem solving, communication, cross-functional teamwork \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} backend services, increasing API response efficiency by 35\% to support enterprise application scalability.}
        \resumeItem{Improved secure access by integrating \textbf{Spring Security} features, reducing vulnerabilities and unauthorized access by 40\%.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, achieving 40\% faster release cycles and higher reliability.}
        \resumeItem{Collaborated with cross-functional teams to design and maintain robust APIs supporting internal and external application needs.}
        \resumeItem{Reviewed and debugged backend code regularly to ensure high code quality and application stability in a cloud environment.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Laravel} backend services integrated with front-end React components, enabling 50+ simultaneous users.}
        \resumeItem{Automated data ingestion and processing pipelines with \textbf{Python}, improving data accuracy and reducing manual effort by 80\%.}
        \resumeItem{Implemented \textbf{API} endpoints and optimized database queries connected to \textbf{SQL/NoSQL} stores, enhancing system responsiveness.}
        \resumeItem{Built AI-powered automation bots to streamline broker data downloads, increasing operational efficiency by 80\%.}
        \resumeItem{Refined RESTful API designs and documentation to improve maintainability and support Agile team workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux}-based lab infrastructures, supporting secure and reliable testing environments for students’ software modules.}
        \resumeItem{Developed automation scripts to grade and validate software assignments, reducing manual effort by 25\% and improving accuracy.}
        \resumeItem{Guided students on debugging and backend code deployment, increasing assignment success rates by 20\%.}
        \resumeItem{Hosted over 15 technical sessions explaining backend concepts such as REST APIs, security, and cloud deployment practices.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls reducing data response time below 100ms, boosting frontend performance.}
        \resumeItem{Upgraded backend services in \textbf{C\#} with \textbf{.NET}, reducing server latency by 30\% and improving data throughput.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, enhancing database operation speed by 15\%.}
        \resumeItem{Collaborated in Agile sprints with frontend developers to ensure seamless integration of backend APIs and data services.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java Spring Boot} microservices for SaaS applications servicing 1000+ concurrent users with low latency.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines using \textbf{Docker} on \textbf{AWS EC2}, accelerating deployment and reducing errors by 35\%.}
        \resumeItem{Built React-based UIs for microservices, improving user experience and page load times by 30\%.}
        \resumeItem{Collaborated in Agile teams to integrate RESTful APIs, ensuring reliable communication between frontend and backend modules.}
        \resumeItem{Wrote comprehensive unit tests with \textbf{JUnit}, achieving 90\% coverage and improving software quality and maintainability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-assisted Backend Code Review Tool} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Integrated \textbf{AI} with \textbf{GitHub Actions} to automate backend \textbf{Python} code reviews, reducing manual effort by 40\%.}
              \resumeItem{Generated automatic documentation and code quality suggestions, improving codebase maintainability and developer efficiency.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable RESTful API for E-commerce} | Java, Spring Boot, MySQL, Docker}{}
          \resumeItemListStart
              \resumeItem{Designed and deployed robust RESTful APIs using \textbf{Java Spring Boot} and \textbf{MySQL}, supporting 500+ daily active users.}
              \resumeItem{Containerized services with \textbf{Docker} and automated deployment, decreasing release time and boosting reliability by 35\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-based Face Recognition Service} | AWS EC2, S3, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Developed a backend face recognition service on \textbf{AWS EC2} using \textbf{Python} and \textbf{Flask}, handling 1000+ requests efficiently.}
              \resumeItem{Implemented auto-scaling and data persistence strategies to ensure low latency and high availability under peak load.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}