\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer with strong expertise in full-stack development, AI automation, and cloud solutions. Proven track record delivering scalable, secure applications using modern frameworks and CI/CD pipelines, enhancing operational efficiency and user engagement. Adept at integrating AI agents to streamline processes and accelerate development cycles in dynamic environments.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, PHP, Go, C\#, C++, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, Django, .NET, HTML, CSS \\
                \textbf{DevOps \& Cloud Platforms:} & AWS (EC2, Lambda, S3), Docker, Jenkins, Kubernetes, Azure, Terraform \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB, Redis \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, n8n, Zapier, Apify, Prompt Engineering \\
                \textbf{Tools \& Other Technologies:} & Git, GitHub, REST API, gRPC, JSON, Linux/Unix, Jira, JUnit, CMS, WordPress \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Spring Boot} microservices scalability and throughput, improving API response speeds by 35\% and system reliability across services.}
        \resumeItem{Implemented secure authentication systems with \textbf{Spring Security}, decreasing unauthorized access incidents by 40\%.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant leveraging \textbf{LLMs} that reduced manual code review time by 45\% and improved code quality.}
        \resumeItem{Automated comprehensive build, test, and deployment pipelines via \textbf{Jenkins} and \textbf{Docker}, reducing release cycles by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to integrate CI/CD practices, enhancing deployment transparency and minimizing production errors by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and developed a \textbf{SaaS} data visualization app using \textbf{Laravel} and \textbf{React}, supporting 50+ simultaneous users without lag.}
        \resumeItem{Automated high-volume stock data workflows in \textbf{Python}, increasing processing speed by 80\% and reducing manual intervention.}
        \resumeItem{Built a tiered e-commerce subscription system with \textbf{PHP}, integrating \textbf{Stripe} and role-based access controls.}
        \resumeItem{Created intelligent \textbf{AI agents} with \textbf{LLM} integration to automate financial broker data retrieval, cutting manual workload by 80\%.}
        \resumeItem{Developed an \textbf{AI-powered} LinkedIn automation tool, boosting qualified lead generation by 40\% through targeted content and outreach.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and secured \textbf{Linux}-based lab infrastructure, ensuring robust environment availability for cybersecurity research.}
        \resumeItem{Facilitated student debugging, testing, and deployment skills, increasing assignment completion success by 20\%.}
        \resumeItem{Developed automation for grading and validation, boosting review accuracy and efficiency by 25\%.}
        \resumeItem{Delivered over 15 in-depth virtual workshops covering Cryptography, Network Protocols, and Security best practices.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} APIs achieving sub-100ms response times for real-time data integration across platforms.}
        \resumeItem{Upgraded frontend with \textbf{Angular.js}, increasing user engagement metrics by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\#} and \textbf{.NET} framework, reducing data response latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, decreasing data access time and enhancing system throughput by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led development of a \textbf{SaaS} automation platform streamlining the \textbf{SDLC} for improved team efficiency and code quality.}
        \resumeItem{Engineered performant \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users with under 200ms latency.}
        \resumeItem{Built and managed containerized deployments using \textbf{Docker} and \textbf{AWS EC2} to enable automated, reliable releases.}
        \resumeItem{Designed intuitive project management UI in \textbf{React.js}, enhancing user workflow with 30\% faster page load times.}
        \resumeItem{Implemented comprehensive unit testing with \textbf{JUnit}, achieving 90\% coverage to guarantee stability of core services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Optimization Assistant} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed an \textbf{AI} assistant integrated with \textbf{GitHub Actions} to analyze and optimize pull requests, reducing review time by 40\%.}
              \resumeItem{Automated generation of standardized \textbf{Python} documentation, ensuring full coverage and consistency across all new code changes.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Automated Customer Support Email Agent} | Gmail API, n8n, LLMs, Google Sheets API}{}
          \resumeItemListStart
              \resumeItem{Built an \textbf{AI}-driven email classifier using \textbf{LLMs}, automating 60\% of routine support queries and reducing response times by 40\%.}
              \resumeItem{Integrated HITL workflows to escalate complex issues, enhancing overall customer satisfaction and maintaining response quality standards.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Elastic Face Recognition Service} | AWS EC2, SQS, S3, Flask, Python}{}
          \resumeItemListStart
              \resumeItem{Designed and deployed a reliable face recognition backend on \textbf{AWS EC2} using asynchronous \textbf{SQS} queues to handle 1000+ requests in 60 seconds.}
              \resumeItem{Implemented scalable data storage with \textbf{S3} enabling efficient persistence and retrieval for high-volume image processing workloads.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}