\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer specialized in Android application development with strong expertise in scalable and efficient system design. Skilled at collaborating with cross-functional teams to create seamless user experiences and maintain reusable, high-performance codebases. Adept at leading technical efforts and optimizing complex mobile applications to support millions of users globally.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Kotlin, Python, TypeScript, C\#, C++, JavaScript, PHP \\
                \textbf{Mobile Development:} & Android SDK, Jetpack, Multithreading, Memory Management, Espresso \\
                \textbf{Web \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, Django \\
                \textbf{Database \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQLite \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, GitHub Actions, CI/CD \\
                \textbf{Tools \& Testing:} & Git, JUnit, REST API, gRPC, Jira, Unit Testing, API Design \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices improving API throughput by 35\%, enhancing responsiveness for scalable backend operations.}
        \resumeItem{Implemented advanced authentication and role-based access controls reducing unauthorized access attempts by 40\% using \textbf{Spring Security}.}
        \resumeItem{Devised an \textbf{AI-driven} code review assistant automating pull request analysis, cutting manual effort by 45\% and accelerating delivery timelines.}
        \resumeItem{Automated build and deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 40\% and increasing deployment reliability.}
        \resumeItem{Collaborated with cross-team members using Agile practices to deliver features adhering to quality standards, improving sprint delivery success by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed a \textbf{React} and \textbf{Laravel} SaaS platform supporting 50+ concurrent users with seamless UI/UX interactions.}
        \resumeItem{Automated complex financial data pipelines by scripting \textbf{Python} processes, reducing manual tasks by 80\% and increasing data accuracy.}
        \resumeItem{Created a multi-tiered e-commerce platform integrating \textbf{Stripe} payments and role-based controls, increasing subscription conversion rates by 25\%.}
        \resumeItem{Implemented \textbf{LLM}-powered automation for FINRA broker data processing, accelerating data workflows by 80\% and lowering manual intervention.}
        \resumeItem{Optimized \textbf{React} component state management, cutting page load times by 25\%, boosting user engagement and retention metrics significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux} infrastructure securing cybersecurity labs, ensuring reliable and compliant software environment availability daily.}
        \resumeItem{Mentored students on debugging and testing core software modules, improving coursework success rates by 20\% through direct guidance.}
        \resumeItem{Developed automation scripts for grading and validation, enhancing accuracy by 25\% while reducing manual administrative workload significantly.}
        \resumeItem{Conducted over 15 detailed webinars on Cryptography and Networking enhancing student understanding and practical implementation skills.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented low-latency \textbf{TypeScript} API calls, achieving average response times below 100ms for improved frontend performance.}
        \resumeItem{Refactored front-end platform with \textbf{Angular.js}, raising user engagement and satisfaction by 25\% through UI enhancements.}
        \resumeItem{Developed backend modules in \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%, enhancing system responsiveness.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures to reduce database load by 15\%, improving overall query efficiency and stability.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led a 5-member team to build \textbf{Java Spring Boot} microservices with \textbf{MySQL} backend, supporting 1000+ concurrent users under 200ms latency.}
        \resumeItem{Designed and maintained \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} with \textbf{Docker}, increasing release frequency by 30\%.}
        \resumeItem{Developed \textbf{React.js} interfaces enhancing project management experience and improving page load speeds by 30\%.}
        \resumeItem{Implemented comprehensive unit tests with \textbf{JUnit}, achieving approximately 90\% test coverage to ensure product reliability and maintainability.}
        \resumeItem{Led API design and feature ownership, coordinating cross-functional tasks to meet deadlines and deliver high-quality software components.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Android Code Optimizer} $|$ Kotlin, Android SDK, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Created an AI-driven tool that analyzes \textbf{Kotlin} Android code, suggesting performance improvements and reducing app memory usage by 20\%.}
              \resumeItem{Integrated with Android Studio facilitating real-time code reviews, streamlining developer productivity and enhancing code quality across teams.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Android Chat Application} $|$ Java, Android SDK, Firebase, Multithreading}{}
          \resumeItemListStart
              \resumeItem{Developed a multi-threaded chat app in \textbf{Java} ensuring smooth user experience and supporting 10,000+ concurrent users.}
              \resumeItem{Optimized backend integration with Firebase, decreasing message latency by 25\% and enhancing real-time communication reliability.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cross-Platform Social Media Aggregator} $|$ React Native, REST APIs, Node.js}{}
          \resumeItemListStart
              \resumeItem{Built a social media aggregator app unifying multiple feeds, improving user engagement by 30\% with consistent UX across platforms.}
              \resumeItem{Designed reusable components and efficient API interactions, reducing network usage by 15\% and improving load times.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}