\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Skilled backend developer with a strong foundation in Java, Python, and cloud environments, experienced in designing robust APIs and data integrations. Adept at Agile workflows, CI/CD pipelines, and collaborative software delivery. Committed to writing clean, efficient code and continuous learning in a fast-paced enterprise environment.

 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, Golang, C++, Bash, TCL, Perl \\
                \textbf{Backend Frameworks \& Tools:} & Spring Boot, Node.js, RESTful API development, Docker, Jenkins, Git \\
                \textbf{Cloud Platforms:} & AWS, Azure, Google Cloud Platform (GCP), Lambda, EC2, S3 \\
                \textbf{Databases:} & SQL, NoSQL, MySQL, PostgreSQL, MongoDB \\
                \textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Docker, Agile Methodologies, DevOps workflows \\
                \textbf{Operating Systems \& Collaboration:} & Linux, Git, Jira, Slack, Agile Scrum \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java Spring Boot} microservices, improving backend service response time by 30\% in support of scalable APIs.}
        \resumeItem{Collaborated with product and frontend teams to design and implement RESTful \textbf{APIs}, enhancing data exchange reliability by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, decreasing deployment errors by 40\% and accelerating release cycles.}
        \resumeItem{Participated in Agile scrums and peer code reviews, improving code quality and reducing bugs by 35\% through constructive collaboration.}
        \resumeItem{Monitored backend services in \textbf{AWS} cloud environment, optimizing resource usage and maintaining 99.9\% uptime.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered backend data integration pipelines in \textbf{Python} and \textbf{Node.js}, processing 15,000+ records daily and reducing manual effort by 70\%.}
        \resumeItem{Implemented RESTful APIs to interface with frontend using \textbf{JavaScript}, improving system responsiveness by 35\%.}
        \resumeItem{Utilized containerization with \textbf{Docker} and continuous deployment via \textbf{GitHub Actions}, cutting deployment time by 50\%.}
        \resumeItem{Enhanced team Agile practices by establishing sprint planning and retrospectives, improving delivery efficiency by 20\%.}
        \resumeItem{Integrated \textbf{AWS} cloud services into application architecture, reducing infrastructure costs by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab servers and applications, ensuring secure and stable operation for 100+ users.}
        \resumeItem{Assisted students with debugging and deploying backend code, increasing assignment success by 20\% through clear guidance.}
        \resumeItem{Automated grading scripts with \textbf{Python} to validate programming assignments, reducing manual workload by 30\%.}
        \resumeItem{Conducted technical workshops on backend development fundamentals, boosting student engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 25\% and improving system stability.}
        \resumeItem{Optimized API response times to under 100ms using \textbf{TypeScript}, enhancing frontend user experience.}
        \resumeItem{Enhanced database query performance with optimized \textbf{PostgreSQL} operations, decreasing load times by 20\%.}
        \resumeItem{Collaborated in Agile team, participating in sprint meetings and delivering features on schedule.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Spring Boot} microservices integrated with \textbf{MySQL}, serving 1000+ users with sub-200ms response times.}
        \resumeItem{Implemented automated CI/CD pipelines with \textbf{Docker} and \textbf{AWS EC2}, enabling zero-downtime deployments.}
        \resumeItem{Built intuitive project tracking UI with \textbf{React.js}, improving usability scores by 30\%.}
        \resumeItem{Wrote comprehensive unit tests in \textbf{JUnit}, achieving 90\% code coverage to ensure software reliability.}
        \resumeItem{Collaborated in Agile teams, participating in scrums and refining development workflows for increased productivity.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Backend Code Review Bot} | GitHub API, OpenAI API, Java, Python}{}
          \resumeItemListStart
              \resumeItem{Created a backend automation bot using \textbf{LLMs} to review pull requests and enforce coding standards, reducing review time by 40\%.}
              \resumeItem{Integrated with \textbf{GitHub Actions} to automatically generate detailed documentation for new backend code, increasing maintainability by 60\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Cloud-based API Service for Data Integration} | AWS, Node.js, Docker, REST APIs}{}
          \resumeItemListStart
              \resumeItem{Designed a scalable \textbf{RESTful API} leveraging \textbf{AWS} services and containerization to process 20,000+ daily data records efficiently.}
              \resumeItem{Implemented robust authentication and monitoring, achieving 99.9\% uptime and reducing system errors by 30\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Containerized Microservices Platform} | Spring Boot, Docker, Jenkins, MySQL}{}
          \resumeItemListStart
              \resumeItem{Engineered microservices architecture using \textbf{Spring Boot} and \textbf{Docker}, deploying with automated pipelines to decrease downtime by 35\%.}
              \resumeItem{Improved data management with \textbf{MySQL} optimizations and seamless integration, reducing response times by 25\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}