\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Results-driven software engineer with 3 years in designing and maintaining scalable applications leveraging OOP and architectural patterns. Expertise includes REST and GraphQL API development, containerization with Docker, and advanced CI/CD automation. Skilled in cloud services like AWS and Kubernetes, with strong focus on security, testing, and performance optimization. Excellent collaborator committed to delivering reliable, maintainable solutions. 
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, PHP, Java, Python, TypeScript, Go \\
                \textbf{Web \& API Development:} & REST, GraphQL, Laravel, Spring Boot, Node.js, React.js \\
                \textbf{Containerization \& Orchestration:} & Docker, Kubernetes, GitOps \\
                \textbf{CI/CD \& DevOps Tools:} & Jenkins, GitHub Actions, AWS (EC2, Lambda, S3), Terraform \\
                \textbf{Databases \& Data Management:} & MySQL, PostgreSQL, SQL, ETL, Data Migration \\
                \textbf{Testing \& Security:} & Unit, Integration, E2E Testing, Secrets Management, Dependency Management \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced scalability by refactoring \textbf{Java Spring Boot} services using SOLID principles, improving response time by 35\% under load.}
        \resumeItem{Designed and integrated \textbf{REST APIs} with robust pagination and retry mechanisms, reducing failures by 30\% across clients.}
        \resumeItem{Implemented containerized development environments with \textbf{Docker}, automating setups and reducing onboarding time by 40\%.}
        \resumeItem{Automated \textbf{CI/CD} pipelines utilizing \textbf{Jenkins} to streamline deployments, minimizing release errors by 20\%.}
        \resumeItem{Collaborated on Kubernetes production monitoring and GitOps workflows to enhance incident response time by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{PHP}/\textbf{Laravel} e-commerce APIs adhering to REST standards with rate limiting, improving throughput by 40\%.}
        \resumeItem{Built secure containerized environments with \textbf{Docker}, optimizing local and staging environments for developer productivity by 35\%.}
        \resumeItem{Led \textbf{CI/CD} pipeline designs integrating automated testing and versioning, accelerating release cadence by 30\%.}
        \resumeItem{Optimized data processing pipelines involving \textbf{ETL} techniques and SQL tuning, reducing latency by 25\%.}
        \resumeItem{Integrated cloud services on \textbf{AWS} ensuring cost-effective resource use balanced with performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained Linux-based lab infrastructure supporting secure software deployments and student development testing environments.}
        \resumeItem{Automated test validation for cybersecurity assignments, increasing grading accuracy by 30\% and grading speed by 20\%.}
        \resumeItem{Conducted lab sessions focused on secure coding practices, concurrency issues, and architectural design patterns.}
        \resumeItem{Supported integration of API testing tools to reinforce understanding of REST and security fundamentals among students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{TypeScript} API calls to support high throughput microservices, reducing response times by 25\%.}
        \resumeItem{Refined front-end components with \textbf{Angular.js} improving user engagement metrics by 20\%.}
        \resumeItem{Implemented backend improvements in \textbf{C\#} \textbf{.NET} framework optimizing concurrent database queries by 30\%.}
        \resumeItem{Enhanced \textbf{PostgreSQL} schema and queries to support efficient data migration and ETL processes.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and built \textbf{microservices} with \textbf{Spring Boot}, applying SOLID and DI patterns to elevate maintainability and scalability.}
        \resumeItem{Implemented \textbf{Docker}-based containerization for continuous deployment pipelines, improving deployment speed by 50\%.}
        \resumeItem{Managed \textbf{CI/CD} workflows on AWS EC2 using \textbf{GitOps} for automated deployment and version control.}
        \resumeItem{Optimized database access and ETL batch jobs using \textbf{MySQL} and \textbf{SQL} for large-scale data migration projects.}
        \resumeItem{Developed unit and integration tests with \textbf{JUnit} ensuring 90\%+ coverage to uphold product reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Assistant} $|$ GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Created an AI-assisted \textbf{CI/CD} bot to analyze pull requests for architectural compliance and style, reducing manual reviews by 40\%.}
              \resumeItem{Automated generation of comprehensive code documentation using \textbf{Python} and \textbf{OpenAI} models, improving codebase maintainability.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{E-Commerce API with Rate Limiting} $|$ Laravel, REST, Docker}{}
          \resumeItemListStart
              \resumeItem{Built a containerized \textbf{PHP Laravel} API supporting robust pagination and rate limiting, improving client request handling by 50\%.}
              \resumeItem{Integrated automated testing covering unit and integration tests achieving 85\% coverage and supporting CI pipeline.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Face Recognition Service} $|$ AWS, EC2, S3, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Engineered a \textbf{Kubernetes}-orchestrated face recognition backend on \textbf{AWS EC2}, scaling to handle 1000+ requests in under 60 seconds.}
              \resumeItem{Implemented logging and monitoring solutions to maintain real-time observability and reduce incident response time by 30\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}