\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices boosting system throughput by 35\% for high-demand production environments.}
        \resumeItem{Refined authentication with \textbf{Spring Security} to tighten \textbf{role-based access control}, cutting unauthorized access attempts by 40\%.}
        \resumeItem{Deployed \textbf{AI-driven} code review tools utilizing \textbf{LLMs} to reduce manual reviews by 45\%, accelerating development cycles by 25\%.}
        \resumeItem{Automated continuous integration/deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, trimming release times by 40\%.}
        \resumeItem{Collaborated on feature design and performance tuning resulting in improved API stability for 1000+ daily active users.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed SaaS data visualization platform with \textbf{Laravel} and \textbf{React}, reliably supporting 50+ concurrent users.}
        \resumeItem{Built automated \textbf{Python} pipelines processing 10,000+ daily stock data points, reducing manual effort by 80\%.}
        \resumeItem{Developed multi-tier e-commerce platform using \textbf{PHP}, integrating \textbf{Stripe} and WooCommerce for secure subscriptions.}
        \resumeItem{Automated FINRA broker data downloads leveraging \textbf{LLMs} and AI agents, decreasing manual processing by 80\%.}
        \resumeItem{Optimized \textbf{React} state management, cutting page load times by 25\% and boosting user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab infrastructure ensuring secure configurations and reliable operations for students.}
        \resumeItem{Mentored students in debugging and testing software modules, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts increasing validation accuracy by 25\% while reducing manual review workload significantly.}
        \resumeItem{Delivered 15+ interactive sessions covering Cryptography, Networking Protocols, and Web Security fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} APIs achieving sub-100ms response times to ensure seamless frontend-backend data exchange.}
        \resumeItem{Refined platform with \textbf{Angular.js}, increasing user engagement metrics by 25\% post-upgrade.}
        \resumeItem{Developed a high-performance backend in \textbf{C\#} using \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend load by 15\% and enhancing overall efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Java Spring Boot} microservice architecture serving 1000 concurrent users with sub-200ms response times.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Docker} on \textbf{AWS EC2}, accelerating deployment and system reliability.}
        \resumeItem{Built interactive project tracking UI using \textbf{React.js} improving load time and usability by 30\%.}
        \resumeItem{Authored unit tests in \textbf{JUnit} framework achieving 90\% coverage for critical backend modules.}
        \resumeItem{Collaborated on automating SDLC workflows to streamline build, test and deploy processes actively used by dev teams.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Accelerated Compiler Optimization Framework} | LLVM, Python, PyTorch}
          {}
          \resumeItemListStart
              \resumeItem{Engineered AI models in \textbf{PyTorch} to guide compiler optimizations, improving execution speed of ML workloads by 22\%.}
              \resumeItem{Developed LLVM-based compiler passes automating code transformations that reduced runtime bottlenecks for neural network training.}
              \resumeItem{Integrated optimization framework with ML workflows, enabling scalable training acceleration on distributed systems.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Distributed AI Training Infrastructure} | Kubernetes, Python, JAX}
          {}
          \resumeItemListStart
              \resumeItem{Designed a distributed training cluster using \textbf{Kubernetes} and \textbf{JAX} to scale ML model training across 100+ accelerators.}
              \resumeItem{Implemented fault-tolerant parameter synchronization reducing training convergence time by 30\% at scale.}
              \resumeItem{Automated resource scheduling and monitoring pipelines to optimize hardware utilization for large AI workloads.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C, C++, Python, Java, JavaScript, TypeScript, C\#, Perl, Shell Scripting \\
                \textbf{Hardware \& RTL Design:} & Verilog, FPGA Development, RTL Modeling, Hardware Architecture Basics \\
                \textbf{Machine Learning Frameworks:} & PyTorch, JAX, TensorFlow, Compiler Optimization \\
                \textbf{Distributed Systems \& Infrastructure:} & Kubernetes, AWS (EC2, S3, Lambda), Docker, Fleet Management \\
                \textbf{DevOps \& Tooling:} & Jenkins, CI/CD, Git, Linux/Unix, Performance Analysis Tools \\
                \textbf{Web \& Systems Software:} & Spring Boot, React.js, Angular.js, Firmware & Driver Development, Runtime Systems \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}