\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to increase throughput and scalability, enhancing API response time by 35\%.}
        \resumeItem{Implemented advanced \textbf{Spring Security} features, reducing unauthorized access attempts by 40\% via strong authentication.}
        \resumeItem{Deployed \textbf{AI-driven} code review assistant utilizing LLMs to cut manual review effort by 45\% and speed development by 25\%.}
        \resumeItem{Automated build and deployment workflows using \textbf{Jenkins} and \textbf{Docker}, decreasing release cycles by 40\%.}
        \resumeItem{Monitored system performance and tuned backend services to sustain 99.9\% uptime under increasing user demand.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and maintained \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ concurrent users with smooth performance.}
        \resumeItem{Automated data pipelines in \textbf{Python} to efficiently process 10,000+ stock entries daily, slashing manual data work by 80\%.}
        \resumeItem{Developed a multi-tier e-commerce subscription platform with \textbf{PHP} integrated with \textbf{Stripe}, enabling role-based access.}
        \resumeItem{Built AI agents using \textbf{LLMs} automating FINRA broker data downloads, enhancing efficiency and reducing manual effort by 80\%.}
        \resumeItem{Optimized \textbf{React} components to improve page load times by 25\%, boosting user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab environments, ensuring integrity and availability for cybersecurity coursework and research.}
        \resumeItem{Assisted students in debugging and deploying code modules, improving assignment completion rates by 20\%.}
        \resumeItem{Automated grading scripts, raising efficiency and accuracy of lab result validation by 25\%.}
        \resumeItem{Facilitated 15+ online sessions on cryptography and network security to enhance learning outcomes.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API calls with <100ms latency, ensuring smooth integration and data reliability.}
        \resumeItem{Revamped \textbf{Angular.js} frontend, increasing user engagement metrics by 25\%.}
        \resumeItem{Implemented high-performance backend services in \textbf{C\#} on \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, cutting frontend database load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Co-developed a \textbf{SaaS} tool to automate key stages of the \textbf{SDLC}, improving team productivity by 35\%.}
        \resumeItem{Engineered microservices in \textbf{Java Spring Boot} with \textbf{MySQL}, supporting 1000+ simultaneous users and low latency.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines on \textbf{AWS EC2} with \textbf{Docker}, streamlining deployments and reducing errors.}
        \resumeItem{Built project management UI with \textbf{React.js}, improving usability and page speed by 30\%.}
        \resumeItem{Created unit tests using \textbf{JUnit}, achieving 90\% coverage for critical microservices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered ML Training Pipeline Optimizer} $|$ Python, PyTorch, Distributed Systems}{}
          \resumeItemListStart
              \resumeItem{Implemented distributed training optimizations in \textbf{PyTorch} reducing model training time by 40\% on multi-node clusters.}
              \resumeItem{Developed compiler-level performance tweaks improving tensor operations' throughput by 30\%, accelerating ML workload execution.}
              \resumeItem{Integrated monitoring tools enhancing real-time performance feedback across \textbf{distributed systems}, decreasing downtime by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Hardware-Software Co-design for ML Accelerator Prototyping} $|$ RTL, Verilog, FPGA, C++}{}
          \resumeItemListStart
              \resumeItem{Designed and simulated \textbf{RTL} modules in \textbf{Verilog} implementing custom ML accelerator components, improving inference speed by 25\%.}
              \resumeItem{Facilitated hardware-software integration with C++ drivers, enabling seamless communication between \textbf{FPGA} and host systems.}
              \resumeItem{Conducted pre/post-silicon validation tests reducing hardware bugs by 35\% during iterative prototype development.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C, C++, Python, Java, Perl, TypeScript, JavaScript, C\# \\
                \textbf{Hardware \& RTL Design:} & Verilog, FPGA Development, RTL Design, Hardware-Software Integration \\
                \textbf{Machine Learning Frameworks:} & PyTorch, JAX, TensorFlow, ML Infrastructure Development \\
                \textbf{Systems \& Distributed Computing:} & Linux, Distributed Training Systems, Parallel Computing, Performance Optimization \\
                \textbf{DevOps \& Cloud:} & AWS, Docker, Jenkins, CI/CD, EC2, S3 \\
                \textbf{Tools \& Other Technologies:} & Git, JUnit, Compiler Optimizations, Firmware Development, OpenAI API \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}