\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices to increase scalability, boosting API throughput and reducing latency by 35\%.}
        \resumeItem{Improved security protocols using \textbf{Spring Security}, decreasing unauthorized access attempts by 40\%.}
        \resumeItem{Implemented an \textbf{AI-driven} code review assistant analyzing pull requests, reducing manual review time by 45\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating deployment cycles by 40\%.}
        \resumeItem{Collaborated on cross-functional teams to deliver user-centric features enhancing product reliability and developer efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{SaaS} data visualization platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, handling 10,000+ stock entries and reducing manual efforts by 80\%.}
        \resumeItem{Created \textbf{AI agents} leveraging \textbf{LLMs} for automating data downloads and processing, reducing manual labor by 80\%.}
        \resumeItem{Enhanced \textbf{React} components and state management, decreasing page load times by 25\% and improving user engagement.}
        \resumeItem{Built an AI-driven LinkedIn outreach bot automating content posting and targeting, generating 40\% more qualified leads.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity labs, ensuring secure configurations and reliable software execution environments for students.}
        \resumeItem{Assisted students with debugging and testing software, improving assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts for lab assignments, increasing evaluation accuracy by 25\% and reducing manual workload.}
        \resumeItem{Led interactive sessions explaining advanced topics like cryptography, network protocols, and web security fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls achieving sub-100ms response times, optimizing data exchange efficiency.}
        \resumeItem{Upgraded \textbf{Angular.js} frontend components, increasing user engagement and satisfaction by 25\%.}
        \resumeItem{Developed a high-performance backend in \textbf{C\#} with \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, decreasing frontend load by 15\% and improving database operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed \textbf{Java Spring Boot} microservices with \textbf{MySQL}, supporting 1000 concurrent users and reducing response time below 200ms.}
        \resumeItem{Deployed microservices on \textbf{AWS EC2} using \textbf{Docker} in CI/CD pipelines, improving deployment efficiency.}
        \resumeItem{Built project management UI with \textbf{React.js}, enhancing usability and increasing page load speed by 30\%.}
        \resumeItem{Wrote and maintained \textbf{JUnit} tests, achieving approximately 90\% coverage on core SDLC automation modules.}
        \resumeItem{Led technology integration efforts to improve full-stack performance and ensure accessibility compliance in products.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Sales CRM Optimization} | Java, Spring Boot, React, AI Integration}{}
          \resumeItemListStart
              \resumeItem{Developed scalable \textbf{full-stack} features optimizing CRM workflow, improving sales team efficiency by 30\%.}
              \resumeItem{Implemented real-time data pipelines with \textbf{Java} and \textbf{SQL}, reducing data latency by 50\%.}
              \resumeItem{Integrated \textbf{AI} tools to personalize customer insights, boosting advertiser engagement by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Ad Interaction Analytics Platform} | Java, SQL, TypeScript, Distributed Systems}{}
          \resumeItemListStart
              \resumeItem{Engineered backend APIs using \textbf{Java} and \textbf{SQL} handling millions of ad interactions daily, achieving 99.9\% uptime.}
              \resumeItem{Designed frontend dashboards in \textbf{TypeScript} and \textbf{HTML/CSS}, improving ad data visualization clarity and usability.}
              \resumeItem{Collaborated on distributed system design, ensuring fault tolerance and efficient processing for large-scale data.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, JavaScript, TypeScript, Python, C\#, PHP, Go \\
                \textbf{Frameworks \& Web Development:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, HTML, CSS, .NET \\
                \textbf{Databases:} & SQL, MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, n8n, Zapier \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Git, CI/CD Pipelines \\
                \textbf{Tools \& Others:} & REST API, gRPC, Linux/Unix, JUnit, GitHub, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}