\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Coordinated release schedules and communicated product changes to business leaders, improving transparency by 30\%.}
        \resumeItem{Designed and automated \textbf{QA} test cases using \textbf{Selenium}, decreasing regression testing time by 40\%.}
        \resumeItem{Managed backlog and tracked progress through \textbf{JIRA}, ensuring timely resolution of 90\% of tickets weekly.}
        \resumeItem{Developed and executed end-to-end product tests, identifying and fixing 25+ bugs prior to release.}
        \resumeItem{Created comprehensive training materials and video guides, increasing end-user adoption by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Facilitated communication between developers and business leaders to define new product requirements effectively.}
        \resumeItem{Engineered API integrations using \textbf{Java} and \textbf{Spring Boot}, enhancing product data flow by 35\%.}
        \resumeItem{Utilized \textbf{Selenium} to automate \textbf{QA} tests, reducing manual testing hours by 50\%.}
        \resumeItem{Managed \textbf{JIRA} ticketing system, tracking defect status and coordinating fixes with developers.}
        \resumeItem{Scheduled product releases and conducted training sessions, improving team release efficiency by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Tested software modules for security vulnerabilities, raising lab assignment pass rates by 20\%.}
        \resumeItem{Collaborated with students to troubleshoot issues, improving debugging skills and lab efficiency.}
        \resumeItem{Created automated validation scripts to improve grading accuracy by 25\%.}
        \resumeItem{Provided detailed documentation and training for lab software, enhancing user understanding and satisfaction.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed and optimized \textbf{API} calls in \textbf{TypeScript}, boosting data retrieval speed by 30\%.}
        \resumeItem{Tested and debugged platform features using automated and manual techniques, reducing defects by 15\%.}
        \resumeItem{Collaborated in release planning and documentation to support smooth deployment cycles.}
        \resumeItem{Tracked and communicated defects via \textbf{JIRA}, improving issue resolution turnaround by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java Spring Boot} microservices, improving system scalability by 50\%.}
        \resumeItem{Automated \textbf{QA} processes using \textbf{Selenium}, reducing testing cycles by 30\%.}
        \resumeItem{Handled \textbf{JIRA} ticket tracking and coordinated between developers and business stakeholders.}
        \resumeItem{Created and maintained training documents and user guides, increasing client onboarding efficiency by 20\%.}
        \resumeItem{Tested product releases and managed deployments, cutting downtime during rollouts by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Automated QA Test Suite} | Java, Selenium, JIRA Integration}{}
          \resumeItemListStart
              \resumeItem{Developed automated \textbf{QA} tests using \textbf{Selenium} and integrated with \textbf{JIRA}, reducing manual testing time by 60\%.}
              \resumeItem{Implemented ticket tracking and bug prioritization processes, increasing defect resolution efficiency by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Release Management and Training Portal} | React.js, Node.js, Video Production}{}
          \resumeItemListStart
              \resumeItem{Designed a training portal with video tutorials, improving user onboarding and training completion rates by 40\%.}
              \resumeItem{Coordinated release schedules and functionality updates, decreasing time-to-market by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, JavaScript, Python, TypeScript, C\#, PHP \\
                \textbf{Testing \& Automation:} & Selenium, JUnit, TestNG, Automated QA, API Testing \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Node.js, Laravel, .NET \\
                \textbf{DevOps \& Tools:} & JIRA, Jenkins, Docker, Git, GitHub, CI/CD Pipelines \\
                \textbf{Database \& Data Storage:} & MySQL, PostgreSQL, MongoDB, SQL \\
                \textbf{Other Technologies:} & REST API, Web Services, Agile Methodologies, Video Training Production \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}