\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced core microservices in \textbf{Java Spring Boot}, improving API throughput by 35\% and scalability for users.}
        \resumeItem{Secured authentication workflows using \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Integrated \textbf{AI-driven} code review tools, cutting manual review time by 45\% and accelerating delivery.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, decreasing release time by 40\%.}
        \resumeItem{Collaborated cross-functionally to deliver features aligned with business goals for enhanced customer experience.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{React} front-end and \textbf{Laravel} backend for a SaaS platform supporting 50+ concurrent users.}
        \resumeItem{Automated data pipelines with \textbf{Python}, processing 10,000+ daily entries, reducing manual workflows by 80\%.}
        \resumeItem{Built subscription e-commerce modules with \textbf{PHP}, integrating \textbf{Stripe} and WooCommerce for payments.}
        \resumeItem{Enhanced \textbf{React} components to reduce page load times by 25\%, boosting user engagement significantly.}
        \resumeItem{Deployed AI-powered automation bots using \textbf{LLMs} to streamline broker data collection and LinkedIn outreach.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity labs ensuring secure environments and maximum uptime.}
        \resumeItem{Assisted students with debugging and deploying software, improving assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts to increase accuracy by 25\%, reducing manual review workload.}
        \resumeItem{Conducted over 15 sessions explaining cryptography, networking, and web security concepts to peers.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} APIs with sub-100ms latency supporting smooth data exchange across systems.}
        \resumeItem{Revamped user interface using \textbf{Angular.js}, increasing user engagement and satisfaction by 25\%.}
        \resumeItem{Developed high-performance backend services in \textbf{C\#} and \textbf{.NET}, reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures to improve database query efficiency by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built \textbf{Java Spring Boot} microservices scalable to 1000+ users with response times under 200ms.}
        \resumeItem{Developed \textbf{React.js} UI improving usability and reducing load times by 30\%.}
        \resumeItem{Automated deployment via \textbf{Docker} and \textbf{AWS EC2}, creating smooth CI/CD pipelines for microservices.}
        \resumeItem{Wrote \textbf{JUnit} unit tests achieving 90\% coverage for the pipelines module to ensure quality.}
        \resumeItem{Collaborated in a team of 5 to deliver SLA-backed SaaS tools that improved SDLC automation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Core Ecommerce React Application} | React, Node.js, AWS}
          \resumeItemListStart
              \resumeItem{Developed and optimized consumer-facing \textbf{React} app, supporting millions of users and seamless shopping experiences.}
              \resumeItem{Implemented backend APIs with \textbf{Node.js} hosted on \textbf{AWS}, improving response times by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Real-time Inventory Management System} | NestJS, SQL, AWS}
          \resumeItemListStart
              \resumeItem{Engineered \textbf{NestJS} backend managing real-time inventory data with relational \textbf{SQL} modeling for accuracy.}
              \resumeItem{Deployed scalable infrastructure on \textbf{AWS} to maintain 99.9\% uptime during high traffic periods.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, Java, Python, C\#, PHP \\
                \textbf{Frontend Development:} & React, React Native, Angular.js, HTML, CSS \\
                \textbf{Backend Development:} & Node.js, NestJS, Express.js, Spring Boot, Laravel \\
                \textbf{Databases:} & SQL, MySQL, PostgreSQL, MongoDB, NoSQL \\
                \textbf{Cloud \& DevOps:} & AWS, Docker, Jenkins, Git, GitHub, Jira, Slack \\
                \textbf{Other Technologies:} & Shopify, REST API, Version Control, Agile Methodologies \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}