\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed interactive web features using \textbf{JavaScript} to improve user engagement by 30\%.}
        \resumeItem{Optimized page load speed by 40\% implementing best practices in \textbf{SEO} and accessibility.}
        \resumeItem{Collaborated with UI/UX teams to implement responsive animations, enhancing visual appeal and story-telling.}
        \resumeItem{Led deployment of microsites for marketing campaigns, increasing conversion rate by 25\%.}
        \resumeItem{Streamlined content publishing workflow, reducing release cycle times by 35\% through automation.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built dynamic landing pages in \textbf{React} that improved SEO rankings and boosted traffic by 50\%.}
        \resumeItem{Implemented localization support to serve global users, increasing non-English traffic by 40\%.}
        \resumeItem{Created polished UI animations improving user interaction time by 20\%.}
        \resumeItem{Worked with marketing to align site elements with brand storytelling, increasing lead generation by 35\%.}
        \resumeItem{Enhanced site accessibility features, achieving WCAG 2.1 compliance and expanding user base.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported web-based lab environments ensuring 99\% uptime and secure access for 100+ students.}
        \resumeItem{Automated lab deployment scripts improving setup efficiency by 30\%.}
        \resumeItem{Created documentation and tutorials, increasing student success rates on assignments by 20\%.}
        \resumeItem{Conducted workshops enhancing student knowledge on web security best practices and debugging.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced front-end UI with \textbf{Angular.js} to increase user interactions by 25\%.}
        \resumeItem{Developed fast, SEO-friendly pages reducing load time by 35\%.}
        \resumeItem{Collaborated on animations and transitions improving user satisfaction scores by 15\%.}
        \resumeItem{Optimized backend \textbf{C\#} APIs to ensure sub-100ms response times and high reliability.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and launched interactive website features to elevate brand presence and user engagement.}
        \resumeItem{Developed fast-loading, SEO-optimized pages using \textbf{React.js} improving traffic by 30\%.}
        \resumeItem{Implemented multilingual support ensuring localization and accessibility for global users.}
        \resumeItem{Created visual animations using CSS and JS to enhance storytelling leading to 20\% longer session durations.}
        \resumeItem{Collaborated closely with marketing to align site content with brand messaging, increasing conversions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Interactive Marketing Microsite} | React, CSS Animations, SEO, Localization}{}
          \resumeItemListStart
              \resumeItem{Developed a responsive, animated microsite increasing user engagement by 40\% and achieving top SEO rankings.}
              \resumeItem{Implemented localization features providing seamless experience for 3 languages and improving global reach.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Content Publishing Automation Tool} | Node.js, Express, MongoDB, GitHub Actions}{}
          \resumeItemListStart
              \resumeItem{Engineered a fast content publishing pipeline reducing update time by 50\% and streamlining editorial workflow.}
              \resumeItem{Automated deployment scripts ensuring zero downtime and consistent website performance across global locations.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Python, Java, PHP, C\# \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Node.js, Laravel, Spring Boot, HTML, CSS \\
                \textbf{Animation \& UI Tools:} & CSS Animations, Motion, Web Animations API \\
                \textbf{Localization \& SEO:} & i18n, GEO targeting, SEO best practices, Multilingual support \\
                \textbf{DevOps \& Automation:} & GitHub Actions, Docker, AWS, Jenkins, CI/CD pipelines \\
                \textbf{Other Technologies:} & Accessibility (WCAG), REST APIs, CMS, Cloudflare Workers \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}