\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices scalability, boosting API throughput by 35\% and system reliability.}
        \resumeItem{Implemented \textbf{Spring Security} for authentication, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Developed AI-driven code review assistant using \textbf{LLMs}, cutting manual review effort by 45\% and speeding development 25\%.}
        \resumeItem{Automated build and deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to align CI/CD processes and improve overall software quality.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{React} frontend components, improving user engagement by 25\% via faster page loads.}
        \resumeItem{Automated data processing pipelines in \textbf{Python}, reducing manual effort by 80\% and increasing accuracy.}
        \resumeItem{Developed SaaS platform features using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users flawlessly.}
        \resumeItem{Built AI agents using \textbf{LLMs} to automate FINRA data extraction, cutting manual processing by 80\%.}
        \resumeItem{Created AI-powered LinkedIn bot to automate outreach and content posting, generating 40\% more qualified leads.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} infrastructure for cybersecurity labs, ensuring reliable and protected environments.}
        \resumeItem{Assisted students debugging and deploying software, raising assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts, reducing manual review workload and boosting result accuracy by 25\%.}
        \resumeItem{Led interactive sessions explaining Cryptography and Networking, enhancing student comprehension effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API calls, delivering sub-100ms response times for seamless data exchanges.}
        \resumeItem{Refined \textbf{Angular.js} frontend, increasing user engagement and satisfaction by 25\%.}
        \resumeItem{Created high-performance backend services in \textbf{C\#} with \textbf{.NET}, reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} database procedures, cutting frontend load by 15\% and accelerating queries.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users, reducing response times below 200ms.}
        \resumeItem{Configured \textbf{Docker}-based CI/CD pipelines to deploy microservices seamlessly on \textbf{AWS EC2} instances.}
        \resumeItem{Built responsive frontend with \textbf{React.js}, improving usability and page speeds by 30\%.}
        \resumeItem{Implemented unit testing for microservices using \textbf{JUnit}, achieving roughly 90\% code coverage and reliability.}
        \resumeItem{Collaborated on SaaS tool for SDLC automation, improving development cycle efficiency and consistency across teams.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Smart Pool IoT Mobile App} | React Native, TypeScript, RESTful APIs}{}
          \resumeItemListStart
              \resumeItem{Designed and developed cross-platform mobile app with \textbf{React Native} integrating smart pool controls, boosting user interaction by 30\%.}
              \resumeItem{Implemented API integrations to backend \textbf{Node.js} services, ensuring real-time device status updates and robust connectivity.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud Microservices for IoT Device Management} | Node.js, AWS, Docker, GraphQL}{}
          \resumeItemListStart
              \resumeItem{Built scalable microservice architecture on \textbf{AWS} using \textbf{Docker} containers, improving deployment efficiency by 40\%.}
              \resumeItem{Developed \textbf{GraphQL} APIs enabling efficient communication between IoT devices and cloud backend, reducing data retrieval latency by 20\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, C\#, PHP, Kotlin \\
                \textbf{Mobile \& Web Frameworks:} & React Native, React.js, Node.js, Angular.js, Laravel, Spring Boot \\
                \textbf{Cloud \& Containerization:} & AWS (EC2, Lambda, S3), Docker, Kubernetes, CI/CD pipelines \\
                \textbf{API \& Integration:} & RESTful APIs, GraphQL, JSON, OAuth, JWT authentication \\
                \textbf{DevOps \& Tools:} & Jenkins, Git, GitHub Actions, Xcode, Android Studio, Gradle, CocoaPods \\
                \textbf{Operating Systems \& Networking:} & Linux, Windows, Networking fundamentals, Security best practices \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}