\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered backend services using \textbf{Java Spring Boot}, enhancing throughput and lowering latency by 35\%.}
        \resumeItem{Integrated \textbf{Spring Security} for role-based access, reducing unauthorized access by 40\%.}
        \resumeItem{Developed an \textbf{AI-driven} code review tool leveraging LLMs, cutting manual review time by 45\%.}
        \resumeItem{Automated continuous integration with \textbf{Jenkins} and containerization using \textbf{Docker}, accelerating releases by 40\%.}
        \resumeItem{Collaborated in cross-functional teams to deploy scalable microservices improving system reliability by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{SaaS} data visualization platform with \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users.}
        \resumeItem{Automated data ingestion pipelines using \textbf{Python}, processing 10,000+ daily entries, reducing manual workload by 80\%.}
        \resumeItem{Built a subscription e-commerce platform with \textbf{PHP} integrating \textbf{Stripe}, enabling effective role access control.}
        \resumeItem{Created \textbf{AI-powered} agents using LLMs to automate financial data retrieval, improving efficiency by 80\%.}
        \resumeItem{Optimized \textbf{React} component rendering, lowering load times by 25\% and increasing user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based infrastructure ensuring cybersecurity lab environments were secure and reliable.}
        \resumeItem{Assisted students in debugging and testing complex software modules, increasing assignment success by 20\%.}
        \resumeItem{Developed automated grading scripts improving accuracy and reducing manual work for lab assessments by 25\%.}
        \resumeItem{Conducted over 15 interactive sessions on cryptography and web security, enhancing student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} APIs achieving sub-100ms response, ensuring seamless frontend-backend data exchange.}
        \resumeItem{Enhanced platform UI by upgrading to \textbf{Angular.js}, boosting user engagement by 25\%.}
        \resumeItem{Developed \textbf{C\#} backend services with \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, lowering frontend load by 15\% and improving DB efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Produced \textbf{Java Spring Boot} microservices with \textbf{MySQL}, supporting 1000+ users with <200ms latency.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{Docker} on \textbf{AWS EC2}, enabling rapid deployment cycles.}
        \resumeItem{Developed React.js frontend improving usability and reducing load time by 30\%.}
        \resumeItem{Architected SaaS automation tools streamlining the software delivery lifecycle for enhanced efficiency.}
        \resumeItem{Authored unit tests with \textbf{JUnit} achieving approximately 90\% coverage for critical modules.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Custom Platform Feature Integration} | C\#, Typescript, PostgreSQL, Redis}
          \resumeItemListStart
              \resumeItem{Designed and implemented new platform features integrating \textbf{C\#} backend with \textbf{Typescript} frontend, improving user workflows by 25\%.}
              \resumeItem{Optimized database queries in \textbf{PostgreSQL} and caching with \textbf{Redis}, reducing data access latency by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Microservices Deployment Automation} | Docker, Kubernetes, CI/CD}
          \resumeItemListStart
              \resumeItem{Automated deployment pipelines using \textbf{Docker} containers orchestrated by \textbf{Kubernetes}, reducing deployment time by 40\%.}
              \resumeItem{Implemented observability with \textbf{Prometheus} and \textbf{Grafana}, improving system monitoring and issue detection efficiency by 35\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\#, Typescript, Java, Python, JavaScript, PHP, Go, C++ \\
                \textbf{Web Development \& Frameworks:} & .NET, Spring Boot, React.js, Angular.js, Laravel, Node.js \\
                \textbf{Databases:} & PostgreSQL, MS SQL, MySQL, Redis, DynamoDB \\
                \textbf{Cloud \& Containerization:} & AWS, Azure, Docker, Kubernetes, Nomad \\
                \textbf{DevOps \& CI/CD:} & Git, Jenkins, GitHub Actions, CI/CD Pipelines \\
                \textbf{Monitoring \& Observability:} & Prometheus, Grafana, OpenTelemetry \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}