\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{AWS EC2} infrastructure with VPC and security groups, ensuring 99.9\% uptime.}
        \resumeItem{Implemented \textbf{Terraform} scripts for automated provisioning, reducing manual setup time by 60\%.}
        \resumeItem{Configured \textbf{CloudWatch} monitoring and alarms enabling rapid detection and response to system issues.}
        \resumeItem{Managed \textbf{IAM} roles and policies to enforce least privilege access, decreasing security risks by 40\%.}
        \resumeItem{Automated SSL certificate installation on load balancers, enhancing secure application delivery and reducing errors.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{AWS S3} storage solutions and automated backups to maintain data durability and recovery.}
        \resumeItem{Implemented network ACLs and subnet configurations within \textbf{VPC} for secure and efficient traffic routing.}
        \resumeItem{Integrated monitoring agents like \textbf{Splunk} and \textbf{Qualys} for enhanced infrastructure security visibility.}
        \resumeItem{Orchestrated \textbf{CloudFormation} templates for scalable environment setup, increasing deploy speed by 50\%.}
        \resumeItem{Deployed bastion hosts and hardened access points to secure administrative entry, reducing attack surface.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Configured and maintained \textbf{Linux} lab environments with secure subnetting and firewall rules.}
        \resumeItem{Assisted in setting up \textbf{AWS IAM} policies for student projects, ensuring controlled and auditable access.}
        \resumeItem{Monitored lab infrastructure using logging tools to identify security events, improving incident detection by 30\%.}
        \resumeItem{Supported deployment of backup solutions, validating recoverability and data integrity for lab exercises.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Configured \textbf{AWS EC2} instances and implemented load balancers to optimize application availability.}
        \resumeItem{Enhanced platform security by setting up \textbf{IAM} roles and policies and applying SSL certificates.}
        \resumeItem{Automated monitoring setups with \textbf{CloudWatch} and alerting, improving response times to failures.}
        \resumeItem{Validated backup and storage solutions to ensure business continuity and data protection.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered and maintained \textbf{AWS EC2} environments with secured subnets and routing for SaaS products.}
        \resumeItem{Authored \textbf{CloudFormation} templates and \textbf{Jenkins} jobs to streamline environment provisioning.}
        \resumeItem{Managed \textbf{IAM} user roles and permissions across projects, enhancing cloud security compliance.}
        \resumeItem{Integrated monitoring tools like \textbf{New Relic} to track application health and performance.}
        \resumeItem{Deployed secure load balancers with \textbf{SSL} certificates automating traffic distribution and encryption.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Infrastructure as Code Automation} | Terraform, AWS EC2, CloudFormation}{}
          \resumeItemListStart
              \resumeItem{Developed reusable \textbf{Terraform} modules to provision secure \textbf{VPCs}, subnets, and IAM roles, reducing setup time by 50\%.}
              \resumeItem{Implemented \textbf{CloudFormation} templates to automate scalable deployment of load balancers and EC2 instances.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud Security Monitoring Framework} | AWS CloudWatch, Splunk, IAM}{}
          \resumeItemListStart
              \resumeItem{Built a centralized security monitoring solution using \textbf{CloudWatch} and \textbf{Splunk} for real-time incident detection.}
              \resumeItem{Configured comprehensive \textbf{IAM} policies enforcing least privilege, enhancing system security posture by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Cloud Platforms \& Services:} & AWS (EC2, S3, VPC, IAM, CloudFormation, CloudWatch, Load Balancers, Subnets, Routing, Security Groups), Azure \\
                \textbf{Infrastructure as Code \& Automation:} & Terraform, CloudFormation, Jenkins, Chef, Git, Docker \\
                \textbf{Security \& Monitoring:} & IAM, Network ACLs, SSL Certificates, Qualys, CrowdStrike, Splunk, New Relic, Prisma \\
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, Shell Scripting \\
                \textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Docker, Kubernetes \\
                \textbf{Operating Systems \& Tools:} & Linux/Unix, Git, REST APIs, JSON, Jira \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}