\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led backend API development using \textbf{Python} to increase data throughput by 35\% with scalable microservices.}
        \resumeItem{Implemented frontend features in \textbf{TypeScript} with \textbf{React}, enhancing user interface responsiveness by 25\%.}
        \resumeItem{Deployed AI models in production pipelines to automate data validation, reducing manual errors by 30\%.}
        \resumeItem{Coordinated cross-team design sessions to build scalable architecture that supports rapid growth of platform features.}
        \resumeItem{Optimized CI/CD workflows improving deployment frequency by 40\% using \textbf{Docker} and automated testing.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed full-stack web features using \textbf{React} and \textbf{Python Django}, boosting platform stability by 30\%.}
        \resumeItem{Integrated real-time AI models into production workflows, improving processing speeds by 40\%.}
        \resumeItem{Enhanced frontend web experience by refactoring \textbf{TypeScript} components, reducing load times by 20\%.}
        \resumeItem{Automated data ingestion pipelines with \textbf{Python} to process 15,000+ records daily with 99.9\% accuracy.}
        \resumeItem{Collaborated closely with onsite teams to refine product direction and accelerate feature delivery cycles by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Configured \textbf{Linux}-based environments ensuring 100\% uptime for cybersecurity lab infrastructure.}
        \resumeItem{Assisted students with debugging and deploying \textbf{Python} and \textbf{TypeScript} software projects, improving success rates by 20\%.}
        \resumeItem{Automated lab grading scripts, increasing accuracy and reducing manual workload by 25\%.}
        \resumeItem{Led interactive sessions on network protocols and cryptography, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented API enhancements in \textbf{TypeScript}, achieving response times under 100ms for critical endpoints.}
        \resumeItem{Refactored frontend features with \textbf{Angular.js}, increasing user engagement metrics by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\# .NET}, reducing data retrieval latencies by 30\%.}
        \resumeItem{Optimized SQL queries in \textbf{PostgreSQL}, decreasing server load by 15\% and improving efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Created scalable microservices with \textbf{Java Spring Boot} handling 1000+ users, reducing latency under 200ms.}
        \resumeItem{Designed and deployed React frontend improving UI responsiveness by 30\% and user satisfaction ratings.}
        \resumeItem{Automated deployment with \textbf{Docker} and AWS \textbf{EC2}, accelerating release cycles by 40\%.}
        \resumeItem{Developed unit tests using \textbf{JUnit}, achieving 90\% test coverage and reducing bug rates by 35\%.}
        \resumeItem{Coordinated feature development across teams to streamline SDLC processes, boosting overall productivity by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Real-Time Logistics Dashboard} | TypeScript, React, Next.js, Python, FastAPI}{}
          \resumeItemListStart
              \resumeItem{Built a real-time dashboard integrating AI models to visualize logistics data, improving decision speed by 40\%.}
              \resumeItem{Developed robust backend APIs with \textbf{FastAPI} to support scalable data streaming for 500+ concurrent users.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered User Interaction Platform} | React, Typescript, Django, Python, AI Integration}{}
          \resumeItemListStart
              \resumeItem{Engineered a full-stack platform embedding AI for user interaction analysis, boosting engagement by 35\%.}
              \resumeItem{Implemented scalable backend services using \textbf{Django} to support AI-driven workflows with 99.8\% uptime.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Python, TypeScript, Java, JavaScript, C\#, PHP \\
                \textbf{Frontend Frameworks:} & React, Next.js, Angular.js \\
                \textbf{Backend Frameworks:} & FastAPI, Django, Spring Boot, .NET, Laravel \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins \\
                \textbf{AI \& Automation:} & OpenAI API, AI Model Integration, LLMs, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}