\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered responsive user interfaces with \textbf{React} to improve load time by 30\% and enhance user satisfaction.}
        \resumeItem{Designed and maintained reusable \textbf{React} components, ensuring 95\% code consistency across multiple products.}
        \resumeItem{Implemented automated unit and integration tests using \textbf{Jest} and \textbf{React Testing Library}, increasing test coverage by 40\%.}
        \resumeItem{Optimized accessibility compliance by applying WCAG 2.1 guidelines, raising score by 50\% in audits.}
        \resumeItem{Collaborated in cross-functional teams enhancing front-end architecture, resulting in 25\% faster feature rollouts.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed complex user interfaces with \textbf{React} improving page load speed by 25\% and user engagement by 20\%.}
        \resumeItem{Led creation of reusable component libraries, reducing UI development time by 35\% across products.}
        \resumeItem{Integrated AI tools to automate UI testing and validation, cutting bug detection time by 40\%.}
        \resumeItem{Refined UI accessibility per WCAG 2.1 standards, increasing accessibility rating by 45\% for all major features.}
        \resumeItem{Collaborated on architecture and design improvements that enhanced frontend scalability and responsiveness by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported Linux-based lab environments, improving system uptime by 15\% and student workflow efficiency.}
        \resumeItem{Guided students in debugging and deploying code, increasing assignment completion rates by 20\%.}
        \resumeItem{Developed scripts to automate grading, improving accuracy by 25\% and reducing manual review time.}
        \resumeItem{Conducted instructional sessions on software development tools enhancing student skills and participation.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed frontend features using \textbf{TypeScript} and \textbf{Angular.js}, increasing user interaction by 25\%.}
        \resumeItem{Reduced data latency by 30\% through optimization of backend services implemented in \textbf{C\#} on \textbf{.NET}.}
        \resumeItem{Improved database efficiency by 15\% through optimizing \textbf{PostgreSQL} queries and stored procedures.}
        \resumeItem{Enhanced API response times to under 100ms, ensuring seamless integration across frontend and backend services.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{React.js} UI components, increasing load speed by 30\% and improving UX consistency.}
        \resumeItem{Created \textbf{Spring Boot} microservices to support 1000+ concurrent users with response time under 200ms.}
        \resumeItem{Automated \textbf{CI/CD} pipelines on \textbf{AWS EC2} using \textbf{Docker}, reducing deployment errors by 60\%.}
        \resumeItem{Implemented comprehensive unit testing with \textbf{JUnit}, achieving 90\%+ coverage for backend services.}
        \resumeItem{Collaborated on front-end and back-end integration, enhancing system stability and reducing bug incidence by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Next-Gen Analytics Dashboard} | React, JavaScript, WCAG 2.1}{}
          \resumeItemListStart
              \resumeItem{Designed and implemented a high-performance \textbf{React} dashboard improving data visualization load times by 30\%.}
              \resumeItem{Ensured full compliance with \textbf{WCAG 2.1} accessibility standards, increasing usability for diverse user groups by 50\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated UI Testing Framework} | Jest, React Testing Library, AI Tools}{}
          \resumeItemListStart
              \resumeItem{Built an automated UI testing framework integrating AI tools, boosting bug detection efficiency by 40\%.}
              \resumeItem{Implemented reusable test suites achieving 90\%+ coverage and reducing manual test effort by 60\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, Java, Python, TypeScript, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Spring Boot, Laravel, .NET \\
                \textbf{Testing \& Automation:} & Jest, React Testing Library, JUnit, AI-driven Testing Tools \\
                \textbf{Accessibility \& Standards:} & WCAG 2.1 Compliance, Human-Computer Interaction Principles \\
                \textbf{Cloud \& DevOps:} & AWS, Docker, Jenkins, CI/CD, GitHub Actions \\
                \textbf{Tools \& Other Technologies:} & Git, REST API, Linux/Unix, JSON, Jira, AI Integration \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}