\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected scalable \textbf{Java Spring Boot} microservices improving API throughput by 35\% under high load.}
        \resumeItem{Enhanced security with \textbf{Spring Security} by implementing advanced roles and OAuth2, cutting breaches 40\%.}
        \resumeItem{Deployed \textbf{AI-driven} code review assistant using \textbf{LLMs}, slashing manual review time by 45\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and containerized deployment via \textbf{Docker}, reducing release time 40\%.}
        \resumeItem{Improved database schema design and optimized queries, increasing data retrieval performance by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ concurrent users flawlessly.}
        \resumeItem{Engineered automated \textbf{Python} pipelines processing 10,000+ stock records daily, increasing efficiency by 80\%.}
        \resumeItem{Built multi-tier e-commerce platform using \textbf{PHP} integrating \textbf{Stripe} and WooCommerce with RBAC control.}
        \resumeItem{Created AI agents using \textbf{LLMs} to automate broker data downloads, reducing manual tasks by 80\%.}
        \resumeItem{Optimized \textbf{React} components improving load speed by 25\% and enhancing user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} infrastructure securing cybersecurity labs and ensuring stable environments for 100+ students.}
        \resumeItem{Improved student success by 20\% through hands-on guidance in debugging, deployment, and testing software modules.}
        \resumeItem{Automated grading scripts increased scoring accuracy by 25\%, reducing professor workload significantly.}
        \resumeItem{Conducted 15+ webinars on Cryptography and Web Security aiding student understanding and exam readiness.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented low-latency \textbf{TypeScript} API endpoints achieving sub-100ms response times for client data.}
        \resumeItem{Enhanced platform usability by upgrading to \textbf{Angular.js}, boosting user engagement by 25\%.}
        \resumeItem{Developed performant \textbf{C\# .NET} backend services, reducing database latency by 30\%.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} procedures reducing frontend load and improving query efficiency by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices with \textbf{MySQL} database serving 1000 users under 200ms response.}
        \resumeItem{Led design and deployment of microservices on \textbf{AWS EC2} using \textbf{Docker}, automating CI/CD processes.}
        \resumeItem{Enhanced frontend usability and speed by 30\% through \textbf{React.js} UI improvements.}
        \resumeItem{Authored 90\%+ coverage unit tests for pipelines module using \textbf{JUnit}, reducing post-release bugs.}
        \resumeItem{Collaborated on building SaaS tool automating SDLC pipelines, increasing development speed across teams.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Backend Microservice Optimizer} | Kubernetes, Docker, AWS, Spring Boot}
          {}
          \resumeItemListStart
              \resumeItem{Developed microservice optimizer that dynamically adjusts \textbf{Spring Boot} service scaling on \textbf{AWS}, reducing response latency 30\%.}
              \resumeItem{Implemented monitoring and alerting via custom metrics integrated with cloud-native tools, ensuring 99.9\% uptime.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure RESTful API Platform} | Python, Django, PostgreSQL, OAuth2}
          {}
          \resumeItemListStart
              \resumeItem{Built scalable RESTful API with \textbf{Django} enforcing authentication and authorization using \textbf{OAuth2}, reducing security risks by 40\%.}
              \resumeItem{Optimized database schema and queries in \textbf{PostgreSQL}, improving data retrieval performance by 25\% under peak loads.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages} & Java, Python, Go, PHP, JavaScript, TypeScript, C\#, C++, Shell Scripting \\
                \textbf{Backend Frameworks} & Spring Boot, Django, Express.js, Laravel, .NET, Node.js \\
                \textbf{Databases} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{Cloud \& DevOps} & AWS (EC2, S3, Lambda), Azure, Docker, Kubernetes, Jenkins, CI/CD Pipelines \\
                \textbf{Security \& Compliance} & OAuth2, Spring Security, Encryption, Authentication, Authorization \\
                \textbf{Tools \& Technologies} & REST API, GraphQL, Microservices, Distributed Systems, Git, JUnit, Monitoring Systems \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}