\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices, improving RESTful API throughput and scalability by 35\%.}
        \resumeItem{Implemented secure role-based access authentication using \textbf{Spring Security}, reducing breaches by 40\%.}
        \resumeItem{Launched AI-assisted code review bot with \textbf{LLMs}, cutting manual review time by 45\% and boosting deployment speed 25\%.}
        \resumeItem{Automated CI/CD pipelines via \textbf{Jenkins} and \textbf{Docker}, decreasing deployment cycles by 40\%.}
        \resumeItem{Proactively monitored backend systems to identify issues early, improving customer experience and system reliability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed scalable backend services with \textbf{Node.js} and \textbf{React}, supporting 50+ concurrent SaaS users efficiently.}
        \resumeItem{Automated Python data pipelines processing 10,000+ daily records, increasing operational efficiency by 80\%.}
        \resumeItem{Developed AI agents using \textbf{LLMs} to automate broker data workflow, reducing manual tasks 80\%.}
        \resumeItem{Created LinkedIn AI bot automating outreach and posts, generating 40\% more high-quality sales leads.}
        \resumeItem{Improved \textbf{React} UI components, cutting load times 25\% and increasing user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} cybersecurity lab environments, ensuring reliable student access and testing.}
        \resumeItem{Assisted 100+ students debugging and deploying network security projects, boosting assignment success by 20\%.}
        \resumeItem{Automated grading scripts for lab assignments, increasing evaluation accuracy and reducing manual effort 25\%.}
        \resumeItem{Led 15+ instructional sessions covering cryptography and web security, enhancing student comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency \textbf{TypeScript} API calls, reducing average response time below 100ms consistently.}
        \resumeItem{Upgraded legacy platform using \textbf{Angular.js}, increasing user activity and satisfaction by 25\%.}
        \resumeItem{Designed \textbf{C\#/.NET} backend services, reducing data retrieval latency by 30\% for improved throughput.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, lowering frontend database load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1000+ concurrent users with sub-200ms response times.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines deploying microservices seamlessly on \textbf{AWS EC2} with containerization \textbf{Docker}.}
        \resumeItem{Created React.js-based project management UI, enhancing usability and speeding load times by 30\%.}
        \resumeItem{Delivered comprehensive \textbf{JUnit} tests achieving 90\% coverage, improving code quality and stability.}
        \resumeItem{Collaborated cross-functionally to design scalable SaaS tool automating key software development lifecycle processes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered REST API Monitoring Platform} | Java Spring Boot, ElasticSearch, AWS}
          \resumeItemListStart
              \resumeItem{Built backend RESTful service monitoring platform using \textbf{Spring Boot} and \textbf{ElasticSearch}, reducing downtime by 30\% via proactive alerts.}
              \resumeItem{Implemented scalable architecture on \textbf{AWS}, handling large data volumes with high availability and fault tolerance.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Distributed Data Pipeline Framework} | Java, Spring Boot, Kafka, NoSQL}
          \resumeItemListStart
              \resumeItem{Designed resilient distributed data pipeline using \textbf{Java Spring Boot} and \textbf{Kafka}, processing millions of records daily with 99.9\% uptime.}
              \resumeItem{Integrated NoSQL databases to optimize storage and query performance, reducing latency by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, JavaScript, TypeScript, C\#, PHP \\
                \textbf{Backend Frameworks:} & Spring Boot, Node.js, Laravel, Django, .NET \\
                \textbf{Web Technologies:} & React.js, Angular.js, HTML5, CSS3, REST APIs, JSON \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, ElasticSearch, DynamoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Tools \& Others:} & Git, Linux/Unix, JUnit, Jira, API Design, Concurrent Programming \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}