\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} back-end services resulting in 35\% API throughput improvement and system scalability.}
        \resumeItem{Implemented \textbf{Spring Security} role-based access, reducing unauthorized access attempts by 40\% and increasing security.}
        \resumeItem{Deployed an \textbf{AI-driven} code reviewer using LLMs, reducing manual review time by 45\% and increasing code quality.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker} that cut release cycles by 40\%, enabling faster deployments.}
        \resumeItem{Analyzed and optimized back-end microservices architecture for high availability and minimized latency by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed scalable \textbf{Laravel} and \textbf{React} SaaS platform, supporting 50+ users with 99.9\% uptime.}
        \resumeItem{Automated daily data pipelines in \textbf{Python} to process 10,000+ entries, reducing manual efforts by 80\%.}
        \resumeItem{Created AI-powered data agents leveraging \textbf{LLMs} to automate broker data processing, improving efficiency by 80\%.}
        \resumeItem{Built an \textbf{AI-driven} LinkedIn outreach bot that increased qualified leads by 40\% via automated content posting.}
        \resumeItem{Refined \textbf{React} components to reduce page load times by 25\%, increasing user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab environment, ensuring secure and stable infrastructure for 100+ users.}
        \resumeItem{Assisted students debugging and deploying code modules, improving lab success rates by 20\% through guidance.}
        \resumeItem{Automated grading scripts, increasing evaluation accuracy by 25\% and reducing manual checking workload.}
        \resumeItem{Presented 15+ sessions on network protocols, cryptography, and security, clarifying complex technical concepts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency \textbf{TypeScript} APIs ensuring average responses under 100 ms for seamless data flow.}
        \resumeItem{Upgraded platform UI using \textbf{Angular.js} leading to 25\% boost in user satisfaction and engagement.}
        \resumeItem{Built backend services in \textbf{C\# .NET} reducing database response time by 30\% and improving stability.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures cutting frontend load by 15\%, enhancing overall database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices handling 1000+ simultaneous users with sub-200ms latency.}
        \resumeItem{Integrated APIs and databases to automate SDLC tasks, improving team productivity by 35\%.}
        \resumeItem{Managed \textbf{CI/CD} pipelines deploying six microservices on \textbf{AWS EC2} with containerization using \textbf{Docker}.}
        \resumeItem{Implemented comprehensive unit tests with \textbf{JUnit} achieving 90\% coverage, ensuring code stability and reliability.}
        \resumeItem{Developed management interface in \textbf{React} improving user experience and reducing load times by 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI Code Quality Evaluator} | Python, OpenAI API, REST APIs}{}
          \resumeItemListStart
              \resumeItem{Built tool to evaluate AI-generated code quality and performance across multiple languages, increasing accuracy of feedback by 30\%.}
              \resumeItem{Integrated human-readable explanations for coding tradeoffs, improving code comprehension and review efficiency by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Backend System for Code Solutions} | Node.js, MongoDB, Docker}{}
          \resumeItemListStart
              \resumeItem{Designed backend architecture to host and run coding problem solutions supporting hundreds of concurrent users seamlessly.}
              \resumeItem{Optimized database queries and system performance, reducing latency by 40\% and improving scalability under load.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, JavaScript, TypeScript, C\#, PHP, Go, C++, C \\
                \textbf{Back-end Frameworks \& Tools:} & Spring Boot, Node.js, Laravel, .NET, Docker, Jenkins, REST APIs \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, SQL, DynamoDB \\
                \textbf{Cloud Platforms:} & AWS (EC2, S3, Lambda), Azure \\
                \textbf{DevOps \& Automation:} & CI/CD, Docker, Jenkins, Git, GitHub Actions \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}