\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed scalable \textbf{Java Spring Boot} microservices enhancing system throughput by 35\% under heavy load.}
        \resumeItem{Engineered role-based authentication via \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Implemented AI-powered code review assistant to cut manual reviews by 45\% and speed delivery by 25\%.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing release cycles by 40\%.}
        \resumeItem{Collaborated in Agile team ceremonies improving sprint delivery consistency by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ concurrent users with 99.9\% uptime.}
        \resumeItem{Automated \textbf{Python} data pipelines for daily processing of 10,000+ stock entries, saving 80\% manual time.}
        \resumeItem{Developed AI agents leveraging \textbf{LLMs} for broker data processing, reducing manual work by 80\%.}
        \resumeItem{Enhanced \textbf{React} UI performance cutting page load times by 25\% and improving user retention.}
        \resumeItem{Built subscription platform with \textbf{PHP} integrating \textbf{Stripe} for role-based e-commerce access control.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments for cybersecurity labs, improving system uptime by 15\%.}
        \resumeItem{Automated grading scripts to reduce review workload by 25\% and increase test accuracy.}
        \resumeItem{Guided 100+ students in debugging and deploying software, improving assignment success rates by 20\%.}
        \resumeItem{Led online sessions on Cryptography, Networking, and Web Security to enhance student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API calls with sub-100ms response times improving data exchange by 25\%.}
        \resumeItem{Improved user engagement 25\% upgrading front-end with \textbf{Angular.js} and optimizing UI components.}
        \resumeItem{Built backend services in \textbf{C\#} with \textbf{.NET} reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, decreasing database query time by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices with \textbf{MySQL} supporting 1000 concurrent users under 200ms latency.}
        \resumeItem{Implemented CI/CD pipelines deploying 6 core microservices on \textbf{AWS EC2} using \textbf{Docker} containers.}
        \resumeItem{Built project management UI with \textbf{React.js}, improving load speed and usability by 30\%.}
        \resumeItem{Authored unit tests in \textbf{JUnit} achieving 90\% coverage for pipelines module.}
        \resumeItem{Collaborated within Agile teams to deliver scalable SDLC automation SaaS tool features on time.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Inventory Management Microservices} | C#, .NET, AWS}
          {}
          \resumeItemListStart
              \resumeItem{Designed and deployed scalable \textbf{C# .NET} web services on \textbf{AWS Elastic Beanstalk}, reducing dealer listing latency 30\%.}
              \resumeItem{Implemented advanced pricing intelligence algorithms improving vehicle pricing accuracy by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-native Dealer Tools UI} | Stencil, JavaScript, AWS}
          {}
          \resumeItemListStart
              \resumeItem{Developed responsive dealer workflow UIs using \textbf{Stencil} and \textbf{JavaScript}, increasing user efficiency by 25\%.}
              \resumeItem{Integrated with \textbf{AWS S3} and backend services to support high-volume inventory updates seamlessly.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C\#, Java, JavaScript, Python, TypeScript, PHP \\
                \textbf{Frameworks \& Libraries:} & .NET, Spring Boot, Stencil, React.js, Angular.js, Laravel \\
                \textbf{Databases:} & MSSQL, MySQL, PostgreSQL, DynamoDB, Redis \\
                \textbf{Cloud \& DevOps:} & AWS SDK, Elastic Beanstalk, EC2, S3, ElastiCache, Docker, Jenkins \\
                \textbf{Web Development:} & REST APIs, Microservices, UI/UX Design, Agile, Scrum \\
                \textbf{Tools \& Others:} & Git, GitHub, NewRelic, Splunk, Test-Driven Development, Code Reviews \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}