\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} APIs, increasing application response time by 35\% for high traffic services.}
        \resumeItem{Secured endpoints with \textbf{Spring Security}, reducing unauthorized access attempts by 40\% through role-based controls.}
        \resumeItem{Implemented automated code review tool using \textbf{LLMs}, cutting manual review time by 45\% and improving code quality.}
        \resumeItem{Streamlined CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 40\% and errors in production.}
        \resumeItem{Collaborated with cross-functional teams to integrate new features, achieving 25\% faster delivery within Agile sprint cycles.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed \textbf{RESTful APIs} for SaaS platform using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users efficiently.}
        \resumeItem{Automated daily stock data pipelines in \textbf{Python}, reducing manual work by 80\% with reliable processing of 10,000+ entries.}
        \resumeItem{Developed subscription e-commerce system with \textbf{PHP} and \textbf{Stripe}, implementing access control and boosting revenue by 20\%.}
        \resumeItem{Leveraged \textbf{LLMs} to automate FINRA broker data downloads, decreasing processing time by 80\% with error reduction.}
        \resumeItem{Improved \textbf{React} UI components, cutting page load times by 25\% and increasing user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity lab environments, ensuring secure configurations and uptime for student use.}
        \resumeItem{Guided students through software deployment and debugging, improving assignment success rates by 20\% across multiple courses.}
        \resumeItem{Automated grading scripts, increasing accuracy by 25\% and reducing manual workload for instructors.}
        \resumeItem{Delivered 15+ online sessions explaining cryptography and network security concepts to enhance student understanding.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs with sub-100ms response times for real-time data exchange in client applications.}
        \resumeItem{Enhanced platform frontend using \textbf{Angular.js}, increasing user engagement and satisfaction by 25\%.}
        \resumeItem{Built backend services in \textbf{C\#} with \textbf{.NET} to reduce data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, improving database query efficiency and reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices to support 1000 concurrent users with under 200ms response times.}
        \resumeItem{Built and maintained \textbf{MySQL} databases, including complex queries and DDL creation to support application features.}
        \resumeItem{Configured \textbf{CI/CD} pipelines on \textbf{AWS EC2} using \textbf{Docker}, enabling frequent seamless deployments.}
        \resumeItem{Created project management UI in \textbf{React.js}, improving user experience and loading speed by 30\%.}
        \resumeItem{Implemented \textbf{JUnit} unit tests with 90\% coverage to ensure application stability and quality assurance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Financial Services RESTful API Platform} | Java, Spring Boot, Swagger, PostgreSQL}{}
          \resumeItemListStart
              \resumeItem{Designed and developed secure, documented \textbf{RESTful APIs} with \textbf{Swagger} to support financial transactions.}
              \resumeItem{Integrated complex database queries and optimized \textbf{PostgreSQL} performance to improve backend response times by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Agile-based Microservices Development Toolkit} | Java, Spring Boot, Jenkins, Docker}{}
          \resumeItemListStart
              \resumeItem{Built microservices framework supporting Agile sprint-based development, enabling fast iterations and continuous delivery.}
              \resumeItem{Automated testing and deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing release cycle times by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & Java, Spring Boot, Python, JavaScript, TypeScript, PHP, C\#, React.js, Angular.js \\
                \textbf{API \& Web Services:} & RESTful APIs, Swagger, JSON, Web Services, API Security \\
                \textbf{Databases:} & PostgreSQL, MySQL, SQL, MongoDB, Database Design, DDL, Complex Queries \\
                \textbf{DevOps \& CI/CD:} & Jenkins, Docker, AWS EC2, CI/CD Pipelines, Agile \\
                \textbf{Testing \& Tools:} & JUnit, Git, Bitbucket, Code Reviews, Agile/SCRUM, Impact Analysis \\
                \textbf{Methodologies \& Practices:} & Agile, SCRUM, Waterfall, SDLC, On-call Rotation, Code Quality Improvement \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}