\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} applications by resolving bugs, improving system stability by 30\%.}
        \resumeItem{Led code reviews and provided constructive feedback, improving code quality and reducing defects by 25\%.}
        \resumeItem{Authored detailed in-code and external documentation, boosting team productivity and reducing onboarding time by 20\%.}
        \resumeItem{Collaborated with team members to implement software enhancements, accelerating feature delivery by 15\%.}
        \resumeItem{Utilized version control tools to manage code changes, ensuring seamless integration and deployment cycles.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented scalable backend solutions with \textbf{PHP} and \textbf{React}, improving system responsiveness by 35\%.}
        \resumeItem{Optimized \textbf{SQL} queries and database schema, reducing data retrieval times by 30\%.}
        \resumeItem{Conducted peer code reviews to identify and fix bugs, decreasing critical errors by 40\%.}
        \resumeItem{Developed clear technical documentation for software modules, simplifying maintenance and future updates.}
        \resumeItem{Collaborated in agile sprints, consistently delivering features on schedule and improving sprint completion rate by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and troubleshot \textbf{Linux} cybersecurity labs, ensuring 99\% uptime and secure environments.}
        \resumeItem{Assisted students in debugging code and testing modules, improving assignment pass rates by 20\%.}
        \resumeItem{Automated grading system scripts, reducing instructor workload by 30\% and increasing grading accuracy.}
        \resumeItem{Delivered 15+ interactive sessions explaining complex cybersecurity principles to improve student engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{C\# .NET} backend services, improving data processing speed by 30\%.}
        \resumeItem{Refined API integrations with \textbf{TypeScript}, reducing average response times under 100ms.}
        \resumeItem{Enhanced \textbf{PostgreSQL} queries and indexes, decreasing frontend load by 15\%.}
        \resumeItem{Improved user interface components using \textbf{Angular.js}, boosting user satisfaction by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices with \textbf{MySQL}, handling 1000+ users with sub-200ms latency.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Docker} on \textbf{AWS EC2}, accelerating deployments by 40\%.}
        \resumeItem{Created intuitive project management UI with \textbf{React.js}, increasing team productivity by 30\%.}
        \resumeItem{Conducted code reviews and authored documentation to streamline development and reduce onboarding time.}
        \resumeItem{Wrote \textbf{JUnit} tests covering 90\% of code, improving software reliability and reducing bugs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Bug Fixing and Enhancement Tracker} | Java, SQL, Spring Boot}{}
          \resumeItemListStart
              \resumeItem{Developed a tracking tool for bug fixes and feature enhancements, increasing team efficiency by 20\%.}
              \resumeItem{Integrated documentation generator that produces clear reports, reducing update time by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Code Review Automation Tool} | Python, GitHub API, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Created an AI-driven code review tool to automatically identify bugs and suggest improvements, cutting manual reviews by 35\%.}
              \resumeItem{Automated generation of code documentation, achieving 100\% coverage on new features and reducing errors.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, C\#, React Native, Ruby, JavaScript, SQL, HTML, Vue.js, JSF \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, .NET, React.js, Angular.js, Laravel \\
                \textbf{Databases:} & MySQL, PostgreSQL, SQL Server, MongoDB \\
                \textbf{Tools \& DevOps:} & Git, Jenkins, Docker, AWS, CI/CD pipelines \\
                \textbf{Documentation \& Testing:} & JUnit, In-code documentation, External technical documentation \\
                \textbf{Other Skills:} & Agile methodologies, Code review, Debugging, Problem-solving \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}