\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Java Spring Boot} microservices improving backend scalability by 35\% with robust API design.}
        \resumeItem{Enhanced security by configuring \textbf{Spring Security} for role-based access, cutting unauthorized access attempts 40\%.}
        \resumeItem{Developed scalable testable code modules reducing bugs by 30\% and improving maintainability in production environment.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker} cutting release cycles by 40\% and minimizing errors.}
        \resumeItem{Collaborated with frontend team to integrate \textbf{React} UI, improving user experience and reducing page load times 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed frontend features using \textbf{React} and \textbf{JavaScript}, decreasing user-reported issues by 25\%.}
        \resumeItem{Built backend services in \textbf{PHP} integrated with SQL and \textbf{NoSQL databases}, handling 10,000+ transactions daily efficiently.}
        \resumeItem{Optimized database queries for \textbf{MongoDB} and \textbf{MySQL}, improving data retrieval times by 30\%.}
        \resumeItem{Implemented automated testing frameworks boosting test coverage by 40\% and reducing defects during deployment.}
        \resumeItem{Led frontend and backend integration improving client satisfaction scores by 20\% through rapid bug fixes and feature releases.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Developed and maintained test scripts enhancing software reliability and accuracy of lab experiments by 25\%.}
        \resumeItem{Managed \textbf{Linux}-based systems ensuring secure lab infrastructure with zero downtime during assignments.}
        \resumeItem{Provided technical guidance on deploying secure code, boosting student project success rate by 20\%.}
        \resumeItem{Facilitated teaching sessions, clearly explaining software development lifecycle concepts and deployment mechanisms.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{Angular.js} components improving user engagement metrics by 25\% across web platform.}
        \resumeItem{Implemented backend APIs in \textbf{C\#} reducing data retrieval latency by 30\%, enhancing overall system responsiveness.}
        \resumeItem{Tuned \textbf{PostgreSQL} stored procedures cutting query execution time by 15\%, enhancing performance of web services.}
        \resumeItem{Collaborated with frontend team integrating APIs to ensure seamless data flow and reduced error rates by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed scalable \textbf{Java Spring Boot} microservices with \textbf{MySQL} achieving 200ms response across 1000 users.}
        \resumeItem{Implemented full-stack features using \textbf{React.js} enhancing UI load time by 30\% and user navigation flow.}
        \resumeItem{Developed and executed \textbf{JUnit} tests achieving 90\% unit test coverage for critical pipeline components.}
        \resumeItem{Established \textbf{CI/CD} pipelines utilizing \textbf{Docker} and \textbf{AWS EC2}, cutting deployment times by 35\%.}
        \resumeItem{Collaborated on product design improving scalable codebase and meeting strict business timelines with high quality.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scalable Microservices for Inventory Management} | Java, Spring Boot, MongoDB}
          {}
          \resumeItemListStart
              \resumeItem{Developed scalable microservices handling 1000+ concurrent requests with 200ms response time using \textbf{Spring Boot}.}
              \resumeItem{Implemented \textbf{MongoDB} data storage optimizing query performance and supporting fast, reliable transactions.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Interactive Web Dashboard} | React, JavaScript, CSS}
          {}
          \resumeItemListStart
              \resumeItem{Created dynamic dashboard with \textbf{React} showcasing data visualizations, reducing user load time by 25\%.}
              \resumeItem{Optimized state management improving responsiveness and seamless integration with backend APIs for real-time updates.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, JavaScript, Python, PHP, TypeScript, C\#, SQL \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, JUnit, .NET \\
                \textbf{Databases:} & SQL, MySQL, PostgreSQL, MongoDB, Cassandra \\
                \textbf{Web Technologies:} & HTML, CSS, REST APIs, GraphQL \\
                \textbf{DevOps \& Tools:} & Docker, Jenkins, AWS, Git, CI/CD pipelines \\
                \textbf{Other Skills:} & Agile methodologies, Test-driven development, Microservices architecture \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}