\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed scalable backend services with \textbf{Java Spring Boot}, increasing API efficiency by 35\%.}
        \resumeItem{Implemented secure role-based access control using \textbf{Spring Security}, reducing breaches by 40\%.}
        \resumeItem{Automated code reviews with \textbf{AI-driven} tools, cutting manual effort by 45\% and speeding releases 25\%.}
        \resumeItem{Streamlined deployment through \textbf{Jenkins} and \textbf{Docker} pipelines, decreasing release cycles by 40\%.}
        \resumeItem{Collaborated cross-functionally to translate business needs into technical improvements, enhancing system usability.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built a \textbf{SaaS} platform using \textbf{Laravel} and \textbf{React} supporting 50+ users with smooth concurrent operations.}
        \resumeItem{Automated daily data pipelines in \textbf{Python}, decreasing manual workload by 80\% for stock entries.}
        \resumeItem{Developed e-commerce subscription platform with \textbf{PHP} and Stripe, enabling role-based application access.}
        \resumeItem{Created AI agents with \textbf{LLMs} automating broker data processing, reducing manual steps by 80\%.}
        \resumeItem{Enhanced \textbf{React} components to improve page load speed by 25\% and bolster user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} infrastructure for labs, ensuring safe execution of cybersecurity modules.}
        \resumeItem{Assisted students with debugging and testing software, improving success rates by 20\%.}
        \resumeItem{Automated grading scripts increased accuracy by 25\% and reduced manual workload in assessments.}
        \resumeItem{Led interactive sessions on Cryptography and Web Security, enhancing student comprehension significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed fast API calls in \textbf{TypeScript}, reducing response times to under 100ms for seamless data flow.}
        \resumeItem{Upgraded platform frontend in \textbf{Angular.js}, enhancing user engagement and satisfaction by 25\%.}
        \resumeItem{Implemented high-performance backend in \textbf{C\#} with \textbf{.NET}, cutting data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures reducing frontend load by 15\% and improving database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL} supporting 1000+ users under 200ms latency.}
        \resumeItem{Orchestrated \textbf{CI/CD} pipelines deploying key microservices on \textbf{AWS EC2} using \textbf{Docker}.}
        \resumeItem{Constructed project management UI with \textbf{React.js}, boosting usability and performance by 30\%.}
        \resumeItem{Authored unit tests covering 90\% code using \textbf{JUnit}, ensuring robust pipeline reliability.}
        \resumeItem{Collaborated in a team to build a \textbf{SaaS} tool automating SDLC processes and increasing efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Franchise Operations Management Portal} | .NET Core, React, SQL Server}
          \resumeItemListStart
              \resumeItem{Developed an internal business portal improving franchisees’ operations efficiency, reducing process time by 30\%.}
              \resumeItem{Integrated \textbf{RESTful APIs} to sync real-time data between corporate and franchise partners, enhancing reliability.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Customer Performance Dashboard} | Angular, C\#, Azure, SQL Server}
          \resumeItemListStart
              \resumeItem{Built an interactive dashboard providing real-time analytics to customers, boosting engagement by 40\%.}
              \resumeItem{Implemented cloud deployment on \textbf{Azure} ensuring 99.9\% uptime and scalable resource management.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C\#, Java, Python, JavaScript, TypeScript, PHP \\
                \textbf{Frameworks \& Libraries:} & .NET Core, ASP.NET MVC, Spring Boot, React, Angular, Laravel \\
                \textbf{Databases:} & SQL Server, MySQL, PostgreSQL, MongoDB \\
                \textbf{Cloud \& DevOps:} & Azure, AWS, Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Web Technologies:} & RESTful APIs, Microservices, HTML, CSS, Git \\
                \textbf{Tools \& Others:} & Agile Methodologies, Jira, Unit Testing, UI/UX Principles \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}