\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and maintained scalable \textbf{Java Spring Boot} applications improving API response times by 35\%.}
        \resumeItem{Implemented access control and authentication using \textbf{Spring Security}, reducing security breaches by 40\%.}
        \resumeItem{Integrated databases and \textbf{Message Queues} to enhance asynchronous processing efficiency by 30\%.}
        \resumeItem{Automated build and deployment pipelines with \textbf{Jenkins} and \textbf{Docker}, cutting release cycles by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to deliver high-quality solutions under tight deadlines.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed backend APIs and integrated \textbf{Message Queues} to support real-time data processing with 99.9\% uptime.}
        \resumeItem{Applied \textbf{Data Structures} and \textbf{Algorithms} to optimize data visualization features, improving load times by 25\%.}
        \resumeItem{Built AI-driven automation tools using \textbf{Python} and \textbf{LLMs} to streamline manual stock data processing by 80\%.}
        \resumeItem{Enhanced \textbf{React} front-end performance, boosting user engagement by 30\%.}
        \resumeItem{Documented APIs adhering to REST standards and assisted in API integration testing with \textbf{Postman}.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based infrastructure ensuring secure and stable environments for cybersecurity labs.}
        \resumeItem{Guided students in debugging and deploying applications, improving success rates in lab completions by 20\%.}
        \resumeItem{Automated grading scripts using \textbf{Python}, reducing manual grading time by 25\%.}
        \resumeItem{Maintained documentation and conducted workshops on data structures, algorithms, and security concepts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed high-performance backend modules with \textbf{C\# .NET} resulting in 30\% lower data retrieval latency.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, which decreased frontend load time by 15\%.}
        \resumeItem{Implemented API integrations in \textbf{TypeScript} with sub-100ms response times for improved user experience.}
        \resumeItem{Upgraded existing platforms using \textbf{Angular.js} enhancing user engagement by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, reducing API latency to under 200ms.}
        \resumeItem{Deployed 6 microservices on \textbf{AWS EC2} using \textbf{Docker} with automated CI/CD pipelines.}
        \resumeItem{Enhanced UI with \textbf{React.js} improving usability and load speed by 30\%.}
        \resumeItem{Wrote unit tests achieving 90\% coverage for pipelines with \textbf{JUnit} framework.}
        \resumeItem{Collaborated with team to design scalable solutions leveraging OOP and design patterns.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Virtual Receptionist Platform} | Java, Spring Boot, REST API, SQL}{}
          \resumeItemListStart
              \resumeItem{Developed core \textbf{Java} services handling scheduling and client inquiries with 99.9\% uptime.}
              \resumeItem{Integrated SMS and web chat APIs for seamless 24/7 communication, improving customer contact rates by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Notification System} | Java, Message Queues, MySQL, Docker}{}
          \resumeItemListStart
              \resumeItem{Designed asynchronous notification delivery with \textbf{Message Queues}, reducing processing delays by 50\%.}
              \resumeItem{Optimized database queries in \textbf{MySQL} enabling support for 1000+ concurrent users with minimal latency.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, SQL, JavaScript, TypeScript, C\# \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Databases \& Messaging:} & MySQL, MS SQL, PostgreSQL, Message Queues, REST API \\
                \textbf{DevOps \& Cloud:} & AWS EC2, Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Tools \& Version Control:} & Git, JUnit, Postman, Jira \\
                \textbf{AI \& Automation:} & Conversational AI, LLMs, OpenAI API, Python Scripting, Chatbots \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}