\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Python} workflows to automate data processes, improving system throughput by 40\% via cloud deployment.}
        \resumeItem{Implemented performance benchmarks using profiling tools, enhancing CPU and GPU efficiency by 30\% across key microservices.}
        \resumeItem{Integrated \textbf{Docker} and \textbf{CI/CD} pipelines with Git to automate deployment, reducing release cycles by 35\%.}
        \resumeItem{Collaborated with cross-functional teams to design APIs supporting machine learning training and robotics simulation environments.}
        \resumeItem{Contributed to open-source projects enhancing simulation parameter tuning, leading to 25\% more accurate physics-based models.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected \textbf{Python}-based data pipelines automating 10,000+ stock records, increasing processing efficiency by 80\%.}
        \resumeItem{Enhanced React components and managed state, reducing page load time by 25\% and improving UI responsiveness for users.}
        \resumeItem{Built AI-driven automation with \textbf{LLMs} for broker data extraction, cutting manual effort by 80\% and errors by 15\%.}
        \resumeItem{Deployed scalable backend microservices integrating \textbf{Stripe} for subscriptions, improving revenue flow by 30\%.}
        \resumeItem{Designed automated test suites in \textbf{Python} and enhanced debugging workflows to improve CI/CD pipeline robustness by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Automated grading workflows using \textbf{Python}, improving assessment accuracy and reducing manual workload by 25\%.}
        \resumeItem{Supported Linux-based lab infrastructure to maintain secure and stable environments for 50+ cybersecurity students.}
        \resumeItem{Guided students troubleshooting security protocols, increasing assignment completion rates by 20\% for diverse software projects.}
        \resumeItem{Conducted live sessions explaining protocols, cryptography, and debugging, enhancing understanding across virtual and physical labs.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized database interactions using \textbf{PostgreSQL} stored procedures, reducing query times by 15\% and improving scaling.}
        \resumeItem{Developed backend features in \textbf{C\#} and \textbf{.NET}, cutting data retrieval latency by 30\% for web applications.}
        \resumeItem{Implemented fast API requests in \textbf{TypeScript}, reducing response time below 100ms and boosting user experience.}
        \resumeItem{Upgraded frontend components in \textbf{Angular.js}, enhancing user engagement by 25\% with modern UI practices.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices handling 1000+ concurrent users, reducing response latency below 200ms.}
        \resumeItem{Built and maintained \textbf{Docker}-based CI/CD pipelines on \textbf{AWS EC2}, improving deployment speed by 35\%.}
        \resumeItem{Designed comprehensive unit tests using \textbf{JUnit}, achieving 90\% test coverage and reducing bugs by 40\%.}
        \resumeItem{Created React.js frontends, improving project tracking usability and decreasing page load times by 30\%.}
        \resumeItem{Automated SDLC process for SaaS tool development, reducing cycle time by 25\% and improving release reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Robotics Simulation & Reinforcement Learning Platform} | Python, PyTorch, Isaac Sim}
          {}
          \resumeItemListStart
              \resumeItem{Developed a platform integrating multi-agent reinforcement learning using \textbf{PyTorch}, improving training speed by 35\%.}
              \resumeItem{Automated simulation workflows on \textbf{Isaac Sim} to enable scalable tele-operation data collection, reducing manual effort by 50\%.}
              \resumeItem{Performed extensive profiling to optimize CPU/GPU workloads, enhancing system scalability by 40\% during large-scale runs.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Robotics Policy Trainer} | Python, TensorFlow, Mujoco}
          {}
          \resumeItemListStart
              \resumeItem{Engineered simulation training for robotic control policies using \textbf{TensorFlow} and \textbf{Mujoco}, achieving 20\% improvement in sim-to-real transfer.}
              \resumeItem{Executed trajectory optimization and motion planning simulations, improving policy accuracy and response times significantly.}
              \resumeItem{Contributed to open-source integration for physics parameter tuning, achieving 25\% higher fidelity in robot behavior predictions.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, C++, Java, TypeScript, C\#, JavaScript, Shell Scripting \\
                \textbf{Robotics \& Simulation:} & Isaac Sim, Mujoco, Reinforcement Learning, Trajectory Optimization, Motion Planning \\
                \textbf{AI \& Deep Learning Frameworks:} & PyTorch, TensorFlow, Jax, OpenAI API \\
                \textbf{DevOps \& Cloud:} & Docker, Git, CI/CD workflows, Jenkins, AWS, Kubernetes \\
                \textbf{Tools \& Performance:} & GitHub, Profiling & Performance Analysis, Debugging Methodologies, Linux \\
                \textbf{Web \& Backend Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}