\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices, improving API throughput by 35\%, enhancing system scalability and response times.}
        \resumeItem{Implemented \textbf{Spring Security} enhancements, reducing unauthorized access attempts by 40\% via refined role-based authentication.}
        \resumeItem{Integrated \textbf{AI-driven} code review tools, cutting manual pull request reviews by 45\%, accelerating team development velocity.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing deployment times by 40\% and improving release reliability.}
        \resumeItem{Collaborated on cross-functional teams with Agile practices, participating in stand-ups to deliver features on a tight schedule.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{React} SaaS platform, supporting 50+ concurrent users with optimized frontend performance and user engagement.}
        \resumeItem{Scripted \textbf{Python} automation pipelines processing 10,000+ stock entries daily, reducing manual work by 80\% and errors.}
        \resumeItem{Developed multi-tier \textbf{PHP} e-commerce with role-based access, integrating \textbf{Stripe} payments to streamline subscriptions.}
        \resumeItem{Built AI agents using \textbf{LLMs} to automate complex FINRA broker data tasks, improving efficiency by 80\%.}
        \resumeItem{Enhanced \textbf{React} component states, decreasing page load times by 25\% and boosting overall user participation.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab infrastructure, ensuring secure, reliable environments for student cybersecurity projects.}
        \resumeItem{Assisted students in debugging and deploying software, increasing assignment pass rates by 20\% through hands-on guidance.}
        \resumeItem{Automated grading scripts boosting accuracy by 25\%, reducing manual review workload and speeding feedback delivery.}
        \resumeItem{Conducted over 15 interactive sessions covering cryptography, network protocols, and web security concepts effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented fast API calls in \textbf{TypeScript} with sub-100ms latency, improving real-time data exchange significantly.}
        \resumeItem{Refactored \textbf{Angular.js} frontend, increasing user engagement and satisfaction metrics by 25\% through UI enhancements.}
        \resumeItem{Developed \textbf{C\# .NET} backend services that reduced data retrieval latency by 30\%, optimizing server response times.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, lowering frontend server load by 15\% and boosting efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices with \textbf{MySQL}, supporting 1000+ concurrent users with <200ms response times.}
        \resumeItem{Built a \textbf{React.js} UI increasing usability by 30\%, enhancing user experience significantly across multiple products.}
        \resumeItem{Configured CI/CD pipelines using \textbf{Docker} on \textbf{AWS EC2}, enabling smooth deployment of critical microservices.}
        \resumeItem{Wrote unit tests with \textbf{JUnit}, achieving approximately 90\% coverage and improving code reliability.}
        \resumeItem{Collaborated on SaaS tool development that automated software lifecycle processes, improving team workflow efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Automated Code Review Bot} $|$ GitHub Actions, OpenAI API, Python}
          \resumeItemListStart
              \resumeItem{Created a \textbf{CI/CD} bot utilizing \textbf{LLMs} to auto-review code and generate Python docstrings, cutting review time by 25\%.}
              \resumeItem{Integrated dynamic bug detection and style checks into pull requests, raising code quality and consistency across teams.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Face Recognition as a Service} $|$ AWS EC2, SQS, Python, Flask}
          \resumeItemListStart
              \resumeItem{Engineered backend system to auto-scale and handle 1000+ facial recognition requests under 60 seconds efficiently.}
              \resumeItem{Implemented decoupled architecture using \textbf{SQS}, improving system resilience and fault tolerance.}
              \resumeItem{Utilized \textbf{S3} for persistent storage, maintaining robust data availability and security.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, JavaScript, C\#, TypeScript, PHP, C++, Ruby \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React, Angular, Laravel, Node.js, Django \\
                \textbf{Web Technologies:} & HTML5, CSS3, REST APIs, gRPC, jQuery \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, Lambda, S3), Docker, Jenkins, Git, CI/CD Pipelines \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, n8n, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}