\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{full stack} web applications by optimizing \textbf{backend APIs} and integrating front end features, improving responsiveness 28\%.}
        \resumeItem{Developed user stories collaboratively, estimating effort and scope to streamline sprint planning and successful feature delivery.}
        \resumeItem{Maintained microservices architecture on \textbf{AWS}, ensuring high availability and reducing downtime by 20\%.}
        \resumeItem{Integrated \textbf{JavaScript} front end with \textbf{Spring Boot} backend, resulting in 35\% improved data flow efficiency.}
        \resumeItem{Tracked emerging technologies continuously, applying new tools to enhance code quality and development speed by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and maintained \textbf{full stack} features using \textbf{React} and \textbf{Node.js}, boosting user engagement by 30\%.}
        \resumeItem{Automated deployment pipelines on \textbf{AWS} to reduce build failures and deployment time by 40\%.}
        \resumeItem{Built RESTful APIs consuming \textbf{JavaScript} data services, enhancing data retrieval speed by 25\%.}
        \resumeItem{Collaborated on microservices to maintain database integrity and scaled features to support 1,000+ concurrent users.}
        \resumeItem{Refined CSS and \textbf{webpack} configurations to improve front end load times by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Assisted in debugging and deploying web applications, improving lab project success rates by 20\%.}
        \resumeItem{Automated infrastructure scripts to maintain \textbf{Linux} lab environments, reducing manual setup time by 30\%.}
        \resumeItem{Managed secure network configurations, protecting lab assets from unauthorized access incidents by 15\%.}
        \resumeItem{Instructed students on \textbf{web protocols} and application data flows enhancing understanding of full stack operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{JavaScript} API calls reducing average response latency to under 100ms and improving UX.}
        \resumeItem{Enhanced front end with \textbf{Angular.js}, increasing user retention by 25\% through performance improvements.}
        \resumeItem{Created robust back end services using \textbf{C\#} and \textbf{.NET}, decreasing server load times by 18\%.}
        \resumeItem{Improved \textbf{PostgreSQL} queries and indexing, boosting data retrieval speed by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Implemented scalable \textbf{Java Spring Boot} microservices integrating with \textbf{MySQL}, handling 1,000 concurrent users efficiently.}
        \resumeItem{Designed and deployed responsive \textbf{React.js} UIs, improving page load speed and usability by 30\%.}
        \resumeItem{Managed CI/CD pipeline creation with \textbf{Docker} and \textbf{AWS EC2} to automate deployments and reduce downtime 25\%.}
        \resumeItem{Enhanced application security by refining authentication flows and integrating role-based access controls.}
        \resumeItem{Wrote comprehensive \textbf{JUnit} unit tests covering 90\% of backend code, increasing robustness and lowering bugs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Assisted Full Stack Code Review Tool} | GitHub Actions, OpenAI API, JavaScript}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-powered code review system for \textbf{JavaScript} and \textbf{React} projects, reducing manual reviews 40\%.}
              \resumeItem{Automated documentation and style enforcement for front end and backend code, increasing code consistency by 35\%.}
              \resumeItem{Integrated with \textbf{GitHub Actions} to process pull requests continuously, accelerating deployment cycles by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-Native Full Stack App for Customer Feedback} | React, Node.js, AWS}{}
          \resumeItemListStart
              \resumeItem{Built a cloud-native feedback portal using \textbf{React} front end and \textbf{Node.js} microservices on \textbf{AWS}, serving 500+ daily users.}
              \resumeItem{Optimized data flow and API integrations resulting in a 30\% faster response time and improved user satisfaction.}
              \resumeItem{Implemented secure authentication and role-based access, decreasing unauthorized access attempts by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, Java, Python, TypeScript, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & React.js, Node.js, Spring Boot, Angular.js, Laravel, HTML, CSS, Webpack \\
                \textbf{Database \& Data Storage:} & MySQL, PostgreSQL, MongoDB, SQL \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD \\
                \textbf{Tools \& Technologies:} & Git, REST APIs, Web Protocols, Microservices, Spring Security \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}