\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices improving distributed system throughput and latency by 35\% through efficient API design.}
        \resumeItem{Designed and implemented \textbf{RESTful APIs} interacting with databases to optimize data workflows, reducing processing time by 25\%.}
        \resumeItem{Containerized microservices using \textbf{Docker} and deployed in \textbf{Kubernetes}, enhancing scalability and deployment reliability by 40\%.}
        \resumeItem{Integrated \textbf{Kafka} queues for messaging between microservices, boosting data transfer efficiency and fault tolerance by 30\%.}
        \resumeItem{Automated build and deployment pipelines using \textbf{Jenkins}, shortening release cycles by 40\% and improving deployment consistency.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable data pipelines using \textbf{Python} to process over 10,000 stock entries daily, increasing processing efficiency by 80\%.}
        \resumeItem{Implemented role-based access control and backend APIs to secure subscription services built on \textbf{PHP} and \textbf{Stripe}, improving authorization accuracy.}
        \resumeItem{Established \textbf{AI agents} leveraging \textbf{LLMs} to automate complex data downloads, reducing manual data processing effort by 80\%.}
        \resumeItem{Enhanced \textbf{React} frontend performance, reducing load times by 25\% and delivering smoother user interaction experience.}
        \resumeItem{Built AI-powered LinkedIn outreach bot automating lead generation processes, boosting qualified leads by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based infrastructure for cybersecurity labs, ensuring 99\% uptime and system integrity for student use.}
        \resumeItem{Assisted students in debugging and deploying code modules, improving project success rates by 20\% through hands-on guidance.}
        \resumeItem{Developed automated grading scripts, enhancing evaluation accuracy by 25\% and streamlining instructor workload effectively.}
        \resumeItem{Conducted interactive sessions on cryptography and network protocols, improving student comprehension and engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} APIs delivering sub-100ms response times, enhancing platform performance and reliability in data exchange.}
        \resumeItem{Refactored \textbf{Angular.js} components, improving user engagement metrics by 25\% through faster load times and smoother UI flow.}
        \resumeItem{Implemented backend services in \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\% from existing systems.}
        \resumeItem{Optimized \textbf{PostgreSQL} database procedures, lowering data load on frontend by 15\% and improving query efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices managing data analytics workflows, handling 1000 concurrent users with sub-200ms latency.}
        \resumeItem{Established \textbf{Docker}-based \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2}, increasing deployment frequency by 50\%.}
        \resumeItem{Created efficient database queries in \textbf{MySQL} and managed data persistence to optimize application responsiveness by 20\%.}
        \resumeItem{Built and maintained project management UI in \textbf{React.js}, improving usability and reducing load times by 30\%.}
        \resumeItem{Implemented unit tests in \textbf{JUnit} with 90\% coverage for backend services, improving code quality and reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Distributed Microservice Analytics Platform} | Java, Spring Boot, Kafka, Docker, Kubernetes}{}
          \resumeItemListStart
              \resumeItem{Architected microservices using \textbf{Spring Boot} and \textbf{Kafka} to process streaming data with 99.9\% uptime in distributed environment.}
              \resumeItem{Deployed services in \textbf{Docker} containers managed by \textbf{Kubernetes} improving scalability and fault tolerance for critical applications.}
              \resumeItem{Built backend RESTful APIs to query relational databases, optimizing workflow latency by 35\% and supporting concurrent user loads.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Automation} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed an AI assistant integrating \textbf{OpenAI API} with \textbf{GitHub Actions} to auto-review pull requests, reducing manual effort 30\%.}
              \resumeItem{Automated documentation generation using LLM, ensuring codebase doc coverage reached 100\% while improving developer productivity.}
              \resumeItem{Integrated CI/CD workflow automation to validate and merge pull requests with higher accuracy and faster release cycles.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, TypeScript, C\#, PHP, Shell Scripting \\
                \textbf{Frameworks \& Web Development:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, SQL \\
                \textbf{DevOps \& Containers:} & Docker, Kubernetes, Jenkins, AWS (EC2, S3, Lambda) \\
                \textbf{Messaging \& Streaming:} & Kafka, RabbitMQ, REST API, gRPC \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, GitHub Actions, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}