\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} backend services yielding 35\% higher scalability and 40\% improved throughput for API response times.}
        \resumeItem{Integrated \textbf{AI/LLM} modules for code optimization, accelerating development velocity by 25\% with automated code review assistant.}
        \resumeItem{Implemented \textbf{Docker} and \textbf{Jenkins} pipelines automating deployments and testing, reducing release cycles by 40\%.}
        \resumeItem{Enhanced authentication via \textbf{Spring Security}; diminished unauthorized access attempts by 40\% improving system security posture.}
        \resumeItem{Collaborated with cross-functional teams improving backend reliability and observability with monitoring tools, boosting uptime by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable data processing pipelines in \textbf{Python}, automating 10,000+ stock entries daily with an 80\% manual effort reduction.}
        \resumeItem{Implemented AI-driven \textbf{LLM} agents to automate broker data extraction, boosting data accuracy by 50\% and efficiency by 80\%.}
        \resumeItem{Built a subscription platform with role-based controls using \textbf{PHP} and payment APIs, increasing user retention by 20\%.}
        \resumeItem{Refined \textbf{React} frontend cutting load times by 25\%, enhancing user engagement and session durations.}
        \resumeItem{Automated LinkedIn outreach leveraging AI bots, generating 40\% more qualified leads and increasing conversion rates significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab infrastructure improving uptime by 15\% and streamlining student software deployment.}
        \resumeItem{Led debugging and deployment sessions raising student assignment completion rates by 20\%.}
        \resumeItem{Developed automated grading scripts reducing manual review workload by 25\% while increasing grading accuracy.}
        \resumeItem{Hosted 15+ sessions elucidating complex cybersecurity topics enhancing overall student comprehension and performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls achieving under 100ms average response times enhancing data exchange.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, reducing frontend load by 15\% enabling smoother database interactions.}
        \resumeItem{Improved backend efficiency implementing high-performance \textbf{C\# .NET} services cutting data latency by 30\%.}
        \resumeItem{Upgraded user interface with \textbf{Angular.js}, increasing user engagement by 25\% through improved UX design.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed \textbf{Java Spring Boot} microservices supporting 1000 concurrent users with sub-200ms response times using \textbf{MySQL}.}
        \resumeItem{Automated \textbf{CI/CD} pipelines deploying microservices on \textbf{AWS EC2} via \textbf{Docker}, reducing deployment errors by 50\%.}
        \resumeItem{Developed project management UI with \textbf{React.js}, accelerating page load by 30\% and boosting user satisfaction.}
        \resumeItem{Implemented robust \textbf{JUnit} unit tests achieving 90\%+ coverage improving code reliability.}
        \resumeItem{Collaborated in a 5-member team to create a SaaS tool automating SDLC process, increasing developer productivity by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GenAI-powered Pricing API Integration} | Java, Python, Kafka, Cassandra, GCP}
          \resumeItemListStart
              \resumeItem{Developed backend APIs in \textbf{Java} integrating GenAI LLMs, improving dynamic pricing accuracy by 25\%.}
              \resumeItem{Implemented real-time data streaming with \textbf{Kafka} ensuring sub-second latency for price updates.}
              \resumeItem{Optimized distributed storage using \textbf{Cassandra} for scalable pricing data handling supporting millions of users.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-driven Big Data ETL Pipeline} | Apache Spark, Airflow, Python, GCP}
          \resumeItemListStart
              \resumeItem{Engineered an automated ETL pipeline using \textbf{Spark} and \textbf{Airflow} processing terabytes daily on \textbf{GCP}.}
              \resumeItem{Integrated ML models for anomaly detection, improving pipeline fault tolerance by 30\%.}
              \resumeItem{Monitored workflows with Grafana dashboards enhancing system observability and reducing downtime by 20\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, Kotlin, TypeScript, C\# \\
                \textbf{Backend Frameworks \& APIs:} & Spring Boot, Django, REST API, gRPC \\
                \textbf{Big Data \& Streaming:} & Apache Spark, Kafka, Airflow, Cassandra \\
                \textbf{Cloud Platforms:} & Google Cloud Platform (GCP), AWS, Docker \\
                \textbf{Monitoring \& DevOps:} & Grafana, Jenkins, CI/CD Pipelines \\
                \textbf{AI \& Machine Learning:} & GenAI LLMs integration, ML models deployment, OpenAI API \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}