\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{Java Spring Boot} microservices, improving system scalability and reliability by 35\%.}
        \resumeItem{Collaborated with business teams to refine requirements, ensuring delivered features met customer expectations and timelines.}
        \resumeItem{Implemented secure role-based access control using \textbf{Spring Security}, reducing unauthorized activities by 40\%.}
        \resumeItem{Automated CI/CD processes with \textbf{Jenkins} and \textbf{Docker}, accelerating deployment frequency by 40\%.}
        \resumeItem{Utilized Agile ceremonies to effectively manage sprint goals, improving on-time delivery of software features by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed front-end application components with \textbf{React.js} and \textbf{JavaScript}, reducing load time by 25\% and enhancing UX.}
        \resumeItem{Built backend microservices using \textbf{PHP} and integrated payment gateways supporting subscription models with high reliability.}
        \resumeItem{Automated backend data processing pipelines in \textbf{Python}, reducing manual input by 80\% and increasing accuracy.}
        \resumeItem{Deployed \textbf{AI agents} using large language models to automate data extraction tasks, cutting manual work by 80\%.}
        \resumeItem{Strengthened React components with better state management, boosting user retention by 15\% across key platform features.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Configured and maintained \textbf{Linux}-based labs supporting cybersecurity experiments, ensuring 99\% uptime for students.}
        \resumeItem{Assisted students in deploying and debugging software, raising project success rates by 20\% through hands-on guidance.}
        \resumeItem{Developed automated grading scripts to validate assignments, improving evaluation accuracy by 25\%.}
        \resumeItem{Conducted comprehensive labs on cryptography and networking, enhancing student understanding and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced backend service APIs using \textbf{TypeScript}, reducing average response time to under 100ms for data queries.}
        \resumeItem{Upgraded frontend with \textbf{Angular.js} improving user engagement by 25\% through better UI responsiveness.}
        \resumeItem{Implemented high-performance backend systems with \textbf{C\#} and \textbf{.NET}, cutting data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, improving database efficiency and reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users with under 200ms latency.}
        \resumeItem{Built responsive project management UI with \textbf{React.js}, raising page load speed and usability by 30\%.}
        \resumeItem{Automated deployment pipelines on \textbf{AWS EC2} using \textbf{Docker}, reducing manual release errors by 50\%.}
        \resumeItem{Implemented unit tests with \textbf{JUnit} achieving 90\% coverage on core backend services, improving software quality.}
        \resumeItem{Led Agile collaboration to align deliverables with business requirements, improving sprint delivery consistency by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Software Validation Bot} | GitHub Actions, OpenAI API, Java, React}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-powered bot to automatically validate pull requests against design requirements, reducing review time by 30\%.}
              \resumeItem{Integrated \textbf{React} frontend with backend \textbf{Java} services for seamless real-time code quality feedback.}
              \resumeItem{Leveraged \textbf{GitHub Actions} for continuous integration and automatic issue detection in codebase, improving code health.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Enterprise Microservices for Business Process Automation} | Java, Spring Boot, SQLServer, React}{}
          \resumeItemListStart
              \resumeItem{Engineered multiple \textbf{Spring Boot} microservices interfacing with \textbf{SQLServer}, providing scalable business workflow automation.}
              \resumeItem{Designed \textbf{React} front-end UI components to enhance user interaction and reporting feature completion by 25\%.}
              \resumeItem{Implemented RESTful APIs and integrated authentication mechanisms, ensuring secure role-based access and data integrity across services.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, JavaScript, SQL, Python, TypeScript, PHP, C\# \\
                \textbf{Front-End Technologies:} & React.js, HTML, JavaScript, JQuery \\
                \textbf{Back-End Frameworks:} & Spring Boot, Microservices, Node.js, .NET, Laravel \\
                \textbf{Databases:} & SQLServer, Oracle Database, MySQL, PostgreSQL \\
                \textbf{DevOps Tools:} & Docker, Jenkins, AWS EC2, Git, CI/CD Pipelines \\
                \textbf{Other Technologies:} & Agile / SCRUM, REST APIs, Microservices Architecture, Spring Security \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}