\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{.NET 6} backend services to enhance API throughput, decreasing average response time by 30\% and improving reliability.}
        \resumeItem{Implemented secure authentication using \textbf{Azure AD} and \textbf{JWT}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Developed responsive front-end components with \textbf{React 16}, boosting user satisfaction scores by 25\% through optimized UI.}
        \resumeItem{Streamlined database interactions using \textbf{MS SQL} T-SQL procedures, enhancing query efficiency by 35\%.}
        \resumeItem{Led Agile sprint ceremonies, enabling continuous integration and deployment pipelines to accelerate release cycles by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and integrated seamless RESTful APIs using \textbf{Node.js} and \textbf{PHP 6}, improving backend scalability by 30\%.}
        \resumeItem{Engineered dynamic front-end interfaces with \textbf{React 16} and \textbf{JavaScript} lowering load times by 20\% and enhancing UX.}
        \resumeItem{Optimized \textbf{Oracle PL/SQL} database procedures, reducing data retrieval times by 25\% across multiple client projects.}
        \resumeItem{Implemented role-based authentication with \textbf{OAuth} and \textbf{JWT}, improving application security and user management.}
        \resumeItem{Coordinated code reviews and unit testing to boost code quality, raising bug detection rate before release by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Configured and maintained secure \textbf{Linux} lab environments, enhancing system uptime and lab reliability by 15\%.}
        \resumeItem{Assisted students in debugging and testing software modules to increase assignment accuracy and reduce errors by 20\%.}
        \resumeItem{Automated script workflows for grading and validation improving grading turnaround time by 30\%.}
        \resumeItem{Hosted interactive sessions on web security and cryptography, improving student comprehension and performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed backend components in \textbf{C\#} with \textbf{ASP.NET Core}, lowering latency by 30\% for critical API endpoints.}
        \resumeItem{Improved frontend \textbf{JavaScript} and \textbf{React} integration, resulting in 25\% faster page load and smoother interactions.}
        \resumeItem{Optimized \textbf{MS SQL Server} queries for faster data retrieval, reducing database load by 20\%.}
        \resumeItem{Worked closely with cross-functional teams following Scrum, improving sprint delivery efficiency and team collaboration by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed backend APIs using \textbf{PHP 6} and integrated \textbf{MySQL} databases, supporting 1000+ concurrent users with 99.5\% uptime.}
        \resumeItem{Built front-end UI with \textbf{React.js} and \textbf{JavaScript}, enhancing responsiveness and reducing user wait times by 25\%.}
        \resumeItem{Designed and executed {\textbf TSQL} and \textbf{PL/SQL} database operations, improving data processing speed by 35\%.}
        \resumeItem{Automated deployment using Docker and CI/CD pipelines, reducing release time and errors by 40\%.}
        \resumeItem{Collaborated in Agile teams to deliver features incrementally, reducing time-to-market by 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enhanced Frontend Performance Optimizer} | React, JavaScript, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Integrated \textbf{OpenAI API}-powered analysis to dynamically optimize \textbf{React} components, reducing page load times by 30\%.}
              \resumeItem{Developed intelligent code refactor suggestions that improved maintainability and boosted user engagement metrics by 20\%.}
              \resumeItem{Automated component testing workflows with AI assistance, increasing test coverage by 35\% while reducing manual efforts.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure API Gateway with Adaptive Authentication} | .NET 6, Azure AD, MS SQL}{}
          \resumeItemListStart
              \resumeItem{Engineered a robust \textbf{.NET 6} API gateway integrating \textbf{Azure AD} and \textbf{JWT} for adaptive user authentication.}
              \resumeItem{Optimized backend \textbf{MS SQL} queries to support rapid authorization checks, reducing overall API response time by 25\%.}
              \resumeItem{Implemented CI/CD pipelines to enable automated deployment and testing, accelerating release cadence by 35\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C\#, JavaScript, PHP, Python, T-SQL, PL/SQL, Java \\
                \textbf{Web Development Frameworks:} & .NET 6, React 16, Node.js, ASP.NET Core, Laravel \\
                \textbf{Databases:} & MS SQL Server, Oracle, MySQL, PostgreSQL \\
                \textbf{Authentication \& Security:} & Azure AD, OAuth, JWT, Role-Based Access Control \\
                \textbf{DevOps \& CI/CD Tools:} & Docker, Jenkins, GitHub Actions, Azure DevOps \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI-Assisted Code Review \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}