\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices, enhancing scalability and increasing API throughput by 35\% for high traffic loads.}
        \resumeItem{Implemented role-based access control policies using \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Deployed AI-powered code review assistant via \textbf{LLMs} that cut manual code review efforts by 45\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, decreasing release cycle duration by 40\%.}
        \resumeItem{Collaborated cross-functionally to optimize backend workflows and improved service reliability with 99.9\% uptime.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{SaaS} data visualization platform leveraging \textbf{Laravel} and \textbf{React} supporting 50+ simultaneous users.}
        \resumeItem{Automated daily stock data processing pipelines in \textbf{Python}, reducing manual efforts by 80\%.}
        \resumeItem{Developed subscription e-commerce platform using \textbf{PHP} integrating \textbf{Stripe}, enabling secure role-based access control.}
        \resumeItem{Built AI agents using \textbf{LLMs} to automate FINRA data processing, cutting manual data handling by 80\%.}
        \resumeItem{Improved \textbf{React} component efficiency, lowering page load latency by 25\% and boosting user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cyber lab infrastructure to ensure secure and stable environments for student projects.}
        \resumeItem{Assisted students with software debugging and deployment, raising assignment success rates by 20\%.}
        \resumeItem{Created automated grading scripts, improving grading accuracy and reducing instructor workload by 25\%.}
        \resumeItem{Delivered 15+ instructional sessions on Cryptography, Networking, and Web Security to enhance student comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{TypeScript} API calls, achieving average response times below 100ms for seamless data transactions.}
        \resumeItem{Refined \textbf{Angular.js} frontend codebase, increasing user engagement metrics by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\#} using \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Enhanced \textbf{PostgreSQL} stored procedures, cutting frontend query load by 15\% to improve efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Collaborated on a \textbf{SaaS} tool automating SDLC processes, enhancing team productivity with efficient workflows.}
        \resumeItem{Built \textbf{Java Spring Boot} microservices with \textbf{MySQL}, supporting 1000 concurrent users with sub-200ms response times.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines deploying 6 microservices on \textbf{AWS EC2} using \textbf{Docker} containers efficiently.}
        \resumeItem{Developed \textbf{React.js} UI, improving project management usability and reducing page load times by 30\%.}
        \resumeItem{Created unit tests using \textbf{JUnit} with 90\% coverage to ensure pipeline stability and code quality.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, Python}
          \resumeItemListStart
              \resumeItem{Built a \textbf{CI/CD} bot integrating \textbf{LLMs} to detect bugs and enforce code style, enhancing review quality by 25\%.}
              \resumeItem{Automated Python docstring generation ensuring 100\% coverage and reducing manual documentation workload significantly.}
              \resumeItem{Streamlined pull request workflows improving team code review efficiency and accelerating feature integration speed.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Customer Support AI Email Agent} | Gmail API, LLMs, Google Sheets}
          \resumeItemListStart
              \resumeItem{Developed an email classification system using \textbf{LLMs} that auto-responded to 60\% of FAQs, speeding response time by 40\%.}
              \resumeItem{Implemented HITL workflows ensuring accuracy on sensitive queries while automating common customer support interactions.}
              \resumeItem{Connected email data to Google Sheets for analytics, enabling performance tracking and continuous optimization.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming:} & Java, Python, JavaScript, C\#, PHP, TypeScript, C++, Ruby \\
                \textbf{Frameworks \& Libraries:} & Spring Boot, React.js, Angular.js, Laravel, Node.js, Vue.js \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, Lambda, S3), Docker, Jenkins, GitHub Actions \\
                \textbf{Front-end Technologies:} & HTML, CSS, React.js, Angular.js, jQuery \\
                \textbf{AI \& Automation:} & OpenAI API, n8n, LLMs, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}