\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and optimized backend APIs using \textbf{PHP} and \textbf{Laravel}, improving data processing speed by 30\% for multiple client projects.}
        \resumeItem{Integrated third-party APIs and payment gateways, increasing transactional efficiency and reducing failure rates by 25\%.}
        \resumeItem{Collaborated with front-end team to implement responsive interfaces using \textbf{React.js}, improving user experience and accessibility scores.}
        \resumeItem{Implemented automated unit tests and CI/CD pipelines using \textbf{GitHub Actions}, reducing deployment errors by 40\%.}
        \resumeItem{Led agile sprint planning and code reviews, improving development velocity by 20\% and maintaining code quality standards.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built and maintained RESTful APIs in \textbf{PHP Laravel}, supporting 1000+ users with data synchronization and authorization.}
        \resumeItem{Developed web scraping tools with \textbf{Guzzle} and \textbf{Puppeteer}, improving data ingestion pipelines by 35\%.}
        \resumeItem{Implemented responsive front-end components using \textbf{Vue.js}, boosting client application load speed by 20\%.}
        \resumeItem{Managed database modeling and queries with \textbf{Doctrine ORM}, optimized SQL queries to reduce response times by 25\%.}
        \resumeItem{Collaborated with cross-functional teams in Agile environment using \textbf{Git} for version control and continuous integration.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure Linux-based lab environments, deployed PHP web applications to support cybersecurity course exercises.}
        \resumeItem{Assisted students in debugging web application code, improving assignment success rates by 15\%.}
        \resumeItem{Automated lab assignment validation scripts using Python, accelerating grading by 30\% and reducing manual errors.}
        \resumeItem{Conducted workshops on web application security concepts, enhancing students' understanding of PHP and API vulnerabilities.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed API integrations using \textbf{TypeScript} that improved data exchange reliability and reduced errors by 20\%.}
        \resumeItem{Enhanced front-end modules with \textbf{Angular.js}, increasing user engagement metrics by 25\%.}
        \resumeItem{Optimized backend queries in \textbf{PostgreSQL}, reducing average load times by 15\% for critical pages.}
        \resumeItem{Collaborated in Agile teams using Git for version control, ensuring smooth deployment workflows with minimal downtime.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{PHP Symfony} web applications, increasing client satisfaction by delivering scalable solutions.}
        \resumeItem{Developed data scraping pipelines using \textbf{cURL} and \textbf{Guzzle}, improving data accuracy and update frequency by 40\%.}
        \resumeItem{Integrated third-party APIs and payment gateways, enhancing application features and reducing transaction failures by 30\%.}
        \resumeItem{Implemented front-end components with \textbf{React.js} and CSS, improving mobile responsiveness and load times by 20\%.}
        \resumeItem{Set up automated deployment pipelines using \textbf{Docker} and \textbf{AWS EC2}, cutting deployment times by 50\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Hotel Review Analysis Tool} | PHP, Symfony, OpenAI API}
          {}
          \resumeItemListStart
              \resumeItem{Developed a PHP Symfony web app that analyzes hotel reviews using \textbf{OpenAI API}, improving sentiment analysis accuracy by 35\%.}
              \resumeItem{Created data ingestion pipelines with \textbf{Guzzle} for continuous scraping and integration of client review data from multiple sources.}
              \resumeItem{Built a responsive frontend interface that visualizes analysis results, boosting user engagement and decision-making speed by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Web Scraping and API Integration Platform} | PHP, Laravel, Puppeteer}
          {}
          \resumeItemListStart
              \resumeItem{Engineered a robust PHP Laravel platform that automates web scraping using \textbf{Puppeteer} to acquire and normalize data daily.}
              \resumeItem{Implemented RESTful APIs allowing third-party systems to consume real-time scraped data, increasing client usage by 40\%.}
              \resumeItem{Optimized database interactions with \textbf{Doctrine ORM}, reducing query times by 30\% and improving overall system performance.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & PHP, JavaScript, Python, Java, TypeScript, C\#, Shell Scripting \\
                \textbf{Web Development Frameworks:} & Symfony, Laravel, React.js, Vue.js, Angular.js, HTML, CSS \\
                \textbf{Databases:} & MySQL, PostgreSQL, Doctrine ORM, SQL, MongoDB \\
                \textbf{DevOps \& Cloud:} & Git, Docker, AWS (EC2, S3), CI/CD pipelines \\
                \textbf{API \& Integration:} & RESTful APIs, Web Scraping Tools (Guzzle, cURL, Puppeteer) \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}