\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and maintained secure, scalable \textbf{Java Spring Boot} applications according to business requirements and MasterCard standards.}
        \resumeItem{Implemented robust production incident management processes, reducing downtime incidents by 30\% through proactive issue identification.}
        \resumeItem{Collaborated with cross-functional teams to research and evaluate technical solutions, integrating modern frameworks to enhance system performance.}
        \resumeItem{Created comprehensive documentation aligning with QA/QC practices, improving team knowledge transfer efficiency by 25\%.}
        \resumeItem{Automated testing and deployment pipelines via \textbf{Jenkins} and \textbf{Docker}, accelerating release frequency by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered a multi-user \textbf{Laravel} and \textbf{React} platform implementing role-based access, increasing application security compliance by 40\%.}
        \resumeItem{Developed automation scripts using \textbf{Python} for data processing pipelines, cutting manual workloads by 75\%.}
        \resumeItem{Designed and deployed scalable subscription services integrated with \textbf{Stripe}, enhancing billing accuracy and reducing errors by 30\%.}
        \resumeItem{Implemented AI-powered agents to automate data extraction, accelerating financial data workflow by 50\%.}
        \resumeItem{Optimized \textbf{React} components and state flow, reducing page load times by 25\%, resulting in higher user retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} environments for cybersecurity labs, improving system reliability and reducing downtime by 15\%.}
        \resumeItem{Assisted students in system deployment and debugging, increasing assignment success rates by 20\% through focused guidance.}
        \resumeItem{Automated grading scripts with enhanced validation, raising accuracy and reducing manual review time by 25\%.}
        \resumeItem{Conducted technical workshops on encryption, network protocols, and security best practices to improve student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API integrations with sub-100ms response times, enhancing real-time data access across the platform.}
        \resumeItem{Refactored legacy \textbf{Angular.js} interfaces, improving user engagement metrics by 25\% and overall application stability.}
        \resumeItem{Developed high-performance backend services in \textbf{C\# .NET}, reducing data fetch latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, resulting in 15\% quicker database query responses and streamlined front-end operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented microservices using \textbf{Java Spring Boot} and \textbf{MySQL}, achieving sub-200ms response times for 1000 concurrent users.}
        \resumeItem{Built and enhanced CI/CD pipelines with \textbf{Docker} for automated deployment on \textbf{AWS EC2}, improving deployment speed by 40\%.}
        \resumeItem{Developed a React.js based project management UI, boosting user efficiency and improving load speed by 30\%.}
        \resumeItem{Authored comprehensive \textbf{JUnit} test suites resulting in 90\% code coverage and improved application reliability significantly.}
        \resumeItem{Analyzed software requirements and created detailed system flowcharts, reducing development errors and enhancing adherence to specifications.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Automated Code Review System} | GitHub Actions, GitHub API, OpenAI API}
          \resumeItemListStart
              \resumeItem{Developed an AI-driven code review system that automatically detects bugs and style issues, reducing manual QA time by 30\%.}
              \resumeItem{Integrated documentation generation for Python projects ensuring 100\% coverage and enhancing maintainability across development teams.}
              \resumeItem{Implemented GitHub Actions workflows that speed up PR reviews and enforce MasterCard quality standards consistently.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure Incident Management Dashboard} | React.js, Node.js, AWS, Docker}
          \resumeItemListStart
              \resumeItem{Engineered a secure web dashboard to triage and manage production incidents, decreasing resolution time by 35\% via real-time metrics.}
              \resumeItem{Implemented role-based access controls and audit logging, increasing application security and regulatory compliance by 40\%.}
              \resumeItem{Deployed on \textbf{AWS} with containerized microservices using \textbf{Docker}, ensuring scalable and resilient infrastructure.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, TypeScript, C\#, PHP, JavaScript, Go, C++ \\
                \textbf{Frameworks \& Web Technologies:} & Spring Boot, React.js, Laravel, Angular.js, Node.js, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Tools \& Methodologies:} & Git, REST APIs, Agile, Jira, Unit Testing (JUnit), Security Best Practices \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}