\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and reviewed \textbf{Java Spring Boot} services ensuring scalable and maintainable code, improving system performance by 28\%.}
        \resumeItem{Designed and implemented unit tests with \textbf{JUnit}, increasing code coverage and reducing bugs by 35\%.}
        \resumeItem{Collaborated with product owners and engineers in \textbf{Agile} sprints to deliver high-quality features meeting user needs.}
        \resumeItem{Documented software design and workflows clearly, facilitating seamless maintenance and onboarding for the engineering team.}
        \resumeItem{Researched new technologies and frameworks enhancing application performance and team productivity by 22\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Implemented backend APIs with \textbf{Python} and \textbf{React} front-end features, boosting platform responsiveness by 30\%.}
        \resumeItem{Automated data ingestion pipelines processing 10K+ daily records, reducing manual workload by 75\% using \textbf{Python}.}
        \resumeItem{Contributed to \textbf{Agile} ceremonies, enhancing cross-team communication and feature delivery speed by 20\%.}
        \resumeItem{Built reusable \textbf{React} components, decreasing page load times by 18\% and enhancing user experience.}
        \resumeItem{Designed role-based access control modules integrating \textbf{Stripe} payment APIs, increasing subscription conversion by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} environment for cybersecurity labs ensuring 99.9\% uptime and secure configurations.}
        \resumeItem{Assisted students in debugging and testing network security modules, improving pass rates by 25\%.}
        \resumeItem{Automated grading scripts using \textbf{Python}, reducing instructor workload by 30\% and improving accuracy.}
        \resumeItem{Conducted interactive tutorials clarifying cryptography and network security protocols for 40+ students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed efficient backend logic in \textbf{C\#} .NET reducing data retrieval latency by 30\%.}
        \resumeItem{Enhanced \textbf{Angular.js} frontend modules improving user engagement scores by 25\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures cutting query wait times by 15\%.}
        \resumeItem{Ensured seamless data flow through precise \textbf{TypeScript} API integrations achieving sub-100ms response times.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices handling 1000 concurrent users with response times below 200ms.}
        \resumeItem{Led \textbf{CI/CD} pipeline development for Dockerized services on \textbf{AWS EC2}, increasing deployment frequency by 40\%.}
        \resumeItem{Designed responsive \textbf{React.js} frontend reducing page load times by 30\% and increasing usability.}
        \resumeItem{Wrote robust unit tests with \textbf{JUnit}, achieving 90\% test coverage and lowering defect rates.}
        \resumeItem{Collaborated in cross-functional teams adopting \textbf{Agile} methodologies, improving project delivery times by 22\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Every Defect Matters (EDM) Defect Aggregation Tool} | Java, Spring Boot, PostgreSQL, Agile}{}
          \resumeItemListStart
              \resumeItem{Developed defect aggregation backend processing multiple sources, improving defect tracking accuracy by 40\%.}
              \resumeItem{Integrated remediation plan management with clear owner assignments, reducing defect resolution time by 25\%.}
              \resumeItem{Collaborated in \textbf{Agile} team meetings to gather requirements ensuring user-centric feature deliverables.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-based Code Review Assistant} | Python, GitHub API, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Built an \textbf{AI-driven} assistant analyzing pull requests for defects and style issues, reducing manual review time by 30\%.}
              \resumeItem{Automated \textbf{Python} docstring generation ensuring consistent documentation coverage across codebase.}
              \resumeItem{Implemented continuous integration hooks for real-time feedback accelerating developer productivity by 20\%.}
          \resumeItemListEnd
          \vspace{-16pt}
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, C\#, C++, SQL \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET, Node.js \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3), Docker, Jenkins, Git \\
                \textbf{Tools \& Technologies:} & Linux/Unix, REST API, JUnit, Agile/Scrum, GitHub \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, CI/CD Automation, AI Agents \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}