\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices optimizing response times by 35\% and supporting high-volume data transactions.}
        \resumeItem{Enhanced security by integrating \textbf{Spring Security}, cutting unauthorized login attempts by 40\% across user authentication services.}
        \resumeItem{Pioneered an \textbf{AI-driven} code review assistant leveraging LLMs, reducing manual review time by 45\% and boosting deployment velocity by 25\%.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, accelerating release cycles by 40\% and improving build reliability.}
        \resumeItem{Collaborated cross-functionally to design ML workflows, enabling real-time analytics and intelligent automation features on core products.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{React} and \textbf{Laravel} based SaaS platform supporting 50+ concurrent users with robust data visualizations.}
        \resumeItem{Developed automated \textbf{Python} data pipelines processing 10,000+ records daily that decreased manual labor by 80\%.}
        \resumeItem{Built AI agents utilizing \textbf{LLMs} to automate financial data extraction, lowering manual broker data processing by 80\%.}
        \resumeItem{Implemented an AI-powered LinkedIn outreach bot that improved lead generation by 40\% and automated marketing workflows.}
        \resumeItem{Optimized front-end \textbf{React} components, reducing page load time by 25\% and enhancing user engagement metrics significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab infrastructure, enhancing stability and security posture for over 100 cybersecurity students.}
        \resumeItem{Automated software testing and grading scripts, improving accuracy by 25\% and reducing manual evaluation workload.}
        \resumeItem{Conducted 15+ sessions teaching advanced cybersecurity concepts, increasing student competency by 20\% in lab exercises.}
        \resumeItem{Provided hands-on debugging and deployment support, accelerating student project completion rates and system reliability.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed low-latency API endpoints in \textbf{TypeScript}, achieving sub-100ms response times for critical client communications.}
        \resumeItem{Revamped front-end \textbf{Angular.js} components, increasing user engagement by 25\% and enhancing platform usability.}
        \resumeItem{Built efficient \textbf{C\#} backend services within \textbf{.NET} framework that cut data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures reducing frontend loads by 15\%, thereby streamlining database operations.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed microservices using \textbf{Java Spring Boot} catering to 1000+ concurrent users with response time under 200ms.}
        \resumeItem{Implemented CI/CD pipelines on \textbf{AWS EC2} with \textbf{Docker}, reducing deployment errors and accelerating release cadence.}
        \resumeItem{Built a React.js based project tracking UI enhancing page load speeds by 30\%, improving team productivity.}
        \resumeItem{Designed and tested pipeline modules using \textbf{JUnit}, achieving approximately 90\% unit test coverage for reliability.}
        \resumeItem{Collaborated in developing an automated software delivery tool enhancing SDLC workflows for the engineering team.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered On-Device Android Assistant} | Android, Python, LLMs, Machine Learning}{}
          \resumeItemListStart
              \resumeItem{Developed an AI assistant leveraging \textbf{LLMs} integrated on-device, improving user task automation and privacy compliance.}
              \resumeItem{Built ML pipelines to fine-tune models on personalized data, enhancing natural language understanding by 30\%.}
              \resumeItem{Optimized on-device model performance reducing latency by 25\% while maintaining battery efficiency.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Large Scale Machine Learning Pipeline for NLP} | Python, TensorFlow, NLP, LLMs}{}
          \resumeItemListStart
              \resumeItem{Engineered data ingestion and preprocessing pipelines handling 10M+ text samples to train state-of-the-art NLP models.}
              \resumeItem{Implemented fine-tuning of LLMs for entity recognition tasks, improving downstream task accuracy by 18\%.}
              \resumeItem{Collaborated with researchers to apply novel contextual embedding techniques to optimize model generalization and robustness.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, C++, Java, TypeScript, C\#, JavaScript, PHP, Go \\
                \textbf{Machine Learning \& AI:} & TensorFlow, PyTorch, LLM Integration, NLP, Computer Vision, On-device ML, Prompt Engineering \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Django, Spring Boot, Laravel, Node.js \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{Cloud \& DevOps Tools:} & AWS (EC2, S3, Lambda), Docker, Jenkins, GitHub Actions \\
                \textbf{Tools \& Platforms:} & Linux/Unix, Git, REST API, gRPC, Jira, JUnit, Automation (n8n, Zapier) \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}