\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} applications by implementing secure, scalable code meeting strict MasterCard quality and process standards.}
        \resumeItem{Designed and executed application program tests reducing software defects by 30\% while adhering to MasterCard control frameworks.}
        \resumeItem{Led production incident resolution efforts, improving uptime by 25\% and sustaining client satisfaction through rapid problem solving.}
        \resumeItem{Collaborated with team to research alternative technologies and implemented solutions aligned with evolving business needs and security requisites.}
        \resumeItem{Drafted and updated technical documentation following best practices, streamlining onboarding and product maintenance activities by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed secure, role-based \textbf{PHP Laravel} applications enhancing user access management and compliance with data protection policies.}
        \resumeItem{Automated daily data ingestion pipelines in \textbf{Python} increasing data processing efficiency by 75\% and reducing errors.}
        \resumeItem{Collaborated cross-functionally on scalable SaaS features supporting 50+ users, improving adoption through improved response times by 30\%.}
        \resumeItem{Engineered AI-powered automation agents integrating \textbf{LLMs} to streamline regulatory data handling, cutting manual workload by 60\%.}
        \resumeItem{Refined front-end components in \textbf{React} achieving a 25\% faster load time and increased user engagement scores by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments, ensuring compliance with cybersecurity protocols and reducing system downtime by 15\%.}
        \resumeItem{Assisted students with software deployment and debugging, increasing assignment success rates by 20\% through targeted coaching sessions.}
        \resumeItem{Created automated grading scripts that improved accuracy by 25\%, significantly reducing instructors' manual workload.}
        \resumeItem{Delivered over 15 virtual workshops on cryptography and networking protocols, enhancing lab participant comprehension and skills.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed responsive API endpoints in \textbf{TypeScript}, achieving sub-100ms response times and improving client app performance.}
        \resumeItem{Upgraded front-end interfaces using \textbf{Angular.js}, increasing user interaction metrics by 25\% through enhanced usability.}
        \resumeItem{Implemented backend services in \textbf{C\# .NET} reducing data retrieval latency by 30\% for strategic platform components.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, lowering server load and improving overall system efficiency by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Docker} and \textbf{AWS EC2}, accelerating deployment cycles by 35\% and improving reliability.}
        \resumeItem{Developed interactive project management tools using \textbf{React.js}, boosting user productivity and reducing page load times by 30\%.}
        \resumeItem{Authored unit tests with \textbf{JUnit} achieving 90\% test coverage, improving code quality and regression detection.}
        \resumeItem{Coordinated SDLC process automation, reducing manual development efforts and increasing delivery speed by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Based Software Incident Prediction Tool} | Python, Docker, AWS, LLMs}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-driven platform using \textbf{LLMs} for predictive incident detection, decreasing production outages by 30\%.}
              \resumeItem{Automated monitoring and alerting pipelines with \textbf{Docker} containers hosted on \textbf{AWS}, improving system reliability.}
              \resumeItem{Prepared detailed technical documentation aiding rapid team adoption and ongoing maintenance processes.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure Role-Based Access Platform} | Java Spring Boot, Spring Security, MySQL}{}
          \resumeItemListStart
              \resumeItem{Designed and implemented a role-based access control system enhancing application security and reducing unauthorized access attempts by 40\%.}
              \resumeItem{Conducted feasibility analysis and created detailed flowcharts for system workflows, improving design clarity and stakeholder alignment.}
              \resumeItem{Utilized \textbf{Spring Security} features to ensure compliance with corporate security standards and best practices.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, TypeScript, PHP, C\#, JavaScript, Shell Scripting, Go \\
                \textbf{Frameworks \& Web Development:} & Spring Boot, React.js, Laravel, Angular.js, .NET, Node.js, Django \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, Lambda, S3), Docker, Jenkins, Azure \\
                \textbf{Software Methodologies:} & Agile, CI/CD, Software Development Life Cycle (SDLC), Quality Assurance \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, n8n, Zapier \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}