\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and optimized network management features, improving switch performance by 30\% using \textbf{C++} and \textbf{Python}.}
        \resumeItem{Led integration of SONiC features into existing switch software, enhancing deployment speed by 25\% in continuous environments.}
        \resumeItem{Automated switch configuration validations with \textbf{Linux shell scripting}, reducing manual errors and improving delivery time by 20\%.}
        \resumeItem{Collaborated with cross-functional teams for improved network protocols, boosting system stability and throughput by 15\%.}
        \resumeItem{Implemented security enhancements using \textbf{Python} to decrease unauthorized access attempts by 40\% on network devices.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered new L2/L3 networking features using \textbf{Python} for dynamic cloud switch management, increasing efficiency by 22\%.}
        \resumeItem{Improved network automation scripts via \textbf{Linux shell scripting}, reducing setup time by 35\% for multiple switch setups.}
        \resumeItem{Designed and implemented chassis management modules with \textbf{C++}, enabling seamless control across varied hardware platforms.}
        \resumeItem{Collaborated in Scrum teams, accelerating feature delivery cycles and increasing sprint completion rate by 30\%.}
        \resumeItem{Upgraded network protocol handlers, improving packet forwarding reliability by 18\% across NAT and VLAN scenarios.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux} networking environments, ensuring 99\% uptime and secure configurations for cyber lab experiments.}
        \resumeItem{Assisted students in network debugging and protocol testing, increasing assignment success rates by 20\%.}
        \resumeItem{Developed automation scripts for lab validation using \textbf{Shell scripting}, improving grading efficiency by 25\%.}
        \resumeItem{Hosted workshops covering \textbf{Networking Protocols} and \textbf{Linux} fundamentals for 100+ students.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Improved API integration using \textbf{TypeScript}, reducing average response time by 35ms across switch communication modules.}
        \resumeItem{Enhanced backend services with \textbf{C\#} and \textbf{.NET}, increasing data retrieval speed by 30\%.}
        \resumeItem{Optimized SQL procedures, reducing query execution time by 15\% and easing network service load.}
        \resumeItem{Upgraded network monitoring scripts with \textbf{Linux shell scripting}, improving alert responsiveness by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed network-aware microservices in \textbf{Java Spring Boot}, enhancing concurrency for 1000+ users with sub-200ms latency.}
        \resumeItem{Integrated SONiC-based networking features into SaaS tools, improving network management automation by 40\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Docker} on \textbf{AWS EC2}, decreasing deployment time by 30\%.}
        \resumeItem{Improved switch protocol simulation modules, raising test coverage to 90\% with \textbf{JUnit} framework.}
        \resumeItem{Built React management UI enhancing network switch status visibility, boosting user engagement by 35\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Network Configuration Validator} | Python, LLMs, Linux Shell Scripting}{}
          \resumeItemListStart
              \resumeItem{Developed AI-based tool to validate SONiC network configurations automatically, reducing misconfigurations by 40\%.}
              \resumeItem{Integrated \textbf{Python} and \textbf{shell scripts} to analyze switch health and suggest remediation steps with 95\% accuracy.}
              \resumeItem{Reduced manual network verification time by 60\%, accelerating continuous deployment cycles for NVIDIA switches.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated SONiC Feature Integration Framework} | C++, Python, Linux}{}
          \resumeItemListStart
              \resumeItem{Created a modular framework to automate SONiC features integration for NVIDIA switches, improving integration speed by 35\%.}
              \resumeItem{Designed unit tests in \textbf{Python} to validate new network protocols, achieving 90\% test coverage on release builds.}
              \resumeItem{Collaborated with open-source community, incorporating feedback to increase framework robustness and ease of use.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C++, Python, C, Shell Scripting, Java, TypeScript, PHP, C\# \\
                \textbf{Networking \& Protocols:} & L2/L3 Protocols, Switch Management, Network Automation, SONiC NOS, Linux Networking \\
                \textbf{Operating Systems:} & Linux, Unix, Windows \\
                \textbf{DevOps \& Automation:} & Docker, Jenkins, CI/CD, AWS (EC2, S3), Git, GitHub Actions \\
                \textbf{Frameworks \& Tools:} & Spring Boot, React.js, Angular.js, .NET, JUnit, Jira \\
                \textbf{AI \& Machine Learning:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}