\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered backend microservices using \textbf{Java Spring Boot} to improve API responsiveness by 35\% under high user load scenarios.}
        \resumeItem{Integrated \textbf{Spring Security} for robust role-based access control, decreasing unauthorized access incidents by 40\%.}
        \resumeItem{Launched an \textbf{AI-powered} code review assistant with \textbf{LLMs} that cut manual review time by 45\% and boosted developer productivity.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, accelerating deployment by 40\% while ensuring stability.}
        \resumeItem{Collaborated cross-functionally to ensure security and scalability of services, enhancing platform reliability and customer satisfaction.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed secure and scalable \textbf{React} features for SaaS platform, serving 50+ concurrent users with 25\% faster load times.}
        \resumeItem{Automated stock data processing pipelines with \textbf{Python}, reducing manual workload by 80\% and increasing data accuracy.}
        \resumeItem{Implemented AI-driven \textbf{LLM-based} agents to automate broker data downloads, cutting processing times by 80\%.}
        \resumeItem{Enhanced lead generation by 40\% through an \textbf{AI-powered} LinkedIn outreach bot automating posting and targeting workflows.}
        \resumeItem{Improved front-end state management in \textbf{React}, decreasing page load latency by 25\% and improving user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab environments supporting student projects in cybersecurity coursework.}
        \resumeItem{Guided students in debugging, deploying, and testing systems, raising assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts to improve accuracy by 25\%, reducing manual evaluation workloads significantly.}
        \resumeItem{Delivered 15+ interactive sessions covering cryptography, networking, and web security concepts effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed high-performance APIs in \textbf{TypeScript} with sub-100ms response time, supporting seamless data flow.}
        \resumeItem{Upgraded user interface components using \textbf{Angular.js}, contributing to a 25\% increase in user engagement.}
        \resumeItem{Designed robust backend services in \textbf{C\# .NET} that improved data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and procedures, reducing frontend database load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built scalable \textbf{Spring Boot} microservices integrated with \textbf{MySQL} to handle 1000 concurrent users with sub-200ms latencies.}
        \resumeItem{Led CI/CD pipeline deployment on \textbf{AWS EC2} using \textbf{Docker}, ensuring smooth rollouts with zero downtime.}
        \resumeItem{Created efficient \textbf{React.js} interfaces improving project management usability and enhancing load speed by 30\%.}
        \resumeItem{Implemented 90\% coverage unit testing using \textbf{JUnit} framework across critical microservice components.}
        \resumeItem{Collaborated actively in cross-functional teams to design data collection and processing systems ensuring data integrity and scalability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Enhanced Data Collection Platform} | Python, React, PostgreSQL, TypeScript}
          {}
          \resumeItemListStart
              \resumeItem{Designed and implemented a scalable data collection system integrating secure APIs with \textbf{React} frontend enhancing user experience.}
              \resumeItem{Applied \textbf{Python} pipelines for human data generation, increasing data accuracy and throughput by 35\%.}
              \resumeItem{Optimized database schemas in \textbf{PostgreSQL} for efficient storage and retrieval, reducing query latency by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Intelligent Agent Framework for Reasoning} | Rust, Python, Express, React}
          {}
          \resumeItemListStart
              \resumeItem{Developed a reasoning engine enhancing AI agent capabilities, improving model decision accuracy by 30\% using \textbf{Rust} and \textbf{Python}.}
              \resumeItem{Built responsive UIs in \textbf{React} enabling real-time interaction with agent controls and diagnostics.}
              \resumeItem{Deployed backend \textbf{Express} services to manage agent orchestration with increased reliability and scalability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, TypeScript, Rust, Java, JavaScript, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & React, Express, Spring Boot, Angular.js, Laravel \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins \\
                \textbf{AI \& Automation:} & LLM Integration, AI Agents, OpenAI API, Data Collection Pipelines \\
                \textbf{Tools \& Others:} & Linux, Git, REST APIs, CI/CD, Security Best Practices \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}