\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices to improve scalability, boosting API throughput by 35\% and reducing response latency.}
        \resumeItem{Implemented security upgrades with \textbf{Spring Security} to enforce role-based access, cutting unauthorized access attempts by 40\%.}
        \resumeItem{Deployed an \textbf{AI-powered} code review assistant to automate bug detection, shortening review times by 25\% and increasing code quality.}
        \resumeItem{Automated continuous integration using \textbf{Jenkins} and \textbf{Docker}, reducing build and deployment times by 40\% across multiple services.}
        \resumeItem{Collaborated with senior engineers to troubleshoot complex issues, enhancing product stability and improving user satisfaction by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{React} and \textbf{Laravel} SaaS platform supporting 50+ users, improving data visualization and user interaction.}
        \resumeItem{Automated daily stock data processing with \textbf{Python}, reducing manual work by 80\% and increasing data accuracy.}
        \resumeItem{Created AI agents leveraging \textbf{LLMs} to automate FINRA broker data downloads, boosting processing speed by 80\%.}
        \resumeItem{Built an AI-driven LinkedIn outreach bot in \textbf{React} that increased qualified lead generation by 40\%.}
        \resumeItem{Optimized frontend components to decrease page load times by 25\%, significantly enhancing user engagement and retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based environments ensuring secure and reliable infrastructure for hands-on cybersecurity lab exercises.}
        \resumeItem{Coached students in \textbf{debugging} and deployment, improving lab submission success rates by 20\% through targeted guidance.}
        \resumeItem{Developed automated grading scripts, increasing evaluation accuracy by 25\% and decreasing manual workload.}
        \resumeItem{Conducted over 15 interactive sessions covering cryptography and web security, enhancing student comprehension and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient \textbf{TypeScript} API calls achieving average response times under 100ms for seamless frontend data updates.}
        \resumeItem{Boosted user engagement by 25\% by enhancing an existing platform with \textbf{Angular.js} through UI and feature improvements.}
        \resumeItem{Built backend services using \textbf{C\# .NET} that lowered data retrieval latency by 30\%, improving system responsiveness.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures to streamline database operations, reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed microservices in \textbf{Java Spring Boot} integrated with \textbf{MySQL}, supporting 1000 concurrent users with sub-200ms response times.}
        \resumeItem{Led \textbf{CI/CD} pipeline creation on \textbf{AWS EC2} with \textbf{Docker}, improving deployment efficiency by 30\%.}
        \resumeItem{Built and enhanced a \textbf{React.js} UI for project management, improving usability and speed by 30\%.}
        \resumeItem{Authored unit tests using \textbf{JUnit} covering 90\% functionality, boosting code reliability and maintainability.}
        \resumeItem{Collaborated cross-functionally to design an SDLC automation \textbf{SaaS tool}, increasing team productivity by 25\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Debugging Assistant} | GitHub Actions, OpenAI API, Python}
          {}
          \resumeItemListStart
              \resumeItem{Created an AI assistant to analyze Python pull requests, automatically identifying bugs and style issues, reducing manual reviews 25\%.}
              \resumeItem{Integrated automated docstring generation with \textbf{OpenAI API} to achieve 100\% code documentation coverage swiftly and accurately.}
              \resumeItem{Deployed via \textbf{GitHub Actions}, enabling continuous feedback to developers and accelerating release cycles by 20\%.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Healthcare Compliance Dashboard} | Django, React, PostgreSQL}
          {}
          \resumeItemListStart
              \resumeItem{Built a full-stack compliance dashboard for healthcare providers to track clinical quality metrics and simplify administrative tasks.}
              \resumeItem{Leveraged \textbf{PostgreSQL} to design efficient queries enabling real-time data insights and improved compliance reporting accuracy.}
              \resumeItem{Developed user-friendly \textbf{React} interfaces focused on seamless navigation to enhance healthcare team productivity by 35\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, JavaScript, TypeScript, Java, C\#, PHP \\
                \textbf{Web Development \& Frameworks:} & Django, FastAPI, React, Next.js, Laravel, Spring Boot \\
                \textbf{Databases \& Querying:} & PostgreSQL, SQL, MySQL \\
                \textbf{AI \& Machine Learning Tools:} & OpenAI API, LLM Integration, AI Agents, GitHub Copilot, Gemini \\
                \textbf{DevOps \& Automation:} & Docker, Jenkins, AWS EC2, GitHub Actions \\
                \textbf{Version Control \& Tools:} & Git, GitHub, REST APIs, Browser & IDE Debugging Tools \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}