\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable \textbf{Java Spring Boot} REST APIs boosting microservice throughput by 35\% and enhancing system reliability.}
        \resumeItem{Enhanced authentication modules using \textbf{Spring Security}, decreasing unauthorized access attempts by 40\% and strengthening security posture.}
        \resumeItem{Developed an \textbf{AI-driven} code review assistant integrating \textbf{LLMs}, reducing code review time by 25\% and improving code quality.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating deployment efficiency and cutting release time by 40\%.}
        \resumeItem{Collaborated closely with cross-functional teams to translate requirements into intuitive user features employed in production at scale.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and launched a \textbf{React} front-end with \textbf{Laravel} backend supporting 50+ concurrent users and high responsiveness.}
        \resumeItem{Automated stock data pipelines using \textbf{Python}, processing over 10,000 entries daily and reducing manual workload by 80\%.}
        \resumeItem{Implemented AI-powered \textbf{LLM agents} automating FINRA broker data processing, decreasing manual tasks by 80\% and speeding workflows.}
        \resumeItem{Optimized \textbf{React} components for faster page loads, cutting load times by 25\% and increasing user engagement metrics.}
        \resumeItem{Built subscription e-commerce platform integrating \textbf{Stripe} payments with role-based access control and multi-tier features.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and secured \textbf{Linux}-based lab infrastructure, ensuring stable environments for student cybersecurity projects.}
        \resumeItem{Assisted over 15 students per semester in \textbf{debugging} and deploying cybersecurity modules, improving assignment success by 20\%.}
        \resumeItem{Created automated grading scripts enhancing accuracy by 25\% and significantly lowering manual validation workload.}
        \resumeItem{Led interactive instructional sessions clarifying complex topics like Cryptography, Networking Protocols, and Web Security fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Executed \textbf{TypeScript} API calls reducing average response time below 100ms and improving frontend-backend communication.}
        \resumeItem{Refined \textbf{Angular.js} frontend, raising user engagement by 25\% through improved UI components and responsiveness.}
        \resumeItem{Developed \textbf{C\# .NET} backend services, cutting data retrieval latency by 30\% and boosting system throughput.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, decreasing frontend database load by 15\% and streamlining queries.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices backed by \textbf{MySQL}, supporting 1000 concurrent users with response times below 200ms.}
        \resumeItem{Directed CI/CD automation using \textbf{Docker} and \textbf{AWS EC2}, enabling seamless deployment of 6 microservices with zero downtime.}
        \resumeItem{Developed a \textbf{React.js} project management UI, enhancing usability and load speeds by 30\% across multiple platforms.}
        \resumeItem{Implemented unit tests with \textbf{JUnit}, achieving 90\% code coverage and raising build stability substantially.}
        \resumeItem{Collaborated in a team of five to architect a \textbf{SaaS} platform streamlining the SDLC process for faster feature deployment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Knowledge Discovery Assistant} | React, Golang, OpenAPI, LLMs}
          \resumeItemListStart
              \resumeItem{Built a React frontend integrated with \textbf{Golang} backend exposing \textbf{OpenAPI} REST endpoints for seamless knowledge search.}
              \resumeItem{Implemented AI assistant using \textbf{LLMs} to interpret queries, enhancing user search accuracy by 40\% in large datasets.}
              \resumeItem{Designed scalable backend architecture supporting rapid feature iteration with minimal latency in a modern browser environment.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Automated REST API Generator for Enterprise Apps} | Go, TypeScript, React}
          \resumeItemListStart
              \resumeItem{Developed Go-based service generating future-proof REST APIs, accelerating backend development cycles by 30\% with type-safe specs.}
              \resumeItem{Created React-based dashboard for API configuration and monitoring, improving client flexibility and product adaptability.}
              \resumeItem{Enhanced API usability using TypeScript for strict contract enforcement, reducing runtime errors and improving maintainability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Go, TypeScript, Python, JavaScript, C\#, PHP, C++, Shell Scripting \\
                \textbf{Web Development:} & React.js, Angular.js, Laravel, Spring Boot, Node.js, .NET, HTML, CSS \\
                \textbf{API & Backend:} & REST API, OpenAPI, Microservices, gRPC, SQL, NoSQL (MongoDB, DynamoDB) \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Cloud & DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Azure, CI/CD pipelines \\
                \textbf{AI & Automation:} & OpenAI API, LLM Integration, AI Agents, Prompt Engineering, n8n, Zapier \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}