\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices integrating distributed data to improve API throughput by 35\%.}
        \resumeItem{Implemented robust \textbf{Spring Security} role-based controls, enhancing data security and cutting unauthorized access attempts by 40\%.}
        \resumeItem{Developed AI-powered code review \textbf{tools} using \textbf{LLMs} that reduced manual reviews by 45\% and boosted deployment speed by 25\%.}
        \resumeItem{Automated \textbf{Jenkins} and \textbf{Docker} build pipelines, accelerating release cycles and cutting deployment time by 40\%.}
        \resumeItem{Collaborated on cloud-based secure data integration patterns to enable real-time analytics for enterprise data solutions.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{React} and \textbf{Laravel} SaaS platform enabling secure real-time multi-agency data sharing for 50+ users.}
        \resumeItem{Developed automated \textbf{Python} data pipelines processing 10,000+ daily records, improving data exchange reliability by 80\%.}
        \resumeItem{Built API-driven subscription services integrating \textbf{Stripe}, enabling secure role-based access for e-commerce users.}
        \resumeItem{Implemented AI \textbf{LLM} agents automating financial data extraction, decreasing manual workflows by 80\%.}
        \resumeItem{Enhanced \textbf{React} UI and state management, reducing page load latency by 25\% and boosting user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab environments aligned with data governance standards, improving system reliability by 20\%.}
        \resumeItem{Assisted in debugging and deploying software modules, enhancing cybersecurity lab success rates by 20\%.}
        \resumeItem{Automated grading scripts increasing accuracy by 25\%, reducing manual intervention in validation processes.}
        \resumeItem{Led instructional sessions covering cryptography and data security, elevating student comprehension and lab performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed performant \textbf{TypeScript} API calls to ensure sub-100ms response times for distributed data services.}
        \resumeItem{Enhanced \textbf{Angular.js} platform features, increasing user engagement metrics by 25\%.}
        \resumeItem{Implemented scalable backend modules in \textbf{C\#} with \textbf{.NET}, reducing data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, decreasing frontend database load and improving throughput by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Co-developed microservice architecture using \textbf{Java Spring Boot} to support 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Designed and deployed \textbf{AWS EC2} containerized services with \textbf{Docker}, boosting system resilience and scalability.}
        \resumeItem{Implemented common entity frameworks and data lineage models to enhance cross-service data discoverability by 30\%.}
        \resumeItem{Developed UI components in \textbf{React.js}, improving user interaction efficiency and reducing load times by 30\%.}
        \resumeItem{Achieved 90\% unit test coverage on data pipeline modules using the \textbf{JUnit} framework, increasing reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Federated Data Integration Bot} | Python, AWS Lambda, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI-powered data integration bot enabling real-time, secure data exchange across distributed sources using \textbf{Python} and \textbf{AWS Lambda}.}
              \resumeItem{Implemented privacy-compliant workflows leveraging \textbf{OpenAI API} for automated data cataloging and discoverability, reducing manual labor by 40\%.}
              \resumeItem{Engineered a scalable event-driven architecture facilitating data federation while preserving agency autonomy and regulatory compliance.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Enterprise Data Catalog and Lineage System} | React.js, Node.js, MongoDB}{}
          \resumeItemListStart
              \resumeItem{Designed a metadata management platform to track data lineage and support data governance, increasing data discoverability by 50\%.}
              \resumeItem{Built interactive UI in \textbf{React.js} and backend services in \textbf{Node.js} to enable seamless multi-agency data collaboration.}
              \resumeItem{Integrated role-based access and compliance checks to ensure secure data availability adhering to HIPAA and PCI regulations.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, SQL, JavaScript, TypeScript, PowerShell, PHP, C\# \\
                \textbf{Data Architecture \& Integration:} & Data Modeling, APIs, Data Pipelines, Data Lakehouse, Master Data Management (MDM), Metadata, Data Catalog \\
                \textbf{Cloud \& Infrastructure:} & AWS (Lambda, EC2, S3), Azure, Docker, Kubernetes, Hybrid Cloud \\
                \textbf{Web \& Frontend Frameworks:} & React.js, Angular.js, Node.js \\
                \textbf{Security \& Compliance:} & HIPAA, CJIS, PCI, Data Governance, Role-Based Access Control, Spring Security \\
                \textbf{Analytics \& BI Tools:} & Power BI, Tableau, Amazon Quick Sight \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}