\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Led frontend redesign of microservices dashboard using \textbf{React}, improving real-time data visibility by 30\%.}
        \resumeItem{Implemented role-based access and security enhancements with \textbf{Spring Security}, reducing unauthorized access incidents by 40\%.}
        \resumeItem{Developed and deployed new interactive UI features with \textbf{JavaScript} and \textbf{CSS}, increasing user engagement by 25\%.}
        \resumeItem{Automated code review processes using an \textbf{AI-driven} tool, cutting manual effort by 45\% and enhancing code quality.}
        \resumeItem{Streamlined CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing deployment cycle time by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected \textbf{React}-based SaaS platform with real-time data flow, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Refined \textbf{React} state management and UI components, decreasing load times by 25\%, boosting customer retention.}
        \resumeItem{Automated data workflows in \textbf{Python}, processing 10k+ daily records, improving accuracy by 30\%.}
        \resumeItem{Built an \textbf{AI-powered} lead generation bot using \textbf{LLMs}, generating 40\% more qualified leads.}
        \resumeItem{Developed mobile-friendly front end with \textbf{TypeScript}, enhancing cross-device accessibility and UX.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based cybersecurity labs, ensuring secure, stable environments for 100+ students weekly.}
        \resumeItem{Guided students in debugging and deployment processes, raising successful lab submissions by 20\%.}
        \resumeItem{Automated grading scripts with \textbf{Python}, decreasing manual review workload and errors by 25\%.}
        \resumeItem{Presented 15+ interactive sessions explaining core topics including Cryptography and web security fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced frontend responsiveness and functionality using \textbf{Angular.js}, increasing user engagement by 25\%.}
        \resumeItem{Developed RESTful services in \textbf{TypeScript} with optimized response times under 100ms.}
        \resumeItem{Built performant backend APIs in \textbf{C\#} with \textbf{.NET}, reducing data response latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and procedures, reducing load times on front end by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{React.js} UI for a SaaS platform, improving load speed and usability by 30\%.}
        \resumeItem{Designed and implemented \textbf{Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000 concurrent users.}
        \resumeItem{Built and maintained CI/CD pipelines with \textbf{Docker} on \textbf{AWS EC2}, enabling faster deployments.}
        \resumeItem{Implemented unit tests using \textbf{JUnit}, achieving 90\% code coverage and improving reliability.}
        \resumeItem{Led front-end feature porting with \textbf{TypeScript}, enhancing code modularity and maintainability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Real-Time Store Operations Dashboard} | React, TypeScript, AWS, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed a responsive dashboard integrating \textbf{React} and \textbf{TypeScript} for real-time operational data and AI alerts, improving decision speed by 30\%.}
              \resumeItem{Integrated \textbf{OpenAI API} for automated insights and anomaly detection, reducing manual monitoring efforts by 50\%.}
              \resumeItem{Deployed scalable app on \textbf{AWS}, ensuring low latency and high availability during peak store hours.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Multi-Platform Mobile App for Store Operations} | React Native, JavaScript, CSS}{}
          \resumeItemListStart
              \resumeItem{Led development of cross-platform mobile app using \textbf{React Native} improving store staff’s task management efficiency by 40\%.}
              \resumeItem{Implemented offline data sync and intuitive UI controls, reducing errors and increasing user adoption.}
              \resumeItem{Conducted usability testing and iterated UI based on feedback, boosting customer satisfaction scores by 25\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, Java, Python, C\#, PHP \\
                \textbf{Frontend Development:} & React, Angular.js, React Native, HTML, CSS \\
                \textbf{Backend \& Frameworks:} & Spring Boot, Node.js, Laravel, .NET \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, Lambda, S3), Docker, Jenkins \\
                \textbf{AI \& Automation Tools:} & OpenAI API, LLM Integration, AI Agents, n8n, Zapier \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}