\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{AI-driven} microservices using \textbf{Java Spring Boot} improving API throughput by 35\%.}
        \resumeItem{Integrated \textbf{Spring Security} to enhance authentication, resulting in 40\% fewer unauthorized access attempts.}
        \resumeItem{Implemented an \textbf{AI code review} assistant reducing manual PR review effort by 45\% and decreasing development cycle by 25\%.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating release cycles by 40\%.}
        \resumeItem{Collaborated in cross-functional teams to design machine learning solutions meeting customer performance metrics and accuracy goals.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built \textbf{AI agent} workflows using \textbf{LLMs} to automate data downloads, reducing manual effort by 80\%.}
        \resumeItem{Developed \textbf{React} enhancements improving load times by 25\% and increasing user engagement by a similar margin.}
        \resumeItem{Designed AI-driven LinkedIn automation bot leading to 40\% increase in qualified leads via targeted outreach.}
        \resumeItem{Automated stock data pipelines using \textbf{Python}, handling 10,000+ entries daily and cutting manual work by 80\%.}
        \resumeItem{Architected a SaaS visualization platform with \textbf{Laravel} and \textbf{React} supporting 50+ concurrent users robustly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab infrastructure securing environment for machine learning and cybersecurity experiments.}
        \resumeItem{Guided students debugging and testing software modules enhancing lab assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts to boost evaluation accuracy by 25\%, speeding up feedback for ML assignments.}
        \resumeItem{Conducted 15+ sessions teaching complex topics related to networking and security aligning with AI platform security needs.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed sub-100ms response APIs in \textbf{TypeScript}, enabling seamless integration with ML-powered services.}
        \resumeItem{Improved platform UI with \textbf{Angular.js}, boosting user engagement by 25\% through enhanced experience.}
        \resumeItem{Built backend services in \textbf{C\# .NET} reducing latency by 30\%, enabling faster ML data processing workflows.}
        \resumeItem{Optimized \textbf{PostgreSQL} procedures, enhancing database efficiency and lowering frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{microservices} in \textbf{Java Spring Boot} supporting 1000+ users with response times below 200ms.}
        \resumeItem{Established reliable CI/CD pipelines deploying services on \textbf{AWS EC2} using \textbf{Docker}, reducing downtime.}
        \resumeItem{Built \textbf{React.js} UI modules improving project management usability and speeding load times by 30\%.}
        \resumeItem{Implemented unit tests with \textbf{JUnit} achieving 90\% code coverage, boosting software quality and reliability.}
        \resumeItem{Collaborated on SaaS tool automating the \textbf{SDLC} lifecycle, enhancing team productivity by 20\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Generative AI Model Serving Platform} | Python, PyTorch, Hugging Face, Docker}{}
          \resumeItemListStart
              \resumeItem{Developed an end-to-end \textbf{GenAI} workflow integrating \textbf{transformers} with optimized model serving, reducing inference latency by 30\%.}
              \resumeItem{Implemented hyper-parameter tuning and quantization, enhancing model accuracy and reducing size by 40\% for deployment ease.}
              \resumeItem{Deployed scalable microservices on \textbf{Docker} containers yielding seamless model updates with zero downtime.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-powered Data Insights and Optimization Tool} | Python, TensorFlow, NLP, Docker}{}
          \resumeItemListStart
              \resumeItem{Developed ML models using \textbf{TensorFlow} to generate predictive analytics, improving data-driven decisions accuracy by 25\%.}
              \resumeItem{Engineered data pipelines and feature engineering automations to support reproducible training and inference workflows.}
              \resumeItem{Built REST APIs for model inference enabling integration into existing business platforms with 99\% uptime reliability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Python, Java, C++, TypeScript, C\#, JavaScript, PHP, Shell Scripting \\
                \textbf{Machine Learning \& AI Frameworks:} & PyTorch, TensorFlow, Hugging Face, Transformers, GenAI Frameworks, LLMs \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Spring Boot, Laravel, .NET, Node.js, Django \\
                \textbf{Cloud \& DevOps Technologies:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Azure, CI/CD Pipelines \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL \\
                \textbf{Tools \& Other Technologies:} & Linux/Unix, Git, REST APIs, gRPC, JUnit, LLM Integration, AI Agents, Prompt Engineering \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}