\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to improve API throughput by 35\%, enhancing system scalability and reliability.}
        \resumeItem{Implemented \textbf{Spring Security} updates to reduce unauthorized accesses by 40\%, strengthening overall authentication controls.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant, cutting manual review time by 45\% and boosting development speed by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, reducing release cycles by 40\% and improving deployment reliability.}
        \resumeItem{Collaborated in debugging and profiling backend services to optimize system performance and stability under heavy user load.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a scalable \textbf{SaaS} dashboard using \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users without latency.}
        \resumeItem{Automated data ingestion pipelines with \textbf{Python}, processing 10,000+ stock records daily, reducing manual intervention by 80\%.}
        \resumeItem{Developed a role-based access platform with \textbf{PHP}, \textbf{Stripe}, and WooCommerce, enhancing security and user management.}
        \resumeItem{Built \textbf{LLM}-powered AI agents automating financial data processing, cutting manual labor by 80\% and improving accuracy.}
        \resumeItem{Refined \textbf{React} component performance, reducing load times by 25\% and improving user engagement metrics significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based environments to maintain secure and reliable cybersecurity lab infrastructure for student use.}
        \resumeItem{Guided students through debugging and deployment, increasing software assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts that improved assessment accuracy by 25\% and streamlined instructor review workload.}
        \resumeItem{Delivered 15+ interactive sessions on cryptography and network security, enhancing student understanding of complex topics.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{TypeScript} API calls with sub-100ms response times, achieving efficient and scalable data interactions.}
        \resumeItem{Modernized frontend using \textbf{Angular.js}, elevating user engagement and satisfaction by 25\%.}
        \resumeItem{Developed high-performance backend services with \textbf{C\#} and \textbf{.NET}, reducing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries reducing frontend loading overhead by 15\%, enhancing database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices handling 1000+ concurrent sessions, reducing latency below 200ms.}
        \resumeItem{Designed and deployed \textbf{Docker}-based CI/CD pipelines on \textbf{AWS EC2}, accelerating software release cycles.}
        \resumeItem{Implemented project tracking UI with \textbf{React.js}, improving load speeds by 30\% and user workflows significantly.}
        \resumeItem{Wrote \textbf{JUnit} unit tests achieving 90\%+ coverage for core pipeline modules, ensuring code reliability.}
        \resumeItem{Collaborated on SaaS automation tool development, streamlining SDLC and boosting team productivity.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Android Performance Analyzer} | Android, Java, Kotlin, C++}{}
          \resumeItemListStart
              \resumeItem{Designed an Android app to profile app performance and visualize latency, improving responsiveness by 30\%.}
              \resumeItem{Integrated \textbf{C++} native modules to optimize resource-heavy computations, reducing CPU usage by 25\%.}
              \resumeItem{Developed debugging tools within the app that triage system issues and improve fault localization accuracy by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Assisted Accessibility Enhancement Tool} | Android, Kotlin, Accessibility APIs, ML}{}
          \resumeItemListStart
              \resumeItem{Engineered an Android accessibility tool using \textbf{Kotlin} and AI models to improve screen reader responsiveness by 40\%.}
              \resumeItem{Developed user behavior analytics and adaptive feedback, boosting accessibility feature adoption by 20\%.}
              \resumeItem{Automated accessibility issue detection, reducing manual audits by 50\% and ensuring compliance with standards.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Kotlin, C++, Python, JavaScript, C\#, PHP, TypeScript \\
                \textbf{Mobile & Frameworks:} & Android SDK, Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Data Structures \& Algorithms:} & Algorithms, Large Scale Systems, Performance Analysis, Debugging Techniques \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{AI \& Automation:} & LLM Integration, OpenAI API, AI Agents, Automation Workflows, Accessibility Technologies \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}