\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{Java Spring Boot} microservices to increase scalability and throughput, improving API performance by 35\%.}
        \resumeItem{Implemented \textbf{Spring Security} enhancements for authentication and role-based access, reducing unauthorized attempts by 40\%.}
        \resumeItem{Created an \textbf{AI-driven} code review assistant using \textbf{LLMs} to reduce manual review time by 45\% and enhance code quality.}
        \resumeItem{Automated build, test, and deployment pipelines using \textbf{Jenkins} and \textbf{Docker}, cutting release time by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to improve internal platforms’ automation, scalability, and performance metrics by over 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a scalable \textbf{SaaS} data visualization platform with \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Automated data pipelines using \textbf{Python}, processing 10,000+ stock entries daily and decreasing manual effort by 80\%.}
        \resumeItem{Developed subscription e-commerce platform with \textbf{PHP, Stripe} integration enabling secure role-based user access control.}
        \resumeItem{Built AI agents leveraging \textbf{LLMs} to automate FINRA broker data workflows, reducing manual processing effort by 80\%.}
        \resumeItem{Enhanced \textbf{React} components for optimized load times, improving page responsiveness by 25\% and user retention.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{Linux}-based lab infrastructure ensuring secure configurations and reliable environment for cybersecurity exercises.}
        \resumeItem{Assisted students in debugging, deploying, and testing software, increasing assignment success rates by 20\%.}
        \resumeItem{Automated grading and validation scripts to reduce manual review workload and improve accuracy by 25\%.}
        \resumeItem{Conducted 15+ interactive sessions explaining cryptography, networking protocols, and web security concepts effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API calls achieving sub-100ms response times, ensuring smooth and fast data exchanges.}
        \resumeItem{Enhanced platform usability by upgrading frontend with \textbf{Angular.js}, boosting user engagement by 25\%.}
        \resumeItem{Built backend services using \textbf{C\#} and \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, cutting frontend load by 15\% and improving query efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Java Spring Boot} microservices suite integrated with \textbf{MySQL}, handling 1000+ users and response times below 200ms.}
        \resumeItem{Implemented and maintained \textbf{CI/CD} pipelines on \textbf{AWS EC2} with \textbf{Docker} to enable seamless deployments.}
        \resumeItem{Designed and developed React.js project tracking UI, improving usability and reducing page load times by 30\%.}
        \resumeItem{Authored unit tests for pipelines using \textbf{JUnit} framework achieving 90\% coverage and improving code reliability.}
        \resumeItem{Collaborated on SaaS automation tools enhancing the SDLC process, improving team productivity and deployment efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered CI/CD Automation Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{CI/CD} automation bot using \textbf{GitHub Actions} and \textbf{OpenAI API} to analyze pull requests reducing review times by 30\%.}
              \resumeItem{Automated generation of accurate \textbf{Python} docstrings with AI assistance ensuring 100\% documentation coverage on new code.}
              \resumeItem{Integrated bot into development workflows, increasing code quality and accelerating release cycles by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-Native Container Orchestration Platform} | Docker, Kubernetes, Terraform}{}
          \resumeItemListStart
              \resumeItem{Engineered a container orchestration platform using \textbf{Docker} and \textbf{Kubernetes}, improving deployment consistency and scalability by 40\%.}
              \resumeItem{Automated infrastructure provisioning with \textbf{Terraform}, reducing cloud resource setup time by 50\%.}
              \resumeItem{Collaborated with developers to optimize microservice deployment workflows, increasing system uptime to 99.9\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Bash, Java, TypeScript, C\#, JavaScript, PHP \\
                \textbf{Cloud Platforms \& DevOps:} & AWS, Azure, Google Cloud, Docker, Kubernetes, Terraform, GitHub Actions, GitLab CI/CD \\
                \textbf{Web Development Frameworks:} & Spring Boot, React.js, Angular.js, Laravel, .NET \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Automation \& CI/CD Tools:} & Jenkins, Git, GitHub, Terraform, n8n \\
                \textbf{Operating Systems \& Tools:} & Linux/Unix, Shell Scripting, REST APIs, JUnit, Security Frameworks (ISO 27001, NIST) \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}