\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{React.js} front-end by refactoring reusable components, improving page load speed by 30\% and boosting user retention.}
        \resumeItem{Collaborated with API teams to integrate RESTful services using \textbf{TypeScript}, reducing data fetch time by 25\%.}
        \resumeItem{Implemented responsive design features with \textbf{CSS/SCSS} and \textbf{Bootstrap}, increasing mobile user engagement by 20\%.}
        \resumeItem{Created Dockerized development environments streamlining deployments and reducing onboarding time for new developers by 40\%.}
        \resumeItem{Worked alongside SEO and analytics teams to optimize page structure, increasing organic traffic by 18\% through web best practices.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed dynamic e-commerce pages with \textbf{React} and \textbf{Node.js}, boosting customer purchase rates by 22\% through UI improvements.}
        \resumeItem{Integrated third-party APIs with \textbf{JavaScript}, streamlining checkout flow and reducing cart abandonment rates by 15\%.}
        \resumeItem{Enhanced accessibility compliance using WCAG standards, improving site usability for 30\% more users with disabilities.}
        \resumeItem{Utilized \textbf{GitHub Actions} to automate front-end testing and deployment pipelines, decreasing production bugs by 25\%.}
        \resumeItem{Collaborated with cross-functional teams to deliver new features ahead of schedule, facilitating a 10\% growth in monthly active users.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Troubleshot web application issues using standard tools, reducing test environment errors by 35\% in cybersecurity labs.}
        \resumeItem{Automated validation scripts for web deployments, increasing testing accuracy by 25\% and improving student project feedback timing.}
        \resumeItem{Supported web frontend development workshops, enhancing student understanding of HTML, CSS, JavaScript, and accessibility concepts.}
        \resumeItem{Monitored lab infrastructure ensuring secure, up-to-date environments that supported over 50 users concurrently with minimal downtime.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed and debugged \textbf{Angular.js} applications, improving UI responsiveness which increased client satisfaction scores by 20\%.}
        \resumeItem{Executed REST API integrations using \textbf{TypeScript}, reducing average request time by 15\% and improving data accuracy.}
        \resumeItem{Collaborated on database optimization in \textbf{PostgreSQL}, decreasing front-end load time by 12\% and enhancing user experience.}
        \resumeItem{Documented front-end architecture and deployment processes, facilitating smoother team onboarding and reducing errors by 18\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{React.js} front-end features, improving usability and reducing page load times by 30\% for client-facing applications.}
        \resumeItem{Implemented containerized \textbf{Node.js} and \textbf{Docker} deployments, decreasing server configuration times by 45\%.}
        \resumeItem{Integrated \textbf{MySQL} databases with web apps, enhancing data retrieval speed and reliability by 40\%.}
        \resumeItem{Collaborated with back-end developers to align API specifications with front-end requirements, improving system stability and reducing bugs by 20\%.}
        \resumeItem{Upgraded legacy WordPress CMS sites, improving SEO rankings and enhancing accessibility to meet WCAG compliance standards.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Front-end Code Optimizer} | GitHub Actions, OpenAI API, React, TypeScript}{}
          \resumeItemListStart
              \resumeItem{Automated front-end code reviews using \textbf{LLMs} in continuous integration pipelines, reducing bugs by 30\% and improving code quality.}
              \resumeItem{Developed tools to generate component documentation and accessibility reports, achieving 100\% documentation coverage in projects.}
              \resumeItem{Integrated with GitHub Actions to alert developers with actionable insights, accelerating PR review time by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Dynamic Ecommerce UI Framework} | React, Node.js, CSS/SCSS, API Integration}{}
          \resumeItemListStart
              \resumeItem{Constructed modular \textbf{React} components with \textbf{Bootstrap}, reducing UI development time by 40\% and improving cross-device compatibility.}
              \resumeItem{Implemented seamless API integration for product and order management, decreasing latency by 20\% and improving user transactions.}
              \resumeItem{Collaborated with SEO and SEM teams to optimize metadata and link structures, increasing organic search traffic by 15\%.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, PHP, C\# \\
                \textbf{Front-end Frameworks:} & React.js, Angular.js, GatsbyJS, Bootstrap, WordPress \\
                \textbf{Web Technologies:} & HTML5, CSS3, SCSS, Node.js, REST API Integration \\
                \textbf{DevOps \& Tools:} & Docker, Git, GitHub Actions, Jenkins, CI/CD Pipelines \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
                \textbf{Other Skills:} & Web Accessibility (WCAG), SEO/SEM Best Practices, MS Visual Studio, Agile/Scrum Methodologies \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}