\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{microservices} scalability by optimizing \textbf{Java Spring Boot} APIs, increasing throughput by 35\% with reduced latency.}
        \resumeItem{Implemented secure access controls with \textbf{Spring Security}, cutting unauthorized logins by 40\% and strengthening platform protection.}
        \resumeItem{Automated code reviews using \textbf{AI-driven} tools that detected bugs and suggested improvements, decreasing manual efforts by 45\%.}
        \resumeItem{Streamlined CI/CD pipelines via \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 40\% while ensuring frequent releases.}
        \resumeItem{Collaborated with cross-functional teams to define scalable architecture and maintain high-quality code for evolving product features.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and developed a \textbf{React} UI integrating with \textbf{Laravel} backends to support 50+ users with 99.9\% uptime.}
        \resumeItem{Automated stock data processing pipelines in \textbf{Python}, increasing data accuracy and reducing manual work by 80\%.}
        \resumeItem{Built scalable subscription e-commerce system with \textbf{PHP Stripe} integrations to support role-based user access and payments.}
        \resumeItem{Led development of AI-powered automation agents using \textbf{LLMs} for FINRA broker data downloads, improving efficiency by 80\%.}
        \resumeItem{Refined \textbf{React} components to enhance performance, reducing page load times by 25\% and boosting user engagement metrics.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Managed \textbf{Linux}-based lab environments, ensuring secure and stable configurations for cybersecurity experiments and student use.}
        \resumeItem{Assisted students in debugging and testing software modules, increasing assignment success rates by 20\% through guided support.}
        \resumeItem{Created automated grading scripts that improved result accuracy and cut manual review time by 25\% for lab assignments.}
        \resumeItem{Conducted online sessions explaining Cryptography, Networking, and Web Security concepts to over 60 students effectively.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript} API integrations guaranteeing sub-100ms response times for real-time financial data retrievals.}
        \resumeItem{Enhanced front-end user experience by upgrading \textbf{Angular.js} features, increasing engagement by 25\% during the internship.}
        \resumeItem{Built efficient back-end services in \textbf{C\# .NET} that reduced data fetching latency by 30\%, boosting overall system response.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, lowering frontend load by 15\% and improving data processing speed.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices for SaaS tool supporting 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Led building of \textbf{React.js} front-end improving usability and page load speed by 30\% across project management UI modules.}
        \resumeItem{Designed \textbf{CI/CD} pipelines using \textbf{Docker} on \textbf{AWS EC2} to automate deployment of core microservices.}
        \resumeItem{Implemented comprehensive \textbf{JUnit} unit tests with 90\% coverage, enhancing code quality and reliability.}
        \resumeItem{Collaborated with cross-functional teams to ensure modular architecture and maintainable code for scalability and future features.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Assisted Game UI Testing Framework} | Jest, React Testing Library, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Built an AI-powered framework automating UI test generation for \textbf{React} components, improving test coverage by 40\%.}
              \resumeItem{Integrated \textbf{OpenAI API} to generate user interaction scenarios, reducing manual test creation time by 35\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cross-Device Netflix Game Controller UI} | React, TypeScript, WebSocket}{}
          \resumeItemListStart
              \resumeItem{Developed a responsive UI for Netflix Games Controller using \textbf{React} and \textbf{TypeScript} supporting seamless control across devices.}
              \resumeItem{Implemented efficient real-time communication with \textbf{WebSocket}, lowering input latency by 30\% and enhancing user experience.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{AI-Powered Personalization System for Interactive Media} | Python, TensorFlow, AWS}{}
          \resumeItemListStart
              \resumeItem{Designed an AI personalization engine using \textbf{TensorFlow} to deliver tailored interactive media recommendations, increasing engagement by 25\%.}
              \resumeItem{Deployed scalable backend on \textbf{AWS} enabling low-latency inference and robust data processing for real-time experience adjustments.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, Java, Python, C\#, PHP \\
                \textbf{Frontend Technologies:} & React.js, Angular.js, HTML, CSS, React Testing Library \\
                \textbf{Backend Technologies:} & Spring Boot, Node.js, Laravel, .NET, Flask \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{DevOps \& Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, GitHub Actions \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, TensorFlow, AI Agents, Automated Testing \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}