\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices architecture, improving scalability and achieving 35\% better API throughput.}
        \resumeItem{Implemented robust role-based access control with \textbf{Spring Security}, decreasing unauthorized requests by 40\%.}
        \resumeItem{Deployed an \textbf{AI-driven} code review assistant using pull request analysis, reducing manual reviews by 45\%.}
        \resumeItem{Automated CI/CD pipelines via \textbf{Jenkins} and \textbf{Docker}, cutting release cycle duration by 40\%.}
        \resumeItem{Researched GenAI tools to boost developer productivity, integrating AI models to support coding and testing activities.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected scalable \textbf{SaaS} data visualization with \textbf{Laravel} and \textbf{React}, enabling 50+ concurrent users.}
        \resumeItem{Automated stock data pipelines using \textbf{Python}, reducing manual processing time by 80\% for 10,000+ daily entries.}
        \resumeItem{Developed role-based e-commerce subscription platform integrating \textbf{Stripe} and WooCommerce for seamless payments.}
        \resumeItem{Built \textbf{AI agents} with \textbf{LLMs} to automate stock broker data workflows, slashing manual effort by 80\%.}
        \resumeItem{Optimized \textbf{React} components enhancing user experience, reducing page load times by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Supported \textbf{Linux}-based environments for cybersecurity labs, ensuring stability and secure system configurations.}
        \resumeItem{Assisted students in debugging and testing software, increasing assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts with improved validation, boosting accuracy and reducing manual workload by 25\%.}
        \resumeItem{Delivered online sessions covering Cryptography and Networking Protocols, enhancing student comprehension substantially.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed responsive \textbf{TypeScript} API calls, processing data under 100ms for efficient frontend-backend sync.}
        \resumeItem{Upgraded UI with \textbf{Angular.js}, increasing user engagement by 25\% and streamlining workflows.}
        \resumeItem{Implemented efficient back-end services in \textbf{C\#} with \textbf{.NET}, reducing data latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, enhancing database efficiency reducing frontend data load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led development of \textbf{Java Spring Boot} microservices supporting 1000 concurrent users with response times below 200ms.}
        \resumeItem{Designed and deployed \textbf{Docker}-based \textbf{CI/CD} pipelines on \textbf{AWS EC2}, ensuring rapid microservices deployment.}
        \resumeItem{Created React.js UI for project management, improving load speed by 30\% and enhancing overall user experience.}
        \resumeItem{Implemented unit tests covering 90\% of codebase in the pipelines module using the \textbf{JUnit} framework.}
        \resumeItem{Collaborated in a 5-member team to build a \textbf{SaaS} tool automating SDLC processes, improving developer throughput.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GenAI-Powered Test Automation Bot} | GitHub Actions, OpenAI API, TypeScript}
          \resumeItemListStart
              \resumeItem{Built an AI-based bot using \textbf{OpenAI API} to automate test case generation and analysis, improving test coverage by 30\%.}
              \resumeItem{Integrated the bot with CI/CD workflows via \textbf{GitHub Actions} to streamline continuous quality assurance processes.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Device Test Management Dashboard} | React.js, Node.js, MongoDB, Express}
          \resumeItemListStart
              \resumeItem{Developed a responsive dashboard in \textbf{React.js} for managing test devices, boosting device utilization efficiency by 25\%.}
              \resumeItem{Implemented RESTful services using \textbf{Node.js} and \textbf{MongoDB} to handle device metadata and real-time status.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Network Debugging Toolkit} | TypeScript, Node.js, Linux}
          \resumeItemListStart
              \resumeItem{Created a toolkit for analyzing HTTP, TCP, and DNS protocols using \textbf{TypeScript}, aiding developers in faster debugging by 35\%.}
              \resumeItem{Designed platform-agnostic CLI utilities compatible with \textbf{Linux} to facilitate cross-team network diagnostics.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, C\#, PHP, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Node.js, Spring Boot, Angular.js, Laravel, Express \\
                \textbf{Datastores \& Databases:} & MongoDB, PostgreSQL, MySQL, DynamoDB \\
                \textbf{DevOps \& Cloud:} & Docker, AWS (EC2, S3, Lambda), Jenkins, CI/CD Pipelines \\
                \textbf{Networking \& Tools:} & HTTP, TCP, DNS Protocols, Linux, Git, REST API, JUnit \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, GitHub Actions, AI Agents, Automation Workflows \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}