\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java Spring Boot} microservices to scale distributed systems, increasing throughput and reducing latency by 35\%.}
        \resumeItem{Enhanced \textbf{Spring Security} access controls, cutting unauthorized access incidents by 40\% across multiple services.}
        \resumeItem{Deployed an AI code review assistant leveraging LLMs, automating code audits and reducing manual reviews by 45\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, accelerating release frequency by 40\%.}
        \resumeItem{Collaborated on cross-functional teams to improve product observability and developer experience, boosting deployment stability by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a scalable SaaS data visualization platform with \textbf{Laravel} and \textbf{React}, supporting 50+ concurrent users seamlessly.}
        \resumeItem{Automated complex data pipelines in \textbf{Python}, processing 10,000+ entries daily, cutting manual work by 80\%.}
        \resumeItem{Implemented AI agents utilizing \textbf{LLMs} to automate FINRA data workflows, reducing manual processing by 80\%.}
        \resumeItem{Developed an AI-driven LinkedIn bot to automate lead generation, increasing qualified leads by 40\%.}
        \resumeItem{Optimized \textbf{React} components and state management to reduce page load times by 25\%, enhancing user engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} infrastructures for labs, ensuring 99\% uptime and reliable student access to resources.}
        \resumeItem{Guided students on debugging and deploying software modules, boosting assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts leading to 25\% faster and more accurate assignment evaluations and feedback.}
        \resumeItem{Led interactive sessions on Cryptography and Networking, improving student comprehension in complex security topics.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient API calls in \textbf{TypeScript}, achieving average response times below 100ms.}
        \resumeItem{Upgraded platform using \textbf{Angular.js}, improving user satisfaction and engagement by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, reducing data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, decreasing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Built \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000 concurrent users with <200ms latency.}
        \resumeItem{Automated CI/CD deployment pipelines on \textbf{AWS EC2} with \textbf{Docker}, increasing release reliability by 35\%.}
        \resumeItem{Created a React.js UI for project tracking, enhancing usability and load speed by 30\%.}
        \resumeItem{Implemented unit tests with \textbf{JUnit} covering 90\%+ of core pipeline code, improving code quality.}
        \resumeItem{Collaborated with the team on distributed system features, improving service scalability and fault tolerance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Created an AI-driven bot using \textbf{GitHub Actions} and \textbf{OpenAI API} to review pull requests, cutting manual review time by 25\%.}
              \resumeItem{Automated docstring generation and style fixes to ensure code quality, boosting developer productivity and documentation coverage.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Distributed Content Workflow Platform} | Java, Spring Boot, AWS, Docker}{}
          \resumeItemListStart
              \resumeItem{Engineered a microservice-based platform to streamline content production workflows, handling thousands of operations daily with low latency.}
              \resumeItem{Implemented robust data modeling and API design optimizing integration across content management and production systems at scale.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Event-Driven Face Recognition Service} | AWS EC2, SQS, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Developed a scalable face recognition microservice using event-driven architecture, handling 1000+ requests under 60 seconds efficiently.}
              \resumeItem{Utilized \textbf{AWS SQS} for asynchronous communication and \textbf{S3} for data storage, enabling smooth scaling and fault tolerance.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, C\#, Python, JavaScript, TypeScript, PHP, Go, C++, Shell Scripting \\
                \textbf{Frameworks \& Platforms:} & Spring Boot, .NET, React.js, Angular.js, Laravel, Node.js, Flask \\
                \textbf{Distributed Systems \& Cloud:} & Microservices, AWS (EC2, S3, Lambda, SQS), Docker, Kubernetes, Event-Driven Architecture \\
                \textbf{Databases \& Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB, SQL, NoSQL \\
                \textbf{APIs \& Protocols:} & REST, gRPC, GraphQL, JSON, Webhooks \\
                \textbf{DevOps \& Automation:} & Jenkins, GitHub Actions, CI/CD, Monitoring, Observability, Unit Testing (JUnit) \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}