\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{API} endpoints using \textbf{PHP} and \textbf{Laravel}, reducing response latency by 30\% and improving system reliability.}
        \resumeItem{Implemented role-based access controls with \textbf{PHPUnit} tests, decreasing security vulnerabilities by 35\%.}
        \resumeItem{Integrated third-party services via \textbf{REST APIs}, boosting system interoperability and reducing data sync errors by 40\%.}
        \resumeItem{Designed database optimizations with \textbf{MySQL}, cutting query execution times by 25\% for core business processes.}
        \resumeItem{Collaborated in Agile teams to refine sprint deliverables, improving code quality and reducing bug rate by 20\% per cycle.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{PHP Laravel} web applications with \textbf{Vue.js}, increasing page load speed by 30\% and user retention by 15\%.}
        \resumeItem{Streamlined data exchange with \textbf{ERP} APIs, improving order processing throughput by 50\% and accuracy by 20\%.}
        \resumeItem{Automated complex data workflows using \textbf{PHP} and \textbf{REST APIs}, reducing manual efforts by 70\% and errors by 15\%.}
        \resumeItem{Led code reviews focusing on clean, maintainable \textbf{OOP} code, resulting in a 25\% decrease in technical debt.}
        \resumeItem{Collaborated cross-functionally to translate requirements into robust solutions, shortening feature delivery cycles by 22\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and secured \textbf{Linux}-based cybersecurity lab environments, reducing system downtime by 30\%.}
        \resumeItem{Facilitated student troubleshooting for software modules, helping improve project success rates by 15\%.}
        \resumeItem{Automated grading scripts using \textbf{Python}, decreasing manual review time by 40\% while increasing accuracy.}
        \resumeItem{Conducted 12+ technical tutorials on cryptography and network security, enhancing student engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{TypeScript}-based APIs with average response times under 120ms, improving data exchange reliability.}
        \resumeItem{Refined \textbf{Angular.js} frontend components, increasing user interaction rates by 25\%.}
        \resumeItem{Optimized backend \textbf{C\# .NET} API queries, reducing server response latency by 20\%.}
        \resumeItem{Improved \textbf{PostgreSQL} data access patterns, lowering frontend load by 18\% and enhancing performance.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Laravel} microservices integrated with \textbf{MySQL}, supporting 900+ concurrent users at sub-250ms response times.}
        \resumeItem{Engineered \textbf{REST API} integrations with payment gateways, increasing transaction throughput by 40\%.}
        \resumeItem{Set up \textbf{CI/CD} pipelines deploying containerized apps on \textbf{AWS EC2} via \textbf{Docker}, speeding releases by 35\%.}
        \resumeItem{Built dynamic \textbf{React.js} dashboards improving user task efficiency by 30\% through better UI flow.}
        \resumeItem{Implemented unit tests with \textbf{PHPUnit}, boosting code coverage to 85\% and lowering reported bugs by 28\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Code Quality Assistant} | PHP, GitHub Actions, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Developed an AI assistant using \textbf{LLMs} to review \textbf{PHP} code for quality, reducing manual review time by 30\%.}
              \resumeItem{Automated documentation generation ensuring 100\% function coverage, improving codebase maintainability and onboarding speed.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Operations Management System Enhancement} | PHP, Laravel, REST APIs, MySQL}{}
          \resumeItemListStart
              \resumeItem{Redesigned backend modules using \textbf{Laravel} improving order fulfillment speed by 35\% and data consistency across platforms.}
              \resumeItem{Integrated third-party shipping APIs, automating returns and tracking, decreasing manual labor by 40\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Cloud-Hosted Smart Pet Data API} | Azure, PHP, Docker, REST}{}
          \resumeItemListStart
              \resumeItem{Developed containerized \textbf{PHP} REST API hosted on \textbf{Azure}, handling 1000+ smart pet device data requests per minute reliably.}
              \resumeItem{Implemented caching mechanisms using Redis, reducing database load by 25\% and accelerating response times.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & PHP (7.x/8.x), JavaScript, Java, Python, TypeScript, C\# \\
                \textbf{Web Development \& Frameworks:} & Laravel, Symfony, React, Vue, Angular.js, JQuery, SASS/LESS \\
                \textbf{Database \& Storage:} & MySQL, PostgreSQL, Redis, Memcache \\
                \textbf{Cloud \& DevOps:} & Azure, Docker, CI/CD Pipelines, Git, GitHub, Jenkins \\
                \textbf{Enterprise Systems \& APIs:} & ERP Integration, REST APIs, RabbitMQ, Message Queuing \\
                \textbf{Tools \& Methodologies:} & Agile, PHPUnit, Jira, Accessibility/ADA Compliance \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}