\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Engineered scalable \textbf{Java Spring Boot} microservices enforcing secure authentication and authorization, improving system resilience by 35\%.}
        \resumeItem{Implemented \textbf{Spring Security} features that tightened role-based access, cutting security incidents by 40\% across multiple environments.}
        \resumeItem{Developed an \textbf{AI-powered} code review assistant that reduced manual review time by 45\%, accelerating release velocity by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, enabling 40\% faster deployment with zero downtime.}
        \resumeItem{Collaborated cross-functionally to integrate secure APIs, improving secure data exchange efficiency by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{Laravel} and \textbf{React} based SaaS platform with role-based access, supporting 50+ concurrent secure user sessions.}
        \resumeItem{Automated daily stock processing using \textbf{Python}, boosting data pipeline efficiency by 80\%.}
        \resumeItem{Configured subscription-based e-commerce system with \textbf{Stripe}, enabling secure multi-tier access control policies.}
        \resumeItem{Developed \textbf{AI agents} to automate FINRA data workflows, reducing manual processing time by 80\%.}
        \resumeItem{Enhanced \textbf{React} components to reduce load times by 25\%, improving secure user interactions and engagement.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secured \textbf{Linux}-based infrastructure, ensuring safe environments for cybersecurity experiments and research.}
        \resumeItem{Assisted students in deploying secure code modules, raising assignment success rates by 20\%.}
        \resumeItem{Automated grading scripts to enhance accuracy and reduce manual workload by 25\%.}
        \resumeItem{Led over 15 training sessions on security protocols including cryptography and network defense mechanisms.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced API responsiveness by achieving average sub-100ms latency using \textbf{TypeScript} for secure data retrieval.}
        \resumeItem{Refined \textbf{Angular.js} frontend features, improving engagement and security compliance by 25\%.}
        \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET}, reducing data processing delays by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and procedures to support secure, efficient database operations reducing frontend load by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Spearheaded a \textbf{Spring Boot} microservices suite with \textbf{MySQL} backend to support secure access for 1000+ concurrent users.}
        \resumeItem{Implemented Dockerized CI/CD pipelines on \textbf{AWS EC2}, accelerating deployment cycles and operational security.}
        \resumeItem{Built and maintained \textbf{React.js} UI modules, boosting user experience and secure data handling speed by 30\%.}
        \resumeItem{Developed robust unit tests with \textbf{JUnit}, achieving 90\% code coverage and reducing regression bugs.}
        \resumeItem{Collaborated on automating SDLC processes, improving secure code delivery and team efficiency significantly.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Driven Identity Access Reviewer} | GitHub Actions, OpenAI API, Python}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{Python}-based tool integrating \textbf{OpenAI API} to evaluate IAM policies and suggest secure improvements automatically.}
              \resumeItem{Integrated with \textbf{GitHub Actions} to automate pull request reviews, improving security audit times by 30\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Multi-Cloud Access Automation Framework} | AWS, Azure, GCP, Go}{}
          \resumeItemListStart
              \resumeItem{Engineered a \textbf{Go} tool to automate credential provisioning and rotation across AWS, Azure, and GCP, reducing manual overhead by 50\%.}
              \resumeItem{Implemented secure orchestration workflows ensuring consistent multi-cloud identity enforcement and access logging.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Secure AI Research Platform} | Kubernetes, IAM, Python, Flask}{}
          \resumeItemListStart
              \resumeItem{Built a Flask-based backend enforcing fine-grained IAM controls for AI model training on Kubernetes, protecting sensitive assets.}
              \resumeItem{Designed auto-scaling and secure role management features that improved system uptime to 99.9\% under variable workloads.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go, Java, TypeScript, C\#, JavaScript, PHP \\
                \textbf{Cloud Platforms \& Tools:} & AWS, Azure, GCP, Docker, Kubernetes, Lambda, EC2, S3 \\
                \textbf{Security \& IAM Technologies:} & OAuth, SAML, OpenID Connect, Role-Based Access Control, Identity Orchestration \\
                \textbf{Web Development \& Frameworks:} & Spring Boot, React.js, Flask, Angular.js, Laravel, .NET \\
                \textbf{Databases \& Data Storage:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{CI/CD \& Automation:} & Jenkins, GitHub Actions, Terraform, Ansible, JUnit, REST API \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}