\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #3}, \textbf{\small #1}, \small #4 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape \textbf{Shahil Mohammed}} \\ \vspace{1pt}
    \small (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Node.js} microservices to scale integration data flows, improving API throughput by 35\% and reducing latency for 100+ clients.}
        \resumeItem{Implemented robust authorization and rate limiting in \textbf{AWS Lambda} functions, decreasing unauthorized access attempts by 40\%.}
        \resumeItem{Developed automated monitoring tooling for integration pipelines using \textbf{TypeScript}, cutting debugging time by 30\% and boosting reliability.}
        \resumeItem{Collaborated on evolving integration framework, contributing improvements that simplified adding new \textbf{REST API} connectors and webhook handlers.}
        \resumeItem{Led cross-team technical discussions to clarify complex integration issues, enhancing communication between engineers and non-technical stakeholders.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and shipped scalable data pipeline integrations using \textbf{React} and \textbf{Node.js} to automate enrichment for marketing workflows.}
        \resumeItem{Built \textbf{SQL}-based data ingestion system to support ETL processes, increasing data availability for customer insights by 50\%.}
        \resumeItem{Automated API request queueing and rate limiting logic, reducing data sync errors by 35\% across multiple 3rd party service integrations.}
        \resumeItem{Developed AI-driven outreach tool integrating \textbf{LLMs} that boosted qualified lead generation by 40\% through targeted content automation.}
        \resumeItem{Refined React UI components for data enrichment dashboard, improving user satisfaction feedback by 25\% through enhanced usability.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based environments supporting cybersecurity labs, increasing lab uptime and reducing configuration errors by 20\%.}
        \resumeItem{Assisted students in debugging, deploying, and testing \textbf{Python} and \textbf{Java} code relevant to web security assignments with 90\% success rate.}
        \resumeItem{Automated lab grading scripts, improving evaluation speed by 35\% and accuracy of assignment scoring through consistent feedback loops.}
        \resumeItem{Conducted technical workshops on cryptography and networking concepts, enhancing student engagement and topic comprehension by 30\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented performant \textbf{TypeScript} API clients reducing average response latency under 100ms, enabling smoother data integration workflows.}
        \resumeItem{Upgraded frontend components using \textbf{Angular.js} improving user engagement metrics for data visualization modules by 25\%.}
        \resumeItem{Developed backend logic with \textbf{C\#} and \textbf{.NET} to optimize data retrieval, decreasing latency by 30\% and enhancing throughput.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and stored procedures, cutting frontend database load by 15\% and accelerating data processing pipelines.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices integrated with \textbf{MySQL}, supporting 1000+ concurrent users with sub-200ms latency.}
        \resumeItem{Designed and maintained CI/CD pipelines deploying microservices on \textbf{AWS EC2} using \textbf{Docker}, enhancing deployment frequency by 50\%.}
        \resumeItem{Created comprehensive project management UI in \textbf{React.js}, reducing page load times by 30\% and boosting user productivity.}
        \resumeItem{Implemented automated unit testing with \textbf{JUnit}, achieving 90\% coverage and reducing production bugs by 40\%.}
        \resumeItem{Led design improvements for custom integrations and API endpoints, simplifying third-party integration processes and boosting reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Integration Validation Bot} | GitHub Actions, OpenAI API, TypeScript}
          \resumeItemListStart
              \resumeItem{Built a CI/CD bot utilizing \textbf{LLMs} and \textbf{GitHub Actions} to validate new integrations, reducing integration bugs by 30\%.}
              \resumeItem{Automated generation of API documentation and error detection, improving development feedback loops for third-party connectors by 25\%.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Scalable Data Enrichment Platform} | AWS Lambda, Node.js, SQL}
          \resumeItemListStart
              \resumeItem{Engineered a serverless data ingestion pipeline on \textbf{AWS Lambda}, processing 100K+ requests daily with dynamic rate limiting and queuing.}
              \resumeItem{Implemented authorization layers and monitoring tools, boosting data pipeline reliability by 40\% and enabling smoother third-party API integrations.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{Custom Webhook Integration Framework} | React, Node.js, REST APIs}
          \resumeItemListStart
              \resumeItem{Designed and developed a flexible webhook framework to intake diverse data sources, improving integration speed by 50\% for new providers.}
              \resumeItem{Enhanced user interface in \textbf{React} for managing webhooks, leading to a 20\% increase in user satisfaction and feature adoption.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \footnotesize
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, Node.js, JavaScript, Python, C\#, PHP, Go \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Spring Boot, Laravel, .NET, Express.js \\
                \textbf{Cloud \& Serverless:} & AWS Lambda, AWS EC2, S3, DynamoDB, Docker, Jenkins \\
                \textbf{Databases:} & SQL, MySQL, PostgreSQL, MongoDB \\
                \textbf{Integration \& APIs:} & REST API, Webhooks, OAuth, Rate Limiting, Queueing Systems \\
                \textbf{AI \& Automation:} & OpenAI API, LLMs, GitHub Actions, CI/CD Pipelines, Automation Bots \\
            \end{tabular}
        \end{table}

 \vspace{-15pt}

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science, Tempe, AZ}{GPA: 4.00/4.00}

    \educationSubheading
      {Manipal Institute of Technology}{07/2018 -- 07/2022}
      {Bachelor of Technology in Computer and Communication Engineering, Manipal, India}{GPA: 8.83/10.00}
  \resumeSubHeadingListEnd

\end{document}