\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative full-stack engineer experienced in building scalable web applications with robust backend APIs and engaging front-end features. Skilled in Ruby on Rails and React, optimizing database queries for high-traffic environments, and ensuring high site performance, stability, and security for millions of users. Collaborative product-focused developer passionate about user experience and engineering best practices.  
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Backend Frameworks:} & \textbf{Ruby on Rails}, Spring Boot, Django, Laravel, Node.js \\
                \textbf{Frontend Technologies:} & \textbf{React.js}, Vue.js, Angular, CSS-in-JS, Redux, Jest \\
                \textbf{Databases:} & \textbf{PostgreSQL}, MySQL, MongoDB, SQL Optimization, Database Schema Design \\
                \textbf{DevOps and Cloud:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Programming Languages:} & JavaScript, TypeScript, Java, Python, PHP, Go, C\# \\
                \textbf{Tools and Practices:} & REST APIs, gRPC, Git, Agile, Unit Testing, Performance Tuning, Security Best Practices \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Java Spring Boot} microservices scalability, improving API throughput by 35\% to handle increased service demands.}
        \resumeItem{Implemented role-based authentication with \textbf{Spring Security}, reducing unauthorized access attempts by 40\%.}
        \resumeItem{Developed an \textbf{AI-driven} code review assistant to analyze pull requests, accelerating development velocity by 25\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Docker}, decreasing software release times by 40\%.}
        \resumeItem{Monitored and troubleshot system issues during on-call rotations, maintaining 99.9\% uptime across critical backend services.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented a \textbf{Laravel} and \textbf{React} SaaS platform supporting 50+ concurrent users with seamless scalability.}
        \resumeItem{Automated stock data pipelines in \textbf{Python}, processing over 10,000 entries daily and reducing manual effort by 80\%.}
        \resumeItem{Built a subscription e-commerce platform with \textbf{PHP} integrating \textbf{Stripe} payments and role-based access control.}
        \resumeItem{Leveraged \textbf{LLMs} to create AI agents automating FINRA data downloads, cutting manual processes by 80\%.}
        \resumeItem{Optimized state management in \textbf{React}, improving page load times by 25\% and boosting user engagement significantly.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based lab infrastructure, ensuring reliability for cybersecurity coursework and research.}
        \resumeItem{Assisted students in debugging and deploying software modules, increasing assignment pass rates by 20\%.}
        \resumeItem{Automated grading scripts improving evaluation accuracy by 25\%, reducing instructor manual workload.}
        \resumeItem{Led 15+ interactive sessions covering cryptography, networking, and web security concepts.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented fast \textbf{TypeScript} API calls maintaining sub-100ms response times for improved frontend performance.}
        \resumeItem{Enhanced platform with \textbf{Angular.js}, raising user engagement and satisfaction by 25\%.}
        \resumeItem{Developed backend services in \textbf{C\#} with \textbf{.NET}, lowering data retrieval latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures to reduce frontend load by 15\% and streamline queries.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Led development of \textbf{Java Spring Boot} microservices with \textbf{MySQL} optimizing response times below 200ms for 1000 concurrent users.}
        \resumeItem{Built project tracking UI in \textbf{React.js}, increasing usability and page load speed by 30\%.}
        \resumeItem{Devised and maintained CI/CD pipelines deploying microservices on \textbf{AWS EC2} with \textbf{Docker} containers for seamless delivery.}
        \resumeItem{Authored \textbf{JUnit} tests covering 90\% of pipelines, improving product reliability.}
        \resumeItem{Collaborated with a 5-member team to create a SaaS solution automating software development lifecycle processes efficiently.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Created an automated \textbf{CI/CD} bot using \textbf{GitHub Actions} and \textbf{LLMs} to review code and generate documentation, cutting review time by 40\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Collaborative Lyrics Annotation Platform} | React.js, Ruby on Rails, PostgreSQL}{}
          \resumeItemListStart
              \resumeItem{Developed a full-stack web app enabling fans to collaboratively transcribe and annotate song lyrics with real-time editing and version control features.}
              \resumeItem{Optimized \textbf{PostgreSQL} queries to scale large datasets with over 1 billion rows, ensuring fast load times under high traffic.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Music Streaming Metrics Dashboard} | React.js, Rails API, AWS}{}
          \resumeItemListStart
              \resumeItem{Built a responsive dashboard visualizing streaming performance data using a \textbf{Rails} backend and \textbf{React} frontend, enhancing user analysis capabilities.}
              \resumeItem{Implemented caching and query optimizations improving data fetch latency by 30\%, supporting tens of thousands of requests per minute.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}