\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer with a passion for biotechnology and scalable solutions, experienced in full-stack development and system design. Proven ability to develop impactful scientific applications with ownership from prototype to deployment while collaborating across teams to accelerate research progress and meet product goals. Eager to contribute to next-gen life sciences R&D platforms with strong problem-solving and technical mentorship aptitude.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, C++, C, Shell Scripting \\
                \textbf{Web Development \& Frameworks:} & React.js, Angular.js, Spring Boot, Node.js, Django \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, CI/CD Pipelines \\
                \textbf{Tools \& Others:} & Git, REST API, GraphQL, JUnit, Agile, Jira \\
                \textbf{AI \& Automation:} & OpenAI API, LLM Integration, Prompt Engineering, n8n, Zapier \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and optimized \textbf{Java Spring Boot} microservices for scientific workflows, enhancing API responsiveness by 35\% under load.}
        \resumeItem{Implemented role-based security with \textbf{Spring Security}, reducing unauthorized access by 40\% across key product modules.}
        \resumeItem{Developed an AI-assisted code review tool using \textbf{OpenAI API} that cut review time by 45\% and improved code quality.}
        \resumeItem{Automated containerized deployments via \textbf{Jenkins} and \textbf{Docker}, accelerating release cadence by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to refine product features, contributing to 3 major feature launches supporting scientist workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built and scaled a \textbf{React} and \textbf{Laravel} SaaS platform supporting 50+ users for complex data visualization of scientific data.}
        \resumeItem{Automated large-scale data pipelines with \textbf{Python}, improving processing speed by 80\% for research datasets.}
        \resumeItem{Developed AI agents using \textbf{LLM Integration} to automate extraction and processing of scientific records, reducing manual effort 80\%.}
        \resumeItem{Improved frontend performance by 25\% through refactoring \textbf{React} components and optimizing state management strategies.}
        \resumeItem{Created a targeted AI-driven outreach tool using \textbf{OpenAI API} that increased qualified lead conversions by 40\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained and secured \textbf{Linux}-based lab environments, ensuring reliability for over 50 student users weekly.}
        \resumeItem{Implemented automated grading scripts improving evaluation accuracy by 25\% and reducing instructor workload.}
        \resumeItem{Provided hands-on guidance troubleshooting software deployments, boosting student success rates by 20\%.}
        \resumeItem{Led interactive online tutorials explaining complex cybersecurity topics, enhancing student engagement and comprehension.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Developed efficient API endpoints in \textbf{TypeScript} achieving sub-100ms response times on data-intensive queries.}
        \resumeItem{Modernized frontend interfaces using \textbf{Angular.js}, increasing user engagement metrics by 25\%.}
        \resumeItem{Engineered backend services with \textbf{C\# .NET} reducing data processing latency by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} stored procedures, lowering frontend load times by 15\% and improving database efficiency.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Spring Boot} microservices with \textbf{MySQL}, supporting 1000+ concurrent users with under 200ms response time.}
        \resumeItem{Integrated CI/CD pipelines using \textbf{Docker} and \textbf{AWS EC2} for six microservices, increasing deployment efficiency by 50\%.}
        \resumeItem{Built responsive project management UI in \textbf{React.js}, improving user satisfaction and speeding load by 30\%.}
        \resumeItem{Authored unit tests covering 90\% of critical modules using \textbf{JUnit}, increasing codebase reliability.}
        \resumeItem{Led architecture discussions to design scalable platform features aligned with company and customer needs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Code Review Bot} | GitHub Actions, OpenAI API, LLMs}{}
          \resumeItemListStart
              \resumeItem{Created a \textbf{CI/CD} bot using \textbf{GitHub Actions} and \textbf{OpenAI API} to auto-review code and generate documentation, reducing manual reviews by 40\%.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Scientific Data Platform} | React.js, Spring Boot, PostgreSQL, AWS}{}
          \resumeItemListStart
              \resumeItem{Developed a \textbf{React} frontend and \textbf{Spring Boot} backend supporting real-time scientific data workflows used by multiple research labs.}
              \resumeItem{Designed database schema and APIs on \textbf{PostgreSQL} and deployed with \textbf{AWS}, achieving sub-second query latency at scale.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{AI Workflow Automation for Biotech Labs} | Python, Flask, OpenAI API}{}
          \resumeItemListStart
              \resumeItem{Engineered an AI-driven automation tool with \textbf{Python} and \textbf{OpenAI API} to streamline biotech experiment data classification and reporting.}
              \resumeItem{Achieved 60\% reduction in manual data processing time through AI-assisted workflow integration.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}