\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative server software engineer with 3+ years building scalable, secure backend systems and cloud services focused on health data integration. Experienced in healthcare standards and privacy-driven architectures enabling impactful user health management solutions at scale.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, Scala, TypeScript, C\# \\
                \textbf{Backend \& Frameworks:} & Spring Boot, Django, .NET, Node.js \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, Lambda), Docker, Jenkins, Azure \\
                \textbf{Web Services \& APIs:} & REST, HTTPS, JSON, SMART, FHIR \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Security \& Privacy:} & OAuth2, Spring Security, Data Privacy Practices \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} backend services integrating health data, increasing API throughput by 30\% while ensuring compliance with privacy standards.}
        \resumeItem{Engineered role-based access control using \textbf{Spring Security} to enhance data protection, reducing unauthorized access incidents by 35\%.}
        \resumeItem{Automated deployment pipelines with \textbf{Docker} and \textbf{Jenkins}, decreasing release cycles by 40\% and improving code quality assurance.}
        \resumeItem{Collaborated across teams to implement scalable cloud infrastructure on \textbf{AWS EC2}, supporting millions of concurrent health app users.}
        \resumeItem{Led knowledge sharing sessions on secure API design and \textbf{FHIR} standard integration, enhancing team expertise and project delivery speed.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed and deployed scalable backend services supporting user health analytics, increasing data processing speed by 25\% using \textbf{Python} and \textbf{Django}.}
        \resumeItem{Implemented \textbf{FHIR} and \textbf{SMART} protocols enabling secure external health data integration, improving interoperability with partners.}
        \resumeItem{Automated ingestion pipelines processing 20,000+ health records daily, reducing manual validation time by 70\% through \textbf{Python} scripting.}
        \resumeItem{Refined client-server communication protocols using \textbf{REST} and \textbf{JSON}, enhancing response times by 30\% in user-facing applications.}
        \resumeItem{Created security policies embedding privacy-by-design principles, ensuring HIPAA compliance across backend services and APIs.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux} lab environments aligned with cybersecurity best practices for 50+ students and staff users.}
        \resumeItem{Developed automated grading tools improving evaluation accuracy and reducing manual workload by 30\% for programming assignments.}
        \resumeItem{Assisted in configuring secure backend services following cryptographic protocols, enhancing lab system integrity and resilience.}
        \resumeItem{Led interactive workshops on network security concepts and backend service vulnerabilities, increasing student success rates by 20\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Implemented efficient API endpoints using \textbf{TypeScript}, reducing response latency by 30\% for enterprise data retrieval services.}
        \resumeItem{Enhanced backend performance with \textbf{.NET} and \textbf{C\#}, cutting database call latency by 25\% and improving throughput.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and functions, resulting in 20\% faster data access and less server load.}
        \resumeItem{Upgraded front-end components in \textbf{Angular.js} for better integration with backend APIs, increasing user satisfaction scores by 15\%.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting 1500 concurrent users with latency under 200ms, enhancing system scalability.}
        \resumeItem{Established \textbf{CI/CD} pipelines using \textbf{Docker} and \textbf{AWS EC2}, decreasing deployment time by 50\% for key services.}
        \resumeItem{Designed database schemas with \textbf{MySQL} optimizing health data models, improving query efficiency by 30\%.}
        \resumeItem{Built responsive front-end UI in \textbf{React.js} improving user workflow speed and reducing load times by 25\%.}
        \resumeItem{Created unit and integration tests with \textbf{JUnit}, maintaining 90\% code coverage and reducing bugs post-deployment by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{GPA: 4.0/4.0}
  \resumeSubHeadingListEnd
\vspace{-10pt}
%%%%%%
  
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Health Data Integration Bot} | Python, OpenAI API, FHIR, AWS Lambda}{}
          \resumeItemListStart
              \resumeItem{Developed an AI bot using \textbf{OpenAI API} and \textbf{FHIR} standards to automate health record normalization with 95\% data accuracy.}
              \resumeItem{Deployed on \textbf{AWS Lambda}, enabling scalable processing of 10,000+ health records daily while maintaining HIPAA-compliant security protocols.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Scalable Backend for Health Monitoring App} | Java, Spring Boot, AWS EC2, DynamoDB}{}
          \resumeItemListStart
              \resumeItem{Engineered \textbf{Java Spring Boot} microservices to support 1M+ users with less than 200ms latency and high availability on \textbf{AWS EC2}.}
              \resumeItem{Implemented \textbf{DynamoDB} for efficient health event data storage, reducing retrieval time by 40\% under heavy traffic.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Secure RESTful API for Clinical Data Exchange} | Python, Django, OAuth2, SMART on FHIR}{}
          \resumeItemListStart
              \resumeItem{Designed and implemented a secure API supporting \textbf{SMART on FHIR} healthcare standards to facilitate clinical data sharing with 99.9\% uptime.}
              \resumeItem{Integrated OAuth2 authentication ensuring robust data privacy, reducing security incidents by 35\% during QA testing phases.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}