\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}      
\renewcommand\familydefault{\sfdefault} 

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Shahil Mohammed}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (832) 620-5379 ~ • ~ \href{mailto:shahilmohammed14786@gmail.com}{shahilmohammed14786@gmail.com} ~ • ~  
    \href{https://www.linkedin.com/in/shahil-mohammed-9652931a1/}{\color{blue}\underline{LinkedIn}}  ~ • ~ 
    \href{https://github.com/freakbeast14}{\color{blue}\underline{GitHub}} ~ • ~ 
    \href{https://shahil-mohammed.netlify.app/}{\color{blue}\underline{Portfolio}}
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
Innovative software engineer focused on designing scalable, secure backend services for healthcare. Experienced in cloud infrastructure, healthcare standards, and privacy principles to deliver reliable health data solutions for millions.
 \vspace{-5pt}
 
\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, Scala, Go, TypeScript \\
                \textbf{Web Services \& Frameworks:} & Spring Boot, Django, Node.js, REST, HTTPS, JSON, gRPC \\
                \textbf{Healthcare Standards:} & FHIR, SMART, HL7 \\
                \textbf{Cloud Platforms \& DevOps:} & AWS (EC2, Lambda, S3), Docker, Jenkins, Azure \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Security \& Privacy:} & OAuth, JWT, Role-based Access Control, Spring Security \\
            \end{tabular}
        \end{table}
 \vspace{-15pt}
 
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Profile DM, Inc.}{06/2025 – Present}
        {Software Developer II}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Designed \textbf{Spring Boot} backend services, scaling APIs to serve 2M+ users with 40\% performance improvement.}
        \resumeItem{Implemented healthcare \textbf{FHIR} integration, enabling seamless clinical data exchange and compliance with SMART standards.}
        \resumeItem{Enhanced system security using \textbf{Spring Security}, reducing unauthorized access attempts by 45\%.}
        \resumeItem{Automated \textbf{Jenkins} pipelines deploying microservices on \textbf{AWS EC2}, cutting release cycles by 35\%.}
        \resumeItem{Collaborated cross-functionally to embed privacy-by-design in backend architecture, ensuring HIPAA-compliant data handling.}
      \resumeItemListEnd
    \resumeSubheading
        {HomeTree Digital, Inc.}{06/2024 – 06/2025}
        {Software Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Built \textbf{Python} data pipelines processing 15,000 healthcare records daily, automating workflows and increasing efficiency 75\%.}
        \resumeItem{Developed \textbf{React} frontend with \textbf{Laravel} backend integrating healthcare APIs, supporting 30+ concurrent clinicians.}
        \resumeItem{Implemented cloud messaging on \textbf{AWS Lambda} for scalable alerts, reducing system latency by 20\%.}
        \resumeItem{Designed role-based access using \textbf{OAuth} and API security protocols, improving data privacy compliance by 30\%.}
        \resumeItem{Led integration of \textbf{FHIR} protocol in backend services aligning with current healthcare data standards and interoperability.}
      \resumeItemListEnd
    \resumeSubheading
        {Arizona State University}{10/2023 – 05/2024}
        {Cybersecurity Lab Support Specialist}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Maintained secure \textbf{Linux}-based environments supporting healthcare software testing and privacy validation labs.}
        \resumeItem{Developed scripts to automate security audits, increasing vulnerability detection accuracy by 25\%.}
        \resumeItem{Guided students on debugging backend health data APIs, improving assignment pass rates by 18\%.}
        \resumeItem{Delivered 15+ workshops on network security practices relevant to health software compliance and data protection.}
      \resumeItemListEnd
    \resumeSubheading
        {Amrock, LLC.}{05/2023 – 08/2023}
        {Software Engineer Intern}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{C\# .NET} backend APIs, cutting average data retrieval times by 30\% for health-related applications.}
        \resumeItem{Optimized \textbf{PostgreSQL} schema designs, reducing query response by 18\% and improving data integrity.}
        \resumeItem{Implemented \textbf{Angular.js} frontend optimizations, increasing user interaction efficiency by 22\%.}
        \resumeItem{Executed secure API calls via \textbf{TypeScript}, achieving sub-100ms average response for clinical data workflows.}
      \resumeItemListEnd
    \resumeSubheading
        {Apice Tech Pvt. Ltd.}{05/2021 – 06/2022}
        {Full Stack Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java Spring Boot} microservices supporting over 1,200 concurrent users with sub-200ms response latency.}
        \resumeItem{Implemented CI/CD using \textbf{Docker} and \textbf{AWS EC2}, enabling automated health data service deployments.}
        \resumeItem{Engineered \textbf{MySQL} data models compliant with healthcare privacy regulations, improving query efficiency by 20\%.}
        \resumeItem{Created a \textbf{React} UI for clinical data tracking, reducing access time by 25\% and enhancing usability.}
        \resumeItem{Wrote \textbf{JUnit} tests achieving 90\% coverage, increasing software reliability for medical record services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Clinical Data Validator} | Python, FHIR, OpenAI API, AWS Lambda}{}
          \resumeItemListStart
              \resumeItem{Developed an AI tool automating clinical record validation against \textbf{FHIR} standards, improving data accuracy by 35\%.}
              \resumeItem{Leveraged \textbf{AWS Lambda} for scalable execution, processing 50k+ records daily with 99.9\% uptime reliability.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{Secure Health Data API Gateway} | Java, Spring Boot, OAuth, AWS EC2}{}
          \resumeItemListStart
              \resumeItem{Designed a secure API gateway implementing \textbf{OAuth} and encryption, reducing unauthorized requests by 50\%.}
              \resumeItem{Deployed on \textbf{AWS EC2}, supporting 1M+ daily API calls for clinical health applications with high availability.}
          \resumeItemListEnd
          \vspace{-12pt}
      \resumeProjectHeading
          {\textbf{FHIR-Compliant Backend Microservices} | Scala, Akka, PostgreSQL, Docker}{}
          \resumeItemListStart
              \resumeItem{Implemented microservices in \textbf{Scala} supporting \textbf{FHIR} protocols, improving interoperability between healthcare systems by 40\%.}
              \resumeItem{Configured containerized deployments using \textbf{Docker}, enabling 30\% faster rollout and seamless scaling on cloud platforms.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}